### 2015-04-28 Latex files/paper.tex
First Commit

%% This skeleton file requires IEEEtran.cls version 1.6 or later.
%%
\documentclass[conference,letterpaper]{IEEEtran}
% If the IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it:
% \documentclass[conference]{../sty/IEEEtran}
\IEEEoverridecommandlockouts
\overrideIEEEmargins

% some very useful LaTeX packages include:

%\usepackage{cite}      % Written by Donald Arseneau
                        % V1.6 and later of IEEEtran pre-defines the format
                        % of the cite.sty package \cite{} output to follow
                        % that of IEEE. Loading the cite package will
                        % result in citation numbers being automatically
                        % sorted and properly "ranged". i.e.,
                        % [1], [9], [2], [7], [5], [6]
                        % (without using cite.sty)
                        % will become:
                        % [1], [2], [5]--[7], [9] (using cite.sty)
                        % cite.sty's \cite will automatically add leading
                        % space, if needed. Use cite.sty's noadjust option
                        % (cite.sty V3.8 and later) if you want to turn this
                        % off. cite.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/

\usepackage[dvips]{graphicx}  % Written by David Carlisle and Sebastian Rahtz
                        % Required if you want graphics, photos, etc.
                        % graphicx.sty is already installed on most LaTeX
                        % systems. The latest version and documentation can
                        % be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/graphics/
                        % Another good source of documentation is "Using
                        % Imported Graphics in LaTeX2e" by Keith Reckdahl
                        % which can be found as esplatex.ps and epslatex.pdf
                        % at: http://www.ctan.org/tex-archive/info/

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

\begin{document}
% paper title
\title{\huge Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence $^{*}$\footnoterule\thanks{$^{*}$This work is partially
supported by NSF Grant RI-Medium: \#IIS-1162095 to }}

% author names and affiliations
\author{\authorblockN{Haiyuan Li}
\authorblockA{\textit{School of Mechanical Engineering}\\
\textit{Beihang University}\\
\textit{Beijing, China}\\
\textit{lihaiyuan@buaa.edu.cn}\\}%
\and
\authorblockN{Gregory S. Chirikjian}
\authorblockA{\textit{Department of Intelligent Robotics}\\
\textit{Johns Hopkins University}\\
\textit{Baltimore, Maryland, USA}\\
\textit{gregc@jhu.edu}\\}}%

% make the title area
\maketitle
\begin{abstract}
abstract

abstract
\\
\end{abstract}

% key words
\begin{keywords}
AX=YB, Sensor Calibration, Probabilistic Modeling
\end{keywords}

\section{Introduction}
% no \PARstart

Image-guided system has been widely used in robotics such as robot assisted surgery. A sensor such as camera, laser scanner or ultrasound probe is usually mounted on the hand of a robotic manipulator. To use the "hand-eye" system, the problem of determining the coordination relationship between the sensor frame with respect to the end-effector frame must be solved, which is widely known $\textbf{AX=XB}$ problem for the hand-eye calibration. With an extension of this problem, $\textbf{AX=YB}$ problem without knowing the relationship between the world frame and the robot base frame is proposed to achieve the robot-world calibration as well as hand-eye calibration. In a dynamic setup environment, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist. Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to changing environments.

In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively calculated using different sensors. The data streams are in an asynchronous fashion due to different timing sequences. The asynchrony causes a shift between the two streams of data that results in missing the correspondences between $As$ and $Bs$. In this paper, we present a method to solve for an $X$ and $Y$ without needing know a priori knowledge of correspondence between $As$ and $Bs$.

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=2in]{fig1.eps}
\caption{
(1) The hand-eye calibration problem which is formulated in a matrix as AX=XB. (2) The hand-eye and robot-robot calibration problem which is formulated as AX=YB.
}
\label{fig1}
\end{figure}
\end{center}

The hand-eye calibration problem can be generalized as the $\textbf{AX = XB}$ formulation. $A$ and $B$ are respectively the homogeneous transformation matrices of end-effector and sensor movement using $A = A^{i}(A^{i+1})^{-1}; B = B^{i}(B^{i+1})^{-1}$ as shown in Fig.~\ref{fig1}. The homogeneous transformation matrix can be described with the form.
\begin{equation}\label{equ0}
    g(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right)
\end{equation}

where $R \in SO(3)$ is a rotation matrix and $t \in R^{3}$ is a translation vector.

According to multiple pairs $(A,B) \in SE(3) \times SE(3)$ which are known a prior, many methods for the only $X$ have been proposed including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence. Considering data streams containing the $A$ and $B$ will be asynchronous that are discussed in many instances
in the literature, several methods regardless of the correspondence or recovering the correspondence between two data sets are presented \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye transformation and robot-world one
has been viewed as $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1}, $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation. The $A$ and $B$ in $\textbf{AX=YB}$ calibration is different from ones in $\textbf{AX=XB}$ from a physical view. This problem has been studied in different methods such as SVD, closed-form, quaternion and nonlinear optimization \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Another approach integrate multiple robots to calibrate hand-eye, tool-flange and robot-robot transformation in $\textbf{AXB=YCZ}$ problem \cite{Wang2014}. Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue. In the above methods, the correspondence between $A$ and $B$ is known a prior. In this paper, our solution for $\textbf{AX=YB}$ doesn't require a priori knowledge of correspondences.

The rest of the paper is organized as follows. In Section
\ref{sect2} we present the probabilistic theory to solve for $X$ and $Y$. In Section \ref{sect3} a algorithmic solution involving correlation theorem and Euclidean group invariants is posed to recover the correspondence. The simulation results, including known  and unknown correspondence, are illustrated in Section \ref{sect4}. Finally, we draw some conclusions.

\section{Solving AX=YB using a probabilistic theory on motion groups}
\label{sect2}

Given a large set of pairs $(A_{i},B_{i})\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equations

\begin{equation}\label{equ1}
A_{i}X=YB_{i}
\end{equation}

In the case of $SE(3)$, a Dirac delta function, or $\delta$ function, is thought of as a function which is zero everywhere except at the identity where it is infinite.

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{ll}
+\infty, & H=I \\
0, & H \neq I
\end{array}
\right.
\end{equation}

Dirac delta function is also constrained to satisfy the identity.

\begin{equation}\label{equ3}
\int_{SE(3)}\delta{(H)}dH=1
\end{equation}

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given two functions $f_{1}(g)$ and $f_{2}(g)$, their convolution in Lie group is defined as follows,

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(g)=\int_{SE(3)}f_{1}(h)f_{2}(h^{-1}\circ g)dh
\end{equation}

Considering the properties of $\delta$ function, the following equation is built.

\begin{equation}\label{equ5}
(f\ast \delta)(g)=\int_{SE(3)}f(h)\delta(h^{-1}\circ g)dh=f(g)
\end{equation}

Therefore, for each $A_{i}$ and $B_{i}$ can get

\begin{IEEEeqnarray}{l}\label{equ6}
(\delta_{A_{i}}\ast \delta_{X})(g)=\delta(A_{i}^{-1} g X^{-1}) \IEEEyessubnumber
\\*
(\delta_{Y}\ast \delta_{B_{i}})(g)=\delta(Y^{-1} g B_{i}^{-1}) \IEEEyessubnumber
\end{IEEEeqnarray}

Together with $g=A_{i}X=YB_{i}$, we can obtain the convolution equation

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast \delta_{B_{i}})(g)
\end{equation}

Convolution provides a linear operation on functions with additional properties. We can add up $n$ instances into a single function.

\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}g) \IEEEyessubnumber
\\*
f_{B}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}g) \IEEEyessubnumber
\end{IEEEeqnarray}

Therefore,

\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

In each transformation set $A_i$s and $B_i$s, we are using small relative motions between consecutive reference frames. Given a measure of distance between reference frames, e.g.

\begin{eqnarray}\label{equ10}
d^{2}(A_{i},A_{j})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
\end{eqnarray}

we have that  $\Delta A = A_{i}-A_{j}$ and $0 < \epsilon \ll 1 $

The convolution of "highly focused" distributions corresponding to closely clumped sets of reference frames have some interesting properties that we can exploit to solve for $X$. In particular, let the mean and covariance of a probability density, $f(g)$(e.g. $f_{A}(g),f_{B}(g)$), be defined by the conditions.

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)}log(M^{-1}g))f(g)dg=0 \IEEEyessubnumber
\\*
\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T}f(g)dg \IEEEyessubnumber
\end{IEEEeqnarray}

A discrete version as for $f_{A}(g)$ is

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M^{-1}g))=0 \IEEEyessubnumber
\\*
\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T} \IEEEyessubnumber
\end{IEEEeqnarray}

While the cloud of frames ${A_{i}}$ is clustered around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008}.

\begin{equation}\label{equ13}
    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})]
\end{equation}

An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$,then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$. A similar procedure is used for computing $M_B$.

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly focused functions, $f_{1}$ and $f_{2}$ can be computed as

\begin{IEEEeqnarray}{l}\label{equ14}
M_{1 \ast 2} = M_{1}M_{2} \IEEEyessubnumber
\\*
\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2} \IEEEyessubnumber
\end{IEEEeqnarray}

where

$$Ad(g)=\left(
               \begin{array}{cc}
                 R & O \\
                 \hat{t}R & R \\
               \end{array}
             \right)$$

Due to $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$,$\Sigma_{X}=0$ and $M_{Y}=Y$,$\Sigma_{Y}=0$, respectively, therefore we can obtain

\begin{IEEEeqnarray}{l}
M_{A} X = Y M_{B} \IEEEyessubnumber\label{equ15a}
\\*
Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B} \IEEEyessubnumber\label{equ15b}
\end{IEEEeqnarray}

From (\ref{equ15a}), we can obtain

\begin{IEEEeqnarray}{l}
R_{M_{A}} R_{X} = R_{Y} R_{M_{B}} \IEEEyessubnumber\label{equ16a}
\\*
R_{M_{A}} t_{X} + t_{M_{A}}= R_{Y} t_{M_{B}} + t_{Y} \IEEEyessubnumber\label{equ16b}
\end{IEEEeqnarray}

$\Sigma_{M_{A}}$ and $\Sigma_{M_{B}}$ can be decomposed into blocks as
$\left(\begin{array}{cc}
       \Sigma_{M_{A}}^{1} & \Sigma_{M_{A}}^{2} \\
       \Sigma_{M_{A}}^{3} & \Sigma_{M_{A}}^{4} \\
       \end{array}
       \right)$
and
$\left(\begin{array}{cc}
       \Sigma_{M_{B}}^{1} & \Sigma_{M_{B}}^{2} \\
       \Sigma_{M_{B}}^{3} & \Sigma_{M_{B}}^{4} \\
       \end{array}
       \right)$, respectively. Using
$ X^{-1}=X^{T}=\left(\begin{array}{cc}
       R_{X}^{T} & -R_{X}^{T}t_{X}  \\
       0 & 1 \\
       \end{array}
       \right)$,
then we can write the first two blocks of (\ref{equ15b}) as follows,

\begin{IEEEeqnarray}{l}
\Sigma_{M_{B}}^{1} = R_{X}^{T}\Sigma_{M_{A}}^{1} R_{X} \IEEEyessubnumber\label{equ17a}
\\*
\Sigma_{M_{B}}^{2} = R_{X}^{T}\Sigma_{M_{A}}^{1} R_{X} (\widehat{R_{X}^{T}t_{X}}) + R_{X}^{T}\Sigma_{M_{A}}^{2}R_{X}
 \IEEEyessubnumber\label{equ17b}
\end{IEEEeqnarray}

The first blocks(\ref{equ17a}) is eigendecomposed with the same diagonal matrix due to matrix similarity $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\wedge Q_{M_{A}}^{T}$, $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\wedge Q_{M_{B}}^{T}$. Then,

\begin{equation}\label{equ18}
    \wedge = (Q_{M_{A}}^{T}R_{X}Q_{M_{B}}) \wedge (Q_{M_{B}}^{T}R_{X}^{T}Q_{M_{A}})= P \wedge P^{T}
\end{equation}

In $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$, $Q_{M_{A}}$ and $Q_{M_{B}}$ are constrained to be a rotation matrix and therefore $P \in \Omega$,

\begin{equation}\label{equ19}
\Omega= \left(
\begin{array}{ccc}
\left( \begin{array}{ccc}
       1 & 0 & 0 \\
       0 & 1 & 0 \\
       0 & 0 & 1 \\
\end{array} \right),&
\left( \begin{array}{ccc}
       -1 & 0 & 0 \\
       0 & -1 & 0 \\
       0 & 0 & 1 \\
\end{array} \right)
\\
\left( \begin{array}{ccc}
       -1 & 0 & 0 \\
       0 & 1 & 0 \\
       0 & 0 & -1 \\
\end{array} \right),&
\left( \begin{array}{ccc}
       1 & 0 & 0 \\
       0 & -1 & 0 \\
       0 & 0 & -1 \\
\end{array} \right)
\end{array}
\right)
\end{equation}

Therefore, there are four possibilities of $R_{X}, R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$. Then, from \ref{equ17b},four $t_{X}$ corresponding to $R_{X}$ can be directly found. Furthermore,four candidate $R_{Y} and t_{Y}$ can be found. At last, there are four possibilities of solution $(X_{i},Y_{i}), i = 1,2,3,4$.
where,

\begin{equation}\label{equ20}
\begin{array}{cc}
X_{i}= \left( \begin{array}{cc}
       R_{X} & t_{X} \\
       \mathbf{0}^{T} & \mathbf{1}\\
\end{array} \right),&
Y_{i}= \left( \begin{array}{cc}
       R_{Y} & t_{Y} \\
       \mathbf{0}^{T} & \mathbf{1}\\
\end{array} \right)
\end{array}
\end{equation}

Based on the screw theory, it is known that a homogeneous transformation $H$ can be written in the form with four parameters $(\theta,d,\mathbf{n},\mathbf{p})$.

\begin{equation}\label{equ21}
H = \left( \begin{array}{cc}
       e^{\theta \hat{\mathbf{n}}} & (\mathbf{I}_{3} - e^{\theta \hat{\mathbf{n}}})\mathbf{p} + d\mathbf{n} \\
       \mathbf{0}^{T} & \mathbf{1}
\end{array} \right)
\end{equation}

$AX=YB$ can be written as $AX=X(X^{-1}YB)$ and let $B' = X^{-1}YB$ . In the form $AX=XB'$, there exit two Euclidean-Group Invariant relationships for one of four groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,2,3,4)$ as follows,

\begin{equation}\label{equ22}
    \theta_{A_{i}}=\theta_{B_{i}^{k}}, d_{A_{i}}=d_{B_{i}^{k}}
\end{equation}

From among the four pairs $(X_{i},Y_{i})$, we can find a correct solution to minimize the leat absolute deviations,

\begin{equation}\label{equ23}
    (X,Y) = \mathop{\mathbf{arg}min}_{(X_{i},Y_{i})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel)
\end{equation}

\section{Solution with unknown correspondence of $A_{i}$ and $B_{i}^{k}$}
\label{sect3}

In most cases, the homogeneous transformations with $A$ and $B$ are given based on the data from different sensors. Due to asynchronous timing of the measurement transmissions, the correspondences between $A_{i}$ and $B_{i}^{k}$ is unknown. The advantage of the above probabilistic solution lie that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence. However, there are still four possible candidate results $(X_{i},Y_{i})$. Using Euclidean-Group Invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$   can be known.

The Discrete Fourier transform (DFT) decomposes a time-domain signal into its constituent frequencies. The input is a finite list of equally spaced samples of a function. Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N_1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$

\begin{equation}\label{equ21}
    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa)
\end{equation}
And the Inverse Discrete Fourier transform (IDFT) denoted by

\begin{equation}\label{equ22}
    X_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
\end{equation}

The discrete convolution of two sequences $f_{n}$ and $g_{n}$  are defined

\begin{equation}\label{equ23}
    (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau)
\end{equation}

In convolution theorem, the Fourier transform of a convolution is the product of the Fourier transforms, namely,

\begin{equation}\label{equ24}
    f \ast g = \mathcal{F}^{-1} [\mathcal{F}(f) \cdot \mathcal{F}(g)]
\end{equation}

The correlation theorem indicates that the correlation function, $Corr(f,g)$, will have a large value at a shift vector if the two sequences $f$ and $g$ contain similar features. The correlation can be obtained based on the convolution theorem. The DFT of the correlation $Corr(f,g)$ is equal to the product of the DFT of a sequence $f_{n}$ and the complex conjugate $\mathcal{F}^{*}$ of the DFT of the other sequence $g_n$.

\begin{equation}\label{equ25}
    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}]
\end{equation}

Compared with the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the fast Fourier transform (FFT).

There are two sequences $\theta_{A_{i}}$ and $\theta_{B_{i}^{k}}$ from each pair $(A_{i},B_{i}^{k})$. For homogeneous transformations from which the range of $\theta$ can vary, two sequences $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ can be first normalized.

\begin{equation}\label{equ26}
    \theta_{1}=\frac{(\theta_{A_{i}}-\mu_{A_{i}})}{\sigma_{A_{i}}}, \theta_{2}=\frac{(\theta_{B_{i}^{k}}-\mu_{B_{i}^{k}})}{\sigma_{B_{i}^{k}}}
\end{equation}

where $\mu_{A_{i}}(\mu_{B_{i}^{k}})$ is the average of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A_{i}}(\sigma_{B_{i}^{k}})$ is the standard deviation.

Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $(n)$ which describes the probability that these two sequences are separated by this particular unit. The location of the function maximum indicates the amount of shift, $\tau_{shift}$, between the two sequence $\theta_{A_{i}}$ and $\theta_{B_{i}^{k}}$.

\begin{equation}\label{equ27}
    \tau_{shift} = \mathop{\mathbf{arg}max}_{index}(Corr(\theta_{1},\theta_{2}))
\end{equation}

Therefore, the correspondence between the two sequences can be found. The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$. The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the least absolute deviations based on Euclidean-Group Invariants relations using the method in Section \ref{sect2}.

\section{Simulation Studies}
\label{sect4}

In the numerical experiments in this section, a homogeneous matrix   is generated from a PUMA 560 robotic manipulator. $X$ and $Y$ are chosen from reference .

\subsection{Results of solution with known correspondence}

100 pose measurements with $B_{i}$ closely around $B_{start}$ was employed for generating 100 $A_{i}$. As a result by applying the above probabilistic method, four sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=1,\cdots, 100, k=1,2,3,4)$ can be obtained respectively, as shown in Fig.~\ref{fig2} and Fig.~\ref{fig3}. Using $\theta_{A_{i}} - \theta_{B_{i}^{k}}$ and $d_{A_{i}} - d_{B_{i}^{k}}$  in Fig.~\ref{fig4} and Fig.~\ref{fig5}, we can find the ${B_{i}^{k}}(k=3)$  corresponding to the least sum of errors and then, $(X_3,Y_3)$ is the desired solution.

From 1 measurements to 500 measurements, the rotational and translational error for $X$ and $Y$ are measured as  $\parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $\parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $\parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $\parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively as shown in Fig.~\ref{fig6}.

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig2.eps}
\caption{
Calculated four pairs of rotational angles $(\theta_{A_{i}},\theta_{B_{i}^{k}}) (k=1,2,3,4)$  respectively from 100 measurements
}
\label{fig2}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig3.eps}
\caption{
Calculated four pairs of translational displacement  $(d_{A_{i}},d_{B_{i}^{k}}) (k=1,2,3,4)$  respectively from 100 measurements
}
\label{fig3}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig4.eps}
\caption{
Calculated rotational angle deviation $\theta_{A_{i}} - \theta_{B_{i}^{k}} (k=1,2,3,4)$ from Fig.~\ref{fig2}
}
\label{fig4}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig5.eps}
\caption{
Calculated translational deviation $d_{A_{i}} - d_{B_{i}^{k}} (k=1,2,3,4)$ from Fig.~\ref{fig3}
}
\label{fig5}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig6.eps}
\caption{
Solution error with increasing pairs $(A_{i},B_{i}^{k})$ from 1 measurements to 500 measurements
}
\label{fig6}
\end{figure}
\end{center}

\subsection{Results of solution without known correspondence}
As shown in Fig.~\ref{fig7}, the data streams of $A$ were shifted by 10 units. The maximum of cross correlation can be used to find the corresponding shift, which is -10 shown in Fig.~\ref{fig8}, representing the data stream of $B_{i}^{k}$ has been shifted by -10 units respective to ${A_{i}}$ . Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group Invariants.

\begin{center}
\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig7.eps}
\caption{
Shifted Data Streams of $A$ and calculated $B_{i}^{k}$.
}
\label{fig7}
\end{figure}
\end{center}
\begin{center}

\begin{figure}[htbp]
\centering
\includegraphics[width=3.2in]{fig8.eps}
\caption{
The cross correlation of data streams of $(A_{i},B_{i}^{k})$ respectively.
}
\label{fig8}
\end{figure}
\end{center}

\section{Conclusions}
\label{sect5}

Conclusions
%\section{Conclusion}
% conference papers do not normally have an appendix

% use section* for acknowledgment
\section*{Acknowledgment}

acknowledgement
% optional entry into table of contents (if used)
%\addcontentsline{toc}{section}{Acknowledgment}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibIEEEfull}
%\begin{thebibliography}{1}
%
%
%\end{thebibliography}

\end{document}

### 2015-04-28 m file/SolveForXY.m

@@ -1,0 +1,206 @@
+function [outputX,outputY,outputError] =  SolveForXY(length, precision)
+%% 
+% load Asup2;
+% A = Asup2;
+% B = Bsup2;
+% clear;
+% close
+% clc
+%% Times of simulation steps
+len = length;
+e = precision;
+% digits(64);
+%% data
+Y = [-0.99908 -0.03266 0.02786 164.226/1000;
+      0.02737  0.01553 0.99950 301.638/1000;
+     -0.03308  0.99935 -0.01462 -962.841/1000;
+     0.00000   0.00000 0.00000  1.00000;];
+ X = [-0.97651 -0.09468 -0.19356 9.190/1000;
+     0.06362 -0.98493 0.16082 5.397/1000;
+     -0.20587 0.14473 0.96782 62.628/1000;
+     0.00000 0.00000 0.00000 1.00000;];
+ qz = [pi/2,0,pi/2,0,0,0];
+ mdl_puma560;
+ Binitial = p560.fkine(qz);
+ Ainitial = Y * Binitial * X;
+%  trplot(Ainitial,'color','b');
+%  trplot(Y,'color','b');
+%  hold on
+% load invariantrandom.mat 
+ for m = 1:1:len
+     r1 = rand(6,1) - 0.5;
+     B(:,:,m) = Binitial * expm(0.1 * (twist(r1)));
+     A(:,:,m) = Y * B(:,:,m) * X;
+     [OmegaA(:,:,m) thetaA(m)] = rotparam(A(1:3,1:3,m));
+     dA(m) = dot(A(1:3,4,m),OmegaA(:,:,m));
+%      trplot(A(:,:,m),'color','r');
+ end
+
+%% Calculat MA
+sumMA = 0;
+N = len;
+for i = 1:1:N
+    sumMA = sumMA + real(logm(A(:,:,i)));
+    
+end
+MA = expm(sumMA/N);
+
+while(1)
+   %% calculate cost function
+    sumMA = 0;
+    for i = 1:1:N
+        sumMA = sumMA + real(logm(inv(MA)*A(:,:,i)));
+    end
+    costFunA = abs(sumMA);
+    if(sum(sum((costFunA.^2))) < e)
+        break;
+    end
+    MA = MA * expm(sumMA/N);
+    
+end
+
[…]

### 2015-04-28 m file/calmanyXY.m

@@ -1,0 +1,14 @@
+clear all
+close all
+figure(1);
+for k = 1:1:100
+[a(:,:,k),b(:,:,k),c(k,:)]=SolveForXY(100,0.1);
+ trplot(a(:,:,k),'color','b');
+ hold on
+end
+figure
+for m = 1:1:4
+   subplot(4,1,m);
+   plot(c(:,m));
+end
+

### 2015-04-28 m file/li.m

@@ -1,0 +1,33 @@
+function [X,Y]=li(AA,BB)
+% Solves the problem AX=YB
+% using the formulation of
+%
+% Simultaneous robot-world and hand-eye calibration 
+% using dual-quaternions and Kronecker product
+% 
+% Aiguo Li, Lin Wang and Defeng Wu
+%
+% Mili Shah
+% July 2014
+
+[m,n]=size(AA); n = n/4;
+
+A = zeros(12*n,24);
+b = zeros(12*n,1);
+for i = 1:n
+    Ra = AA(1:3,4*i-3:4*i-1);
+    Rb = BB(1:3,4*i-3:4*i-1);
+    ta = AA(1:3,4*i);
+    tb = BB(1:3,4*i);
+    A(12*i-11:12*i-3,1:18) = [kron(Ra,eye(3)) kron(-eye(3),Rb')];
+    A(12*i-2:12*i,10:24) = [kron(eye(3),tb') -Ra eye(3)];
+    b(12*i-2:12*i) = ta;
+end
+x = A\b;
+
+X=reshape(x(1:9),3,3)';
+[u,s,v]=svd(X); X = u*v'; if det(X)<0, X = u*diag([1 1 -1])*v'; end
+X = [X x(19:21);[0 0 0 1]];
+Y=reshape(x(10:18),3,3)';
+[u,s,v]=svd(Y); Y = u*v'; if det(Y)<0, Y = u*diag([1 1 -1])*v'; end
+Y = [Y x(22:24);[0 0 0 1]];

### 2015-04-28 Latex files/paper.tex
Edited first to third paragraphs

@@
 \begin{abstract}
-abstract
 
-abstract
 \\
@@
 Image-guided system has been widely used in robotics such as robot assisted surgery.
-A sensor such as camera, laser scanner or ultrasound probe is usually mounted on the hand of a robotic manipulator.
-To use the "hand-eye" system, the problem of determining the coordination relationship between the sensor frame with respect to the end-effector frame must be solved, which is widely known $\textbf{AX=XB}$ problem for the hand-eye calibration.
-With an extension of this problem, $\textbf{AX=YB}$ problem without knowing the relationship between the world frame and the robot base frame is proposed to achieve the robot-world calibration as well as hand-eye calibration.
-In a dynamic setup environment, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist.
-Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to changing environments.
+Sensors such as a camera, a laser scanner and an ultrasound probe are usually mounted as the end-effector of a robotic manipulator.
+For a typical ``hand-eye" system as described above, the relative transformation of the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well known $\textbf{AX=XB}$ problem.
+A variation of this problem is characterized as the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
+In a typical environment setup, the relationship among the sensor frame, robot frame and world frame either is subject to change or can be disturbed by uncertainties.
+Therefore, simultaneous coordinate calibrations have to be performed frequently in order to enable the robot to respond to dynamic environments.
 
-In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively calculated using different sensors.
-The data streams are in an asynchronous fashion due to different timing sequences.
-The asynchrony causes a shift between the two streams of data that results in missing the correspondences between $As$ and $Bs$.
-In this paper, we present a method to solve for an $X$ and $Y$ without needing know a priori knowledge of correspondence between $As$ and $Bs$.
+In the $\textbf{AX=YB}$ problem, $A$s and $B$s can be respectively obtained via different sensors.
+The data streams can be in an asynchronous fashion due to different working frequencies of the sensors.
+The asynchrony causes a shift between the two streams of data which damages the correspondence between $A$s and $B$s.
+In this paper, we present a method to solve for $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $A$s and $B$s.
 
@@
 \caption{
-(1) The hand-eye calibration problem which is formulated in a matrix as AX=XB. (2) The hand-eye and robot-robot calibration problem which is formulated as AX=YB.
+(1) The hand-eye calibration problem formulated in a matrix as AX=XB. (2) The hand-eye and robot-robot calibration problem formulated as AX=YB.
 }
@@
 
-The hand-eye calibration problem can be generalized as the $\textbf{AX = XB}$ formulation.
-$A$ and $B$ are respectively the homogeneous transformation matrices of end-effector and sensor movement using $A = A^{i}(A^{i+1})^{-1}; B = B^{i}(B^{i+1})^{-1}$ as shown in Fig.~\ref{fig1}.
-The homogeneous transformation matrix can be described with the form.
+The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$s and $B$s are the homogeneous transformation matrices describing the relative motion of the end-effector and the sensor respectively.
+As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and $B = B^{i}(B^{i+1})^{-1}$.
+The homogeneous transformation matrix can be described as:
 \begin{equation}\label{equ0}
@@
 
-According to multiple pairs $(A,B) \in SE(3) \times SE(3)$ which are known a prior, many methods for the only $X$ have been proposed including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
+Given multiple pairs of $(A_{i},B_{i}) \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$ including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
 optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.

### 2015-04-29 Latex files/paper.tex
Edited first 2 pages (abstract to be added)

@@
 
-%\usepackage{cite}      % Written by Donald Arseneau
+\usepackage{cite}      % Written by Donald Arseneau
                         % V1.6 and later of IEEEtran pre-defines the format
@@
 The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$s and $B$s are the homogeneous transformation matrices describing the relative motion of the end-effector and the sensor respectively.
-As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and $B = B^{i}(B^{i+1})^{-1}$.
+As shown in Fig.~\ref{fig1}, $A_{i} = A^{i}(A^{i+1})^{-1}$ and $B_{i} = B^{i}(B^{i+1})^{-1}$.
 The homogeneous transformation matrix can be described as:
@@
 
-Given multiple pairs of $(A_{i},B_{i}) \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$ including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
-optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
-Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence.
-Considering data streams containing the $A$ and $B$ will be asynchronous that are discussed in many instances
-in the literature, several methods regardless of the correspondence or recovering the correspondence between two data sets are presented \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
+Given multiple pairs of $\{A_{i},B_{i}\} \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$.
+To the best of the authors' knowledge, Shiu\cite{Shiu1989} and Tsai\cite{Tsai1989} are the first to solve the $AX=XB$ sensor calibration problem.
+The other methods include but are not limited to quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
+All of the methods above assume a prior knowledge of exact correspondence  between $A_{i}$ and $B_{i}$.
+For data streams $\{A_{i}\}$ and $\{B_{j}\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
 
-Simultaneous estimation of the hand-eye transformation and robot-world one
-has been viewed as $\textbf{AX=YB}$ problem.
-As shown in Fig.~\ref{fig1}, $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation.
-The $A$ and $B$ in $\textbf{AX=YB}$ calibration is different from ones in $\textbf{AX=XB}$ from a physical view.
-This problem has been studied in different methods such as SVD, closed-form, quaternion and nonlinear optimization \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
-Another approach integrate multiple robots to calibrate hand-eye, tool-flange and robot-robot transformation in $\textbf{AXB=YCZ}$ problem \cite{Wang2014}.
-Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue.
-In the above methods, the correspondence between $A$ and $B$ is known a prior.
-In this paper, our solution for $\textbf{AX=YB}$ doesn't require a priori knowledge of correspondences.
+Simultaneous estimation of the hand-eye and robot-world transformations
+has been viewed as the $\textbf{AX=YB}$ problem.
+As shown in Fig.\ref{fig1}, $Y$ is the transformation of the robot base relative to the world frame, $A$ denotes the sensor's pose in the world frame, and $B$ is the transformation of  the end-effector with respect to its fixed base.
+The $A_{i}$ and $B_{i}$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ which can be seen in Fig.\ref{fig1}.
+The $\textbf{AX=YB}$ problem has been solved by different methods such as kronecker product, quaternion, dual quaternion, and nonlinear optimization method \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
+Simultaneous calibration of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_{i}\}$ and $\{B_{j}\}$, which is not the case in real experiments.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014}.
+In this paper, we focus on the $\textbf{AX=YB}$ problem which does not require a priori knowledge of correspondences of the data streams.
 
 The rest of the paper is organized as follows. In Section
-\ref{sect2} we present the probabilistic theory to solve for $X$ and $Y$.
-In Section \ref{sect3} a algorithmic solution involving correlation theorem and Euclidean group invariants is posed to recover the correspondence.
-The simulation results, including known  and unknown correspondence, are illustrated in Section \ref{sect4}.
-Finally, we draw some conclusions.
+\ref{sect2}, we present a probabilistic method to solve for $X$ and $Y$.
+In Section \ref{sect3}, a algorithmic solution involving both the correlation theorem and Euclidean group invariants is posed to recover the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$.
+The simulation results which deal with the data streams with both known and unknown correspondence are illustrated in Section \ref{sect4}.
+Finally, conclusions are drawn based on the numerical results and possible future works are pointed out.
 
@@
 
-Given a large set of pairs $(A_{i},B_{i})\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equations
-
+Given a large set of pairs $\{A_{i},B_{i}\}\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equation:
 \begin{equation}\label{equ1}
-A_{i}X=YB_{i}
+A_{i}X=YB_{i}.
 \end{equation}
-
-In the case of $SE(3)$, a Dirac delta function, or $\delta$ function, is thought of as a function which is zero everywhere except at the identity where it is infinite.
+For a matrix $H \in SE(3)$, a Dirac delta function $\delta(H)$ function is defined to be finite only at the identity and zero everywhere else:
 
@@
 \end{equation}
-
-Dirac delta function is also constrained to satisfy the identity.
-
+It also satisfies the identity constraint as:
 \begin{equation}\label{equ3}
-\int_{SE(3)}\delta{(H)}dH=1
+\int_{SE(3)}\delta{(H)}dH=1.
 \end{equation}
 
-A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given two functions $f_{1}(g)$ and $f_{2}(g)$, their convolution in Lie group is defined as follows,
+A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$.
+Given $K, H \in SE(3)$ and two functions $f_1, f_2 \in (L^1 \cap L^2)(SE(3))$, their convolution on $SE(3)$ is defined as:
 
 \begin{equation}\label{equ4}
-(f_{1}\ast f_{2})(g)=\int_{SE(3)}f_{1}(h)f_{2}(h^{-1}\circ g)dh
+(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}H)dK
+\end{equation}
+where $h \in SE(3)$. Employing the properties of $\delta$ function, it is straightforward to see that:
+
+\begin{equation}\label{equ5}
+(f\ast \delta)(H)=\int_{SE(3)}f(K)\delta(K^{-1}H)dK=f(H).
+\end{equation}
+Therefore, for each $A_{i}$ and $B_{i}$, we have:
+
+\begin{IEEEeqnarray}{l}\label{equ6}
+(\delta_{A_{i}}\ast \delta_{X})(H)=\delta(A_{i}^{-1} H X^{-1}) \IEEEyessubnumber
+\\*
+(\delta_{Y}\ast \delta_{B_{i}})(H)=\delta(Y^{-1} H B_{i}^{-1}) \IEEEyessubnumber
+\end{IEEEeqnarray}
+Together with $A_{i}X=YB_{i}$, we can obtain the convolution equation:
+
+\begin{equation}\label{equ7}
+(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
 \end{equation}
 
-Considering the properties of $\delta$ function, the following equation is built.
+Convolution provides a linear operation on functions with addition properties.  After adding up $n$ instances of $\delta_{A_{i}}(H)$ and $\delta_{B_{i}}(H)$, we obtained the following equations:
 
-\begin{equation}\label{equ5}
-(f\ast \delta)(g)=\int_{SE(3)}f(h)\delta(h^{-1}\circ g)dh=f(g)
+\begin{IEEEeqnarray}{l}\label{equ8}
+f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}H) \IEEEyessubnumber
+\\*
+f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}H) \IEEEyessubnumber
+\end{IEEEeqnarray}
+
+Therefore, we have:
+\begin{equation}\label{equ9}
+(f_{A}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B})(H).
 \end{equation}
 
-Therefore, for each $A_{i}$ and $B_{i}$ can get
+For each of the data stream $\{A_i\}$ and $\{B_i\}$, we are using small relative motions between consecutive reference frames.
+Take $\{A_{i}\}$ for example, one metric of the distance between $A_i$ and $A_j$ can be defined as:
 
-\begin{IEEEeqnarray}{l}\label{equ6}
-(\delta_{A_{i}}\ast \delta_{X})(g)=\delta(A_{i}^{-1} g X^{-1}) \IEEEyessubnumber
+\begin{eqnarray}\label{equ10}
+d^{2}(A_{i},A_{i+1})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
+\end{eqnarray}
+where  $\Delta A = A_{i}-A_{j}$ (or $\Delta A = A_{i}^{-1}A_{j}$) and $0 < \epsilon \ll 1 $
+
+The convolution of two ``highly focused" probability density functions (pdf) has some interesting properties that can be used to solve for $X$.
+In particular, firstly, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:
+
+\begin{IEEEeqnarray}{l}\label{equ11}
+\int_{SE(3)}log(M^{-1}H))f(H)dH=0 \IEEEyessubnumber
 \\*
-(\delta_{Y}\ast \delta_{B_{i}})(g)=\delta(Y^{-1} g B_{i}^{-1}) \IEEEyessubnumber
+\Sigma = 
+\int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
 \end{IEEEeqnarray}
 
-Together with $g=A_{i}X=YB_{i}$, we can obtain the convolution equation
-
-\begin{equation}\label{equ7}
-(\delta_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast \delta_{B_{i}})(g)
-\end{equation}
-
-Convolution provides a linear operation on functions with additional properties. We can add up $n$ instances into a single function.
-
-\begin{IEEEeqnarray}{l}\label{equ8}
-f_{A}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}g) \IEEEyessubnumber
-\\*
-f_{B}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}g) \IEEEyessubnumber
-\end{IEEEeqnarray}
-
-Therefore,
-
-\begin{equation}\label{equ9}
-(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
-\end{equation}
-
-In each transformation set $A_i$s and $B_i$s, we are using small relative motions between consecutive reference frames. Given a measure of distance between reference frames, e.g.
-
-\begin{eqnarray}\label{equ10}
-d^{2}(A_{i},A_{j})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
-\end{eqnarray}
-
-we have that  $\Delta A = A_{i}-A_{j}$ and $0 < \epsilon \ll 1 $
-
-The convolution of "highly focused" distributions corresponding to closely clumped sets of reference frames have some interesting properties that we can exploit to solve for $X$.
-In particular, let the mean and covariance of a probability density, $f(g)$(e.g.
-$f_{A}(g),f_{B}(g)$), be defined by the conditions.
-
-\begin{IEEEeqnarray}{l}\label{equ11}
-\int_{SE(3)}log(M^{-1}g))f(g)dg=0 \IEEEyessubnumber
-\\*
-\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T}f(g)dg \IEEEyessubnumber
-\end{IEEEeqnarray}
-
-A discrete version as for $f_{A}(g)$ is
+Then the corresponding discrete version of $f_{A}(H)$ will be:
 
 \begin{IEEEeqnarray}{l}\label{equ12}
-\sum_{i=1}^{n}log(M^{-1}g))=0 \IEEEyessubnumber
+\sum_{i=1}^{n}log(M_{A}^{-1}H))=0 \IEEEyessubnumber
 \\*
-\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T} \IEEEyessubnumber
+\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M_{A}^{-1}H)[log^{\vee}(M_{A}^{-1)}H)]^{T} \IEEEyessubnumber
 \end{IEEEeqnarray}

### 2015-04-29 Tex_AXYB/paper.tex
changed folder names to be Matlab_AXYB & Tex_AXYB

--- 2015-04-29 Latex files/paper.tex
@@
 \usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
+\usepackage{amsmath}
 \setlength{\columnsep}{0.24in}
@@
 
-While the cloud of frames ${A_{i}}$ is clustered around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008}.
+For the case where $\{A_{i}\}$ is clustered around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:
 
 \begin{equation}\label{equ13}
-    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})]
+    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})].
 \end{equation}
 
-An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$,then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$.
+An initial estimate of $M_{A}$ can be calculated as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then iterations will be performed according to Eq.(\ref{equ13}) until the cost function $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold.
 A similar procedure is used for computing $M_B$.
 
-The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly focused functions, $f_{1}$ and $f_{2}$ can be computed as
+The mean and covariance for the convolution of two highly focused pdf $(f_{1} \ast f_{2})(H)$ can be computed as:
 
@@
 \end{IEEEeqnarray}
-
 where
 
-$$Ad(g)=\left(
+$$Ad(H)=\left(
                \begin{array}{cc}
@@
                \end{array}
-             \right)$$
+             \right).$$
 
-Due to $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$,$\Sigma_{X}=0$ and $M_{Y}=Y$,$\Sigma_{Y}=0$, respectively, therefore we can obtain
+Because $X$ and $Y$ is fixed, the means and covariances for $\delta_{X}(H)$ and $\delta_{Y}(H)$ are $M_{X}=X$, $\Sigma_{X}=0$ and $M_{Y}=Y$, $\Sigma_{Y}=0$ respectively. Therefore, we can obtain
 
@@
 
+%\begin{equation}\label{equ19}
+%\Omega= \left(
+%\begin{array}{ccc}
+%\left( \begin{array}{ccc}
+%       1 & 0 & 0 \\
+%       0 & 1 & 0 \\
+%       0 & 0 & 1 \\
+%\end{array} \right),&
+%\left( \begin{array}{ccc}
+%       -1 & 0 & 0 \\
+%       0 & -1 & 0 \\
+%       0 & 0 & 1 \\
+%\end{array} \right)
+%\\
+%\left( \begin{array}{ccc}
+%       -1 & 0 & 0 \\
+%       0 & 1 & 0 \\
+%       0 & 0 & -1 \\
+%\end{array} \right),&
+%\left( \begin{array}{ccc}
+%       1 & 0 & 0 \\
+%       0 & -1 & 0 \\
+%       0 & 0 & -1 \\
+%\end{array} \right)
+%\end{array}
+%\right)
+%\end{equation}
+
 \begin{equation}\label{equ19}
-\Omega= \left(
-\begin{array}{ccc}
-\left( \begin{array}{ccc}
+\begin{split}
+{\cal Q} = \left\{ \left(\begin{array}{ccc}
+1\,\, & 0 \,\, & 0 \,\, \\
+0 & 1 & 0\\
+0 & 0 & 1 \end{array}\right) , \left(\begin{array}{ccc}
+-1 & 0 & 0 \\
+0 & -1 & 0\\
+0 & 0 & 1 \end{array}\right), \right.\\
+\left. \left(\begin{array}{ccc}
+-1 & 0 & 0 \\
+0 & 1 & 0\\
+0 & 0 & -1 \end{array}\right), \left(\begin{array}{ccc}
 1 & 0 & 0 \\
-       0 & 1 & 0 \\
-       0 & 0 & 1 \\
-\end{array} \right),&
-\left( \begin{array}{ccc}
-       -1 & 0 & 0 \\
-       0 & -1 & 0 \\
-       0 & 0 & 1 \\
-\end{array} \right)
-\\
-\left( \begin{array}{ccc}
-       -1 & 0 & 0 \\
-       0 & 1 & 0 \\
-       0 & 0 & -1 \\
-\end{array} \right),&
-\left( \begin{array}{ccc}
-       1 & 0 & 0 \\
-       0 & -1 & 0 \\
-       0 & 0 & -1 \\
-\end{array} \right)
-\end{array}
-\right)
+0 & -1 & 0\\
+0 & 0 & -1 \end{array}\right)\right\}
+\end{split} 
 \end{equation}

### 2015-06-19 Tex_AXYB/paper.tex
need to be revised

--- 2015-04-28 Latex files/paper.tex
@@
-%% This skeleton file requires IEEEtran.cls version 1.6 or later.
-%%
-\documentclass[conference,letterpaper]{IEEEtran}
-% If the IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it:
-% \documentclass[conference]{../sty/IEEEtran}
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%2345678901234567890123456789012345678901234567890123456789012345678901234567890
+%        1         2         3         4         5         6         7         8
 
-% some very useful LaTeX packages include:
+\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
 
-%\usepackage{cite}      % Written by Donald Arseneau
-                        % V1.6 and later of IEEEtran pre-defines the format
-                        % of the cite.sty package \cite{} output to follow
-                        % that of IEEE. Loading the cite package will
-                        % result in citation numbers being automatically
-                        % sorted and properly "ranged". i.e.,
-                        % [1], [9], [2], [7], [5], [6]
-                        % (without using cite.sty)
-                        % will become:
-                        % [1], [2], [5]--[7], [9] (using cite.sty)
-                        % cite.sty's \cite will automatically add leading
-                        % space, if needed. Use cite.sty's noadjust option
-                        % (cite.sty V3.8 and later) if you want to turn this
-                        % off. cite.sty is already installed on most LaTeX
-                        % systems. The latest version can be obtained at:
-                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
+
+\IEEEoverridecommandlockouts                              % This command is only needed if
+                                                          % you want to use the \thanks command
+
+\overrideIEEEmargins                                      % Needed to meet printer requirements.
+
+% See the \addtolength command later in the file to balance the column lengths
+% on the last page of the document
+
+% The following packages can be found on http:\\www.ctan.org
+%\usepackage{graphics} % for pdf, bitmapped graphics files
+%\usepackage{epsfig} % for postscript graphics files
+%\usepackage{mathptmx} % assumes new font selection scheme installed
+%\usepackage{times} % assumes new font selection scheme installed
+%\usepackage{amsmath} % assumes amsmath package installed
+%\usepackage{amssymb}  % assumes amsmath package installed
 
@@
 \usepackage{multirow}
-\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
-\setlength{\columnsep}{0.24in}
+%\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
+%\setlength{\columnsep}{0.24in}
 % correct bad hyphenation here
@@
 
+\title{\LARGE \bf
+Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*
+}
+
+\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory Chirikjian$^{2}*$% <-this % stops a space
+\thanks{*This work is partially
+supported by NSF Grant RI-Medium: \#IIS-1162095}% <-this % stops a space
+\thanks{$^{1}$Haiyuan Li and Tianmiao Wang is with the School of Mechanical Engineering and Automation, Beihang University,
+        ,Beijing 100191, China
+        {\tt\small lihaiyuan@buaa.edu.cn}}%
+\thanks{$^{2}$Qianli Ma and Gregory Chirikjian with the Department of Mechanical Engineering, Johns Hopkins University,
+        Baltimore, MD 21218, USA
+        {\tt\small gregc@jhu.edu}}%
+}
+
 \begin{document}
-% paper title
-\title{\huge Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence $^{*}$\footnoterule\thanks{$^{*}$This work is partially
-supported by NSF Grant RI-Medium: \#IIS-1162095 to }}
 
-% author names and affiliations
-\author{\authorblockN{Haiyuan Li}
-\authorblockA{\textit{School of Mechanical Engineering}\\
-\textit{Beihang University}\\
-\textit{Beijing, China}\\
-\textit{lihaiyuan@buaa.edu.cn}\\}%
-\and
-\authorblockN{Gregory S. Chirikjian}
-\authorblockA{\textit{Department of Intelligent Robotics}\\
-\textit{Johns Hopkins University}\\
-\textit{Baltimore, Maryland, USA}\\
-\textit{gregc@jhu.edu}\\}}%
+\maketitle
+\thispagestyle{empty}
+\pagestyle{empty}
 
-% make the title area
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
 
-\\
+In image-guided system, relationships of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and simultaneous solution is useful in sensor calibration problem.
+Due to asynchrony of sensors timing, the correspondence between $A$ and $B$ is unknown.
+A probabilistic method is presented to solve the
+homogeneous matrix equations without a priori knowledge of the correspondence.
+Using Euclidean-Group invariants, an exact solution can be found.
+We illustrate the calculation in numeric simulation including various numbers of
+robot movements. The results show the efficiency and robustness of the proposed simultaneous
+method.
+
 \end{abstract}
 
-% key words
-\begin{keywords}
-AX=YB, Sensor Calibration, Probabilistic Modeling
-\end{keywords}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Image-guided system has been widely used in robotics such as robot assisted surgery.
-Sensors such as a camera, a laser scanner and an ultrasound probe are usually mounted as the end-effector of a robotic manipulator.
-For a typical ``hand-eye" system as described above, the relative transformation of the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well known $\textbf{AX=XB}$ problem.
-A variation of this problem is characterized as the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
-In a typical environment setup, the relationship among the sensor frame, robot frame and world frame either is subject to change or can be disturbed by uncertainties.
-Therefore, simultaneous coordinate calibrations have to be performed frequently in order to enable the robot to respond to dynamic environments.
+A sensor such as camera, laser scanner or ultrasound probe is usually mounted on the hand of a robotic manipulator.
+To use the "hand-eye" system, the problem of determining the coordination relationship between the sensor frame with respect to the end-effector frame must be solved, which is widely known $\textbf{AX=XB}$ problem for the hand-eye calibration.
+With an extension of this problem, $\textbf{AX=YB}$ problem without knowing the relationship between the world frame and the robot base frame is proposed to achieve the robot-world calibration as well as hand-eye calibration.
+In a dynamic setup environment, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist.
+Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to changing environments.
 
-In the $\textbf{AX=YB}$ problem, $A$s and $B$s can be respectively obtained via different sensors.
-The data streams can be in an asynchronous fashion due to different working frequencies of the sensors.
-The asynchrony causes a shift between the two streams of data which damages the correspondence between $A$s and $B$s.
-In this paper, we present a method to solve for $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $A$s and $B$s.
+In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively calculated using different sensors.
+The data streams are in an asynchronous fashion due to different timing sequences.
+The asynchrony causes a shift between the two streams of data that results in missing the correspondences between $As$ and $Bs$.
+In this paper, we present a method to solve for an $X$ and $Y$ without needing know a priori knowledge of correspondence between $As$ and $Bs$.
 
@@
 \centering
-\includegraphics[width=2in]{fig1.eps}
+\includegraphics[width=3.2in]{fig1.eps}
 \caption{
-(1) The hand-eye calibration problem formulated in a matrix as AX=XB. (2) The hand-eye and robot-robot calibration problem formulated as AX=YB.
+(1) The hand-eye and robot-robot calibration problem which is formulated as AX=YB. (2) The hand-eye calibration problem which is formulated in a matrix as AX=XB.
 }
@@
 
-The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$s and $B$s are the homogeneous transformation matrices describing the relative motion of the end-effector and the sensor respectively.
-As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and $B = B^{i}(B^{i+1})^{-1}$.
-The homogeneous transformation matrix can be described as:
+The hand-eye calibration problem can be generalized as the $\textbf{AX = XB}$ formulation.
+$A$ and $B$ are respectively the homogeneous transformation matrices of end-effector and sensor movement using $A = A^{i}(A^{i+1})^{-1}; B = B^{i}(B^{i+1})^{-1}$ as shown in Fig.~\ref{fig1}.
+The homogeneous transformation matrix can be described with the form.
 \begin{equation}\label{equ0}
@@
 
-Given multiple pairs of $(A_{i},B_{i}) \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$ including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
+According to multiple pairs $(A,B) \in SE(3) \times SE(3)$ which are known a prior, many methods for the only $X$ have been proposed including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
 optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
@@
 has been viewed as $\textbf{AX=YB}$ problem.
-As shown in Fig.~\ref{fig1}, $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation.
+As shown in Fig.~\ref{fig1} (1), $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation.
 The $A$ and $B$ in $\textbf{AX=YB}$ calibration is different from ones in $\textbf{AX=XB}$ from a physical view.
@@
 In Section \ref{sect3} a algorithmic solution involving correlation theorem and Euclidean group invariants is posed to recover the correspondence.
-The simulation results, including known  and unknown correspondence, are illustrated in Section \ref{sect4}.
+The simulation results, including unknown correspondence and noisy data stream, are illustrated in Section \ref{sect4}.
 Finally, we draw some conclusions.
@@
 
-Therefore, for each $A_{i}$ and $B_{i}$ can get
+Therefore, for each $A_{i}$ and $B_{i}$, we can get
 
@@
 
-An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$,then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$.
+An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$.
 A similar procedure is used for computing $M_B$.
@@
 
-Due to $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$,$\Sigma_{X}=0$ and $M_{Y}=Y$,$\Sigma_{Y}=0$, respectively, therefore we can obtain
+Because $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$, $\Sigma_{X}=0$ and $M_{Y}=Y$, $\Sigma_{Y}=0$, respectively, therefore we can obtain
 
@@
 
-The first blocks(\ref{equ17a}) is eigendecomposed with the same diagonal matrix due to matrix similarity $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\wedge Q_{M_{A}}^{T}$, $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\wedge Q_{M_{B}}^{T}$.
+The first blocks (\ref{equ17a}) is eigendecomposed with the same diagonal matrix due to matrix similarity $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\wedge Q_{M_{A}}^{T}$, $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\wedge Q_{M_{B}}^{T}$.
 Then,
@@
 
-In $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$, $Q_{M_{A}}$ and $Q_{M_{B}}$ are constrained to be a rotation matrix and therefore $P \in \Omega$,
+In $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$, $Q_{M_{A}}$ and $Q_{M_{B}}$ are constrained to be a rotation matrix and therefore $P \in \Omega \bigcup (-\Omega)$,
 
@@
 
-Therefore, there are four possibilities of $R_{X}, R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$.
-Then, from \ref{equ17b},four $t_{X}$ corresponding to $R_{X}$ can be directly found.
-Furthermore,four candidate $R_{Y} and t_{Y}$ can be found.
-At last, there are four possibilities of solution $(X_{i},Y_{i}), i = 1,2,3,4$.
+Therefore, there are eight possibilities of $R_{X}, R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$.
+Then, from \ref{equ17b}, eight $t_{X}$ corresponding to $R_{X}$ can be directly found.
+Furthermore, eight candidate $R_{Y} and t_{Y}$ can be found.
+At last, there are eight possibilities of solution $(X_{i},Y_{i}), i = 1,\dots,8$.
 where,
@@
 $AX=YB$ can be written as $AX=X(X^{-1}YB)$ and let $B' = X^{-1}YB$ .
-In the form $AX=XB'$, there exit two Euclidean-Group Invariant relationships for one of four groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,2,3,4)$ as follows,
+In the form $AX=XB'$, there exit two Euclidean-Group invariant relationships for one of eight groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8), B_i^{k} = X^{-1}YB_i$ as follows,
 
@@
 
-From among the four pairs $(X_{i},Y_{i})$, we can find a correct solution to minimize the leat absolute deviations,
+From among the four pairs $(X_{i},Y_{i})$, we can find a correct solution to minimize the absolute deviations,
 
@@
 
-In most cases, the homogeneous transformations with $A$ and $B$ are given based on the data from different sensors.
+In most cases, the homogeneous transformations with $As$ and $Bs$ are given based on the data from different sensors.
 Due to asynchronous timing of the measurement transmissions, the correspondences between $A_{i}$ and $B_{i}^{k}$ is unknown.
-The advantage of the above probabilistic solution lie that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence.
-However, there are still four possible candidate results $(X_{i},Y_{i})$.
-Using Euclidean-Group Invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$   can be known.
+The advantage of the above probabilistic solution lies on that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence.
+However, there are still eight possible candidate results $(X_{i},Y_{i})$.
+Using Euclidean-Group invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.
 
-The Discrete Fourier transform (DFT) decomposes a time-domain signal into its constituent frequencies.
+The Discrete Fourier Transform (DFT) decomposes a time-domain signal into its constituent frequencies.
 The input is a finite list of equally spaced samples of a function.
-Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N_1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$
+Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N-1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$
 
@@
 \end{equation}
-And the Inverse Discrete Fourier transform (IDFT) denoted by
+The Inverse Discrete Fourier transform (IDFT) denoted by
 
 \begin{equation}\label{equ22}
-    X_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
+    x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
 \end{equation}
@@
 The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$.
-The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the least absolute deviations based on Euclidean-Group Invariants relations using the method in Section \ref{sect2}.
+The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the absolute deviations based on Euclidean-Group invariants relations using the method in Section \ref{sect2}.
 
@@
 
-In the numerical experiments in this section, a homogeneous matrix   is generated from a PUMA 560 robotic manipulator. $X$ and $Y$ are chosen from reference .
-
-\subsection{Results of solution with known correspondence}
-
-100 pose measurements with $B_{i}$ closely around $B_{start}$ was employed for generating 100 $A_{i}$.
-As a result by applying the above probabilistic method, four sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=1,\cdots, 100, k=1,2,3,4)$ can be obtained respectively, as shown in Fig.~\ref{fig2} and Fig.~\ref{fig3}.
-Using $\theta_{A_{i}} - \theta_{B_{i}^{k}}$ and $d_{A_{i}} - d_{B_{i}^{k}}$  in Fig.~\ref{fig4} and Fig.~\ref{fig5}, we can find the ${B_{i}^{k}}(k=3)$  corresponding to the least sum of errors and then, $(X_3,Y_3)$ is the desired solution.
-
-From 1 measurements to 500 measurements, the rotational and translational error for $X$ and $Y$ are measured as  $\parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $\parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $\parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $\parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively as shown in Fig.~\ref{fig6}.
-
 \begin{center}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
-\includegraphics[width=3.2in]{fig2.eps}
+\includegraphics[width=2.6in]{fig3.eps}
 \caption{
-Calculated four pairs of rotational angles $(\theta_{A_{i}},\theta_{B_{i}^{k}}) (k=1,2,3,4)$  respectively from 100 measurements
+$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ \ $x_i \sim \mathcal{N}(0,0.1)$.
 }
@@
 
-\begin{center}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
-\includegraphics[width=3.2in]{fig3.eps}
+\includegraphics[width=2.6in,bb=84 202 501 581]{fig2.eps}
 \caption{
-Calculated four pairs of translational displacement  $(d_{A_{i}},d_{B_{i}^{k}}) (k=1,2,3,4)$  respectively from 100 measurements
+$As$ are calculated using $AX=YB$. $X$ and $Y$ are assumed.
 }
@@
 \end{figure}
-\end{center}
+
+In the numerical experiments in this section, the rotational and translational error for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively.
 
 \begin{center}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 \caption{
-Calculated rotational angle deviation $\theta_{A_{i}} - \theta_{B_{i}^{k}} (k=1,2,3,4)$ from Fig.~\ref{fig2}
+The cross correlation of data streams of $(A_{i},B_{i}^{k})$ respectively.
 }
@@
 \begin{center}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 \caption{
-Calculated translational deviation $d_{A_{i}} - d_{B_{i}^{k}} (k=1,2,3,4)$ from Fig.~\ref{fig3}
+Calculated rotational and translational deviation of $X$ and $Y$ solved using the data in Fig.~\ref{fig2} and Fig.~\ref{fig3}.
 }
@@
 
+$B_{i}$ are generated randomly closely around $B_{init}$ using $B_i = B_{init} exp(\mathbf{\widehat{x}})$ and $i$ pose measurements were employed for generating $i$ $A_{i}$ by $A_{i} = YB_{i}X^{-1}$ as shown in Fig.~\ref{fig2} in which a example shows $A$ and $B$ distribution.
+As a result by applying the above probabilistic method, 8 sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=5,\cdots, 100, k=1,\dots,8)$ can be obtained respectively.
+
+If the data streams of $As$ were shifted by $m$ units compared to the data stream $Bs$.
+The maximum of cross correlation can be used to find the corresponding shift, which is $-m$ shown in Fig.~\ref{fig4}, representing the data stream of $B_{i}^{k}$ has been shifted by -m units with respect to ${A_{i}}$.
+Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group invariants.
+
+Using the minimum sum of $||\theta_{A_{i}} - \theta_{B_{i}^{k}}||$ and $||d_{A_{i}} - d_{B_{i}^{k}}||$, we can find the ${B_{i}^{k}}(k=3)$ corresponding to the least sum of errors and then, only a $(X_k,Y_k)$ is the desired solution.
+In Fig.~\ref{fig5}, as the number of $(A,B)$ pairs increase, the errors of translation and rotations are reduced but when the number comes to a certain value, the errors cannot be reduced furthermore.
+
 \begin{center}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 \caption{
-Solution error with increasing pairs $(A_{i},B_{i}^{k})$ from 1 measurements to 500 measurements
+$Error(R_X)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
 }
@@
 
-\subsection{Results of solution without known correspondence}
-As shown in Fig.~\ref{fig7}, the data streams of $A$ were shifted by 10 units.
-The maximum of cross correlation can be used to find the corresponding shift, which is -10 shown in Fig.~\ref{fig8}, representing the data stream of $B_{i}^{k}$ has been shifted by -10 units respective to ${A_{i}}$ .
-Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group Invariants.
-
 \begin{center}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 \caption{
-Shifted Data Streams of $A$ and calculated $B_{i}^{k}$.
+$Error(R_Y)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
 }
@@
 \end{center}
+
 \begin{center}
-
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 \caption{
-The cross correlation of data streams of $(A_{i},B_{i}^{k})$ respectively.
+$Error(t_X)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
 }
 \label{fig8}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\centering
+\includegraphics[width=3.2in]{fig9.eps}
+\caption{
+$Error(t_Y)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
+}
+\label{fig9}
+\end{figure}
+\end{center}
+
+In the generation of $B_i = B_{init} exp(\mathbf{\widehat{x}})$, each element $x_j$ of $\mathbf{x} = (x_1,x_2,x_3,x_4,x_5,x_6)^T $ is Gaussian with $N \sim (\mu,\sigma)$.
+Small disturbances are exerted to the $B_i$ to make the noisy $B_i^{noise} = B_i exp(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$.
+In Fig.~\ref{fig8},~\ref{fig9},~\ref{fig10} and~\ref{fig11}, $\sigma_{noise}$ is 0.005.
+As $\sigma$ varies from $0.1$ to $2$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are reduced as shown in the box-and-whisker plot.
+There are several outliers not included between the whiskers.
+The median data can be used as the final solved $X$ and $Y$.
+
+\begin{center}
+\begin{figure}
+\centering
+\includegraphics[width=2.6in]{fig10.eps}
+\caption{
+The distribution of solved $X$.
+}
+\label{fig10}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\centering
+\includegraphics[width=2.6in]{fig11.eps}
+\caption{
+The distribution of solved $Y$.
+}
+\label{fig11}
 \end{figure}
@@
 
-Conclusions
+In this paper, we developed a probabilistic approach to simultaneously obtain  $X$ and $Y$ in $AX=YB$ sensor calibration problem.
+Without a prior knowledge of the correspondence between $A$ and $B$, in the algorithm the probability theory in Lie group is used to constrain the solution of $X$ and $Y$ to eight candidates.
+As for the shifted data stream of $A$ and $B$, using the correlation theorem with Euclidean group invariants,the correspondence is recovered to determine the correct solution from eight candidates.
+In numeric simulation, the method perform well with different data samples.
 %\section{Conclusion}
@@
 
-% use section* for acknowledgment
-\section*{Acknowledgment}
+\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
+                                  % on the last page of the document manually. It shortens
+                                  % the textheight of the last page by a suitable amount.
+                                  % This command does not take effect until the next page
+                                  % so it should come on the page before the last. Make
+                                  % sure that you do not shorten the textheight too much.
 
-acknowledgement
-% optional entry into table of contents (if used)
-%\addcontentsline{toc}{section}{Acknowledgment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% references section
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{APPENDIX}
+
+\section*{ACKNOWLEDGMENT}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-06-23 Tex_AXYB/paper.tex
Edited first TWO pages

@@
 %\usepackage{amssymb}  % assumes amsmath package installed
+\usepackage{cite}      % Written by Donald Arseneau
+                        % V1.6 and later of IEEEtran pre-defines the format
+                        % of the cite.sty package \cite{} output to follow
+                        % that of IEEE. Loading the cite package will
+                        % result in citation numbers being automatically
+                        % sorted and properly "ranged". i.e.,
+                        % [1], [9], [2], [7], [5], [6]
+                        % (without using cite.sty)
+                        % will become:
+                        % [1], [2], [5]--[7], [9] (using cite.sty)
+                        % cite.sty's \cite will automatically add leading
+                        % space, if needed. Use cite.sty's noadjust option
+                        % (cite.sty V3.8 and later) if you want to turn this
+                        % off. cite.sty is already installed on most LaTeX
+                        % systems. The latest version can be obtained at:
+                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/
 
@@
 %\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}
+\usepackage{mathtools}   % loads »amsmath«
+\usepackage{amssymb,amsmath}
+\usepackage{amsfonts}
 
@@
 
-Image-guided system has been widely used in robotics such as robot assisted surgery.
-A sensor such as camera, laser scanner or ultrasound probe is usually mounted on the hand of a robotic manipulator.
-To use the "hand-eye" system, the problem of determining the coordination relationship between the sensor frame with respect to the end-effector frame must be solved, which is widely known $\textbf{AX=XB}$ problem for the hand-eye calibration.
-With an extension of this problem, $\textbf{AX=YB}$ problem without knowing the relationship between the world frame and the robot base frame is proposed to achieve the robot-world calibration as well as hand-eye calibration.
-In a dynamic setup environment, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist.
-Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to changing environments.
+Image-guided system has been widely used in robotics such as robot assisted surgery, (more examples).
+Sensors such as a camera, a laser scanner or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
+For a typical ``hand-eye'' system as described above, the relative transformation of the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well known $\textbf{AX=XB}$ problem.
+A variation of this problem is characterized as the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
+In a typical environment setup, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist.
+Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to dynamic environments.
 
-In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively calculated using different sensors.
-The data streams are in an asynchronous fashion due to different timing sequences.
-The asynchrony causes a shift between the two streams of data that results in missing the correspondences between $As$ and $Bs$.
-In this paper, we present a method to solve for an $X$ and $Y$ without needing know a priori knowledge of correspondence between $As$ and $Bs$.
+In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively obtained via different sensors.
+The data streams can be in an asynchronous fashion due to the different working frequencies of the sensors.
+The asynchrony causes a shift between the two streams of data which damages the correspondence between $As$ and $Bs$.
+In this paper, a novel method is presented to solve for an $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $As$ and $Bs$.
 
@@
 \caption{
-(1) The hand-eye and robot-robot calibration problem which is formulated as AX=YB. (2) The hand-eye calibration problem which is formulated in a matrix as AX=XB.
+(1) The hand-eye and robot-world calibration problem which is formulated as AX=YB (The universal robot as shown in the picture is owned by professor Emad Boctor in).
+(2) The hand-eye calibration problem which is formulated as AX=XB.
 }
@@
 \end{center}
+The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing  the relative motions of end-effector and the  sensor respectively.
+As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and  $B = B^{i}(B^{i+1})^{-1}$.
+Given multiple pairs of $\{A,B \}$ with correspondence, many methods have been proposed to solve for $X$.
+To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem.
+The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
+All of the methods above assume a prior knowledge of exact correspondence between $A_i$ and $B_i$.
+For data streams $\{A_i\}$ and $\{B_i\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence.
+Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
 
-The hand-eye calibration problem can be generalized as the $\textbf{AX = XB}$ formulation.
-$A$ and $B$ are respectively the homogeneous transformation matrices of end-effector and sensor movement using $A = A^{i}(A^{i+1})^{-1}; B = B^{i}(B^{i+1})^{-1}$ as shown in Fig.~\ref{fig1}.
-The homogeneous transformation matrix can be described with the form.
+Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem.
+As shown in Fig.~\ref{fig1}, $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the the end-effector to its fixed base.
+The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations.
+This problem has been solved by many different methods such as kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
+Simulatneous calibration of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014}.
+Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue.
+In the above methods, the correspondence between $A$ and $B$ is known a prior.
+In this paper, we focus on the $\textbf{AX=YB}$ problem which does not require a priori knowledge of the correspondence of the data streams.
+
+The rest of the paper is organized as follows. In Section
+\ref{sect2}, a novel probabilistic method is presented to solve for $X$ and $Y$.
+In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$.
+The simulation results which deal with noisy data without correspondence are illustrated in Section \ref{sect4}.
+Finally, conclusions are drawn based on the numerical results and possible future works are pointed out.
+
+\section{Solving AX=YB using a probabilistic method on motion groups}
+\label{sect2}
+In this section, a brief introduction to the concepts of probability density function on the special Eucledian group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ are derived.
+
+Any rigid transformation matrix can be viewed as a group element of $SE(3)$ :
 \begin{equation}\label{equ0}
-    g(R,t)=\left(
+    H(R,t)=\left(
              \begin{array}{cc}
@@
              \end{array}
-           \right)
+           \right) \in SE(3)
 \end{equation}
+where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is translational vector and $H$ is symbol for group element.
 
-where $R \in SO(3)$ is a rotation matrix and $t \in R^{3}$ is a translation vector.
-
-According to multiple pairs $(A,B) \in SE(3) \times SE(3)$ which are known a prior, many methods for the only $X$ have been proposed including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
-optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
-Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence.
-Considering data streams containing the $A$ and $B$ will be asynchronous that are discussed in many instances
-in the literature, several methods regardless of the correspondence or recovering the correspondence between two data sets are presented \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
-
-Simultaneous estimation of the hand-eye transformation and robot-world one
-has been viewed as $\textbf{AX=YB}$ problem.
-As shown in Fig.~\ref{fig1} (1), $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation.
-The $A$ and $B$ in $\textbf{AX=YB}$ calibration is different from ones in $\textbf{AX=XB}$ from a physical view.
-This problem has been studied in different methods such as SVD, closed-form, quaternion and nonlinear optimization \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
-Another approach integrate multiple robots to calibrate hand-eye, tool-flange and robot-robot transformation in $\textbf{AXB=YCZ}$ problem \cite{Wang2014}.
-Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue.
-In the above methods, the correspondence between $A$ and $B$ is known a prior.
-In this paper, our solution for $\textbf{AX=YB}$ doesn't require a priori knowledge of correspondences.
-
-The rest of the paper is organized as follows. In Section
-\ref{sect2} we present the probabilistic theory to solve for $X$ and $Y$.
-In Section \ref{sect3} a algorithmic solution involving correlation theorem and Euclidean group invariants is posed to recover the correspondence.
-The simulation results, including unknown correspondence and noisy data stream, are illustrated in Section \ref{sect4}.
-Finally, we draw some conclusions.
-
-\section{Solving AX=YB using a probabilistic theory on motion groups}
-\label{sect2}
-
-Given a large set of pairs $(A_{i},B_{i})\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equations
+Given a large set of pairs $(A_{i},B_{i})\in SE(3)\times SE(3)$ where $i=1,\cdots,n$, the following equation is true if the correspondence is known as a priori:
 
 \begin{equation}\label{equ1}
-A_{i}X=YB_{i}
+A_{i}X=YB_{i}.
 \end{equation}
-
-In the case of $SE(3)$, a Dirac delta function, or $\delta$ function, is thought of as a function which is zero everywhere except at the identity where it is infinite.
+For a matrix $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere:
 
@@
 \end{equation}
-
-Dirac delta function is also constrained to satisfy the identity.
+It also satisfies the identity constraint as:
 
 \begin{equation}\label{equ3}
-\int_{SE(3)}\delta{(H)}dH=1
+\int_{SE(3)}\delta{(H)}dH=1.
 \end{equation}
 
-A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given two functions $f_{1}(g)$ and $f_{2}(g)$, their convolution in Lie group is defined as follows,
+A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$.
+Given $K,H \in SE(3)$ and two well-defined functions $f_{1}, f_{2} \in \left(L^1 \cap L^2 \right)(SE(3))$, their convolution on $SE(3)$ is defined as:
 
 \begin{equation}\label{equ4}
-(f_{1}\ast f_{2})(g)=\int_{SE(3)}f_{1}(h)f_{2}(h^{-1}\circ g)dh
+(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK.
+\end{equation}
+Employing the properties of $\delta$ function, it is straightforward to see that:
+
+\begin{equation}\label{equ5}
+(f\ast \delta)(H)=\int_{SE(3)}f(K)\delta(K^{-1}\circ H)dK=f(H).
+\end{equation}
+Therefore, for each $A_{i}$ and $B_{i}$, the following equations can be obtained:
+
+\begin{IEEEeqnarray}{l}\label{equ6}
+(\delta_{A_{i}}\ast \delta_{X})(H)=\delta(A_{i}^{-1} H X^{-1}) \IEEEyessubnumber
+\\*
+(\delta_{Y}\ast \delta_{B_{i}})(H)=\delta(Y^{-1} H B_{i}^{-1}). \IEEEyessubnumber
+\end{IEEEeqnarray}
+Using Eq.($\ref{equ1}$), the above two equations can be combined into a single equation as:
+
+\begin{equation}\label{equ7}
+(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
 \end{equation}
 
-Considering the properties of $\delta$ function, the following equation is built.
-
-\begin{equation}\label{equ5}
-(f\ast \delta)(g)=\int_{SE(3)}f(h)\delta(h^{-1}\circ g)dh=f(g)
-\end{equation}
-
-Therefore, for each $A_{i}$ and $B_{i}$, we can get
-
-\begin{IEEEeqnarray}{l}\label{equ6}
-(\delta_{A_{i}}\ast \delta_{X})(g)=\delta(A_{i}^{-1} g X^{-1}) \IEEEyessubnumber
+Define the probability density function of $\{A_i\}$ and $\{B_i\}$ as:
+\begin{IEEEeqnarray}{l}\label{equ8}
+f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}H) \IEEEyessubnumber
 \\*
-(\delta_{Y}\ast \delta_{B_{i}})(g)=\delta(Y^{-1} g B_{i}^{-1}) \IEEEyessubnumber
+f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}H) \IEEEyessubnumber
 \end{IEEEeqnarray}
-
-Together with $g=A_{i}X=YB_{i}$, we can obtain the convolution equation
-
-\begin{equation}\label{equ7}
-(\delta_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast \delta_{B_{i}})(g)
-\end{equation}
-
-Convolution provides a linear operation on functions with additional properties. We can add up $n$ instances into a single function.
-
-\begin{IEEEeqnarray}{l}\label{equ8}
-f_{A}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}g) \IEEEyessubnumber
-\\*
-f_{B}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}g) \IEEEyessubnumber
-\end{IEEEeqnarray}
-
-Therefore,
-
+Using the distributivity of convolution, Eq.(\ref{equ8}) can be substituted into Eq.(\ref{equ7}) to get:
 \begin{equation}\label{equ9}
@@
 
-In each transformation set $A_i$s and $B_i$s, we are using small relative motions between consecutive reference frames. Given a measure of distance between reference frames, e.g.
+For each of the data stream $\{A_i\}$ and $\{B_i\}$, small relative motions are calculated between consecutive reference frames.
+Take $\{A_i\}$ for example, one metric of the distance between $A_i$ and $A_{i+1}$ can be defined as:
 
 \begin{eqnarray}\label{equ10}
-d^{2}(A_{i},A_{j})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
+d^{2}(A_{i},A_{i+1})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
 \end{eqnarray}
+where $\Delta A = A_{i}-A_{i+1}$ and $0 < \epsilon \ll 1 $
 
-we have that  $\Delta A = A_{i}-A_{j}$ and $0 < \epsilon \ll 1 $
-
-The convolution of "highly focused" distributions corresponding to closely clumped sets of reference frames have some interesting properties that we can exploit to solve for $X$.
-In particular, let the mean and covariance of a probability density, $f(g)$(e.g.
-$f_{A}(g),f_{B}(g)$), be defined by the conditions.
+The convolution of two ``highly focused" probability density functions have some interesting properties that can be used to solve for $X$.
+In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:
 
 \begin{IEEEeqnarray}{l}\label{equ11}
-\int_{SE(3)}log(M^{-1}g))f(g)dg=0 \IEEEyessubnumber
+\int_{SE(3)}log(M^{-1}H))f(H)dH=0 \IEEEyessubnumber
 \\*
-\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T}f(g)dg \IEEEyessubnumber
+\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1)}H)]^{T}f(H)dH. \IEEEyessubnumber
 \end{IEEEeqnarray}
-
-A discrete version as for $f_{A}(g)$ is
+Then the corresponding discrete version is:
 
 \begin{IEEEeqnarray}{l}\label{equ12}
-\sum_{i=1}^{n}log(M^{-1}g))=0 \IEEEyessubnumber
+\sum_{i=1}^{n}log(M^{-1}H))=0 \IEEEyessubnumber
 \\*
-\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T} \IEEEyessubnumber
+\Sigma = \sum_{i=1}^{n}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1)}H)]^{T} \IEEEyessubnumber
 \end{IEEEeqnarray}

### 2015-06-23 Tex_AXYB/paper.tex
Revised the 3rd page

@@
 \usepackage{amsfonts}
+\usepackage{color}
 
@@
 \end{eqnarray}
-where $\Delta A = A_{i}-A_{i+1}$ and $0 < \epsilon \ll 1 $
+where $\Delta A = A_{i}-A_{i+1}$ and $0 < \epsilon \ll 1 $.
 
-The convolution of two ``highly focused" probability density functions have some interesting properties that can be used to solve for $X$.
+The convolution of two ``highly focused" probability density functions (PDF) have some interesting properties that can be used to solve for $X$.
 In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:
@@
 \\*
-\Sigma = \sum_{i=1}^{n}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1)}H)]^{T} \IEEEyessubnumber
+\Sigma = \sum_{i=1}^{n}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1)}H)]^{T}. \IEEEyessubnumber
 \end{IEEEeqnarray}
 
-While the cloud of frames ${A_{i}}$ is clustered around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008}.
+Given $\{A_i\}$ where the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:
 
@@
 
-An initial estimate of the iterative procedure can be $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then the process iterates until the cost function, $\parallel \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) \parallel^{2}$ falls below a predefined threshold, where the cost function is minimized and the minimum defines $M_{A}$.
-A similar procedure is used for computing $M_B$.
+An initial estimate of the iterative procedure can be chosen as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then a local minimum of $M_A$ is obtained by solving a nonlinear optimization problem with the cost function being $|| \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) ||^{2}$.
+A similar procedure can be used to compute $M_B$.
+$\Sigma_A$ and $\Sigma_B$ are then straight forward to compute given known $M_A$ and $M_B$.
 
-The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly focused functions, $f_{1}$ and $f_{2}$ can be computed as
+The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:
 
@@
 \\*
-\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2} \IEEEyessubnumber
+\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2}. \IEEEyessubnumber
 \end{IEEEeqnarray}
-
 where
 
-$$Ad(g)=\left(
+$$Ad(H)=\left(
                \begin{array}{cc}
@@
                \end{array}
-             \right)$$
+             \right).$$
 
-Because $X$ and $Y$ is fixed, as for $\delta_{X}(g)$ and $\delta_{Y}(g)$, mean and covariance are $M_{X}=X$, $\Sigma_{X}=0$ and $M_{Y}=Y$, $\Sigma_{Y}=0$, respectively, therefore we can obtain
+Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively.
+Therefore, the following equations can be obtained using Eq.(\ref{equ14}):
 
@@
 \\*
-Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B} \IEEEyessubnumber\label{equ15b}
+Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B}. \IEEEyessubnumber\label{equ15b}
 \end{IEEEeqnarray}
 
-From (\ref{equ15a}), we can obtain
+To solve the above equations, Eq.(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as below:
 
@@
 \\*
-R_{M_{A}} t_{X} + t_{M_{A}}= R_{Y} t_{M_{B}} + t_{Y} \IEEEyessubnumber\label{equ16b}
+R_{M_{A}} t_{X} + t_{M_{A}}= R_{Y} t_{M_{B}} + t_{Y}. \IEEEyessubnumber\label{equ16b}
 \end{IEEEeqnarray}
-
-$\Sigma_{M_{A}}$ and $\Sigma_{M_{B}}$ can be decomposed into blocks as
+$\Sigma_{A}$ and $\Sigma_{B}$ can be decomposed into blocks as
 $\left(\begin{array}{cc}
-       \Sigma_{M_{A}}^{1} & \Sigma_{M_{A}}^{2} \\
-       \Sigma_{M_{A}}^{3} & \Sigma_{M_{A}}^{4} \\
+       \Sigma_{A}^{1} & \Sigma_{A}^{2} \\
+       \Sigma_{A}^{3} & \Sigma_{A}^{4} \\
        \end{array}
@@
 $\left(\begin{array}{cc}
-       \Sigma_{M_{B}}^{1} & \Sigma_{M_{B}}^{2} \\
-       \Sigma_{M_{B}}^{3} & \Sigma_{M_{B}}^{4} \\
+       \Sigma_{B}^{1} & \Sigma_{B}^{2} \\
+       \Sigma_{B}^{3} & \Sigma_{B}^{4} \\
        \end{array}
-       \right)$, respectively. Using
-$ X^{-1}=X^{T}=\left(\begin{array}{cc}
+       \right)$, respectively. Knowing that
+$ X^{-1} = \left(\begin{array}{cc}
        R_{X}^{T} & -R_{X}^{T}t_{X}  \\
@@
        \right)$,
-then we can write the first two blocks of (\ref{equ15b}) as follows,
+then the first two blocks of Eq.(\ref{equ15b}) can be written as follows:
 
@@
 \\*
-\Sigma_{M_{B}}^{2} = R_{X}^{T}\Sigma_{M_{A}}^{1} R_{X} (\widehat{R_{X}^{T}t_{X}}) + R_{X}^{T}\Sigma_{M_{A}}^{2}R_{X}
+\Sigma_{M_{B}}^{2} = R_{X}^{T}\Sigma_{M_{A}}^{1} R_{X} (\widehat{R_{X}^{T}t_{X}}) + R_{X}^{T}\Sigma_{M_{A}}^{2}R_{X}.
  \IEEEyessubnumber\label{equ17b}
 \end{IEEEeqnarray}
-
-The first blocks (\ref{equ17a}) is eigendecomposed with the same diagonal matrix due to matrix similarity $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\wedge Q_{M_{A}}^{T}$, $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\wedge Q_{M_{B}}^{T}$.
-Then,
+Because Eq.(\ref{equ17a}) is a similarity transformation between $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$, they share the same eigenvalues and can be eigendecomposed into   $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\Lambda Q_{M_{A}}^{T}$ and $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\Lambda Q_{M_{B}}^{T}$ where $\Lambda$ is a diagonal matrix whose diagonal elements are the eigenvalues of $\Sigma_{M_{A}}^{1}$ ($\Sigma_{M_{B}}^{1}$), and $Q_{M_{A}}$ ($Q_{M_{B}}$) is a square matrix whose columns are the corresponding eigenvectors.
+Following equation is obtained after substitution into Eq.(\ref{equ17a}):
 
 \begin{equation}\label{equ18}
-    \wedge = (Q_{M_{A}}^{T}R_{X}Q_{M_{B}}) \wedge (Q_{M_{B}}^{T}R_{X}^{T}Q_{M_{A}})= P \wedge P^{T}
+    \Lambda = (Q_{M_{A}}^{T}R_{X}^{T}Q_{M_{B}}) \Lambda (Q_{M_{B}}^{T}R_{X}Q_{M_{A}})= P \Lambda P^{T}
+\end{equation}
+where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.(\ref{equ18}) can be:
+
+\begin{equation}\label{equ19}
+\begin{split}
+{\cal P} = \left\{ \left(\begin{array}{ccc}
+1\,\, & 0 \,\, & 0 \,\, \\
+0 & 1 & 0\\
+0 & 0 & 1 \end{array}\right) , \left(\begin{array}{ccc}
+-1 & 0 & 0 \\
+0 & -1 & 0\\
+0 & 0 & 1 \end{array}\right), \right.\\
+\left. \left(\begin{array}{ccc}
+-1 & 0 & 0 \\
+0 & 1 & 0\\
+0 & 0 & -1 \end{array}\right), \left(\begin{array}{ccc}
+1 & 0 & 0 \\
+0 & -1 & 0\\
+0 & 0 & -1 \end{array}\right)\right\}.
+\end{split} 
 \end{equation}
 
-In $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$, $Q_{M_{A}}$ and $Q_{M_{B}}$ are constrained to be a rotation matrix and therefore $P \in \Omega \bigcup (-\Omega)$,
-
-\begin{equation}\label{equ19}
-\Omega= \left(
-\begin{array}{ccc}
-\left( \begin{array}{ccc}
-       1 & 0 & 0 \\
-       0 & 1 & 0 \\
-       0 & 0 & 1 \\
-\end{array} \right),&
-\left( \begin{array}{ccc}
-       -1 & 0 & 0 \\
-       0 & -1 & 0 \\
-       0 & 0 & 1 \\
-\end{array} \right)
-\\
-\left( \begin{array}{ccc}
-       -1 & 0 & 0 \\
-       0 & 1 & 0 \\
-       0 & 0 & -1 \\
-\end{array} \right),&
-\left( \begin{array}{ccc}
-       1 & 0 & 0 \\
-       0 & -1 & 0 \\
-       0 & 0 & -1 \\
-\end{array} \right)
-\end{array}
-\right)
-\end{equation}
-
-Therefore, there are eight possibilities of $R_{X}, R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$.
-Then, from \ref{equ17b}, eight $t_{X}$ corresponding to $R_{X}$ can be directly found.
-Furthermore, eight candidate $R_{Y} and t_{Y}$ can be found.
-At last, there are eight possibilities of solution $(X_{i},Y_{i}), i = 1,\dots,8$.
-where,
+Therefore, there are eight candidates of $R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$.
+Then the corresponding $t_{X}$ can be obtained  from Eq.(\ref{equ17b}).
+Given known $X$, $Y$ can be solved for by $Y = M_A^{-1}XM_B^{-1}$.
+At last, eight candidate pairs of  $\{X_{i},Y_{i}\}$ can be obtained as:
 
@@
 X_{i}= \left( \begin{array}{cc}
-       R_{X} & t_{X} \\
+       R_{X_i} & t_{X_i} \\
        \mathbf{0}^{T} & \mathbf{1}\\
@@
 Y_{i}= \left( \begin{array}{cc}
-       R_{Y} & t_{Y} \\
+       R_{Y_i} & t_{Y_i} \\
        \mathbf{0}^{T} & \mathbf{1}\\
@@
 \end{equation}
-
-Based on the screw theory, it is known that a homogeneous transformation $H$ can be written in the form with four parameters $(\theta,d,\mathbf{n},\mathbf{p})$.
+The problem then becomes selecting the best pair of $\{X_i, Y_i\}$ from the eight candidates. 
+Based on the screw theory (references?), it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ as:
 
@@
 \end{equation}
+where $\theta$, $d$, $\mathbf{n}$ and $\mathbf{p}$ are ?.
 
-$AX=YB$ can be written as $AX=X(X^{-1}YB)$ and let $B' = X^{-1}YB$ .
-In the form $AX=XB'$, there exit two Euclidean-Group invariant relationships for one of eight groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8), B_i^{k} = X^{-1}YB_i$ as follows,
+Moreover, $AX=YB$ can be written as $AX=X(X^{-1}YB)$.
+If define $B' = X^{-1}YB$, then we will have $AX=XB'$.
+there exit two Euclidean-Group invariant relationships for one of eight groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8), B_i^{k} = X^{-1}YB_i$ as follows,
 

### 2015-06-23 Tex_AXYB/paper.tex
Revised First Two Sections

@@
 Given known $X$, $Y$ can be solved for by $Y = M_A^{-1}XM_B^{-1}$.
-At last, eight candidate pairs of  $\{X_{i},Y_{i}\}$ can be obtained as:
+At last, eight candidate pairs of  $\{X_{k},Y_{k}\}$ can be obtained as:
 
@@
 \begin{array}{cc}
-X_{i}= \left( \begin{array}{cc}
-       R_{X_i} & t_{X_i} \\
+X_{k}= \left( \begin{array}{cc}
+       R_{X_k} & t_{X_k} \\
        \mathbf{0}^{T} & \mathbf{1}\\
 \end{array} \right),&
-Y_{i}= \left( \begin{array}{cc}
-       R_{Y_i} & t_{Y_i} \\
+Y_{k}= \left( \begin{array}{cc}
+       R_{Y_k} & t_{Y_k} \\
        \mathbf{0}^{T} & \mathbf{1}\\
@@
 \end{equation}
-The problem then becomes selecting the best pair of $\{X_i, Y_i\}$ from the eight candidates. 
+where $k = 1,2,...,8$.
+
+The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates. 
 Based on the screw theory (references?), it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ as:
@@
 
-Moreover, $AX=YB$ can be written as $AX=X(X^{-1}YB)$.
-If define $B' = X^{-1}YB$, then we will have $AX=XB'$.
-there exit two Euclidean-Group invariant relationships for one of eight groups of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8), B_i^{k} = X^{-1}YB_i$ as follows,
+Moreover, $AX_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$.
+If define $B^k = X_k^{-1}Y_kB$, then we will have $AX_k=X_kB^k$.
+There exist two Euclidean-Group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
 
@@
 
-From among the four pairs $(X_{i},Y_{i})$, we can find a correct solution to minimize the absolute deviations,
+Among the four pairs $(X_{k},Y_{k})$, one can find an optimal solution which  minimizes the cost function defined as:
 
 \begin{equation}\label{equ23}
-    (X,Y) = \mathop{\mathbf{arg}min}_{(X_{i},Y_{i})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel)
+    (X,Y) = \mathop{\mathbf{arg}min}_{(X_{k},Y_{k})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel)
 \end{equation}
 
-\section{Solution with unknown correspondence of $A_{i}$ and $B_{i}^{k}$}
+\section{Solution with unknown correspondence between $A_{i}$ and $B_{i}^{k}$}
 \label{sect3}

### 2015-06-28 Tex_AXYB/paper.tex

@@
 
-In most cases, the homogeneous transformations with $As$ and $Bs$ are given based on the data from different sensors.
-Due to asynchronous timing of the measurement transmissions, the correspondences between $A_{i}$ and $B_{i}^{k}$ is unknown.
-The advantage of the above probabilistic solution lies on that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence.
-However, there are still eight possible candidate results $(X_{i},Y_{i})$.
-Using Euclidean-Group invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.
+In most cases, the homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors.
+Due to the asynchronous timing of the sensor readings, the correspondences between $\{A_{i}\}$ and $\{B_{j}^{k}\}$ is usually unknown.
+This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and Euclidean-Group invariants are used to recover the correspondence between the data streams.
+{\color{red}The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is not a priori knowledge of the correspondence.} However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-Group invariants, it is straightforward to determine which pair is the optimal one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.
 
@@
 The input is a finite list of equally spaced samples of a function.
-Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N-1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$
+Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N-1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}({x_{n}})$ as:
 
 \begin{equation}\label{equ21}
-    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa)
+    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa).
 \end{equation}
-The Inverse Discrete Fourier transform (IDFT) denoted by
+The Inverse Discrete Fourier transform (IDFT) is denoted as:
 
 \begin{equation}\label{equ22}
-    x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
+    x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa).
 \end{equation}
@@
 \begin{equation}\label{equ23}
-    (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau)
+    (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
 \end{equation}
 
-In convolution theorem, the Fourier transform of a convolution is the product of the Fourier transforms, namely,
+In the convolution theorem, the Fourier transform of a convolution is the product of the Fourier transforms, namely:
 
 \begin{equation}\label{equ24}
-    f \ast g = \mathcal{F}^{-1} [\mathcal{F}(f) \cdot \mathcal{F}(g)]
+    f \ast g = \mathcal{F}^{-1} [\mathcal{F}(f) \cdot \mathcal{F}(g)].
 \end{equation}
 
-The correlation theorem indicates that the correlation function, $Corr(f,g)$, will have a large value at a shift vector if the two sequences $f$ and $g$ contain similar features.
+The correlation theorem indicates that the correlation function, $Corr(f,g)$, will possess a larger value for a shift vector where the two sequences $f_n$ and $g_n$ can share more similar features.
 The correlation can be obtained based on the convolution theorem.
-The DFT of the correlation $Corr(f,g)$ is equal to the product of the DFT of a sequence $f_{n}$ and the complex conjugate $\mathcal{F}^{*}$ of the DFT of the other sequence $g_n$.
+The DFT of $Corr(f,g)$ is equal to the product of the DFT of $f_{n}$ and the complex conjugate $\mathcal{F}^{*}$ of the DFT of $g_n$:
 
 \begin{equation}\label{equ25}
-    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}]
+    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}].
 \end{equation}
 
-Compared with the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the fast Fourier transform (FFT).
+Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the fast Fourier transform (FFT).
 
-There are two sequences $\theta_{A_{i}}$ and $\theta_{B_{i}^{k}}$ from each pair $(A_{i},B_{i}^{k})$.
-For homogeneous transformations from which the range of $\theta$ can vary, two sequences $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ can be first normalized.
+Given two sequences $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$ corresponding to  $\{A_{i}\}$ and $\{B_{i}^{k}\}$, the shift that is needed to recover the data correspondence is obtained as below.
+Firstly, $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ are normalized as:
 
@@
 \end{equation}
-
-where $\mu_{A_{i}}(\mu_{B_{i}^{k}})$ is the average of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A_{i}}(\sigma_{B_{i}^{k}})$ is the standard deviation.
+where $\mu_{A_{i}}(\mu_{B_{i}^{k}})$ is the mean of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A_{i}}(\sigma_{B_{i}^{k}})$ is the standard deviation.
 
 Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $(n)$ which describes the probability that these two sequences are separated by this particular unit.
-The location of the function maximum indicates the amount of shift, $\tau_{shift}$, between the two sequence $\theta_{A_{i}}$ and $\theta_{B_{i}^{k}}$.
+The index corresponding to the maximum of $Corr(\theta_{1},\theta_{2})$  indicates the amount of shift $\tau_{shift}$ between the $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$.
 
@@
 Therefore, the correspondence between the two sequences can be found.
-The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$.
-The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the absolute deviations based on Euclidean-Group invariants relations using the method in Section \ref{sect2}.
+{\color{red}The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$ TO BE REPHRASED}.
+The data stream can be shifted back to regain correspondence once the shift is computed and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using Euclidean-Group invariants as shown in Section \ref{sect2}.
 
@@
 \caption{
-$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ \ $x_i \sim \mathcal{N}(0,0.1)$.
+$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ where $x_i \sim \mathcal{N}(0,0.1)$.
 }

### 2015-06-28 Tex_AXYB/paper.tex
need to be revised by qianli

@@
 \centering
-\includegraphics[width=2.6in]{fig3.eps}
+\includegraphics[width=3.2in]{fig2.eps}
 \caption{
-$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ where $x_i \sim \mathcal{N}(0,0.1)$.
+The errors of translation and rotations versus the data stream shift between $A$ and $B$,
 }
@@
 \centering
-\includegraphics[width=2.6in,bb=84 202 501 581]{fig2.eps}
+\includegraphics[width=3.2in]{fig3.eps}
 \caption{
-$As$ are calculated using $AX=YB$. $X$ and $Y$ are assumed.
+The errors of translation and rotations versus noise covariance exerted to the data $B$".
 }
@@
 \caption{
-The cross correlation of data streams of $(A_{i},B_{i}^{k})$ respectively.
+The solved $X$ (in red) and the actual $X$ (in blue) in 5 trial simulation with noise covariance 0.01 and shift 2.
 }
@@
 \caption{
-Calculated rotational and translational deviation of $X$ and $Y$ solved using the data in Fig.~\ref{fig2} and Fig.~\ref{fig3}.
+The solved $Y$ (in red) and the actual $Y$ (in blue) in 5 trial simulation with noise covariance 0.01 and shift 2.
 }
@@
 
-$B_{i}$ are generated randomly closely around $B_{init}$ using $B_i = B_{init} exp(\mathbf{\widehat{x}})$ and $i$ pose measurements were employed for generating $i$ $A_{i}$ by $A_{i} = YB_{i}X^{-1}$ as shown in Fig.~\ref{fig2} in which a example shows $A$ and $B$ distribution.
+$B_{i}$ are generated randomly closely around $\mu$.
+We get a group of samples $B_i$ from Gaussian distribution over Lie group with a mean $\mu=0 \in G$ and a covariance matrix $\Sigma \in \mathbb{R}^{k \times k}$ as follows.
+
+\begin{IEEEeqnarray}{l}
+\delta \in \mathcal{N}(0;\Sigma) \IEEEyessubnumber\label{equ28a}
+\\*
+x = exp(\delta)\cdot \mu \IEEEyessubnumber\label{equ28b}
+\end{IEEEeqnarray}
+
+$i$ pose measurements were employed for generating $i$ $A_{i}$ by $A_{i} = YB_{i}X^{-1}$.
 As a result by applying the above probabilistic method, 8 sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=5,\cdots, 100, k=1,\dots,8)$ can be obtained respectively.
@@
 If the data streams of $As$ were shifted by $m$ units compared to the data stream $Bs$.
-The maximum of cross correlation can be used to find the corresponding shift, which is $-m$ shown in Fig.~\ref{fig4}, representing the data stream of $B_{i}^{k}$ has been shifted by -m units with respect to ${A_{i}}$.
+The maximum of cross correlation can be used to find the corresponding shift, which is $-m$, representing the data stream of $B_{i}^{k}$ has been shifted by -m units with respect to ${A_{i}}$.
 Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group invariants.
 
-Using the minimum sum of $||\theta_{A_{i}} - \theta_{B_{i}^{k}}||$ and $||d_{A_{i}} - d_{B_{i}^{k}}||$, we can find the ${B_{i}^{k}}(k=3)$ corresponding to the least sum of errors and then, only a $(X_k,Y_k)$ is the desired solution.
-In Fig.~\ref{fig5}, as the number of $(A,B)$ pairs increase, the errors of translation and rotations are reduced but when the number comes to a certain value, the errors cannot be reduced furthermore.
+Using the minimum sum of $||\theta_{A_{i}} - \theta_{B_{i}^{k}}||$ and $||d_{A_{i}} - d_{B_{i}^{k}}||$, we can find a ${B_{i}^{k}}$ corresponding to the least sum of errors and then, only a $(X_k,Y_k)$ is the desired solution.
+In Fig.~\ref{fig2}, as the data stream between $A$ and $B$ shifts increase, the errors of translation and rotations are increased in general.
 
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=3.2in]{fig6.eps}
-\caption{
-$Error(R_X)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
-}
-\label{fig6}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=3.2in]{fig7.eps}
-\caption{
-$Error(R_Y)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
-}
-\label{fig7}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=3.2in]{fig8.eps}
-\caption{
-$Error(t_X)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
-}
-\label{fig8}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=3.2in]{fig9.eps}
-\caption{
-$Error(t_Y)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
-}
-\label{fig9}
-\end{figure}
-\end{center}
-
-In the generation of $B_i = B_{init} exp(\mathbf{\widehat{x}})$, each element $x_j$ of $\mathbf{x} = (x_1,x_2,x_3,x_4,x_5,x_6)^T $ is Gaussian with $N \sim (\mu,\sigma)$.
-Small disturbances are exerted to the $B_i$ to make the noisy $B_i^{noise} = B_i exp(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$.
-In Fig.~\ref{fig8},~\ref{fig9},~\ref{fig10} and~\ref{fig11}, $\sigma_{noise}$ is 0.005.
-As $\sigma$ varies from $0.1$ to $2$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are reduced as shown in the box-and-whisker plot.
+Small disturbances are exerted to the $B_i$ to make the noisy $B_i^{noise} = B_i exp(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}){noise}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$.
+In Fig.~\ref{fig3}, As $\sigma_{noise}$ varies from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are increased as shown in the box-and-whisker plot.
 There are several outliers not included between the whiskers.
 The median data can be used as the final solved $X$ and $Y$.
-
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=2.6in]{fig10.eps}
-\caption{
-The distribution of solved $X$.
-}
-\label{fig10}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=2.6in]{fig11.eps}
-\caption{
-The distribution of solved $Y$.
-}
-\label{fig11}
-\end{figure}
-\end{center}
+Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$) in blue and actual ($X$,$Y$) in red in coordinate frame.
 

### 2015-06-28 Matlab_AXYB_Ver2/Comparion/dataTransAB.m

@@ -1,0 +1,10 @@
+function [A,B] = dataTransAB(AA,BB)
+len = size(AA,3);
+A = zeros(4,4*len);
+B = zeros(4,4*len);
+for i = 1:1:len
+    A(:,(4*i - 3):(4*i)) = AA(:,:,i);
+    B(:,(4*i - 3):(4*i)) = BB(:,:,i);
+end
+
+end

### 2015-06-28 Matlab_AXYB_Ver2/Comparion/dornaika.m

@@ -1,0 +1,141 @@
+function [X,Y]=dornaika(AA,BB)
+% Solves the problem AX=YB
+% using the formulation of
+%
+% Simultaneous robot-world and hand-eye calibration
+% F. Dornaika and R. Horaud
+%
+% Mili Shah
+% July 2014
+
+[m,n]=size(AA); n = n/4;
+
+%Building quaternion representation for A and B
+C = zeros(4,4);
+for i = 1:n
+    A = AA(1:3,4*i-3:4*i-1);
+    B = BB(1:3,4*i-3:4*i-1);
+    
+    qa = rot2q(A);
+    qb = rot2q(B);
+    q0 = qa(4);
+    qx = qa(1);
+    qy = qa(2);
+    qz = qa(3);
+    
+    QA = [...
+        [q0 -qx -qy -qz]; ...
+        [qx  q0 -qz  qy]; ...
+        [qy  qz  q0 -qx]; ...
+        [qz -qy  qx  q0]; ...
+        ];
+    q0 = qb(4);
+    qx = qb(1);
+    qy = qb(2);
+    qz = qb(3);
+    
+    WB = [...
+        [q0 -qx -qy -qz]; ...
+        [qx  q0  qz -qy]; ...
+        [qy -qz  q0  qx]; ...
+        [qz  qy -qx  q0]; ...
+        ];
+    
+    
+    C = C - QA'*WB;
+end
+
+[u,s,v]=svd(C); diag(s);
+[val,in] = min(n-diag(s));
+x = [u(2:4,in);u(1,in)];
+y = [v(2:4,in);v(1,in)];
+
+X = q2rot(x);
+Y = q2rot(y);
+
+A = zeros(3*n,6);
+b = zeros(3*n,1);
+for i = 1:n
+    A(3*i-2:3*i,:) = [-AA(1:3,4*i-3:4*i-1) eye(3)];
+    b(3*i-2:3*i,:) = AA(1:3,4*i) - kron(BB(1:3,4*i)',eye(3))*reshape(Y,9,1);
+end
+t = A\b;
+
+X = [X t(1:3);[0 0 0 1]];
+Y = [Y t(4:6);[0 0 0 1]];
+end
+function q = rot2q(R)
+
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Comparion/main.m

@@ -1,0 +1,125 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+
+nstd = [0.2];% 0.1 0.5]%[0.01 0.02 0.04 0.06 0.08 0.1 0.2 0.4 0.6 0.8 1];  %Gaussian Noise standard deviation Range
+
+counter = 0;
+sig = 0.8;    
+point = [50 10 80];
+for k = point(1):point(2):point(3)
+    waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k, sig,0);
+% [A,B,XActual,YActual] =  ABGen(k,0);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+
+[AA,BB] = dataTransAB(A,B);
+[Xc(:,:,1),Yc(:,:,1)] = dornaika(AA,BB);
+[Xc(:,:,2),Yc(:,:,2)] = li(AA,BB);
+[Xc(:,:,3),Yc(:,:,3)] = shah(AA,BB);
+[Xc(:,:,4),Yc(:,:,4)] = zhuang(AA,BB);
+%% err analysis
+counter = counter + 1;
+num(counter) = k;
+Err(counter,1) = roterror(X,XActual);
+Err(counter,2) = roterror(Y,YActual);
+Err(counter,3) = tranerror(X,XActual);
+Err(counter,4) = tranerror(Y,YActual);
+
+for ne = 1:1:4
+    Errc(counter,1,ne) = roterror(Xc(:,:,ne),XActual);
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Comparion/shah.m

@@ -1,0 +1,43 @@
+function [X,Y]=shah(AA,BB)
+% Solves the problem AX=YB
+% using the formulation of
+%
+% Simultaneous Robot/World and Tool/Flange 
+% Calibration by Solving Homogeneous Transformation 
+% Equations of the form AX=YB
+% M. Shah
+%
+% Mili Shah
+% July 2014
+
+[m,n]=size(AA); n = n/4;
+A = zeros(9*n,18);
+T = zeros(9,9);
+b = zeros(9*n,1);
+for i = 1:n
+    Ra = AA(1:3,4*i-3:4*i-1);
+    Rb = BB(1:3,4*i-3:4*i-1);
+    A(9*i-8:9*i,:) = [kron(Rb,Ra) -eye(9)];
+    T = T + kron(Rb,Ra);
+end
+[u,s,v]=svd(T);
+x = v(:,1);
+y = u(:,1);
+X = reshape(x,3,3);
+X = sign(det(X))/abs(det(X))^(1/3)*X;
+[u,s,v]=svd(X); X = u*v';
+Y = reshape(y,3,3);
+Y = sign(det(Y))/abs(det(Y))^(1/3)*Y;
+[u,s,v]=svd(Y); Y = u*v';
+A = zeros(3*n,6);
+b = zeros(3*n,1);
+for i = 1:n
+    A(3*i-2:3*i,:) = [-AA(1:3,4*i-3:4*i-1) eye(3)];
+    b(3*i-2:3*i,:) = AA(1:3,4*i) - kron(BB(1:3,4*i)',eye(3))*reshape(Y,9,1);
+end
+t = A\b;
+
+X = [X t(1:3);[0 0 0 1]];
+Y = [Y t(4:6);[0 0 0 1]];
+
+

### 2015-06-28 Matlab_AXYB_Ver2/Comparion/zhuang.m

@@ -1,0 +1,130 @@
+function [X,Y]=zhuang(A,B)
+% Solves the problem AX=YB
+% using the formulation of
+%
+% Simultaneous Robot/World and Tool/Flange Calibration 
+% by Solving Homogeneous Transformation Equations of the 
+% form AX=YB
+% H. Zhuang, Z. S. Roth, R. Sudhakar
+%
+% Mili Shah
+% July 2014
+
+[m,n]=size(A);
+n = n/4;
+
+G = zeros(3*n,6);
+c = zeros(3*n,1);
+for i = 1:n
+    RA = A(1:3,4*i-3:4*i-1);
+    RB = B(1:3,4*i-3:4*i-1);
+    qa = rot2q(RA);
+    qb = rot2q(RB);
+    
+    Oa = [0 -qa(3) qa(2); qa(3) 0 -qa(1); -qa(2) qa(1) 0];
+    Ob = [0 -qb(3) qb(2); qb(3) 0 -qb(1); -qb(2) qb(1) 0];
+    
+    G(3*i-2:3*i,:) = [qa(4)*eye(3)+Oa+qa(1:3)*qa(1:3)'/qa(4),...
+        -qb(4)*eye(3)+Ob-qa(1:3)*qb(1:3)'/qa(4)];
+    c(3*i-2:3*i,:) = qb(1:3)-qb(4)/qa(4)*qa(1:3);
+end
+
+w = G\c;
+y = zeros(4,1);
+x = zeros(4,1);
+
+y(4) = (1+w(4)^2+w(5)^2+w(6)^2).^(-1/2);
+y(1:3) = y(4)*w(4:6);
+x(1:3) = y(4)*w(1:3);
+x(4) = (1-x(1)^2-x(2)^2-x(3)^2).^(1/2);
+
+X = q2rot(x);
+Y = q2rot(y);
+
+AA = zeros(3*n,6);
+b = zeros(3*n,1);
+for i = 1:n
+    AA(3*i-2:3*i,:) = [-A(1:3,4*i-3:4*i-1) eye(3)];
+    b(3*i-2:3*i,:) = A(1:3,4*i) - kron(B(1:3,4*i)',eye(3))*reshape(Y,9,1);
+end
+t = AA\b;
+
+X = [X t(1:3);[0 0 0 1]];
+Y = [Y t(4:6);[0 0 0 1]];
+end
+
+function q = rot2q(R)
+
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/ABGen.m

@@ -1,0 +1,53 @@
+function [A,B,X,Y] = ABGen(len,shift)
+
+numPair = len;
+shift = 0;
+
+A = zeros(4,4,numPair);
+B = zeros(4,4,numPair);
+
+num = numPair + 2;
+t2 = (0:(2*pi)/((num + shift)):2*pi);
+twist = 0.0*sin(16*t2);
+
+ElipseParam = [10, 10, 10];
+
+%% data
+Y1 = [-0.99908 -0.03266 0.02786 164.226/1000;
+      0.02737  0.01553 0.99950 301.638/1000;
+     -0.03308  0.99935 -0.01462 -962.841/1000;
+     0.00000   0.00000 0.00000  1.00000;];
+ X1 = [-0.97651 -0.09468 -0.19356 9.190/1000;
+     0.06362 -0.98493 0.16082 5.397/1000;
+     -0.20587 0.14473 0.96782 62.628/1000;
+     0.00000 0.00000 0.00000 1.00000;];
+
+% x = randn(6,1); X = expm(se3_vec(x));
+X=inv(X1);
+Y = Y1;
+trajParam = [.5, .5, .5, 0, 0];
+B1 = createTraj(ElipseParam(1), ElipseParam(2), ElipseParam(3), trajParam(1), trajParam(2), trajParam(3), trajParam(4), trajParam(5), num, twist);
+% [A1, B1] = AB_genTraj(X, ElipseParam, trajParam, num, twist);
+
+trajParam = [.5, .5, .5, 0, 0.5*pi];
+% [A2, B2] = AB_genTraj(X, ElipseParam, trajParam, num, twist);
+B2 = createTraj(ElipseParam(1), ElipseParam(2), ElipseParam(3), trajParam(1), trajParam(2), trajParam(3), trajParam(4), trajParam(5), num/2, twist);
+
+% A = cat(3, A1, A2);
+B = cat(3, B1, B2);
+
+for m = 1:1:size(B,3)
+    A(:,:,m) = Y * B(:,:,m) / X;
+%     figure(1);
+%     trplot(A(:,:,m),'color','r');
+%     axis auto
+%     hold on
+%     figure(2);
+%     trplot(B(:,:,m),'color','b');
+%     axis auto
+%     hold on
+%     pause();
+% end
+% X = inv(X);
+end
+end

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/ABGenerate.m

@@ -1,0 +1,52 @@
+function [A,B,X,Y] =  ABGenerate(length,opt,M,Sig)
+%% 
+% load Asup2;
+% A = Asup2;
+% B = Bsup2;
+% clear;
+% close
+% clc
+%% Times of simulation steps
+len = length;
+% e = precision;
+% digits(64);
+%% generate fixed data X Y
+if opt == 0
+Y = [-0.99908 -0.03266 0.02786 164.226/1000;
+      0.02737  0.01553 0.99950 301.638/1000;
+     -0.03308  0.99935 -0.01462 -962.841/1000;
+     0.00000   0.00000 0.00000  1.00000;];
+ X = inv([-0.97651 -0.09468 -0.19356 9.190/1000;
+     0.06362 -0.98493 0.16082 5.397/1000;
+     -0.20587 0.14473 0.96782 62.628/1000;
+     0.00000 0.00000 0.00000 1.00000;]);
+else 
+%% generate random X and Y
+x=randn(6,1); x=x./norm(x); X=expm(se3_vec(x));    %Generate a Random X
+
+y=randn(6,1); y=y./norm(y); Y=expm(se3_vec(y));    %Generate a Random Y
+end
+% using puma560 to generate tranformation B
+ qz = [pi/6,pi/3,pi/4,pi/4,-pi/4,0];
+ mdl_puma560;
+ Binitial = p560.fkine(qz);
+%  Ainitial = Y * Binitial / X;
+%  trplot(Ainitial,'color','b');
+%  trplot(Y,'color','b');
+%  hold on
+% load invariantrandom.mat 
+ for m = 1:1:len
+%      r1 = rand(6,1) - 0.5;
+%      B(:,:,m) = Binitial * expm(sig * (twist(r1)));
+%      A(:,:,m) = Y * B(:,:,m) / X;
+    B(:,:,m) = expm(se3_vec(mvg(M, Sig, 1)))*Binitial;     
+    A(:,:,m) = Y * B(:,:,m) / X;
+     
+%      A = AA(1:3,4*i-3:4*i-1);
+%      B = BB(1:3,4*i-3:4*i-1);
+%      [OmegaA(:,:,m) thetaA(m)] = rotparam(A(1:3,1:3,m));
+%      dA(m) = dot(A(1:3,4,m),OmegaA(:,:,m));
+%      trplot(A(:,:,m),'color','r');
+ end
+
+end

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/batchAXYB.m

@@ -1,0 +1,114 @@
+function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B)
+
+X_candidate = zeros(4,4,8);
+Y_candidate = zeros(4,4,8);
+thetaA = zeros(size(A,3),1);
+thetaB = zeros(size(A,3),8);
+dA = zeros(size(A,3),1);
+dB = zeros(size(A,3),8);
+deltaTheta = zeros(size(A,3),8);
+deltaD = zeros(size(A,3),8);
+normMin = zeros(8,1);
+
+[ MeanA, SigA ] = distibutionProps(A);
+[ MeanB, SigB ] = distibutionProps(B);
+
+[ VA, ~ ] = eig( SigA(1:3,1:3) );
+[ VB, ~ ] = eig( SigB(1:3,1:3) );
+
+Q1 = eye(3);
+Q2 = [-1 0 0; 0 -1 0; 0 0 1];
+Q3 = [-1 0 0; 0 1 0; 0 0 -1];
+Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+
+% There are 8 possiblities of Rx
+
+Rx_solved(:,:,1) = VA*Q1*VB';
+Rx_solved(:,:,2) = VA*Q2*VB';
+Rx_solved(:,:,3) = VA*Q3*VB';
+Rx_solved(:,:,4) = VA*Q4*VB';
+Rx_solved(:,:,5) = VA*-Q1*VB';
+Rx_solved(:,:,6) = VA*-Q2*VB';
+Rx_solved(:,:,7) = VA*-Q3*VB';
+Rx_solved(:,:,8) = VA*-Q4*VB';
+
+Bnew = zeros(4,4,8);
+for i = 1:1:8
+    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
+    tx = -Rx_solved(:,:,i)*tx_temp;
+    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
+    Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
+end
+% use Fouier transformation to find the correspondence between A and X-1YB
+
+for i = 1:1:size(A,3)
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/batchAXYBshift.m

@@ -1,0 +1,175 @@
+function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(A, B)
+
+X_candidate = zeros(4,4,8);
+Y_candidate = zeros(4,4,8);
+thetaA = zeros(size(A,3),1);
+thetaB = zeros(size(A,3),8);
+dA = zeros(size(A,3),1);
+dB = zeros(size(A,3),8);
+deltaTheta = zeros(size(A,3),8);
+deltaD = zeros(size(A,3),8);
+normMin = zeros(8,1);
+
+[ MeanA, SigA ] = distibutionProps(A);
+[ MeanB, SigB ] = distibutionProps(B);
+
+[ VA, ~ ] = eig( SigA(1:3,1:3) );
+[ VB, ~ ] = eig( SigB(1:3,1:3) );
+
+Q1 = eye(3);
+Q2 = [-1 0 0; 0 -1 0; 0 0 1];
+Q3 = [-1 0 0; 0 1 0; 0 0 -1];
+Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+
+% There are 8 possiblities of Rx
+
+Rx_solved(:,:,1) = VA*Q1*VB';
+Rx_solved(:,:,2) = VA*Q2*VB';
+Rx_solved(:,:,3) = VA*Q3*VB';
+Rx_solved(:,:,4) = VA*Q4*VB';
+Rx_solved(:,:,5) = VA*-Q1*VB';
+Rx_solved(:,:,6) = VA*-Q2*VB';
+Rx_solved(:,:,7) = VA*-Q3*VB';
+Rx_solved(:,:,8) = VA*-Q4*VB';
+
+Bnew = zeros(4,4,8);
+for i = 1:1:8
+    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
+    tx = -Rx_solved(:,:,i)*tx_temp;
+    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
+    Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
+end
+% use Fouier transformation to find the correspondence between A and X-1YB
+
+for i = 1:1:size(A,3)
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/main.m

@@ -1,0 +1,89 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 0;
+sig = 0.2;    
+point = [80 10 100];
+for k = point(1):point(2):point(3)
+    waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k, sig,0);
+% [A,B,XActual,YActual] =  ABGen(k,0);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+% B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+counter = counter + 1;
+num(counter) = k;
+Err(counter,1) = roterror(X,XActual);
+Err(counter,2) = roterror(Y,YActual);
+Err(counter,3) = tranerror(X,XActual);
+Err(counter,4) = tranerror(Y,YActual);
+%% plot 
+% for j = 1:1:k
+%     figure(3);
+%     trplot(A(:,:,j),'color','r');
+%     axis auto
+%     hold on
+%     figure(4);
+%     trplot(B(:,:,j),'color','b');
+%     axis auto
+%     hold on
+% end
+% figure(3);
+% legend('Generated A');
+% figure(4);
+% legend('Generated B');
+
+%% --plot X and Y-------------------------------------------
+% figure(5);
+% trplot(X(:,:),'color','b');
+% axis auto
+% hold on
+% figure(6);
+% trplot(Y(:,:),'color','b');
+% axis auto
+% hold on
+% for n = 1:1:k
+% 	figure(3);
+%     trplot(A(:,:,n),'color','b');
+%     hold on
+% end
+% for n = 1:1:k
+% 	figure(4);
+%     trplot(B(:,:,n),'color','b');
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/main_ABCov.m

@@ -1,0 +1,86 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 0;
+trials = 20;
+sigArray = [0.1 0.2 0.4 0.6 0.8 1 2];
+
+h = waitbar(0);
+for n = 1:1:size(sigArray,2)
+for m = 1:1:trials
+
+point = [50 10 50];
+for k = point(1):point(2):point(3)
+
+waitbar((m + (n-1)*trials)/(trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(m + (n-1)*trials),trials*size(sigArray,2)))
+% waitbar((k-point(1))/(point(3)-point(1)));
+
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k,sigArray(n),0);
+% [A,B,XActual,YActual] =  ABGen(k,0);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+counter = counter + 1;
+num(counter) = k;
+Err(counter,1) = roterror(X,XActual);
+Err(counter,2) = roterror(Y,YActual);
+Err(counter,3) = tranerror(X,XActual);
+Err(counter,4) = tranerror(Y,YActual);
+
+figure(1)
+trplot(X,'color','r');
+hold on
+axis auto
+% legend('solved and actual X');
+figure(2)
+trplot(Y,'color','r');
+hold on
+axis auto
+
+end
+
+rotErrX(m,n) = Err(counter,1);
+rotErrY(m,n) = Err(counter,2);
+tranErrX(m,n) = Err(counter,3);
+tranErrY(m,n) = Err(counter,4);
+end
+end
+
+figure(1)
+trplot(XActual(:,:),'color','k');
+% legend('solved and actual X');
+figure(2)
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/main_ABCovNoise.m

@@ -1,0 +1,86 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+
+nstd = [0.01 0.02 0.04 0.06 0.08 0.1 0.2 0.4 0.6 0.8 1];  %Gaussian Noise standard deviation Range
+
+counter = 0;
+trials = 10;
+sigArray = [0.05 0.1 0.2 0.4 0.6 0.8 1 2 3];
+
+h = waitbar(0);
+
+for n = 1:1:size(sigArray,2)
+    
+    for n_noise = 1:1:size(nstd,2)
+    
+    for m = 1:1:trials
+
+        point = [50 10 50];
+        for k = point(1):point(2):point(3)
+
+            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
+            % waitbar((k-point(1))/(point(3)-point(1)));
+
+           %% --Trajectory Generation-------------------------
+            [A,B,XActual,YActual] =  ABGenerate(k,sigArray(n),1);
+            % [A,B,XActual,YActual] =  ABGen(k,0);
+
+           %% add noise
+            B = sensorNoise(B, gmean, nstd(n_noise), 1);
+
+           %% --using probility methods------------------------
+            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+            % [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+            Y(4,1:3) = [0 0 0];
+            %% err analysis
+            counter = counter + 1;
+            num(counter) = k;
+            Err(counter,1) = roterror(X,XActual);
+            Err(counter,2) = roterror(Y,YActual);
+            Err(counter,3) = tranerror(X,XActual);
+            Err(counter,4) = tranerror(Y,YActual);
+
+        end
+
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/main_ABCovNoiseComparison.m

@@ -1,0 +1,116 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+
+nstd = [0.1];% 0.1 0.5]%[0.01 0.02 0.04 0.06 0.08 0.1 0.2 0.4 0.6 0.8 1];  %Gaussian Noise standard deviation Range
+
+counter = 0;
+trials = 5;
+sigArray = [0.1 0.2 0.6 0.8 2];
+
+h = waitbar(0);
+
+for n = 1:1:size(sigArray,2)
+    
+    for n_noise = 1:1:size(nstd,2)
+    
+    for m = 1:1:trials
+
+        point = [100 10 100];
+        for k = point(1):point(2):point(3)
+
+            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
+            % waitbar((k-point(1))/(point(3)-point(1)));
+
+           %% --Trajectory Generation-------------------------
+            [A,B,XActual,YActual] =  ABGenerate(k,sigArray(n),0);
+            % [A,B,XActual,YActual] =  ABGen(k,0);
+
+           %% add noise
+%             B = sensorNoise(B, gmean, nstd(n_noise), 1);
+
+           %% --using probility methods------------------------
+            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+%             [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+%             [AA,BB] = dataTransAB(A,B);
+%             [X,Y]=zhuang(AA,BB);
+            
+            Y(4,1:3) = [0 0 0];
+            %% err analysis
+            counter = counter + 1;
+            num(counter) = k;
+            Err(counter,1) = roterror(X,XActual);
+            Err(counter,2) = roterror(Y,YActual);
+            Err(counter,3) = tranerror(X,XActual);
+            Err(counter,4) = tranerror(Y,YActual);
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Early Version before 150619/se3_vec.m

@@ -1,0 +1,19 @@
+%Function to vectorize or hat an element of se(3)
+
+%files needed:
+%none
+
+function g = se3_vec(X)
+
+if ( size(X,2) == 4 ) %If input is skew-sym change to vector
+    
+    g = [-X(2,3); X(1,3); -X(1,2); X(1,4); X(2,4); X(3,4)];
+    
+else %If input is vector change to skew-sym 
+    
+    g = [0      -X(3)	X(2)	X(4);
+        X(3)    0       -X(1)   X(5);
+        -X(2)   X(1)    0       X(6);
+          0       0       0       0];
+
+end

### 2015-06-28 Matlab_AXYB_Ver2/Inverse/batchAXYBinverse.m

@@ -1,0 +1,178 @@
+function [ Y_candidate ] = batchAXYBinverse(inMeanA, inMeanB, inSigA, inSigB)
+
+X_candidate = zeros(4,4,8);
+Y_candidate = zeros(4,4,8);
+% thetaA = zeros(size(A,3),1);
+% thetaB = zeros(size(A,3),8);
+% dA = zeros(size(A,3),1);
+% dB = zeros(size(A,3),8);
+% deltaTheta = zeros(size(A,3),8);
+% deltaD = zeros(size(A,3),8);
+% normMin = zeros(8,1);
+
+MeanB = inv(inMeanA);
+SigB = Ad(inMeanA)*inSigA*(Ad(inMeanA))';
+
+MeanA = inv(inMeanB);
+SigA = Ad(inMeanB)*inSigB*(Ad(inMeanB))';
+
+[ VA, ~ ] = eig( SigA(1:3,1:3) );
+[ VB, ~ ] = eig( SigB(1:3,1:3) );
+
+Q1 = eye(3);
+Q2 = [-1 0 0; 0 -1 0; 0 0 1];
+Q3 = [-1 0 0; 0 1 0; 0 0 -1];
+Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+
+% There are 8 possiblities of Rx
+
+Rx_solved(:,:,1) = VA*Q1*VB';
+Rx_solved(:,:,2) = VA*Q2*VB';
+Rx_solved(:,:,3) = VA*Q3*VB';
+Rx_solved(:,:,4) = VA*Q4*VB';
+Rx_solved(:,:,5) = VA*-Q1*VB';
+Rx_solved(:,:,6) = VA*-Q2*VB';
+Rx_solved(:,:,7) = VA*-Q3*VB';
+Rx_solved(:,:,8) = VA*-Q4*VB';
+
+%Bnew = zeros(4,4,8);
+for i = 1:1:8
+    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
+    tx = -Rx_solved(:,:,i)*tx_temp;
+    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
+    Y_candidate(:,:,i) = inv(X_candidate(:,:,i));
+end
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Inverse/batchAXYBshift_inverse.m

@@ -1,0 +1,175 @@
+function [ X_candidate, MeanA, MeanB, SigA, SigB ] = batchAXYBshift_inverse(A, B)
+
+X_candidate = zeros(4,4,8);
+% Y_candidate = zeros(4,4,8);
+% thetaA = zeros(size(A,3),1);
+% thetaB = zeros(size(A,3),8);
+% dA = zeros(size(A,3),1);
+% dB = zeros(size(A,3),8);
+% deltaTheta = zeros(size(A,3),8);
+% deltaD = zeros(size(A,3),8);
+% normMin = zeros(8,1);
+
+[ MeanA, SigA ] = distibutionProps(A);
+[ MeanB, SigB ] = distibutionProps(B);
+
+[ VA, ~ ] = eig( SigA(1:3,1:3) );
+[ VB, ~ ] = eig( SigB(1:3,1:3) );
+
+Q1 = eye(3);
+Q2 = [-1 0 0; 0 -1 0; 0 0 1];
+Q3 = [-1 0 0; 0 1 0; 0 0 -1];
+Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+
+% There are 8 possiblities of Rx
+
+Rx_solved(:,:,1) = VA*Q1*VB';
+Rx_solved(:,:,2) = VA*Q2*VB';
+Rx_solved(:,:,3) = VA*Q3*VB';
+Rx_solved(:,:,4) = VA*Q4*VB';
+Rx_solved(:,:,5) = VA*-Q1*VB';
+Rx_solved(:,:,6) = VA*-Q2*VB';
+Rx_solved(:,:,7) = VA*-Q3*VB';
+Rx_solved(:,:,8) = VA*-Q4*VB';
+
+% Bnew = zeros(4,4,8);
+for i = 1:1:8
+    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
+    tx = -Rx_solved(:,:,i)*tx_temp;
+    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
+%     Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
+end
+% use Fouier transformation to find the correspondence between A and X-1YB
+
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Inverse/defineXY.m

@@ -1,0 +1,30 @@
+function [X, Y] = defineXY(Xc, Yc, MeanA, MeanB)
+min = 10000;
+RA = MeanA(1:3,1:3);
+tA = MeanA(1:3,4);
+RB = MeanB(1:3,1:3);
+tB = MeanB(1:3,4);
+
+for i = 1:1:size(Xc,3)
+    for j = 1:1:size(Yc,3)
+        
+        RX = Xc(1:3,1:3,i);
+        tX = Xc(1:3,4,i);
+        RY = Yc(1:3,1:3,j);
+        tY = Yc(1:3,4,j);
+%         
+%         temp = det(RA*RX)
+               %temp =  norm(logm(MeanA(1:3,1:3) * Xc(1:3,1:3,i)) - logm(Yc(1:3,1:3,j) * MeanB(1:3,1:3)));
+               temp = norm(RA*RX - RY*RB) + norm(RA*tX+tA-RY*tB-tY);
+       if(temp < min)
+           id_x = i;
+           id_y = j;
+           min = temp;       
+       end
+    end
+    
+end
+X = Xc(:,:,id_x);
+Y = Yc(:,:,id_y);
+
+end

### 2015-06-28 Matlab_AXYB_Ver2/Inverse/main.m

@@ -1,0 +1,112 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 1;
+trials = 1;
+
+% point = [50 1 50];
+% sum = zeros(1,4);
+point = [10 10 10];
+sum = zeros( (100 - 100)/10 + 1,4);
+
+shift = 10;
+for k = point(1):point(2):point(3)
+
+for i = 1:1:trials
+%     waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k, 0.2,0);
+% [A,B,X,Y] =  ABGen(k,0);
+length = size(A,3);
+
+% As = A(:,:,1:(length - shift));
+% Bs = B(:,:,(shift + 1):length);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.1;  %Gaussian Noise standard deviation Range
+ C=B;
+ B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+[ Xc, MeanA, MeanB, SigA, SigB ] = batchAXYBshift_inverse(A, B);
+
+[Yc] = batchAXYBinverse(MeanA, MeanB, SigA, SigB);
+
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+[X, Y] = defineXY(Xc, Yc, MeanA, MeanB);
+
+% Y(4,1:3) = [0 0 0];
+%% err analysis
+
+sum(counter,1) = sum(counter,1) + roterror(X,XActual);
+sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
+sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
+sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
+end
+
+num(counter) = k;
+counter = counter + 1;
+
+%% plot 
+for j = 1:1:k
+    figure(4);
+    trplot(C(:,:,j),'color','r');
+    axis auto
+    hold on
+%     figure(5);
+    trplot(B(:,:,j),'color','b');
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/ABGenerate.m

@@ -1,0 +1,53 @@
+function [A,B,X,Y] =  ABGenerate(length,opt,M,Sig)
+%% 
+% load Asup2;
+% A = Asup2;
+% B = Bsup2;
+% clear;
+% close
+% clc
+%% Times of simulation steps
+len = length;
+% e = precision;
+% digits(64);
+%% generate fixed data X Y
+if opt == 0
+Y = [-0.99908 -0.03266 0.02786 164.226/1000;
+      0.02737  0.01553 0.99950 301.638/1000;
+     -0.03308  0.99935 -0.01462 -962.841/1000;
+     0.00000   0.00000 0.00000  1.00000;];
+ X = inv([-0.97651 -0.09468 -0.19356 9.190/1000;
+     0.06362 -0.98493 0.16082 5.397/1000;
+     -0.20587 0.14473 0.96782 62.628/1000;
+     0.00000 0.00000 0.00000 1.00000;]);
+else 
+%% generate random X and Y
+x=randn(6,1); x=x./norm(x); X=expm(se3_vec(x));    %Generate a Random X
+
+y=randn(6,1); y=y./norm(y); Y=expm(se3_vec(y));    %Generate a Random Y
+end
+% using puma560 to generate tranformation B
+ qz = [pi/6,pi/3,pi/4,pi/4,-pi/4,0];
+ mdl_puma560;
+ Binitial = p560.fkine(qz);
+%  Ainitial = Y * Binitial / X;
+%  trplot(Ainitial,'color','b');
+%  trplot(Y,'color','b');
+%  hold on
+% load invariantrandom.mat 
+ for m = 1:1:len
+%      r1 = rand(6,1) - 0.5;
+%      B(:,:,m) = Binitial * expm(sig * (twist(r1)));
+%      A(:,:,m) = Y * B(:,:,m) / X;
+%     B(:,:,m) = expm(se3_vec([0;0;0;mvg(M, SigT, 1)]))*(expm(se3_vec([mvg(M, SigR, 1);0;0;0;]))*Binitial);     
+B(:,:,m) = expm(se3_vec(mvg(M, Sig, 1)))*Binitial;      
+A(:,:,m) = Y * B(:,:,m) / X;
+     
+%      A = AA(1:3,4*i-3:4*i-1);
+%      B = BB(1:3,4*i-3:4*i-1);
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/ABGenerate_rand.m

@@ -1,0 +1,53 @@
+function [A,B,X,Y] =  ABGenerate_rand(length,sig,opt)
+%% 
+% load Asup2;
+% A = Asup2;
+% B = Bsup2;
+% clear;
+% close
+% clc
+%% Times of simulation steps
+len = length;
+% e = precision;
+% digits(64);
+%% generate fixed data X Y
+if opt == 0
+Y = [-0.99908 -0.03266 0.02786 164.226/1000;
+      0.02737  0.01553 0.99950 301.638/1000;
+     -0.03308  0.99935 -0.01462 -962.841/1000;
+     0.00000   0.00000 0.00000  1.00000;];
+ X = inv([-0.97651 -0.09468 -0.19356 9.190/1000;
+     0.06362 -0.98493 0.16082 5.397/1000;
+     -0.20587 0.14473 0.96782 62.628/1000;
+     0.00000 0.00000 0.00000 1.00000;]);
+else 
+%% generate random X and Y
+x=randn(6,1); x=x./norm(x); X=expm(se3_vec(x));    %Generate a Random X
+
+y=randn(6,1); y=y./norm(y); Y=expm(se3_vec(y));    %Generate a Random Y
+end
+% using puma560 to generate tranformation B
+ qz = [pi/6,pi/3,pi/4,pi/4,-pi/4,0];
+ mdl_puma560;
+ Binitial = p560.fkine(qz);
+%  Ainitial = Y * Binitial / X;
+%  trplot(Ainitial,'color','b');
+%  trplot(Y,'color','b');
+%  hold on
+% load invariantrandom.mat 
+ for m = 1:1:len
+     r1 = rand(6,1) - 0.5;
+     B(:,:,m) = Binitial * expm(sig * (twist(r1)));
+%      A(:,:,m) = Y * B(:,:,m) / X;
+%     B(:,:,m) = expm(se3_vec([0;0;0;mvg(M, SigT, 1)]))*(expm(se3_vec([mvg(M, SigR, 1);0;0;0;]))*Binitial);     
+% B(:,:,m) = expm(se3_vec(mvg(M, Sig, 1)))*Binitial;      
+A(:,:,m) = Y * B(:,:,m) / X;
+     
+%      A = AA(1:3,4*i-3:4*i-1);
+%      B = BB(1:3,4*i-3:4*i-1);
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/Ad.m

@@ -1,0 +1,8 @@
+function [G] = Ad(g)
+R = g(1:3,1:3);
+t = g(1:3,4);
+T = [0    -t(3)  t(2);
+    t(3)  0      -t(1);
+    -t(2) t(1)   0;]
+G= [R zeros(3,3); T*R R];
+end

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/batchAXYBshift.m

@@ -1,0 +1,175 @@
+function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(A, B)
+
+X_candidate = zeros(4,4,8);
+Y_candidate = zeros(4,4,8);
+thetaA = zeros(size(A,3),1);
+thetaB = zeros(size(A,3),8);
+dA = zeros(size(A,3),1);
+dB = zeros(size(A,3),8);
+deltaTheta = zeros(size(A,3),8);
+deltaD = zeros(size(A,3),8);
+normMin = zeros(8,1);
+
+[ MeanA, SigA ] = distibutionProps(A);
+[ MeanB, SigB ] = distibutionProps(B);
+
+[ VA, ~ ] = eig( SigA(1:3,1:3) );
+[ VB, ~ ] = eig( SigB(1:3,1:3) );
+
+Q1 = eye(3);
+Q2 = [-1 0 0; 0 -1 0; 0 0 1];
+Q3 = [-1 0 0; 0 1 0; 0 0 -1];
+Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+
+% There are 8 possiblities of Rx
+
+Rx_solved(:,:,1) = VA*Q1*VB';
+Rx_solved(:,:,2) = VA*Q2*VB';
+Rx_solved(:,:,3) = VA*Q3*VB';
+Rx_solved(:,:,4) = VA*Q4*VB';
+Rx_solved(:,:,5) = VA*-Q1*VB';
+Rx_solved(:,:,6) = VA*-Q2*VB';
+Rx_solved(:,:,7) = VA*-Q3*VB';
+Rx_solved(:,:,8) = VA*-Q4*VB';
+
+Bnew = zeros(4,4,8);
+for i = 1:1:8
+    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
+    tx = -Rx_solved(:,:,i)*tx_temp;
+    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
+    Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
+end
+% use Fouier transformation to find the correspondence between A and X-1YB
+
+for i = 1:1:size(A,3)
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/display11.m

@@ -1,0 +1,16 @@
+for i = 1:1:size(sigArray,2)
+figure
+h1 = subplot(4,1,1)
+plot(median(rotErrX(:,1:6,i)));
+axis auto;
+h2 = subplot(4,1,2)
+plot(median(rotErrY(:,1:6,i)));
+axis auto;
+h3 = subplot(4,1,3)
+plot(median(tranErrX(:,1:6,i)));
+
+axis auto;
+h4 = subplot(4,1,4)
+plot(median(tranErrY(:,1:6,i)));
+axis auto;
+end

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/distibutionProps.m

@@ -1,0 +1,81 @@
+function [ M, Sig ] = distibutionProps( X )
+
+
+Xsum = zeros(4);
+
+% 1. Use X to calculate the mean of se(3) Lie algebra
+% 2. Exponentiate the mean of se(3) into Lie group SE(3) 
+for j = 1:size(X,3)
+    Xsum = Xsum + logm(X(:,:,j));
+end
+
+M = expm( (1/size(X,3))*Xsum );
+
+C_old = inf; C = 0;
+
+diff = 0.05; eps = 0.001;
+
+% The six Lie algebra elements for SE(3)
+E(:,:,1) = [0 0 0 0; 0 0 -1 0; 0 1 0 0; 0 0 0 0]; 
+E(:,:,2) = [0 0 1 0; 0 0 0 0; -1 0 0 0; 0 0 0 0]; 
+E(:,:,3) = [0 -1 0 0; 1 0 0 0; 0 0 0 0; 0 0 0 0];
+E(:,:,4) = [0 0 0 1; 0 0 0 0; 0 0 0 0; 0 0 0 0]; 
+E(:,:,5) = [0 0 0 0; 0 0 0 1; 0 0 0 0; 0 0 0 0]; 
+E(:,:,6) = [0 0 0 0; 0 0 0 0; 0 0 0 1; 0 0 0 0];
+
+count = 0;
+while( abs(C-C_old) > diff && count < 10 )
+    
+    C_old = C;
+    
+    for j = 1:6
+        
+        if C_old > 20
+            M1 = M*expm(eps*20*E(:,:,j));
+            M2 = M*expm(-eps*20*E(:,:,j));
+        elseif C_old > 1
+            M1 = M*expm(eps*C_old*E(:,:,j));
+            M2 = M*expm(-eps*C_old*E(:,:,j));
+            
+        else
+            M1 = M*expm(eps*E(:,:,j));
+            M2 = M*expm(-eps*E(:,:,j));
+            
+        end
+        
+        
+        M1sum = zeros(4);
+        M2sum = zeros(4);
+        for k = 1:size(X,3)
+            M1sum = M1sum + logm( M1^-1*X(:,:,k) );
+            M2sum = M2sum + logm( M2^-1*X(:,:,k) );
+            
+        end
+        
+        
+        C1 = norm(M1sum)^2;
+        C2 = norm(M2sum)^2;
+        
+        if (C1 <= C2)
+            C = C1;
+            M = M1;
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/main.m

@@ -1,0 +1,97 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 0;
+
+Mean=[0;0;0;0;0;0];
+
+Cov=0.3*eye(6,6); 
+
+point = [100 10 100];
+for k = point(1):point(2):point(3)
+    waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+% [A,B,XActual,YActual] =  ABGen(k,0);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.05;  %Gaussian Noise standard deviation Range
+
+B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+counter = counter + 1;
+num(counter) = k;
+Err(counter,1) = roterror(X,XActual);
+Err(counter,2) = roterror(Y,YActual);
+Err(counter,3) = tranerror(X,XActual);
+Err(counter,4) = tranerror(Y,YActual);
+%% plot 
+% for j = 1:1:k
+%     figure(3);
+%     trplot(A(:,:,j),'color','r');
+%     axis auto
+%     hold on
+%     figure(4);
+%     trplot(B(:,:,j),'color','b');
+%     axis auto
+%     hold on
+% end
+% figure(3);
+% legend('Generated A');
+% figure(4);
+% legend('Generated B');
+
+%% --plot X and Y-------------------------------------------
+figure(5);
+trplot(X(:,:),'color','b');
+axis auto
+hold on
+figure(6);
+trplot(Y(:,:),'color','b');
+axis auto
+hold on
+% for n = 1:1:k
+% 	figure(3);
+%     trplot(A(:,:,n),'color','b');
+%     axis auto
+%     hold on
+% end
+% for n = 1:1:k
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCovNoise.m

@@ -1,0 +1,102 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+
+nstd = 0.02;%[0.01 0.02 0.04 0.06 0.08];%[0.01 0.02 0.04 0.06 0.08 0.1];  %Gaussian Noise standard deviation Range
+
+counter = 0;
+trials = 5;
+% sigArrayR =  0.3;
+% sigArrayT =  0.3;%[0.1 0.2 0.3];
+sigArray = 0.3;
+Mean=[0;0;0;0;0;0;];
+
+h = waitbar(0);
+
+for n = 1:1:size(sigArray,2)
+    
+    for n_noise = 1:1:size(nstd,2)
+    
+    for m = 1:1:trials
+
+        point = [50 10 50];
+        for k = point(1):point(2):point(3)
+
+            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
+            % waitbar((k-point(1))/(point(3)-point(1)));
+            Cov=sigArray(n)*eye(6,6); 
+%             CovR=sigArrayR(n)*eye(3,3); 
+%             CovT=sigArrayT(1)*eye(3,3);
+           %% --Trajectory Generation-------------------------
+            [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+            % [A,B,XActual,YActual] =  ABGen(k,0);
+
+           %% add noise
+%             B = sensorNoise(B, gmean, nstd(n_noise), 1);
+
+           %% --using probility methods------------------------
+            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+            % [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+            Y(4,1:3) = [0 0 0];
+            %% err analysis
+%             counter = counter + 1;
+%             num(counter) = k;
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCovNoiseComparison.m

@@ -1,0 +1,116 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+
+nstd = [0.01 0.02 0.04 0.06 0.08 0.1 0.2 0.4 0.6 0.8 1];  %Gaussian Noise standard deviation Range
+
+counter = 0;
+trials = 5;
+sigArray = 2;%[0.1 0.2 0.6 0.8 2];
+
+h = waitbar(0);
+
+for n = 1:1:size(sigArray,2)
+    
+    for n_noise = 1:1:size(nstd,2)
+    
+    for m = 1:1:trials
+
+        point = [100 10 100];
+        for k = point(1):point(2):point(3)
+
+            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
+            % waitbar((k-point(1))/(point(3)-point(1)));
+
+           %% --Trajectory Generation-------------------------
+            [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray(n),0);
+            % [A,B,XActual,YActual] =  ABGen(k,0);
+
+           %% add noise
+            B = sensorNoise(B, gmean, nstd(n_noise), 1);
+
+           %% --using probility methods------------------------
+            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+%             [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+%             [AA,BB] = dataTransAB(A,B);
+%             [X,Y]=zhuang(AA,BB);
+            
+            Y(4,1:3) = [0 0 0];
+            %% err analysis
+            counter = counter + 1;
+            num(counter) = k;
+            Err(counter,1) = roterror(X,XActual);
+            Err(counter,2) = roterror(Y,YActual);
+            Err(counter,3) = tranerror(X,XActual);
+            Err(counter,4) = tranerror(Y,YActual);
+%             figure(n)
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCovNoise_rand.m

@@ -1,0 +1,102 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = [0.01 0.02 0.04 0.06 0.08];
+% nstd = [0.01 0.04 0.06 0.08];%[0.01 0.02 0.04 0.06 0.08 0.1];  %Gaussian Noise standard deviation Range
+
+counter = 0;
+trials = 5;
+% sigArrayR =  0.3;
+% sigArrayT =  0.3;%[0.1 0.2 0.3];
+sigArray = [0.1 0.2 0.4 0.6 0.8 1 2];
+Mean=[0;0;0;0;0;0;];
+
+h = waitbar(0);
+
+for n = 1:1:size(sigArray,2)
+    
+    for n_noise = 1:1:size(nstd,2)
+    
+    for m = 1:1:trials
+
+        point = [100 10 100];
+        for k = point(1):point(2):point(3)
+
+            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
+            % waitbar((k-point(1))/(point(3)-point(1)));
+%             Cov=sigArray(n)*eye(6,6); 
+%             CovR=sigArrayR(n)*eye(3,3); 
+%             CovT=sigArrayT(1)*eye(3,3);
+           %% --Trajectory Generation-------------------------
+            [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray(n),0);
+            % [A,B,XActual,YActual] =  ABGen(k,0);
+
+           %% add noise
+            B = sensorNoise(B, gmean, nstd(n_noise), 1);
+
+           %% --using probility methods------------------------
+            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+            % [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+            Y(4,1:3) = [0 0 0];
+            %% err analysis
+%             counter = counter + 1;
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_shift.m

@@ -1,0 +1,109 @@
+
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 1;
+trials = 5;
+Mean=[0;0;0;0;0;0;];
+% point = [50 1 50];
+% sum = zeros(1,4);
+point = [210 5 210];
+sum = zeros(1,4);
+sigArray = 0.3;
+shift = 2;
+for k = point(1):point(2):point(3)
+for i = 1:1:trials
+%     waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+%  [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray,0);
+% [A,B,X,Y] =  ABGen(k,0);
+Cov=sigArray*eye(6,6);
+[A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+ length = size(A,3);
+i
+As = A(:,:,1:(length - shift));
+Bs = B(:,:,(shift + 1):length);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(As, Bs);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+
+% sum(counter,1) = sum(counter,1) + roterror(X,XActual);
+% sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
+% sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
+% sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
+% 
+% 
+% num(counter) = k;
+% counter = counter + 1;
+
+%% plot 
+
+    figure(11);
+    trplot(X,'color','b');
+    axis auto
+    hold on
+    figure(12);
+    trplot(Y,'color','b');
+    axis auto
+    hold on
+end
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_shiftVary.m

@@ -1,0 +1,9 @@
+clear all
+close all
+clc
+errXY=zeros(4,11);
+for shift = 0:1:5
+    errXY(:,shift+1) = shift_main(shift);
+    
+end
+plot(errXY')

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/shift_main.m

@@ -1,0 +1,110 @@
+function errXY = shift_main(shift) 
+% clear all
+% close all
+% clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 1;
+trials = 5;
+Mean=[0;0;0;0;0;0;];
+% point = [50 1 50];
+% sum = zeros(1,4);
+point = [210 5 210];
+sum = zeros(1,4);
+sigArray = 2;
+% shift = 2;
+for k = point(1):point(2):point(3)
+for i = 1:1:trials
+%     waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray,0);
+% [A,B,X,Y] =  ABGen(k,0);
+% Cov=sigArray*eye(6,6);
+% [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+ length = size(A,3);
+
+As = A(:,:,1:(length - shift));
+Bs = B(:,:,(shift + 1):length);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+% B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(As, Bs);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+
+sum(counter,1) = sum(counter,1) + roterror(X,XActual);
+sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
+sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
+sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
+end
+
+num(counter) = k;
+counter = counter + 1;
+
+%% plot 
+% for j = 1:1:k
+%     figure(11);
+%     trplot(A(:,:,j),'color','r');
+%     axis auto
+%     hold on
+%     figure(12);
[…]

### 2015-06-28 Matlab_AXYB_Ver2/Version 2 -Gaussian/test_ABdistribution.m

@@ -1,0 +1,27 @@
+clear all
+%close all
+clc
+
+counter = 0;
+
+Mean=[0;0;0;0;0;0];
+
+Cov=1.2*eye(6,6);   
+
+point = [50 10 50];
+k = 50;
+
+[A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+
+for n = 1:1:k
+	figure(5);
+    trplot(A(:,:,n),'color','b');
+    axis auto
+    hold on
+end
+for n = 1:1:k
+	figure(6);
+    trplot(B(:,:,n),'color','b');
+    axis auto
+    hold on
+end

### 2015-06-28 Matlab_AXYB_Ver2/paperuseddata/main.m

@@ -1,0 +1,109 @@
+
+% clear all
+% close all
+% clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 1;
+trials = 1;
+Mean=[0;0;0;0;0;0;];
+% point = [50 1 50];
+% sum = zeros(1,4);
+point = [110 5 110];
+sum = zeros(1,4);
+sigArray = 1;
+shift = 2;
+for k = point(1):point(2):point(3)
+for i = 1:1:trials
+%     waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+%  [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray,0);
+% [A,B,X,Y] =  ABGen(k,0);
+Cov=sigArray*eye(6,6);
+[A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+ length = size(A,3);
+
+As = A(:,:,1:(length - shift));
+Bs = B(:,:,(shift + 1):length);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+% B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(As, Bs);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+
+sum(counter,1) = sum(counter,1) + roterror(X,XActual);
+sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
+sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
+sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
+end
+
+num(counter) = k;
+counter = counter + 1;
+
+%% plot 
+for j = 1:1:k
+    figure(11);
+    trplot(A(:,:,j),'color','r');
+    axis auto
+    hold on
+    figure(12);
+    trplot(B(:,:,j),'color','b');
[…]

### 2015-06-28 Matlab_AXYB_Ver2/paperuseddata/noise001/main_ABCov.m

@@ -1,0 +1,76 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 0;
+trials = 6;
+sigArray = [0.05 0.1 0.2 0.4 0.6 0.8 1];
+
+h = waitbar(0);
+for n = 1:1:size(sigArray,2)
+for m = 1:1:trials
+
+point = [50 10 50];
+for k = point(1):point(2):point(3)
+
+waitbar((m + (n-1)*trials)/(trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(m + (n-1)*trials),trials*size(sigArray,2)))
+% waitbar((k-point(1))/(point(3)-point(1)));
+
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k,sigArray(n),1);
+% [A,B,XActual,YActual] =  ABGen(k,0);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+counter = counter + 1;
+num(counter) = k;
+Err(counter,1) = roterror(X,XActual);
+Err(counter,2) = roterror(Y,YActual);
+Err(counter,3) = tranerror(X,XActual);
+Err(counter,4) = tranerror(Y,YActual);
+
+end
+
+rotErrX(m,n) = Err(counter,1);
+rotErrY(m,n) = Err(counter,2);
+tranErrX(m,n) = Err(counter,3);
+tranErrY(m,n) = Err(counter,4);
+end
+end
+
+% figure(5)
+% trplot(XActual(:,:),'color','r');
+% % legend('solved and actual X');
+% figure(6)
+% trplot(YActual(:,:),'color','r');
+% % legend('solved and actual Y');
+% figure
[…]

### 2015-06-28 Matlab_AXYB_Ver2/paperuseddata/version 2/main.m

@@ -1,0 +1,106 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 1;
+trials = 1;
+
+% point = [50 1 50];
+% sum = zeros(1,4);
+point = [100 5 100];
+sum = zeros(1,4);
+
+shift = 10;
+for k = point(1):point(2):point(3)
+for i = 1:1:trials
+%     waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A,B,XActual,YActual] =  ABGenerate(k, 0.2,0);
+% [A,B,X,Y] =  ABGen(k,0);
+ length = size(A,3);
+
+As = A(:,:,1:(length - shift));
+Bs = B(:,:,(shift + 1):length);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.01;  %Gaussian Noise standard deviation Range
+
+% B = sensorNoise(B, gmean, nstd, 1);
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(As, Bs);
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+Y(4,1:3) = [0 0 0];
+%% err analysis
+
+sum(counter,1) = sum(counter,1) + roterror(X,XActual);
+sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
+sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
+sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
+end
+
+num(counter) = k;
+counter = counter + 1;
+
+%% plot 
+% for j = 1:1:k
+%     figure(4);
+%     trplot(A(:,:,j),'color','r');
+%     axis auto
+%     hold on
+%     figure(5);
+%     trplot(B(:,:,j),'color','b');
+%     axis auto
+%     hold on
+% end
+% figure(3);
+% legend('Generated A');
+% figure(4);
+% legend('Generated B');
+
[…]

### 2015-07-03 Tex_AXYB/paper.tex
Paper revised except for last for paragraphs & Screw parameter related references will be added & Complete revision will be done by the end of this week

@@
 
-In image-guided system, relationships of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and simultaneous solution is useful in sensor calibration problem.
-Due to asynchrony of sensors timing, the correspondence between $A$ and $B$ is unknown.
+In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem.
+Due to the asynchrony of sensors' timing, the exact correspondence between $A$ and $B$ is unknown, and a common scenario is when there is a constant shift between the two data streams.
 A probabilistic method is presented to solve the
 homogeneous matrix equations without a priori knowledge of the correspondence.
-Using Euclidean-Group invariants, an exact solution can be found.
-We illustrate the calculation in numeric simulation including various numbers of
-robot movements. The results show the efficiency and robustness of the proposed simultaneous
-method.
+Using the Euclidean-Group invariants, an exact solution can be found.
+For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
 
@@
 For a typical ``hand-eye'' system as described above, the relative transformation of the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well known $\textbf{AX=XB}$ problem.
-A variation of this problem is characterized as the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
-In a typical environment setup, the relationship among the sensor frame, robot frame and world frame is variant and the uncertainties exist.
+A variation of this problem is the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
+In a typical environment setup, the relationships among the sensor frame, robot frame and world frame are variant and the uncertainties exist.
 Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to dynamic environments.
@@
 The asynchrony causes a shift between the two streams of data which damages the correspondence between $As$ and $Bs$.
-In this paper, a novel method is presented to solve for an $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $As$ and $Bs$.
+In this paper, a novel method is presented to solve for $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $As$ and $Bs$.
 
@@
 \caption{
-(1) The hand-eye and robot-world calibration problem which is formulated as AX=YB (The universal robot as shown in the picture is owned by professor Emad Boctor in).
+(1) The hand-eye and robot-world calibration problem which is formulated as AX=YB (The universal robot as shown in the picture is owned by professor Emad Boctor in the Johns Hopkins University).
 (2) The hand-eye calibration problem which is formulated as AX=XB.
@@
 \end{center}
-The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing  the relative motions of end-effector and the  sensor respectively.
+The hand-eye calibration problem can be modeled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing  the relative motions of the end-effector and the  sensor respectively.
 As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and  $B = B^{i}(B^{i+1})^{-1}$.
-Given multiple pairs of $\{A,B \}$ with correspondence, many methods have been proposed to solve for $X$.
+Given multiple pairs of $(A_i,B_i)$ with correspondence, many methods have been proposed to solve for $X$.
 To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem.
-The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
+The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
 All of the methods above assume a prior knowledge of exact correspondence between $A_i$ and $B_i$.
-For data streams $\{A_i\}$ and $\{B_i\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence.
-Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
+For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence.
+Theses methods assume that there is exact knowledge of the correspondence between $\{A\}$ and $\{B\}$ \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
 
@@
 The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations.
-This problem has been solved by many different methods such as kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
-Simulatneous calibration of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world.
+This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
+Simulatneous calibrations of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world.
 Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014}.
-Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue.
+Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is a challenging issue.
 In the above methods, the correspondence between $A$ and $B$ is known a prior.
-In this paper, we focus on the $\textbf{AX=YB}$ problem which does not require a priori knowledge of the correspondence of the data streams.
+In this paper, we focus on a case of $\textbf{AX=YB}$ problem where there is  no a priori knowledge of the correspondence between the data streams.
 
@@
              \end{array}
-           \right) \in SE(3)
+           \right) \in SE(3), \; \; R \in SO(3)
 \end{equation}
@@
 \end{equation}
-For a matrix $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere:
+For a group element $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere:
 
@@
 \begin{IEEEeqnarray}{l}\label{equ8}
-f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}H) \IEEEyessubnumber
+f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
 \\*
-f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}H) \IEEEyessubnumber
+f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
 \end{IEEEeqnarray}
-Using the distributivity of convolution, Eq.(\ref{equ8}) can be substituted into Eq.(\ref{equ7}) to get:
+Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in can give:
 \begin{equation}\label{equ9}
@@
 
-For each of the data stream $\{A_i\}$ and $\{B_i\}$, small relative motions are calculated between consecutive reference frames.
+For each of the data stream $\{A_i\}$ and $\{B_i\}$, small relative motions are calculated using consecutive transformations.
 Take $\{A_i\}$ for example, one metric of the distance between $A_i$ and $A_{i+1}$ can be defined as:
@@
 \\*
-\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1)}H)]^{T}f(H)dH. \IEEEyessubnumber
+\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH. \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 \\*
-\Sigma = \sum_{i=1}^{n}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1)}H)]^{T}. \IEEEyessubnumber
+\Sigma = \sum_{i=1}^{n}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}. \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 \end{IEEEeqnarray}
-Because Eq.(\ref{equ17a}) is a similarity transformation between $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$, they share the same eigenvalues and can be eigendecomposed into   $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\Lambda Q_{M_{A}}^{T}$ and $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\Lambda Q_{M_{B}}^{T}$ where $\Lambda$ is a diagonal matrix whose diagonal elements are the eigenvalues of $\Sigma_{M_{A}}^{1}$ ($\Sigma_{M_{B}}^{1}$), and $Q_{M_{A}}$ ($Q_{M_{B}}$) is a square matrix whose columns are the corresponding eigenvectors.
-Following equation is obtained after substitution into Eq.(\ref{equ17a}):
+Because Eq.(\ref{equ17a}) is a similarity transformation between $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$, they share the same eigenvalues and can be eigendecomposed into   $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\Lambda Q_{M_{A}}^{T}$ and $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\Lambda Q_{M_{B}}^{T}$ where $\Lambda$ is a diagonal matrix whose diagonal elements are the eigenvalues of $\Sigma_{M_{A}}^{1}$ (or $\Sigma_{M_{B}}^{1}$), and $Q_{M_{A}}$ (or $Q_{M_{B}}$) is a square matrix whose columns are the corresponding eigenvectors.
+The following equation is obtained after substituting $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$ into Eq.(\ref{equ17a}):
 
@@
 
-Therefore, there are eight candidates of $R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$.
-Then the corresponding $t_{X}$ can be obtained  from Eq.(\ref{equ17b}).
+Therefore, there are eight candidates of $R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained  from Eq.(\ref{equ17b}).
 Given known $X$, $Y$ can be solved for by $Y = M_A^{-1}XM_B^{-1}$.
@@
 Moreover, $AX_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$.
-If define $B^k = X_k^{-1}Y_kB$, then we will have $AX_k=X_kB^k$.
+Define $B^k = X_k^{-1}Y_kB$, and we will have $AX_k=X_kB^k$.
 There exist two Euclidean-Group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
@@
 \end{equation}
-
+The correspondences between $\{A_i\}$ and $\{B_j\}$ need to be recovered to pick the optimal $X$ and $Y$.
 \section{Solution with unknown correspondence between $A_{i}$ and $B_{i}^{k}$}
@@
 Due to the asynchronous timing of the sensor readings, the correspondences between $\{A_{i}\}$ and $\{B_{j}^{k}\}$ is usually unknown.
-This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and Euclidean-Group invariants are used to recover the correspondence between the data streams.
-{\color{red}The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is not a priori knowledge of the correspondence.} However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-Group invariants, it is straightforward to determine which pair is the optimal one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.
+This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-Group invariants are used to recover the correspondence between the data streams.
+The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is not a priori knowledge of the correspondence.
+However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-Group invariants, it is straightforward to determine which pair is the optimal one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.
 
@@
 
-\begin{equation}\label{equ21}
+\begin{equation}\label{equ24}
     X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa).
 \end{equation}
+where $i$ here is the imaginary unit.
+
 The Inverse Discrete Fourier transform (IDFT) is denoted as:
 
-\begin{equation}\label{equ22}
+\begin{equation}\label{equ25}
     x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa).
@@
 
-\begin{equation}\label{equ23}
+\begin{equation}\label{equ26}
     (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
@@
 
-\begin{equation}\label{equ24}
+\begin{equation}\label{equ27}
     f \ast g = \mathcal{F}^{-1} [\mathcal{F}(f) \cdot \mathcal{F}(g)].
@@
 
-The correlation theorem indicates that the correlation function, $Corr(f,g)$, will possess a larger value for a shift vector where the two sequences $f_n$ and $g_n$ can share more similar features.
+The correlation theorem indicates that the correlation function, $Corr(f,g)$, will be larger for a shift vector where the two sequences $f_n$ and $g_n$ can share more similar features.
 The correlation can be obtained based on the convolution theorem.
@@
 
-\begin{equation}\label{equ25}
+\begin{equation}\label{equ28}
     Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}].
@@
 
-\begin{equation}\label{equ26}
+\begin{equation}\label{equ29}
     \theta_{1}=\frac{(\theta_{A_{i}}-\mu_{A_{i}})}{\sigma_{A_{i}}}, \theta_{2}=\frac{(\theta_{B_{i}^{k}}-\mu_{B_{i}^{k}})}{\sigma_{B_{i}^{k}}}
@@
 
-Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $(n)$ which describes the probability that these two sequences are separated by this particular unit.
-The index corresponding to the maximum of $Corr(\theta_{1},\theta_{2})$  indicates the amount of shift $\tau_{shift}$ between the $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$.
+Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $n$ which describes the probability of these two sequences being separated by this particular unit.
+The index corresponding to the maximum of $Corr(\theta_{1},\theta_{2})$  indicates the amount of shift $\tau_{shift}$ between $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$.
 
-\begin{equation}\label{equ27}
+\begin{equation}\label{equ30}
     \tau_{shift} = \mathop{\mathbf{arg}max}_{index}(Corr(\theta_{1},\theta_{2}))
@@
 {\color{red}The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$ TO BE REPHRASED}.
-The data stream can be shifted back to regain correspondence once the shift is computed and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using Euclidean-Group invariants as shown in Section \ref{sect2}.
+The data stream can be shifted back to regain correspondence once the shift is computed, and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using the Euclidean-Group invariants as shown in Section \ref{sect2}.
 
@@
 \centering
-\includegraphics[width=3.2in]{fig2.eps}
+\includegraphics[width=3.2in]{fig3.eps}
 \caption{
-The errors of translation and rotations versus the data stream shift between $A$ and $B$,
+The errors of translation and rotations versus the shift between data streams $A$ and $B$
 }
@@
 \centering
-\includegraphics[width=3.2in]{fig3.eps}
+\includegraphics[width=3.2in]{fig2.eps}
 \caption{
@@
 
-In the numerical experiments in this section, the rotational and translational error for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively.
+For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively.
 
@@
 \caption{
-The solved $X$ (in red) and the actual $X$ (in blue) in 5 trial simulation with noise covariance 0.01 and shift 2.
+The solved $X$ (in blue) and the actual $X$ (in red) in 5 trial simulation with noise covariance 0.01 and shift 2.
 }
@@
 \caption{
-The solved $Y$ (in red) and the actual $Y$ (in blue) in 5 trial simulation with noise covariance 0.01 and shift 2.
+The solved $Y$ (in blue) and the actual $Y$ (in red) in 5 trial simulation with noise covariance 0.01 and shift 2.
 }
@@
 
-$B_{i}$ are generated randomly closely around $\mu$.
-We get a group of samples $B_i$ from Gaussian distribution over Lie group with a mean $\mu=0 \in G$ and a covariance matrix $\Sigma \in \mathbb{R}^{k \times k}$ as follows.
+There are multiple ways of generating the data streams $\{A_i\}$ and $\{B_{i}\}$.
+One way is to first generate $\{B_i\}$ and then map it to $\{A_i\}$ using $A = YBX^{-1}$.
+$\{B_i\}$ can be obtained by randomly sampling on the Lie algebra of $B$ from a zero mean multivariate Gaussian distribution, where the mean $\mu = {\bf 0} \in se(3)$ and covariance matrix $\Sigma \in \mathbb{R}^{6 \times 6}$ are as follows:
 
 \begin{IEEEeqnarray}{l}
-\delta \in \mathcal{N}(0;\Sigma) \IEEEyessubnumber\label{equ28a}
+\delta_i \in \mathcal{N}({\bf 0};\Sigma) \subset \mathbb{R}^{6} \IEEEyessubnumber\label{equ28a}
 \\*
-x = exp(\delta)\cdot \mu \IEEEyessubnumber\label{equ28b}
+B_i = \text{exp}(\hat{\delta_i}) \text{exp}(\mu) \IEEEyessubnumber\label{equ28b}
 \end{IEEEeqnarray}
 
-$i$ pose measurements were employed for generating $i$ $A_{i}$ by $A_{i} = YB_{i}X^{-1}$.
-As a result by applying the above probabilistic method, 8 sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=5,\cdots, 100, k=1,\dots,8)$ can be obtained respectively.
+The data stream $\{A_i\}$ can be easily obtained as described above.
+After employing the proposed probabilistic method, 8 sets of sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ where $ i = 1,\cdots, 100$ and $k = 1,\dots,8$ can be obtained respectively.
 
-If the data streams of $As$ were shifted by $m$ units compared to the data stream $Bs$.
-The maximum of cross correlation can be used to find the corresponding shift, which is $-m$, representing the data stream of $B_{i}^{k}$ has been shifted by -m units with respect to ${A_{i}}$.
-Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group invariants.
+If the data streams $\{A_i\}$ were shifted by $m$ units compared to the data stream $\{B_i\}$, then the maximum of cross correlation can be used to recover the shift.
+Once done, we shift the data stream $\{A_i\}$ back to recover the correspondence, which can help find a correct solution satisfying the Euclidean-Group invariants using Eq.(\ref{equ24}).
+Therefore, only one pair of $(X_k, Y_k)$ can be picked to minimize the cost function.
+In Fig.~\ref{fig2}, as the shift between $\{A_i\}$ and $\{B_i\}$ increases, the errors of translations and rotations increment in general.
 
-Using the minimum sum of $||\theta_{A_{i}} - \theta_{B_{i}^{k}}||$ and $||d_{A_{i}} - d_{B_{i}^{k}}||$, we can find a ${B_{i}^{k}}$ corresponding to the least sum of errors and then, only a $(X_k,Y_k)$ is the desired solution.
-In Fig.~\ref{fig2}, as the data stream between $A$ and $B$ shifts increase, the errors of translation and rotations are increased in general.
-
-Small disturbances are exerted to the $B_i$ to make the noisy $B_i^{noise} = B_i exp(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}){noise}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$.
+To test the robustness of the proposed method, noises are exerted to $\{B_i\}$ by $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}){noise}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$.
 In Fig.~\ref{fig3}, As $\sigma_{noise}$ varies from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are increased as shown in the box-and-whisker plot.

### 2015-07-07 Tex_AXYB/paper.tex
All the paper has been revised excpet for some minor changes to be done

@@
 \caption{
-The errors of translation and rotations versus noise covariance exerted to the data $B$".
+The errors of translation and rotations versus noise covariance exerted to the data $B$.
 }
@@
 
-For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel (t_{X_{Solved}}-t_{X_{true}})\parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel (t_{Y_{Solved}}-t_{Y_{true}})\parallel$ respectively.
+For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel t_{X_{Solved}}-t_{X_{true}} \parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel t_{Y_{Solved}}-t_{Y_{true}} \parallel$ respectively.
 
@@
 \caption{
-The solved $X$ (in blue) and the actual $X$ (in red) in 5 trial simulation with noise covariance 0.01 and shift 2.
+The solved $X$ (in blue) and the actual $X$ (in red) for 5 trials of simulation with noise covariance 0.01 and shift 2.
 }
@@
 \caption{
-The solved $Y$ (in blue) and the actual $Y$ (in red) in 5 trial simulation with noise covariance 0.01 and shift 2.
+The solved $Y$ (in blue) and the actual $Y$ (in red) for 5 trials of simulation with noise covariance 0.01 and shift 2.
 }
@@
 
-To test the robustness of the proposed method, noises are exerted to $\{B_i\}$ by $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}){noise}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$.
-In Fig.~\ref{fig3}, As $\sigma_{noise}$ varies from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are increased as shown in the box-and-whisker plot.
-There are several outliers not included between the whiskers.
-The median data can be used as the final solved $X$ and $Y$.
-Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$) in blue and actual ($X$,$Y$) in red in coordinate frame.
+To test the robustness of the proposed method, noises are exerted to $\{B_i\}$ by the data stream $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each element of the Lie Algebra $\mathbf{x}_{noise}$ is a Gaussian distribution as $N \sim (\mu_{noise},\sigma_{noise})$.
+In Fig.~\ref{fig3}, as $\sigma_{noise}$ increments from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ increase as shown in the box-and-whisker plot.
+There are several outliers outside the whiskers.
+The median value can be used as the final solved $X$ and $Y$.
+Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$)s in blue and the actual ($X$,$Y$) in red in the coordinate frame.
 
@@
 In this paper, we developed a probabilistic approach to simultaneously obtain  $X$ and $Y$ in $AX=YB$ sensor calibration problem.
-Without a prior knowledge of the correspondence between $A$ and $B$, in the algorithm the probability theory in Lie group is used to constrain the solution of $X$ and $Y$ to eight candidates.
-As for the shifted data stream of $A$ and $B$, using the correlation theorem with Euclidean group invariants,the correspondence is recovered to determine the correct solution from eight candidates.
-In numeric simulation, the method perform well with different data samples.
+Without a prior knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie group is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates.
+Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean group invariants,the correspondence is recovered to determine the correct solution among the eight candidates.
+In the numerical simulation, the method performs well with different sets of data samples.
 %\section{Conclusion}

### 2015-08-18 Tex_AXYB/paper.tex
The final version

@@
 
-\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory Chirikjian$^{2}*$% <-this % stops a space
+\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory Chirikjian$^{2}$% <-this % stops a space
 \thanks{*This work is partially
@@
         ,Beijing 100191, China
-        {\tt\small lihaiyuan@buaa.edu.cn}}%
+        {\tt\small haiyuanli@hotmail.com}, {\tt\small itm@buaa.edu.cn}}%
 \thanks{$^{2}$Qianli Ma and Gregory Chirikjian with the Department of Mechanical Engineering, Johns Hopkins University,
         Baltimore, MD 21218, USA
-        {\tt\small gregc@jhu.edu}}%
+        {\tt\small mqianli1@jhu.edu}, {\tt\small gregc@jhu.edu}}%
 }
@@
 
-Image-guided system has been widely used in robotics such as robot assisted surgery, (more examples).
+Image-guided system has been widely used in robotics such as robot assisted surgery, automatic guided vehicle, etc.
 Sensors such as a camera, a laser scanner or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
@@
 
-For each of the data stream $\{A_i\}$ and $\{B_i\}$, small relative motions are calculated using consecutive transformations.
-Take $\{A_i\}$ for example, one metric of the distance between $A_i$ and $A_{i+1}$ can be defined as:
+% small relative motions are calculated using consecutive transformations. Take $\{A_i\}$ for example, one metric % of the distance between $A_i$ and $A_{i+1}$ can be defined as:
 
-\begin{eqnarray}\label{equ10}
-d^{2}(A_{i},A_{i+1})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
-\end{eqnarray}
-where $\Delta A = A_{i}-A_{i+1}$ and $0 < \epsilon \ll 1 $.
+% \begin{eqnarray}\label{equ10}
+% d^{2}(A_{i},A_{i+1})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta % A)^{T}] = \epsilon,\nonumber \\
+% \end{eqnarray}
+% where $\Delta A = A_{i}-A_{i+1}$ and $0 < \epsilon \ll 1 $.
 
-The convolution of two ``highly focused" probability density functions (PDF) have some interesting properties that can be used to solve for $X$.
+Each of the data stream $\{A_i\}$ and $\{B_i\}$ is generated using Gaussian distribution over $SE(3)$.
+The convolution of two "highly focused" probability density functions (PDF) have some interesting properties that can be used to solve for $X$.
 In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:
@@
 \end{equation}
-where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.(\ref{equ18}) can be:
+where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$.
+If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.(\ref{equ18}) can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
 
@@
 The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
-Based on the screw theory (references?), it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ as:
+Based on the screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
 
@@
 \end{equation}
-where $\theta$, $d$, $\mathbf{n}$ and $\mathbf{p}$ are ?.
+where $\theta$ is the angle of rotation, $d$ is the translation along the rotation axis, $\mathbf{n}$ is the unit vector representing the axis of rotation and $\mathbf{p}$ is the position of the line to the origin with $\mathbf{p} \cdot \mathbf{n} = 0$.
 
-Moreover, $AX_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$.
+Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$.
 Define $B^k = X_k^{-1}Y_kB$, and we will have $AX_k=X_kB^k$.
@@
 
-Among the four pairs $(X_{k},Y_{k})$, one can find an optimal solution which  minimizes the cost function defined as:
+Among the eight pairs $(X_{k},Y_{k})$, one can find an optimal solution which  minimizes the cost function defined as:
 
@@
 In most cases, the homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors.
-Due to the asynchronous timing of the sensor readings, the correspondences between $\{A_{i}\}$ and $\{B_{j}^{k}\}$ is usually unknown.
+Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}^{k}\}$ is usually unknown.
 This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-Group invariants are used to recover the correspondence between the data streams.
@@
 Therefore, the correspondence between the two sequences can be found.
-{\color{red}The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$ TO BE REPHRASED}.
-The data stream can be shifted back to regain correspondence once the shift is computed, and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using the Euclidean-Group invariants as shown in Section \ref{sect2}.
+The data of ${\theta_{A_{i}}}$ or ${d_{A_{i}}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $({\theta_{A_{i}}(i+\tau_{shift})},{\theta_{B_{i}^{k}}})$ and $({d_{A_{i}}(i+\tau_{shift})},{d_{B_{i}^{k}}})$, $max(0,\tau_{shift})\leq i \leq min(n,n+\tau_{shift})$.
+The data stream can be shifted back to regain correspondence to synchronize the data streams once the shift is computed, and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using the Euclidean-Group invariants as shown in Section \ref{sect2}.
 
@@
 \centering
-\includegraphics[width=3.2in]{fig3.eps}
+\includegraphics[width=3in]{fig2.eps}
 \caption{
@@
 \centering
-\includegraphics[width=3.2in]{fig2.eps}
+\includegraphics[width=3.2in]{fig3.eps}
 \caption{
-The errors of translation and rotations versus noise covariance exerted to the data $B$.
+Box-and-Whisker plots  of translation and rotation erros versus noise covariance exerted to the data $B$.\vspace{6pt}
 }
@@
 \centering
-\includegraphics[width=3.2in]{fig4.eps}
+\includegraphics[width=3in]{fig4.eps}
 \caption{
-The solved $X$ (in blue) and the actual $X$ (in red) for 5 trials of simulation with noise covariance 0.01 and shift 2.
+(a) The solved $X$ (in red) and the actual $X$ (in black) for 10 trials of simulation with noise covariance 0.05 and shift 2.(b) The solved $Y$ (in blue) and the actual $Y$ (in black) for 10 trials of simulation with noise covariance 0.05 and shift 2.
 }
 \label{fig4}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}
-\centering
-\includegraphics[width=3.2in]{fig5.eps}
-\caption{
-The solved $Y$ (in blue) and the actual $Y$ (in red) for 5 trials of simulation with noise covariance 0.01 and shift 2.
-}
-\label{fig5}
 \end{figure}
@@
 If the data streams $\{A_i\}$ were shifted by $m$ units compared to the data stream $\{B_i\}$, then the maximum of cross correlation can be used to recover the shift.
-Once done, we shift the data stream $\{A_i\}$ back to recover the correspondence, which can help find a correct solution satisfying the Euclidean-Group invariants using Eq.(\ref{equ24}).
+Once done, we shift the data stream $\{A_i\}$ back to recover the correspondence, which can help find a correct solution satisfying the Euclidean-Group invariants using Eq.(\ref{equ22}).
 Therefore, only one pair of $(X_k, Y_k)$ can be picked to minimize the cost function.
-In Fig.~\ref{fig2}, as the shift between $\{A_i\}$ and $\{B_i\}$ increases, the errors of translations and rotations increment in general.
+In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ were calculated accurately, the errors of translations and rotations increase remain similar as that of non-shift data streams.
 
@@
 The median value can be used as the final solved $X$ and $Y$.
-Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$)s in blue and the actual ($X$,$Y$) in red in the coordinate frame.
+Fig.~\ref{fig4} show the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black in the coordinate frame when the noise covariance is 0.05 and shift is 2.
+
+\begin{center}
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig5.eps}
+\caption{
+Error of orientation and position of $X$ and $Y$ versus shift amount when using Li and Shah method without regaining the correspondence.
+}
+\label{fig5}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig6.eps}
+\caption{
+Error of orientation and position of $X$ and $Y$ versus shift amount when using Li and Shah method after regaining correspondence.
+}
+\label{fig6}
+\end{figure}
+\end{center}
+The probabilistic method in this paper can regain the correspondence of the shifted data streams, which is useful for other sensor calibration methods.
+In $AX=YB$ problem, there have been many calibration methods that have been developed for solving $AX=YB$ problem.
+However, few of them considered the cases without correspondence.
+When data streams of ${A}$ and ${B}$ are shifted or asynchronous, the solution is unavailable.
+We shift the data sequence of ${A}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of ${B}$.
+We combine the probabilistic method with other methods.
+In Li's method \cite{Li2010}, $X$ and $Y$ are solved for at the same time while Shah \cite{Shah2013} uses separable solutions to solve for $X$ and $Y$.
+In Fig.~\ref{fig5}, the correspondence between data streams are still unknown and the errors are obvious.
+After the data streams are synchronized using the probabilistic method in Fig.~\ref{fig6}, Li and Shah's methods work as well as that in non-shift situation.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{APPENDIX}
 

### 2015-08-19 Tex_AXYB/paper.tex
Revising the final manuscript

@@
 supported by NSF Grant RI-Medium: \#IIS-1162095}% <-this % stops a space
-\thanks{$^{1}$Haiyuan Li and Tianmiao Wang is with the School of Mechanical Engineering and Automation, Beihang University,
+\thanks{$^{1}$Haiyuan Li and Tianmiao Wang are with the School of Mechanical Engineering and Automation, Beihang University,
         ,Beijing 100191, China
@@
 
-Image-guided system has been widely used in robotics such as robot assisted surgery, automatic guided vehicle, etc.
+Image-guided systems have been widely used in robotics such as robot assisted surgery, automatic guided vehicle, etc.
 Sensors such as a camera, a laser scanner or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
@@
 
-In the $\textbf{AX=YB}$ problem, $As$ and $Bs$ can be respectively obtained via different sensors.
+In the $\textbf{AX=YB}$ problem, data streams $As$ and $Bs$ can be respectively obtained via different sensors.
 The data streams can be in an asynchronous fashion due to the different working frequencies of the sensors.
@@
 \caption{
-(1) The hand-eye and robot-world calibration problem which is formulated as AX=YB (The universal robot as shown in the picture is owned by professor Emad Boctor in the Johns Hopkins University).
-(2) The hand-eye calibration problem which is formulated as AX=XB.
+(1) The Hhand-eye and Robot-world Calibration Problem Which is Formulated as AX=YB (The Universal Robot as Shown in the Picture is Owned by Professor Emad Boctor in the Johns Hopkins University).
+(2) The Hand-eye Calibration Problem which is Formulated as AX=XB.
 }
@@
 The hand-eye calibration problem can be modeled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing  the relative motions of the end-effector and the  sensor respectively.
-As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and  $B = B^{i}(B^{i+1})^{-1}$.
-Given multiple pairs of $(A_i,B_i)$ with correspondence, many methods have been proposed to solve for $X$.
+As shown in Fig.~\ref{fig1} part (2), {\color{red}$A = A^{i}(A^{i+1})^{-1}$ and  $B = B^{i+1}(B^{i})^{-1}$}.
+Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ is the relative transformations obtained from the raw data ), many methods have been proposed to solve for $X$.
 To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem.
@@
 For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence.
-Theses methods assume that there is exact knowledge of the correspondence between $\{A\}$ and $\{B\}$ \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
+Theses methods assume that there is exact knowledge of the correspondence between $\{A_i\}$ and $\{B_i\}$ \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
 
 Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem.
-As shown in Fig.~\ref{fig1}, $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the the end-effector to its fixed base.
+As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base.
 The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations.
 This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
-Simulatneous calibrations of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world.
-Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014}.
-Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is a challenging issue.
+Simulatneous calibrations of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem can be a challenging issue.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here.
 In the above methods, the correspondence between $A$ and $B$ is known a prior.
-In this paper, we focus on a case of $\textbf{AX=YB}$ problem where there is  no a priori knowledge of the correspondence between the data streams.
+In this paper, we focus on one case of $\textbf{AX=YB}$ problem where there is  no a priori knowledge of the correspondence between the data streams.
 
-The rest of the paper is organized as follows. In Section
-\ref{sect2}, a novel probabilistic method is presented to solve for $X$ and $Y$.
-In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$.
-The simulation results which deal with noisy data without correspondence are illustrated in Section \ref{sect4}.
+The rest of the paper is organized as follows. {\color{red}In Section
+\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$.} In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, {\color{red} which is used to select the optimal solution among the candidates}.
+The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}.
 Finally, conclusions are drawn based on the numerical results and possible future works are pointed out.
@@
 \end{equation}
-where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is translational vector and $H$ is symbol for group element.
+where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for group element.
 
@@
 +\infty, & H=I \\
-0, & H \neq I
+0, & H \neq I.
 \end{array}
@@
 \end{equation}
-It also satisfies the identity constraint as:
+The Dirac delta function also satisfies the identity constraint as:
 
@@
 \end{equation}
+where $\circ$ denotes the group product, and in this case it is simply matrix multiplication.
 Employing the properties of $\delta$ function, it is straightforward to see that:
@@
 \end{IEEEeqnarray}
-Using Eq.($\ref{equ1}$), the above two equations can be combined into a single equation as:
+Using Eq.($\ref{equ1}$) and Eq.($\ref{equ2}$), the above two equations can be combined into a single equation as:
 
@@
 \end{IEEEeqnarray}
-Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in can give:
+Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in, and we will have:
 \begin{equation}\label{equ9}
@@
 
-Each of the data stream $\{A_i\}$ and $\{B_i\}$ is generated using Gaussian distribution over $SE(3)$.
-The convolution of two "highly focused" probability density functions (PDF) have some interesting properties that can be used to solve for $X$.
-In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:
+If each of the data stream $\{A_i\}$ and $\{B_i\}$ is generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly focused''.
+The convolution of two highly focused probability density functions (PDF) have some interesting properties that can be used to solve for $X$.
+For simplicity, we will drop the integral interval ``$SE(3)$'' for the rest of equations, and it should be self-clear given the integration variable that is used.
+In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ $f(H)$ as:
 
 \begin{IEEEeqnarray}{l}\label{equ11}
-\int_{SE(3)}log(M^{-1}H))f(H)dH=0 \IEEEyessubnumber
+\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
 \\*
-\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH. \IEEEyessubnumber
+\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH. \IEEEyessubnumber
 \end{IEEEeqnarray}
-Then the corresponding discrete version is:
+where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
+If $f_A(H)$ is given as in Eq.(\ref{equ8}), then its corresponding discrete version of mean $M_A$ and covariance $\Sigma_A$ will be:
 
 \begin{IEEEeqnarray}{l}\label{equ12}
-\sum_{i=1}^{n}log(M^{-1}H))=0 \IEEEyessubnumber
+\sum_{i=1}^{n}log(M_A^{-1}A_i)) = \mathbb{O} \IEEEyessubnumber
 \\*
-\Sigma = \sum_{i=1}^{n}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}. \IEEEyessubnumber
+\Sigma = \sum_{i=1}^{n}log^{\vee}(M_A^{-1}A_i)[log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
 \end{IEEEeqnarray}
 
-Given $\{A_i\}$ where the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:
+Given $\{A_i\}$ with the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:
 
@@
 
-An initial estimate of the iterative procedure can be chosen as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then a local minimum of $M_A$ is obtained by solving a nonlinear optimization problem with the cost function being $|| \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) ||^{2}$.
+An initial estimate of the iterative procedure can be chosen as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then a local minimum of $M_A$ is obtained by solving a nonlinear optimization problem with the cost function of $|| \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) ||^{2}$.
 A similar procedure can be used to compute $M_B$.
@@
 \end{equation}
-The correspondences between $\{A_i\}$ and $\{B_j\}$ need to be recovered to pick the optimal $X$ and $Y$.
+Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$. However,
+the correspondences needs to be recovered to pick the optimal $(X_k, Y_k)$.
 \section{Solution with unknown correspondence between $A_{i}$ and $B_{i}^{k}$}
@@
 
-In most cases, the homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors.
-Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}^{k}\}$ is usually unknown.
+In most cases, the two sets of homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors.
+Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$ is usually unknown.
 This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-Group invariants are used to recover the correspondence between the data streams.
@@
 Firstly, $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ are normalized as:
-
+{\color{red}
 \begin{equation}\label{equ29}
-    \theta_{1}=\frac{(\theta_{A_{i}}-\mu_{A_{i}})}{\sigma_{A_{i}}}, \theta_{2}=\frac{(\theta_{B_{i}^{k}}-\mu_{B_{i}^{k}})}{\sigma_{B_{i}^{k}}}
+    \theta_{1i}=\frac{(\theta_{A_{i}}-\mu_{A})}{\sigma_{A}}, \theta_{2i}=\frac{(\theta_{B_{i}^{k}}-\mu_{B^{k}})}{\sigma_{B^{k}}}
 \end{equation}
-where $\mu_{A_{i}}(\mu_{B_{i}^{k}})$ is the mean of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A_{i}}(\sigma_{B_{i}^{k}})$ is the standard deviation.
-
-Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $n$ which describes the probability of these two sequences being separated by this particular unit.
+where $\mu_{A}(\mu_{B^{k}})$ is the mean of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A}(\sigma_{B^{k}})$ is the standard deviation.
+}
+Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $n$ which describes the probability of these two sequences being separated by this particular index.
 The index corresponding to the maximum of $Corr(\theta_{1},\theta_{2})$  indicates the amount of shift $\tau_{shift}$ between $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$.
@@
 Therefore, the correspondence between the two sequences can be found.
-The data of ${\theta_{A_{i}}}$ or ${d_{A_{i}}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $({\theta_{A_{i}}(i+\tau_{shift})},{\theta_{B_{i}^{k}}})$ and $({d_{A_{i}}(i+\tau_{shift})},{d_{B_{i}^{k}}})$, $max(0,\tau_{shift})\leq i \leq min(n,n+\tau_{shift})$.
+The data of ${\theta_{A_{i}}}$ or ${d_{A_{i}}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $({\theta_{A_{i}}(i+\tau_{shift})},{\theta_{B_{i}^{k}}})$ and $({d_{A_{i}}(i+\tau_{shift})},{d_{B_{i}^{k}}})$, where $max(0,\tau_{shift})\leq i \leq min(n,n+\tau_{shift})$.
 The data stream can be shifted back to regain correspondence to synchronize the data streams once the shift is computed, and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using the Euclidean-Group invariants as shown in Section \ref{sect2}.
@@
 \caption{
-The errors of translation and rotations versus the shift between data streams $A$ and $B$
+The Errors of Translation and Rotation Versus the Shift between Data Streams $\{A_i\}$ and $\{B_i\}$.
 }
@@
 \caption{
-Box-and-Whisker plots  of translation and rotation erros versus noise covariance exerted to the data $B$.\vspace{6pt}
+Box-and-Whisker Plots of Translational and Rotational Errors Versus the Covariance of Noise on Data Stream $\{B_i\}$.\vspace{6pt}
 }
@@
 \caption{
-(a) The solved $X$ (in red) and the actual $X$ (in black) for 10 trials of simulation with noise covariance 0.05 and shift 2.(b) The solved $Y$ (in blue) and the actual $Y$ (in black) for 10 trials of simulation with noise covariance 0.05 and shift 2.
+(a) The Solved $X$ (in Red) and the Actual $X$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.(b) The Solved $Y$ (in Blue) and the Actual $Y$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.
 }
@@
 One way is to first generate $\{B_i\}$ and then map it to $\{A_i\}$ using $A = YBX^{-1}$.
-$\{B_i\}$ can be obtained by randomly sampling on the Lie algebra of $B$ from a zero mean multivariate Gaussian distribution, where the mean $\mu = {\bf 0} \in se(3)$ and covariance matrix $\Sigma \in \mathbb{R}^{6 \times 6}$ are as follows:
+$\{B_i\}$ can be obtained by randomly sampling on the Lie algebra of $B$ from a zero mean multivariate Gaussian distribution as follows:
 
@@
 \end{IEEEeqnarray}
+where the mean $\mu = {\bf 0} \in se(3)$ and the covariance matrix $\Sigma \in \mathbb{R}^{6 \times 6}$ {\color{red} is a diagonal matrix with same diagonal elements $\sigma$}.
+The hat operator $\hat{\delta}$ converts a 6 by 1 vector into its corresponding Lie algebra.
+The data stream $\{A_i\}$ can be easily obtained as described above.
+After employing the proposed probabilistic method, 8 sets of sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ can be obtained respectively where $ i = 1,\cdots, 100$ and $k = 1,\dots,8$.
 
-The data stream $\{A_i\}$ can be easily obtained as described above.
-After employing the proposed probabilistic method, 8 sets of sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ where $ i = 1,\cdots, 100$ and $k = 1,\dots,8$ can be obtained respectively.
+If the data stream $\{A_i\}$ is shifted by $m$ units relative to $\{B_i\}$, then the maximum of the cross correlation can be used to recover the shift.
+After that, we can shift the data stream $\{A_i\}$ back to its original position to recover the correct correspondence with $\{B_i\}$, which will be used to find a correct solution satisfying the Euclidean-Group invariants as defined in Eq.(\ref{equ22}).
+Therefore, a unique pair of $(X_k, Y_k)$ can be selected to minimize the cost function.
+In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ is calculated accurately, the errors of translations and rotations fluctuate by only a small amount compared to the errors of no-shift data streams.
 
-If the data streams $\{A_i\}$ were shifted by $m$ units compared to the data stream $\{B_i\}$, then the maximum of cross correlation can be used to recover the shift.
-Once done, we shift the data stream $\{A_i\}$ back to recover the correspondence, which can help find a correct solution satisfying the Euclidean-Group invariants using Eq.(\ref{equ22}).
-Therefore, only one pair of $(X_k, Y_k)$ can be picked to minimize the cost function.
-In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ were calculated accurately, the errors of translations and rotations increase remain similar as that of non-shift data streams.
-
-To test the robustness of the proposed method, noises are exerted to $\{B_i\}$ by the data stream $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each element of the Lie Algebra $\mathbf{x}_{noise}$ is a Gaussian distribution as $N \sim (\mu_{noise},\sigma_{noise})$.
-In Fig.~\ref{fig3}, as $\sigma_{noise}$ increments from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ increase as shown in the box-and-whisker plot.
-There are several outliers outside the whiskers.
-The median value can be used as the final solved $X$ and $Y$.
-Fig.~\ref{fig4} show the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black in the coordinate frame when the noise covariance is 0.05 and shift is 2.
+To test the robustness of the proposed method, noises are exerted onto $\{B_i\}$ by employing $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each element of the Lie Algebra $\mathbf{x}_{noise}$ belongs to the Gaussian distribution defined as $N \sim (\mu_{noise},\sigma_{noise})$.
+In Fig.~\ref{fig3}, as the covariance of the noise $\sigma_{noise}$ increments from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ increase as shown in the box-and-whisker plot.
+There are several outliers outside the whiskers, while the median is calculated as the final solved $X$ and $Y$.
+Fig.~\ref{fig4} shows the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black when the noise covariance $\sigma = 0.05$ and the shift $n = 2$.
 
@@
 \caption{
-Error of orientation and position of $X$ and $Y$ versus shift amount when using Li and Shah method without regaining the correspondence.
+ErrorS of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method without Correspondence.
 }
@@
 \caption{
-Error of orientation and position of $X$ and $Y$ versus shift amount when using Li and Shah method after regaining correspondence.
+Errors of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method with Correspondence.
 }
@@
 \end{center}
-The probabilistic method in this paper can regain the correspondence of the shifted data streams, which is useful for other sensor calibration methods.
-In $AX=YB$ problem, there have been many calibration methods that have been developed for solving $AX=YB$ problem.
+The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods.
+In $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence.
 However, few of them considered the cases without correspondence.
-When data streams of ${A}$ and ${B}$ are shifted or asynchronous, the solution is unavailable.
-We shift the data sequence of ${A}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of ${B}$.
-We combine the probabilistic method with other methods.
+When data streams of ${A}$ and ${B}$ are shifted or asynchronous, most of these methods fail to give a valid solution.
+To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$.
+We augment other $AX=YB$ solvers with our probabilistic approach.
 In Li's method \cite{Li2010}, $X$ and $Y$ are solved for at the same time while Shah \cite{Shah2013} uses separable solutions to solve for $X$ and $Y$.
-In Fig.~\ref{fig5}, the correspondence between data streams are still unknown and the errors are obvious.
-After the data streams are synchronized using the probabilistic method in Fig.~\ref{fig6}, Li and Shah's methods work as well as that in non-shift situation.
+In Fig.~\ref{fig5}, the correspondence between data streams is unknown and the errors on both rotations and translations are significant.
+After synchronizing the data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as in the no-shift situation as shown in Fig.~\ref{fig6}.
 
@@
 Without a prior knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie group is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates.
-Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean group invariants,the correspondence is recovered to determine the correct solution among the eight candidates.
+Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean group invariants, the correspondence is recovered to determine the correct solution among the eight candidates.
 In the numerical simulation, the method performs well with different sets of data samples.
+Future work will be to further develop the existing algorithm to solve for more general asynchronous cases, such as flipped data pairs or missing data in the data streams.
+
 %\section{Conclusion}
@@
 \section*{ACKNOWLEDGMENT}
+{Chirikjian's contribution to this material is based upon work supported by (while serving at) the National Science Foundation.
+Any opinion, findings, and conclusions or recommendations expressed in this material are those of the author(s)
+and do not necessarily reflect the views of the National Science Foundation.}
 

### 2015-08-20 Tex_AXYB/paper.tex
The final Manusript
Josh's Edits to paper

@@
 \title{\LARGE \bf
-Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*
+%Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*
+Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*
 }
 
-\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory Chirikjian$^{2}$% <-this % stops a space
-\thanks{*This work is partially
-supported by NSF Grant RI-Medium: \#IIS-1162095}% <-this % stops a space
-\thanks{$^{1}$Haiyuan Li and Tianmiao Wang are with the School of Mechanical Engineering and Automation, Beihang University,
-        ,Beijing 100191, China
+\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory S. Chirikjian$^{2}$% <-this % stops a space
+\thanks{*This work \textcolor{blue}{was} %is 
+partially
+supported by NSF Grant RI-Medium: \textcolor{blue}{1162095}}%\#IIS-1162095}% <-this % stops a space
+\thanks{$^{1}$Haiyuan Li and Tianmiao Wang are with the School of Mechanical Engineering and Automation, Beihang University, Beijing 100191, China
         {\tt\small haiyuanli@hotmail.com}, {\tt\small itm@buaa.edu.cn}}%
-\thanks{$^{2}$Qianli Ma and Gregory Chirikjian with the Department of Mechanical Engineering, Johns Hopkins University,
+\thanks{$^{2}$Qianli Ma and Gregory S. Chirikjian \textcolor{red}{are} with the Department of Mechanical Engineering, Johns Hopkins University,
         Baltimore, MD 21218, USA
@@
 
-In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem.
+%In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem.
 Due to the asynchrony of sensors' timing, the exact correspondence between $A$ and $B$ is unknown, and a common scenario is when there is a constant shift between the two data streams.
-A probabilistic method is presented to solve the
-homogeneous matrix equations without a priori knowledge of the correspondence.
+A probabilistic method is presented to solve the homogeneous matrix equations without a priori knowledge of the correspondence.
 Using the Euclidean-Group invariants, an exact solution can be found.
 For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
+\textcolor{blue}{Calibration is often an important and necessary step in the use of image-guided systems.
+In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control.
+As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony is sampling rates and processing time.
+One common scenario is a constant shift between the two data streams.
+Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$s and $B$s.
+We begin by discussing probability density functions on $SE(3)$ and then introduce Euclidean-group invariants to obtain an exact solution for $X$ and $Y$.
+Then, we present a method to simultaneously recover $X$ and $Y$ and the correspondence between the shifted data sets.
+Finally, we numerically simulated the proposed method with shifted, asynchronous data and noise added to the stream of $B$s to verify its efficiency and robustness.
+}
 
@@
 
-Image-guided systems have been widely used in robotics such as robot assisted surgery, automatic guided vehicle, etc.
-Sensors such as a camera, a laser scanner or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
-For a typical ``hand-eye'' system as described above, the relative transformation of the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well known $\textbf{AX=XB}$ problem.
+Image-guided systems have been widely %used
+\textcolor{blue}{employed in applications throughout} %in 
+robotics such as robot\textbf{\textcolor{blue}{-}}assisted surgery, %automatic
+\textcolor{blue}{autonomously} guided vehicle\textcolor{blue}{s}, etc.
+Sensors such as a camera, a laser scanner\textbf{\textcolor{blue}{,}} or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
+For a typical ``hand-eye'' system as described above, the relative transformation %of
+\textcolor{blue}{between} the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well\textbf{\textcolor{blue}{-}}known $\textbf{AX=XB}$ problem.
 A variation of this problem is the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
-In a typical environment setup, the relationships among the sensor frame, robot frame and world frame are variant and the uncertainties exist.
-Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robots to respond to dynamic environments.
+In a typical environment, % setup,
+the relationships %among
+\textcolor{blue}{between} the sensor frame, robot frame\textcolor{blue}{,} and world frame are variant and %the
+ uncertainties exist. Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robot%s
+  to respond to dynamic environments.
 
-In the $\textbf{AX=YB}$ problem, data streams $As$ and $Bs$ can be respectively obtained via different sensors.
-The data streams can be in an asynchronous fashion due to the different working frequencies of the sensors.
-The asynchrony causes a shift between the two streams of data which damages the correspondence between $As$ and $Bs$.
-In this paper, a novel method is presented to solve for $X$ and $Y$ without the need to know a priori knowledge of the correspondence between $As$ and $Bs$.
+In the $\textbf{AX=YB}$ problem, data streams \textcolor{blue}{of} $A$s and $B$s can be respectively obtained via different sensors. The data streams %can be in
+\textcolor{blue}{may arrive in} an asynchronous fashion due to the different working frequencies of the sensors. \textcolor{blue}{This} %The 
+asynchrony causes a shift between the two \textcolor{blue}{data} streams %of data
+which \textcolor{blue}{removes} %damages 
+the correspondence between \textcolor{blue}{the} $A$s and $B$s. In this paper, a novel method is presented to solve for $X$ and $Y$ without %the need to know 
+a priori knowledge of the correspondence between \textcolor{blue}{the} $A$s and $B$s.
 
-\begin{center}
-\begin{figure}[htbp]
+\begin{figure}[t!]
 \centering
@@
 \caption{
-(1) The Hhand-eye and Robot-world Calibration Problem Which is Formulated as AX=YB (The Universal Robot as Shown in the Picture is Owned by Professor Emad Boctor in the Johns Hopkins University).
-(2) The Hand-eye Calibration Problem which is Formulated as AX=XB.
+(1) The hand-eye and robot-world calibration problem %which is 
+formulated as AX=YB. (2) The hand-eye calibration problem %which is 
+formulated as AX=XB. (The Universal Robot \textcolor{blue}{pictured above} %as Shown in the Picture 
+is owned by Prof. Emad Boctor \textcolor{blue}{of} %in the 
+Johns Hopkins University). 
 }
@@
 \end{figure}
-\end{center}
-The hand-eye calibration problem can be modeled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing  the relative motions of the end-effector and the  sensor respectively.
-As shown in Fig.~\ref{fig1} part (2), {\color{red}$A = A^{i}(A^{i+1})^{-1}$ and  $B = B^{i+1}(B^{i})^{-1}$}.
-Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ is the relative transformations obtained from the raw data ), many methods have been proposed to solve for $X$.
+
+The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively.
+As shown in Fig.~\ref{fig1} part (2), {\color{red}$A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$}.
+Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ %is
+\textcolor{blue}{are} the relative transformations obtained from the raw data), many \textcolor{blue}{deterministic} methods have been proposed to solve for $X$.
 To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem.
 The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
-All of the methods above assume a prior knowledge of exact correspondence between $A_i$ and $B_i$.
-For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence.
-Theses methods assume that there is exact knowledge of the correspondence between $\{A_i\}$ and $\{B_i\}$ \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
+All of the methods above assume a prior\textcolor{blue}{i} knowledge of \textcolor{blue}{the} exact correspondence between $A_i$ and $B_i$.
+For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without \textcolor{blue}{a priori knowledge of the} correspondence.
+These %s
+  methods assume that there \textcolor{blue}{are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown}% is exact knowledge of the correspondence between $\{A_i\}$ and $\{B_i\}$
+   \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
 
@@
 This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
-Simulatneous calibrations of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem can be a challenging issue.
-Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here.
-In the above methods, the correspondence between $A$ and $B$ is known a prior.
-In this paper, we focus on one case of $\textbf{AX=YB}$ problem where there is  no a priori knowledge of the correspondence between the data streams.
+Simulatneous calibration %s
+of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why \textcolor{blue}{a} simultaneous solution for $X$ and $Y$ in \textcolor{blue}{the} $\textbf{AX=YB}$ problem can be a challenging issue.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot \textcolor{blue}{transformations}, %system,
+ and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here.
+In the above methods, the correspondence between $A$ and $B$ is known a prior\textcolor{blue}{i}.
+In this paper, we focus on one case of \textcolor{blue}{the} $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.
 
@@
 The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}.
-Finally, conclusions are drawn based on the numerical results and possible future works are pointed out.
+Finally, conclusions are drawn based on the numerical results and possible future work \textcolor{blue}{is} %s are
+pointed out.
 
@@
 \label{sect2}
-In this section, a brief introduction to the concepts of probability density function on the special Eucledian group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ are derived.
+In this section, a brief introduction to the concept %s
+ of probability density function\textcolor{blue}{s (PDFs)} on the special Euclidean group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ \textcolor{blue}{is} %are
+  derived.
 
-Any rigid transformation matrix can be viewed as a group element of $SE(3)$ :
+Any rigid \textcolor{blue}{body} transformation matrix can be viewed as a group element of $SE(3)$ :
 \begin{equation}\label{equ0}
@@
 \end{equation}
-where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for group element.
+where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for \textcolor{blue}{the} group element.
 
@@
 where $\circ$ denotes the group product, and in this case it is simply matrix multiplication.
-Employing the properties of $\delta$ function, it is straightforward to see that:
+Employing the properties of \textcolor{blue}{the} $\delta$ function, it is straightforward to see that:
 
@@
 \end{IEEEeqnarray}
-Using Eq.($\ref{equ1}$) and Eq.($\ref{equ2}$), the above two equations can be combined into a single equation as:
+Using Eq.\textcolor{blue}{~}($\ref{equ1}$) and Eq.\textcolor{blue}{~}($\ref{equ2}$), the above two equations can be combined into a single equation as:
 
@@
 
-Define the probability density function of $\{A_i\}$ and $\{B_i\}$ as:
+Defin\textcolor{blue}{ing} %e 
+the \textcolor{blue}{PDF} %probability density function 
+of $\{A_i\}$ and $\{B_i\}$ as:
 \begin{IEEEeqnarray}{l}\label{equ8}
@@
 \end{IEEEeqnarray}
-Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in, and we will have:
+\textcolor{blue}{then by using the distributivity of convolution, adding $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ8}), and substituting Eq.\textcolor{blue}{~}(\ref{equ7}) in, we have:}
+%Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in, and we will have:
 \begin{equation}\label{equ9}
-(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
+(f_{A_{i}}\ast \delta_{X})(\textcolor{blue}{H})=(\delta_{Y}\ast f_{B_{i}})(\textcolor{blue}{H})
+%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
 \end{equation}
@@
 
-If each of the data stream $\{A_i\}$ and $\{B_i\}$ is generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly focused''.
-The convolution of two highly focused probability density functions (PDF) have some interesting properties that can be used to solve for $X$.
-For simplicity, we will drop the integral interval ``$SE(3)$'' for the rest of equations, and it should be self-clear given the integration variable that is used.
-In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ $f(H)$ as:
+If each of the data stream\textcolor{blue}{s} $\{A_i\}$ and $\{B_i\}$ \textcolor{blue}{are} %is 
+generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly\textbf{\textcolor{blue}{-}}focused''.
+The convolution of two highly\textbf{\textcolor{blue}{-}}focused \textcolor{blue}{PDFs} %probability density functions (PDF)
+have some interesting properties that can be used to solve for $X$. 
+For simplicity, we will drop the integral interval ``$SE(3)$'' for the \textcolor{blue}{remainder of the paper}, 
+%rest of equations, 
+\textcolor{blue}{as} %and 
+it should be self-\textcolor{blue}{evident} %clear 
+given the integration \textcolor{blue}{measure} %variable 
+that is used. %In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ $f(H)$ as:
+\textcolor{blue}{In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:}
 
@@
 \\*
-\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH. \IEEEyessubnumber
+\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
 \end{IEEEeqnarray}
 where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
-If $f_A(H)$ is given as in Eq.(\ref{equ8}), then its corresponding discrete version of mean $M_A$ and covariance $\Sigma_A$ will be:
+If $f_A(H)$ is given as in Eq.\textcolor{blue}{~}(\ref{equ8}), then \textcolor{blue}{the} %its
+ corresponding discrete version of \textcolor{blue}{the} mean $M_A$ and covariance $\Sigma_A$ will be:
 
@@
 
-The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:
+The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly\textbf{\textcolor{blue}{-}}focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:
 
@@
 Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively.
-Therefore, the following equations can be obtained using Eq.(\ref{equ14}):
+Therefore, the following equations can be obtained using Eq.\textcolor{blue}{~}(\ref{equ14}):
 
@@
 
-To solve the above equations, Eq.(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as below:
+To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as \textcolor{blue}{follows:}%below:
 
@@
        \right)$,
-then the first two blocks of Eq.(\ref{equ15b}) can be written as follows:
+then the first two blocks of Eq.\textcolor{blue}{~}(\ref{equ15b}) can be written as follows:
 
@@
 \end{IEEEeqnarray}
-Because Eq.(\ref{equ17a}) is a similarity transformation between $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$, they share the same eigenvalues and can be eigendecomposed into   $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\Lambda Q_{M_{A}}^{T}$ and $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\Lambda Q_{M_{B}}^{T}$ where $\Lambda$ is a diagonal matrix whose diagonal elements are the eigenvalues of $\Sigma_{M_{A}}^{1}$ (or $\Sigma_{M_{B}}^{1}$), and $Q_{M_{A}}$ (or $Q_{M_{B}}$) is a square matrix whose columns are the corresponding eigenvectors.
-The following equation is obtained after substituting $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$ into Eq.(\ref{equ17a}):
+Because Eq.\textcolor{blue}{~}(\ref{equ17a}) is a similarity transformation between $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$, they share the same eigenvalues and can be eigendecomposed into   $\Sigma_{M_{A}}^{1}=Q_{M_{A}}\Lambda Q_{M_{A}}^{T}$ and $\Sigma_{M_{B}}^{1}=Q_{M_{B}}\Lambda Q_{M_{B}}^{T}$ where $\Lambda$ is a diagonal matrix whose diagonal elements are the eigenvalues of $\Sigma_{M_{A}}^{1}$ (or $\Sigma_{M_{B}}^{1}$), and $Q_{M_{A}}$ (or $Q_{M_{B}}$) is a square matrix whose columns are the corresponding eigenvectors.
+The following equation is obtained after substituting $\Sigma_{M_{B}}^{1}$ and $\Sigma_{M_{A}}^{1}$ into Eq.\textcolor{blue}{~}(\ref{equ17a}):
 
@@
 where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$.
-If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.(\ref{equ18}) can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
+If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.\textcolor{blue}{~}(\ref{equ18}) can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
 
@@
 
-Therefore, there are eight candidates of $R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained  from Eq.(\ref{equ17b}).
-Given known $X$, $Y$ can be solved for by $Y = M_A^{-1}XM_B^{-1}$.
+Therefore, there are eight candidates \textcolor{blue}{for} %of 
+$R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained from Eq.\textcolor{blue}{~}(\ref{equ17b}).
+Given known $X$, $Y$  can be solved \textcolor{blue}{from} %for by
+\textcolor{blue}{$Y = M_AXM_B^{-1}$.} %$Y = M_A^{-1}XM_B^{-1}$.
  At last, eight candidate pairs of  $\{X_{k},Y_{k}\}$ can be obtained as:
@@
 The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
-Based on the screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
+Based on %the
+ screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
 
@@
 
-Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$.
-Define $B^k = X_k^{-1}Y_kB$, and we will have $AX_k=X_kB^k$.
-There exist two Euclidean-Group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
+Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$. Defin\textcolor{blue}{ing} %e
+ $B^k = X_k^{-1}Y_kB$, %and 
+ we %will
+  have $AX_k=X_kB^k$. There exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
 
@@
 \end{equation}
-Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$. However,
-the correspondences needs to be recovered to pick the optimal $(X_k, Y_k)$.
-\section{Solution with unknown correspondence between $A_{i}$ and $B_{i}^{k}$}
+Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$ \textcolor{blue}{to be known}. However,
+the correspondences need %s
+ to be recovered to pick the optimal $(X_k, Y_k)$.
+\section{Solution with unknown correspondence between $A_{i}$ and $B_{j}^{k}$}
 \label{sect3}
@@
 Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$ is usually unknown.
-This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-Group invariants are used to recover the correspondence between the data streams.
-The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is not a priori knowledge of the correspondence.
-However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-Group invariants, it is straightforward to determine which pair is the optimal one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.
+This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-%G
+\textcolor{blue}{g}roup invariants are used to recover the correspondence between the data streams.
+The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is no %t
+a priori knowledge of the correspondence. However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-%G
+\textcolor{blue}{g}roup invariants, it is straightforward to determine which \textcolor{blue}{is the optimal pair} %pair is the optimal one 
+if the correspondence between $A_{i}$ and $B_{j}^{k}$ can be known.
 
@@
 
-The Inverse Discrete Fourier transform (IDFT) is denoted as:
+The Inverse Discrete Fourier Transform (IDFT) is denoted as:
 
@@
 
-The discrete convolution of two sequences $f_{n}$ and $g_{n}$  are defined
+The discrete convolution of two sequences $f_{n}$ and $g_{n}$ \textcolor{blue}{is} %are 
+defined \textcolor{blue}{as:}
 
 \begin{equation}\label{equ26}
-    (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
+	\textcolor{blue}{(f \ast g)(\tau)=\sum_{j=0}^{N}f(t_{j})g(t_{j}-\tau).}
+	% Since you are using i for imaginary numbers use j here instead
+    %(f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
 \end{equation}
@@
 
-The correlation theorem indicates that the correlation function, $Corr(f,g)$, will be larger for a shift vector where the two sequences $f_n$ and $g_n$ can share more similar features.
+The correlation theorem indicates that the correlation function, $Corr(f,g)$, will be larger for a shift vector where the two sequences $f_n$ and $g_n$ %can 
+share more similar features.
 The correlation can be obtained based on the convolution theorem.
@@
 \begin{equation}\label{equ28}
-    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}].
+    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot \textcolor{blue}{\mathcal{F^{*}}(g)].}%(\mathcal{F}(g))^{*}].
 \end{equation}
 
-Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the fast Fourier transform (FFT).
+Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the %f
+\textcolor{blue}{F}ast Fourier %t
+\textcolor{blue}{T}ransform (FFT).
 
@@
 The data of ${\theta_{A_{i}}}$ or ${d_{A_{i}}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $({\theta_{A_{i}}(i+\tau_{shift})},{\theta_{B_{i}^{k}}})$ and $({d_{A_{i}}(i+\tau_{shift})},{d_{B_{i}^{k}}})$, where $max(0,\tau_{shift})\leq i \leq min(n,n+\tau_{shift})$.
-The data stream can be shifted back to regain correspondence to synchronize the data streams once the shift is computed, and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using the Euclidean-Group invariants as shown in Section \ref{sect2}.
+The data stream can be shifted back to regain correspondence to synchronize the data streams once the shift is computed, and the \textcolor{blue}{optimal} %correct
+solution of $X$ and $Y$ can also be recovered by minimizing the cost function \textcolor{blue}{in} Eq.\textcolor{blue}{~}(\ref{equ23}) using the Euclidean-%G
+\textcolor{blue}{g}roup invariants as shown in Section \ref{sect2}.
 
@@
 
-\begin{center}
-\begin{figure}
+%\begin{center}
+\begin{figure}[t!]
 \centering
@@
 \caption{
-The Errors of Translation and Rotation Versus the Shift between Data Streams $\{A_i\}$ and $\{B_i\}$.
+%The Errors of Translation and Rotation Versus the Shift between Data Streams $\{A_i\}$ and $\{B_i\}$.
+\textcolor{blue}{The translational and rotational errors versus the shift between data streams $\{A_i\}$ and $\{B_i\}$.} 
 }
@@
 \end{figure}
-\end{center}
+%\end{center}
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
@@
 \caption{
-Box-and-Whisker Plots of Translational and Rotational Errors Versus the Covariance of Noise on Data Stream $\{B_i\}$.\vspace{6pt}
+Box-and-%W
+\textcolor{blue}{w}hisker %P
+\textcolor{blue}{p}lots of %T
+\textcolor{blue}{t}ranslational and %R
+\textcolor{blue}{r}otational %E
+\textcolor{blue}{e}rrors %V
+\textcolor{blue}{v}ersus the %C
+\textcolor{blue}{c}ovariance %of %N
+\textcolor{blue}{n}oise on %D
+\textcolor{blue}{d}ata %S
+\textcolor{blue}{s}tream $\{B_i\}$.\vspace{6pt}
 }
@@
 \caption{
-(a) The Solved $X$ (in Red) and the Actual $X$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.(b) The Solved $Y$ (in Blue) and the Actual $Y$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.
+%(a) The Solved $X$ (in Red) and the Actual $X$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.(b) The Solved $Y$ (in Blue) and the Actual $Y$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.
+\textcolor{blue}{(a) The solved $X$ (in red) and the actual $X$ (in black) for 10 simulation trials with covariance noise of 0.05 and shift of 2.(b) The solved $Y$ (in blue) and the actual $Y$ (in black) for 10 simulation trials with covariance noise of 0.05 and shift of 2.}
 }
@@
 \end{figure}
-\end{center}
+%\end{center}
 
@@
 If the data stream $\{A_i\}$ is shifted by $m$ units relative to $\{B_i\}$, then the maximum of the cross correlation can be used to recover the shift.
-After that, we can shift the data stream $\{A_i\}$ back to its original position to recover the correct correspondence with $\{B_i\}$, which will be used to find a correct solution satisfying the Euclidean-Group invariants as defined in Eq.(\ref{equ22}).
+After that, we can shift the data stream $\{A_i\}$ back to its original position to recover the correct correspondence with $\{B_i\}$, which will be used to find a correct solution satisfying the Euclidean-%G
+group invariants as defined in Eq.\textcolor{blue}{~}(\ref{equ22}).
 Therefore, a unique pair of $(X_k, Y_k)$ can be selected to minimize the cost function.
-In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ is calculated accurately, the errors of translations and rotations fluctuate by only a small amount compared to the errors of no-shift data streams.
+In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ is calculated accurately, the \textcolor{blue}{translational and rotational errors} %errors of translations and rotations
+fluctuate by only a small amount compared to the errors of \textcolor{blue}{the} no-shift data streams.
 
 To test the robustness of the proposed method, noises are exerted onto $\{B_i\}$ by employing $B_i^{noise} = B_i \text{exp}(\mathbf{\widehat{x}}_{noise})$, where each element of the Lie Algebra $\mathbf{x}_{noise}$ belongs to the Gaussian distribution defined as $N \sim (\mu_{noise},\sigma_{noise})$.
-In Fig.~\ref{fig3}, as the covariance of the noise $\sigma_{noise}$ increments from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ increase as shown in the box-and-whisker plot.
+In Fig.~\ref{fig3}, as the covariance %of the
+ noise $\sigma_{noise}$ increments from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ increase as shown in the box-and-whisker plot.
 There are several outliers outside the whiskers, while the median is calculated as the final solved $X$ and $Y$.
-Fig.~\ref{fig4} shows the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black when the noise covariance $\sigma = 0.05$ and the shift $n = 2$.
+Fig.~\ref{fig4} shows the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black %when the noise covariance
+\textcolor{blue}{with covariance noise of}  $\sigma = 0.05$ and %the
+ shift $n = 2$.
 
-\begin{center}
-\begin{figure}
+%\begin{center}
+\begin{figure}[t!]
 \centering
@@
 \caption{
-ErrorS of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method without Correspondence.
+%ErrorS of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method without Correspondence.
+\textcolor{blue}{Orientation and translation errors of $X$ and $Y$ versus shift using Li's and Shah's methods without correspondence.}
 }
@@
 \end{figure}
-\end{center}
+%\end{center}
 
-\begin{center}
-\begin{figure}
+%\begin{center}
+\begin{figure}[t!]
 \centering
@@
 \caption{
-Errors of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method with Correspondence.
+%Errors of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method with Correspondence.
+\textcolor{blue}{Orientation and translation errors of $X$ and $Y$ versus shift using Li's and Shah's methods with correspondence.}
 }
@@
 \end{figure}
-\end{center}
+%\end{center}
+
 The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods.
-In $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence.
+In \textcolor{blue}{the} $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence.
 However, few of them considered the cases without correspondence.
@@
 
-In this paper, we developed a probabilistic approach to simultaneously obtain  $X$ and $Y$ in $AX=YB$ sensor calibration problem.
-Without a prior knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie group is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates.
-Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean group invariants, the correspondence is recovered to determine the correct solution among the eight candidates.
+In this paper, we developed a probabilistic approach to simultaneously obtain $X$ and $Y$ in \textcolor{blue}{the} $AX=YB$ sensor calibration problem.
+Without a prior\textcolor{blue}{i} knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie group\textcolor{blue}{s} is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates.
+Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean\textbf{\textcolor{blue}{-}}group invariants, the correspondence is recovered to determine the correct solution among the eight candidates.
 In the numerical simulation, the method performs well with different sets of data samples.

### 2015-08-26 AXXB_Review/AXXB Review.tex
Josh's edits

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aeronautical Engineering %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[twocolumn,10pt]{asme2ej}
%%\documentclass[twocolumn,15pt]

\usepackage{epsfig} %% for loading postscript figures
\usepackage{amssymb,amsmath}
\usepackage{amsfonts}
\usepackage{multirow}
%\usepackage{natbib}
\usepackage{relsize}
\usepackage{graphicx}
\usepackage{color}
\usepackage{comment}

%\usepackage{algorithm2e}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}
\newtheorem*{main}{Main Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\newtheorem*{problem}{Problem}
%\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}{Remark}
\newtheorem*{notation}{Notation}

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
\newcommand{\uu}{{\bf u}}
\newcommand{\vv}{{\bf v}}
\newcommand{\ww}{{\bf w}}
\newcommand{\WW}{{\bf W}}
\newcommand{\nn}{{\bf n}}
\newcommand{\ttt}{{\bf t}}
\newcommand{\pp}{{\bf p}}
\newcommand{\qq}{{\bf q}}
\newcommand{\aaa}{{\bf a}}
\newcommand{\bbb}{{\bf b}}
\newcommand{\yy}{{\bf y}}
\newcommand{\xx}{{\bf x}}
\newcommand{\OO}{\mathbb{O}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\IR}{\mathbb{R}}
\newcommand{\IZ}{\mathbb{Z}}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\bea}{\begin{eqnarray*}}
\newcommand{\eea}{\end{eqnarray*}}
\newcommand{\bfmu}{\mbox{\boldmath $\mu$ \unboldmath} \hskip -0.05 true in}
\newcommand{\bfphi}{\mbox{\boldmath $\phi$ \unboldmath} \hskip -0.05 true in}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bfomega}{\mbox{\boldmath $\omega$ \unboldmath} \hskip -0.05 true in}
\newcommand{\om}{\omega}
\newcommand{\Om}{\Omega}
\newcommand{\bom}{\bfomega}
\def\tab{ {\hskip 0.15 true in} }
 \def\vtab{ {\vskip 0.1 true in} }
 \def\htab{ {\hskip 0.1 true in} }
  \def\ntab{ {\hskip -0.1 true in} }
 \def\vtabb{ {\vskip 0.0 true in} }

%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

\title{Chapter X : Review of Methods for Solving the AX\raisebox{.2ex}{=}XB Sensor Calibration Problem}

\author{Qianli Ma\thanks{Address all correspondence to this author.}\\ 
		\textbf{Gregory S. Chirikjian}
    \affiliation{
	Robot and Protein Kinematics Laboratory\\
	Laboratory for Computational Sensing and Robotics\\
	Department of Mechanical Engineering\\
	The Johns Hopkins University\\
	Baltimore, Maryland, 21218\\
    Email: \{mqianli1, gchirik1\}@jhu.edu
    }	
}

%%%% first author
%\author{Qianli Ma  \thanks{Address all correspondence related to ASME style format and figures to this author.} \\
%    \affiliation{ 
%	Dep. of Mechanical Engineering\\
%	Johns Hopkins University\\
%	Baltimore, MD 21218\\
%    Email: mqianli1@jhu.edu
%    }
%}
%
%%%% second author
%%%% remove the following entry for single author papers
%%%% add more entries for additional authors
%\author{Gregory S. Chirikjian
%    \affiliation{
%	Dep. of Mechanical Engineering\\
%	Johns Hopkins University\\
%	Baltimore, MD 21218\\
%    Email: gregc@jhu.edu
%    }
%}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it
An often used formulation of sensor calibration in robotics and computer vision is ``AX=XB'', where $A$, $X$, and $B$ are rigid-body motions with $A$ and $B$ given from sensor measurements, and $X$ is the unknown calibration parameter. Many methods have been proposed to solve $X$ given data streams of $A$ and $B$ under different scenarios. This chapter presents the most complete picture of the $AX=XB$ solvers up-to-date.  First, a brief overview of the various important sensor calibration techniques is given and problems of interest are highlighted. Then, a detailed review of the various ``AX=XB'' research algorithms is presented. The notations of the selected algorithms are unified to the largest extent in order to show the interconnections between the selected methods in a straightforward  way. Finally, the criterion for data selection and various error metrics are introduced, which are of critical importance for evaluating the performance of $AX=XB$ solvers. 
}
\end{abstract}

\keywords{Sensor Calibration, Hand-Eye Calibration, Humanoid Robot, Review}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{\textcolor{blue}{Note}}{\textcolor{blue}{For SE(3) and se(3) maybe make the inline matrices into actual matrices, it looks a little strange to me the way they are currently. Also, possibly consider changing $\Xi$ to $\mathfrak{h}$. Also, can you align the beginning of all of the second entries?}}
\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$\textbf{\textcolor{blue}{,}} %and
 $\det(R) = 1$\textbf{\textcolor{blue}{,}} where $R \in \mathbb{R}^{3 \times 3}\}$}
\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \time 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
\entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in \textcolor{blue}{so}%SO
(3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
\entry{$exp()$}{The matrix exponential of a square matrix. }
\entry{$log()$}{The matrix logarithm of a square matrix}
\entry{$H$}{A general rigid body transformation ($H \in SE(3)$) }
\entry{$\mathfrak{H}$}{ If $H$ is an element of a Lie Group, $\mathfrak{H}$ is the corresponding element in the Lie algebra}
\entry{$\mathbb{O}_n$}{$n \times n$ zero matrix}
\entry{$\mathbb{I}_n$}{$n \times n$ identity matrix}
\entry{$\{E_i\}$}{the set of ``natural" basis elements for Lie algebra}
\entry{$^\vee$}{For Lie algebra, the ``vee" operator is defined such that $\left(\displaystyle\sum\limits_{i=1}^n x_iE_i\right)^{\vee}\doteq(x_1,x_2,...,x_n)^T$ where $n = 3$ for $so(3)$ and $n = 6$ for $se(3)$}
\entry{$\hat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator. $\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$}
\entry{$\circ$}{The operator defined for the group product}
\entry{$\odot$}{The operator defined for the quaternion product}
\entry{$\hat{\odot}$}{The operator defined for the dual quaternion product}
\entry{$\otimes$}{The operator defined for the Kronecker product}
\entry{$vec$}{The ``vec'' operator is defined such that $vec(A) = [a_{11},...,a_{1m},a_{21},...,a_{2m},...,a_{n1},...,a_{nm}]^{T}$ for $A = [a_{ij}] \in \mathbb{R}^{m \times n}$}
\entry{\textcolor{blue}{Remark:}}{\textcolor{blue}{I would remove the next entry, it will lead to confusion and generally isn't necessary.}}
\entry{${\bf p}$}{For $P\in G$ (where $G$ is a Lie group, e.g. $SE(3)$ or $SO(3)$), ${\bf p}=(p_1,p_2,...,p_n)^T=\log^{\vee}(P)$}
\entry{$A_i$}{A rigid body transformation ($A_i \in SE(3)$), associated with one sensor measurement source}
\entry{$B_i$}{A rigid body transformation ($B_i \in SE(3)$), usually associated with a different sensor measurement source}
\entry{$X$}{The rigid body transformation ($\textcolor{blue}{X} %X_i 
\in SE(3)$) that relates $A_i$ to $B_i$}
\entry{$R_{H}$}{The rotation matrix of any general transformation matrix $H \in SE(3)$}
\entry{$\ttt_{H}$}{The translation vector of any general transformation matrix $H \in SE(3)$}
\entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
\entry{$\tilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
\entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
\entry{$\rho$}{A probability distribution of $H\in G$ on SE(3)\textcolor{blue}{G not well-defined here}}
\entry{$M$}{For $\rho$, $M$ is the mean of the distribution}
\entry{$\Sigma$}{For $\rho$, $\Sigma$ is the covariance of the distribution about the mean, $M$}
\entry{$Ad$}{For the Lie group $G$ and the Lie algebra $\mathfrak{G}$, the adjoint operator is the transformation\\ Ad: $G \rightarrow$ GL($\mathfrak{G}$), defined as\\ Ad($H_1$)$\mathfrak{H}_2 \doteq \frac{d}{dt}(H_1 \circ e^{t \mathfrak{H}_2} \circ H_1^{-1})$}
\entry{$Ad(H) $}{The adjoint matrix with columns $(H E_i H^{-1})^{\vee}$}
\end{nomenclature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{Intro}
\textcolor{blue}{General Note: Shouldn't alway equations be numbered in an ASME document? It may be IEEE, but I'm just checking}\\

In the fields of robotics and computer vision, sensor calibration problems are often codified using the ``AX=XB'' formulation, (\textcolor{blue}{Figs.~\ref{AXXBfig1}--\ref{AXXBfig3}}%Fig.\ref{AXXBfig1}, Fig.\ref{AXXBfig2}, Fig.\ref{AXXBfig3}
). Example applications include camera calibration, Cartesian robot hand calibration, robot eye-to-hand calibration \cite{tsai1989new}, aerial vehicle sensor calibration \cite{darius1}, image-guided therapy (IGT) sensor calibration and endoscopic surgery \cite{schmidt2003robust}. An alternative name that describes this system is ``hand-eye'' calibration. Several methods \textcolor{blue}{exist} %have existed 
in the literature that can perform hand-eye calibration without directly dealing with the $AX=XB$ formulation such as \cite{malm2000new,heller2012branch,ruland2012globally,wu2014hand,kim,liu2015calibration}. %Camera calibration is also integrated into hand-eye calibration  in some works \cite{,,,}. 
Another problem, called the robot-world and hand-eye calibration, deals with the case where an additional calibration of the robot pose with respect to the world \textcolor{blue}{frame} is needed. This calibration technique is formulated as the ``AX=YB'' problem and multiple methods have been \textcolor{blue}{developed} %brought up 
such as \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative,li2010simultaneous,ernst2012non,heller2014hand}.
Furthermore, a hand-eye, tool-flange, and robot-robot calibration problem is formulated as the ``AXB = YCZ'' problem in \cite{wang2014towards}.

In the ``AX=XB'' formulation $A$, $X$, and $B$ are each homogeneous transformations (i.e., elements of the special Euclidean group, $SE(3)$) with each pair of measurements $(A,B)$ coming from sensors such as cameras, ultrasound probes, optical, or electromagnetic pose tracking systems, among others. $X$ is the unknown rigid-body \textcolor{blue}{transformation} %motion 
that is found as a result of solving $AX=XB$. It is well known that it is not possible to solve for
a unique $X$ from a single pair of exact $(A,B)$, but if there are two instances of independent exact measurements, $(A_1,B_1)$ and $(A_2,B_2)$ satisfying certain constraints,
then the problem can be solved \textcolor{blue}{for a unique, fixed $X$}. However, in practice, sensor noise is always present, and an exact solution is not possible. The goal, therefore, becomes one of finding
an $X$ with the least error given corresponding noisy pairs \textcolor{blue}{of data} $(A_i, B_i)$ for i = 1,2, \ldots,n.

\section{THE $AX=XB$ FORMULATION}
\label{Formulation}
\noindent Any (proper) rigid-body motion in a three-dimensional space can be described as a $4 \times 4$ homogeneous transformation matrix of the form: 
\begin{equation} 
H(R, \ttt) = \left(
\begin{array}{ccc}
R && {\bf t} \\
{\bf 0}^T && 1 
\end{array} 
\right)
\label{homotrans} 
\end{equation}
where $R \in SO(3)$ is a $3\times 3$ (proper) rotation matrix, and ${\bf t} \in \mathbb{R}^3$ is a translation vector. The set of all such matrices can be identified with $SE(3)$, the group of rigid-body motions, where the group law is matrix multiplication.

\textcolor{blue}{This seems like an awkward transition. Can you add a sentence connecting the two paragraphs?}

Given:
\begin{equation}
A X = X B
\label{mainaxxb}
\end{equation}
where $A,  B, X \in SE(3)$, it is well known that, in non-degenerate cases, there are two unspecified degrees of freedom to the problem for a single pair of sensor measurements, $(A,B)$. This situation is rectified by considering two pairs of exact measurements of the form in Eq.~(\ref{mainaxxb}), i.e., $ {A_1}X=X{B_1} {\rm \,\, and \,\,} {A_2}X = X{B_2} $, provided that some mild conditions are observed for the selection of the pairs $(A_1,B_1)$ and $(A_2,B_2)$ \cite{chen91,park1994robot,shiu1989calibration}. Note that $(A_i, B_i)$ here are relative transformation data pairs, so in real experiments at least 3 absolute transformation data pairs \textcolor{blue}{have to} %should 
be measured. Additionally, if there is sensor measurement error, then it may not be possible to find compatible pairs that reproduce the exact value of $X$. For this reason, minimization and least squares approaches are often taken over large sets of $A$s and $B$s.

\begin{figure}[t]
\includegraphics[width=3.3in]{figure/AX=XB(ASME)_v1.png}
\centering
\caption{\textcolor{blue}{Increase the size of text in the image} The AX=XB Sensor Calibration Formulation}
\label{AXXBfig1}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/UR5_Frame_Final.jpg}
\caption{\textcolor{blue}{Capitalization style changed midway through, I would use all lower case besides beginning of sentences} Application of AX=XB in Ultrasound Sensor Calibration: An Ultrasound Probe Is Attached to the End-effector and the Calibration Phantom Is Used for Ultrasound Probe Calibration. (The UR5 robot pictured above is owned by Professor Emad Boctor of Johns Hopkins University)}
\label{AXXBfig2}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/Robot_Patern.jpg}
\caption{\textcolor{blue}{Labels are hard to see in the picture. Also, you change the capitalization style midway through} Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
 \textit{Boston Dynamics} Requires Head-Body Calibration before Turning the Knob. Different pairs of $(A_i, B_i)$ are measured by changing the head pose of the humanoid robot. (This picture was generated using the open-source robot simulation software Gazebo)}
\label{AXXBfig3}
\end{figure}

Performing the matrix multiplication of homogeneous transformations in Eq.~(\ref{mainaxxb}) and separating out the rotational and translational parts results in two equations of the form:
\begin{subequations}
\begin{gather}
R_A R_X = R_X R_B \label{subequ1}\\
R_A {\bf t}_X + {\bf t}_A = R_X {\bf t}_B + {\bf t}_X \label{subequ2}.
\end{gather}
\label{axxb}
\end{subequations}
\textcolor{blue}{One strategy for solving Eq.~(\ref{mainaxxb}) reduces to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A$.}
%One strategy to solve Eq.~(\ref{mainaxxb}) \textcolor{blue}{of data}would appear to reduce to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) so as to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A. $  
The other strategy is to solve for $R_{X}$ and $\ttt_{X}$ simultaneously based on some cost function $f(R_{X}, \ttt_{X})$ or reformulating the matrix equation into \textcolor{blue}{a dual quaternion representation}. %dual quaternion. 
However, when there are only two exact sensor measurements, there are some problems with the first  approach. As pointed out in \cite{park1994robot,shiu1989calibration}, in nondegenerate cases, there is a one-parameter set of solutions to \textcolor{blue}{Eq.~\ref{subequ1}}%the first part in Eq.(\ref{subequ1})
, and the matrix $R_A - \mathbb{I}_{3}$ in general has a rank of $2$. Hence, there are two unspecified degrees of freedom to the
problem, and it cannot be solved uniquely unless additional measurements are taken.

Additionally, if there is sensor error, then it may not be possible to find compatible pairs that reproduce the exact value of $X$. For this reason, minimization approaches are often taken, where for $n>2$ a cost function:
\begin{equation}
C(X) = \sum_{i=1}^{n} w_i \, d^2(A_i X,X B_i)
\label{mainaxxb2}
\end{equation}
is computed for some distance metric $d(\cdot,\cdot)$ on $SE(3)$ and $\{w_i\}$ is a set of weights which can be taken as a partition of unity.

%A wide variety of such metrics are discussed in \cite{axxb13} that have the useful property of left-invariance, $d(H_0 H_1, H_0 H_2) = d(H_1, H_2)$ for any $H_0, H_1, H_2 \in SE(3)$.
%
%
%Perhaps the simplest of the left-invariant ones is based on the weighted Frobenius norm
%$$ d^2(H_1,H_2) = \|H_1 - H_2\|_{W}^{2} = {\rm trace}[(H_1 - H_2)W(H_1 - H_2)^T] $$
%where $W$ is a matrix that weights rotations and translations appropriately, as described in \cite{axxb13}.
%The sets of pairs $(A_i,B_i)$ for $i=1,2...,n$ is chosen such
%that the set $\{A_i\}$ is spread out over a variety of positions and orientations, and likewise for $\{B_i\}$, so that the
%resulting $X$ is robust to measurement errors. 
This chapter is organized as follows. 
In Section~\ref{sec:sol_methods}, a detailed review is given for the existing methods that solve the $AX=XB$ problem using pairs of $\{A_{i}, B_{i}\}$ with correspondence. The notation used throughout the literature is not consistent and the authors \textcolor{blue}{strove} %tried their best 
to standardize the notation used across the reviewed methods
\textcolor{blue}{to provide the readers with a straightforward and consistent representation of the methods and their relationships.} %so that readers can have a straightforward and consistent understanding of the methods and their relationships. 
Some approaches are preferable under certain circumstances and their advantages and disadvantages are also highlighted. 
In Section~\ref{sec:data_selection}, some important criterion for data selection and different errors metrics used in the literature are presented. 
%In section 5, numerical simulations are performed on the selected methods and further conclusions are given based on the results of the simulation. 
Finally, in Section~\ref{sec:conclusion} a complete summary of the $AX=XB$ solvers is provided and open problems are noted as well.

\section{EXISTING SOLUTION METHODS}
\label{sec:sol_methods}

The problem of solving Eq.~(\ref{mainaxxb}) for $X$ when multiple corresponding pairs of $A$s and $B$s are present has a history that stretches back more than a quarter of a century
\cite{chou1991finding, park1994robot,shiu1989calibration}, with the earliest proposed method introduced by Shiu \cite{shiu1987finding, shiu1989calibration} and Tsai \cite{tsai1989new}. \textcolor{blue}{Surprisingly,} applications involving this problem still remain active today \cite{kim,dai}. Shah \cite{shah2012overview} overviewed several different AX = XB methods qualitatively. Fassi and Legnani \cite{fassi2005hand} gave a geometric view of $AX=XB$ and discussed the over-constrained and singular conditions. A more complete list of the traditional $AX=XB$ solvers includes: the Shiu method \cite{shiu1989calibration}, the screw motion method \cite{chen91,zhao2006hand}, the Euclidean \textcolor{blue}{g}%G
roup method \cite{park1994robot,gwak2003numerical}, the quaternion method\cite{chou1988quaternions, chou1991finding, horaud1995hand}, the dual quaternion method \cite{daniilidis1996dual, daniilidis1999hand}, and the Kronecker method \cite{andreff1999line,andreff2001robot}. Several new optimization methods emerged recently such as the convex optimization method \cite{zhao2011hand}, some global optimization methods  \cite{seo2009branch,andreff2001robot,heller2014hand} and a structure from motion (SfM) approach \cite{schmidt2005calibration}. The SfM method deals with the case where a calibration target is not applicable and a scaling factor needs to be calibrated in addition to rotation and translation. The methods mentioned previously are all off-line methods where $X$ can be calculated given a complete list of data pairs. However, several online methods \textcolor{blue}{have been} %are 
proposed that are more preferable to real-time applications \cite{andreff1999line,angeles2000online,ackerman2014online}. All the methods above assume $\{A_i, B_i\}$ data pairs with correspondence. Probabilistic methods that deal with data pairs without correspondence are introduced in \cite{ackermanGSI, ackerman2014information}. In the follow sections, representatives of the above $AX=XB$ solvers will be reviewed in detail.

\begin{comment}
Decompose the 
\begin{equation}
AX = XB,
\label{AXXB}
\end{equation}
decompose Eq.(\ref{AXXB}) into the rotation component and the translation component: 
\begin{equation}
R_{A}R_{X} = R_{X}R_{B}
\label{Rotation}
\end{equation}
\begin{equation}
(R_{A} - I)\ttt_{x} = R_{X}\ttt_{B} - \ttt_{A}
\label{Translation}
\end{equation}
\end{comment}

\subsection{Shiu and Ahmad }
Shiu and Ahmad \cite{shiu1987finding,shiu1989calibration} use two data pairs $(A_{i}, B_{i})$ to solve for X. The necessary condition for the uniqueness of X is that the rotation axes of $R_{A_1}$ and $R_{A_2}$ are neither parallel nor anti-parallel, and the angles of rotation are neither 0 nor $\pi$. Though this method shows tolerance to noise to a certain extent, it is specifically designed to solve for the case where only two sets of $(A, B)$ are given. 
The rotation matrix $R_{X}$ is solved for first and the translation is obtained using a least squares technique given a known $R_{X}$.

The closed form expression for $R_{X}$ is:
\textcolor{blue}{Note: It is hard to \~n in the below equation and also the 2nd subscript on R$_X$}
\begin{equation}
R_{X} = e^{\tilde{\nn}_{A}\beta}R_{X_{P}}
\label{RotationCheng}
\end{equation}
where 
\begin{center}
$R_{X_{p}} =  e^{\tilde{\nn}_{X}\theta_{X}}$\\
$\nn_{X} = \nn_{B} \times \nn_{A}$\\
$\theta_{X} = \rm atan2(|\nn_{B} \times \nn_{A}|,\nn_{B} \cdot \nn_{A})$\\
\end{center}
and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\tilde{\nn}$ is a skew-symmetric matrix defined as below:\\
\begin{equation}
\tilde{\nn}
=
\begin{pmatrix}
0 & -n_{3} & n_{2} \\
n_{3} & 0 & -n_{1} \\
-n_{2} & n_{1} & 0
\end{pmatrix}.
\end{equation}

Equation~(\ref{RotationCheng}) shows that $R_{x}$ has one degree of freedom which is determined by the angle $\beta$. Therefore, two relative arm motions are needed to generate two $(A_{i}, B_{i})$ data pairs in order to calculate the unique solution of $X$. Given two pairs of $A$s and $B$s, two equations can be obtained as:
\begin{subequations}
\begin{gather}
A_{1}X = XB_{1} \label{7a}\\
A_{2}X = XB_{2}.\label{7b}
\end{gather}
\end{subequations}
Instead of giving a closed-form solution, $R_{X}$ is calculated by solving for $\beta$ in Eq.~(\ref{CYD}), which is formulated \textcolor{blue}{as a system of linear equations obtained} by equating two \textcolor{blue}{instances of} Eq.~(\ref{RotationCheng}) that are obtained from data pairs $(A_{1}, B_{1})$ and $(A_{2}, B_{2})$:
\begin{equation}
CY = D.
\label{CYD}
%$${\color{red}(Detailed description of C and D?)}$$
\end{equation}
In Eq.~(\ref{CYD}), $Y = \big( \; \cos(\beta_{1}),\; \sin(\beta_{1}), \; \cos(\beta_{2}),\; 	\sin(\beta_{2}) \;\big)^{T}$ where $\beta_{1}, \, \beta_{2}$ correspond to Eq.~(\ref{7a}) and Eq.~(\ref{7b}) respectively,  $C \in \mathbb{R}^{9 \times 4}$ and $D \in \mathbb{R}^{9 \times 1}$ are determined from $\nn_{A_{1}}$, $\nn_{B_{1}}$, $\nn_{A_{2}}$, and $\nn_{B_{2}}$. The explicit expressions for $C$ and $D$ are given in Eq.~(44) of \cite{shiu1989calibration}.

Similarly, with known $R_{X}$, $\ttt_{x}$ can be calculated using the least squares method:
\begin{equation}
\bigg(\begin{array}{lr}
R_{A_{1}} - \mathbb{I}_{3} \\
R_{A_{2}} - \mathbb{I}_{3}
\end{array}\bigg)\ttt_{X}=
\bigg(\begin{array}{lr}
R_{X}\ttt_{B_{1}} - \ttt_{A_{1}}\\
R_{X}\ttt_{B_{2}} - \ttt_{A_{2}}
\end{array}
\bigg).
\label{trans}
\end{equation}
This is not a closed-form solution and it is constrained to the case where only two data pairs are provided.

\subsection{Lie Group Method }
The Lie Group method \cite{park1994robot} by Park and Martin is the first method to solve the AX = XB problem from the perspective of Lie groups. It uses the axes of rotation of $A_{i}$ and $B_{i}$ to construct $R_{X}$ and gives both the closed-form solution for the no-noise case and the numerical solution for multiple noisy $(A_{i}, B_{i})$ pairs.
\subsubsection{Closed-Form Solution with Two Exact Pairs}
The closed-form solution for $R_{X}$ is as follows:
\begin{equation}
R_{X} = \mathcal{A}\mathcal{B}^{-1}
\label{Lie_Rotation}
\end{equation}
where\\

\begin{center}
$\mathcal{A} = (\nn_{A_{1}}, \nn_{A_{2}}, \nn_{A_{1}} \times \nn_{A_{2}}) \in \mathbb{R}^{3 \times 3}$\\
 $\mathcal{B} = (\nn_{B_{1}}, \nn_{B_{2}}, \nn_{B_{1}} \times \nn_{B_{2}}) \in \mathbb{R}^{3 \times 3} $\\
\textcolor{blue}{I corrected the format of the two below equations, please make sure they are still correct\\}
$\tilde{\nn}_{A_{1}} = \log(R_{A_{i}})/\|\log^\vee(R_{A_i})\|$\\
%(\log R_{A_{i}})^{\vee}||$\\
$\tilde{\nn}_{B_{1}} = \log(R_{B_{i}})/\|\log^\vee(R_{B_i})\|$
%(\log R_{B_{i}})^{\vee}||$.
\end{center}
The solution for $R_X$ is uniquely determined given two pairs of $(A_i, B_i)$, and the solution for $\ttt_{X}$ can be obtained using Eq.~(\ref{trans}) once $R_{X}$ is obtained.\\
\begin{comment}
\begin{equation}
\bigg(\begin{array}{lr}
R_{A_{1}} - I \\
R_{A_{2}} - I
\end{array}\bigg)\ttt_{X}=
\bigg(\begin{array}{lr}
R_{X}\ttt_{B_{1}} - \ttt_{A_{1}}\\
R_{X}\ttt_{B_{2}} - \ttt_{A_{2}}
\end{array}
\bigg)
\label{Lie_Translation}
\end{equation}
\end{comment}

\subsubsection{Estimation of X Using Multiple Pairs with Noise}
When there are multiple pairs of $(A_{i}, B_{i})$ with noise, rotation matrix $R_{X}$ is solved for first and then the translation vector $\ttt_{x}$ is obtained using a least squares method given known $R_{X}$. The closed-form expression for $R_{X}$ is as follows:
\begin{equation}
R_{X} = (M^{T}M)^{-\frac{1}{2}}M^{T}
\end{equation}
where \\
\begin{center}
$M = \sum_{i=1}^{n}{\nn_{B_{i}} \nn_{A_{i}}^{T}}$.
\end{center}
Note that $i \geq 3$ is a necessary condition for $M$ to be a non-singular matrix, but it does not guarantee $M$ to be nonsingular. Theoretically, the Lie group method is more likely to fail when the number of data pairs is small \textcolor{blue}{give an approximation here i.e. (<10 pairs)} while in real application, \textcolor{blue}{failure is rarely} %this is barely 
seen as long as the data pairs are not specially chosen \textcolor{blue}{maybe add: specially chosen as ...}. Given known $R_{X}$, $\ttt_{X}$ can be calculated using the least squares method shown in Eq.~(\ref{t_least}):

\begin{equation}
\ttt_{x} = (C^{T}C)^{-1}C^{T}d
\label{t_least}
\end{equation}
where\\

\begin{center}
$\begin{array}{lr}
C = \begin{pmatrix}
\mathbb{I}_{3} - R_{{A_{1}}}\\
\mathbb{I}_{3} - R_{{A_{2}}}\\
.\\
.\\
.\\
\mathbb{I}_{3} - R_{{A_{n}}}\\
\end{pmatrix}
\; \; 
& \; \;
d = \begin{pmatrix}
\ttt_{A_{1}} - R_{X}\ttt_{B_{1}}\\
\ttt_{A_{2}} - R_{X}\ttt_{B_{2}}\\.\\
.\\
.\\
\ttt_{A_{n}} - R_{X}\ttt_{B_{n}}\\\end{pmatrix} 
\end{array}$.
\end{center}

\subsection{Quaternion Method }
\label{sec:quats}
The Quaternion method proposed by Chou and Kamel \cite{chou1988quaternions,chou1991finding} uses \textcolor{blue}{unit quaternions?} normalized quaternions to transform the rotation parts of $A_{i}X = XB_{i}$ (i = 1,2) into two linear systems. Then a singular value decomposition (SVD) is performed to obtain a closed-form solution for $R_{X}$. In order to estimate $X$ given multiple pairs of $(A_{i}, B_{i})$ with noise, Horaud and Dornaika \cite{horaud1995hand} cast the problem into a nonlinear optimization one. Two different approaches are discussed: (1) estimate the rotation matrix $R_{X}$ by minimizing an objective function, and solve for the translation $\ttt_{X}$ using a least squares method separately and (2) estimate $R_{X}$ and $\ttt_{X}$ simultaneously by minimizing an objective function that incorporates both the rotational and translational information. Method (1) turns out to have a closed-form solution for \textcolor{blue}{the unit quaternion $q_{X}$ representing the rotation $R_{X}$}%$q_{X}$
, while method (2) is a nonlinear optimization problem which requires an initial guess and will be discussed in Section~\ref{sec:optimization}. 
\subsubsection{Closed Form Solution with Two Exact Pairs}
\label{sec:quat_method}
First, the rotation equation in Eq.~(\ref{axxb}) is transformed into the equation of quaternion multiplication as below:
\begin{equation}
R_{A}R_{X} = R_{X}R_{B} 
\; \;
\Leftrightarrow
\; \;
q_{A}\odot q_{X} = q_{X}\odot q_{B}
\label{Quaternion}
\end{equation} 
where $q_{A}$, $q_{B}$ and $q_{X}$ are
unit quaternions that represent the rotation parts of matrices $A$, $B$ and $X$, and $\odot$ denotes quaternion multiplication.

Given two quaternions $q_{\alpha} = \left( \alpha_{0}, \alpha_{1}, \alpha_{2},\alpha_{3} \right)^{T} = \left( \alpha_{0}, \bf{\alpha}^{T} \right)^{T}$ and $q_{\beta} = \left( \beta_{0}, \beta_{1}, \beta_{2},\beta_{3} \right)^{T} = \left(\beta_{0}, \bf{\beta}^{T} \right)^{T}$, quaternion multiplication $\odot$ is defined as:
\begin{equation}
q_{\alpha}\odot q_{\beta} = 
\left(
\begin{matrix}
\alpha_{0} \beta_{0} - \bf{\alpha}^{T}\bf{\beta}\\
\alpha_{0}\bf{\beta} + \beta_{0}\bf{\alpha} + \bf{\tilde{\alpha}\beta}
\end{matrix}
\right).
\end{equation}
$\alpha_{0}$ is called the scalar component and $\bf{\alpha}$ is the vector component of the quaternion $q_{\alpha}$.
In order to solve for $q_{X}$, the quaternion equation is transformed into:
\begin{equation}
E\qq_{X} = \bf 0
\end{equation}
where $E \in \mathbb{R}^{4 \times 4}$ is obtained by grouping $q_{A}$ and $q_{B}$ together, and $\qq_{X} \in \mathbb{R}^4$ is the vector representation of the unit quaternion ${q_X}$.\\

It turns out that the unit quaternion $q_X$ which represents the rotation part of $X$ can be written as: 
\begin{equation}
\qq_{X} = V_{2}\bf y_{2}.
\label{QuaternionUnit}
\end{equation}
To obtain the matrix $V_{2}$ and vector $y_{2}$, $E$ is first written as $E =  \sin(\theta_{A|B}/2)E_0$ with $\theta_{A|B} = \theta_{A} = \theta_{B}$, which is the constraint that the corresponding transformations $A_i$ and $B_i$ should have the same angle of rotation. Next, the SVD of $M$ is computed as $E_0 = U\Sigma V^{T}$ where $V = (V_{1}, V_{2})$,  $V_{1} \in \mathbb{R}^{4 \times 2}$, $V_{2} \in \mathbb{R}^{4 \times 2}$, $U \in \mathbb{R}^{4 \times 4}$ and $\Sigma$ is a diagonal matrix. Vector ${\bf y_{2}}$ is obtained by calculating ${\bf y} =  V^{T}\qq_{x}$ where $\bf y = (\bf y^{T}_{1},\bf y^{T}_{2} )^{T}$, ${\bf y_{1}} \in \mathbb{R}^{2 \times 1}$ and ${\bf y_{2}} \in \mathbb{R}^{2 \times 1}$. Their expressions are also outlined as follows:\\

\begin{center}
$\begin{array}{lcl}
E & = & \sin(\theta_{A|B}/2)E_0\\
M & = & U\Sigma V^{T}\\
V & = & (V_{1}, V_{2})\\
\bf y & = & V^{T}\qq_{x}\\
\bf y & = & (\bf y^{T}_{1},\bf y^{T}_{2} )^{T}.
\end{array}$
\end{center}
The translation vector $\ttt_{x}$ satisfies the following equation:
%{\color{red} write equation of $\ttt_{x}$ in a more concise form by substituting c = (A-I)}
%\begin{equation}
%\ttt_{x} = {\bf \nn_{A}} z - \frac{1}{2}\bigg( \cot(\frac{\theta_{A}}{2})\hat{\nn}_{A} + I %\bigg){\bf c}
%\end{equation}
\begin{equation}
\left(\cot(\dfrac{\theta_{A}}{2})\hat{\nn}_{A}(R_{A}-\mathbb{I}_{3})+ R_{A} + \mathbb{I}_{3}\right)\ttt_{x} = \nn_{A}z
\label{QuaternionTranslation} 
\end{equation}
%\begin{equation}
%{\bf c = (R_{A} - I)\ttt_{x}} \;\; \text{  and  } \;\; z \in \mathbb{R} \text{  is arbitrary} 
%\label{QuaternionTranslation}
%\end{equation}
where $z \in \mathbb{R}$ is arbitrary. A unique solution can be calculated using Eq.~(\ref{QuaternionUnit}) and Eq.~(\ref{QuaternionTranslation}) given two nondegenerate pairs of $(A_{i}, B_{i})$.

\subsubsection{Estimation of X Using Multiple Pairs With Noise}
As shown in \cite{horaud1995hand}, in the case where there are n pairs of $(A_{i}, B_{i})$, the problem of recovering $R_{X}$ is converted into minimizing the following error objective function:
\begin{equation}
\begin{array}{c}
f(R_{X})
= \sum_{i = 1}^{n}||{n_{A_{i}} - q_{X} \odot n_{B{i}} \odot \bar{q}_{X}}||^{2} \\
\\ 
= {\qq_{X}}^{T}\tilde{K}{\qq_{X}}
\end{array}
\label{ErrorQuaternion} 
\end{equation}
where $n_{A_{i}} = \left(0, {\nn_{A_{i}}}^{T}\right)^{T}$ and $n_{B_{i}} = \left(0, {\nn_{B_{i}}}^{T}\right)^{T}$. $\tilde{K} = \sum_{i = 1}^{n}\tilde{K_{i}}$ and $\tilde{K_{i}} \in \mathbb{R}^{4 \times 4}$ is a symmetric positive definite matrix determined by $\nn_{A_{i}}$ and $\nn_{B_{i}}$; $\bar{q}_{X}$ is the conjugate of ${q}_{X}$ where $q_{X} \odot \bar{q}_{X} = 1$.

To minimize  Eq.~(\ref{ErrorQuaternion}) under the constraint that $\qq_{X}$ is a unit quaternion, the Lagrangian multiplier is introduced as:
\begin{equation}
\min_{q} f = \min_{q}({\qq_{X}}^{T}\tilde{K}{\qq_{X}} + \lambda(1 - {\qq_{X}}^{T}{\qq_{X}})).
\label{ErrorLagrangeMultiplier}
\end{equation}
Differentiating the error function with respect to $\qq_{X}$, the 1st order necessary optimality condition is obtained as: 
\begin{equation}
\tilde{K}\qq_{X} = \lambda \qq_{X}.
\label{QuaternionEig}
\end{equation}
It can be shown that the unit quaternion $\qq_{X}$ that minimizes $f$ is the eigenvector of $\tilde{K}$ associated with its smallest positive eigenvalue. After recovering $\qq_{X}$ (or equivalently $R_{X}$), $\ttt_{X}$ can be recovered using the least square techniques introduced in previous methods.

\subsection{Dual Quaternion Method }
The dual quaternion method proposed by Daniilidis and Bayro-Corrochano \cite{daniilidis1996dual} (Daniilidis \cite{daniilidis1999hand}) treats the rotation and translation parts of the matrix X in a unified way and facilitates a new simultaneous solution of X using SVD. To begin, Eq.~(\ref{mainaxxb}) is transformed into an equation \textcolor{blue}{of dual quaternions:} %in dual quaternion form as follows:
\begin{equation}
AX = XB 
\; \;
\Leftrightarrow
\; \;
\check{a} = \check{q}_{X}\hat{\odot}\check{b}\hat{\odot}\bar{\check{q}}_{X}
\label{DualQuaternion}
\end{equation}
where $\check{a}$, $\check{b}$ and $\check{q}$ are the dual quaternions that represent matrices $A$, $B$ and $X$, and $\bar{\check{q}}$ is the conjugate of $\check{q}$.

The dual quaternion that corresponds to a \textcolor{blue}{Be consistent throughout the paper: 4x4} %4 by 4 
rigid transformation matrix is defined as follows:
\begin{equation}
\check{q}_{X} =
\Bigg( 
\begin{array}{c}
\cos(\frac{\theta + \epsilon d}{2})\\
\sin(\frac{\theta + \epsilon d}{2})({\bf l} + \epsilon {\bf m})
\end{array}
\Bigg)
\label{dual_screw}
\end{equation}
where
$\theta$, $d$, ${\bf l}$ and ${\bf m}$ are screw parameters and ${\epsilon}^{2} = 0$. $\theta$ is the rotation angle, $d$ is the pitch, $\vec{\bf l}$ is the direction of the screw, and ${\bf m} = {\bf p} \times {\bf l}$ is the line moment where ${\bf p}$ is a point on the line. The six tuple $({\bf l}, {\bf m})$ defines a line in 3-D space. Furthermore, by expanding the dual terms in $\check{q}_{X}$, Eq.~(\ref{dual_screw}) can also be written as:
\begin{equation}
\check{q}_{X} = q_{X} + \epsilon {q}^{\prime}_{X}.
\end{equation} 
Both $q$ and $q^{\prime}$ are quaternions satisfying the following constraints:
\begin{equation}
{\bf q}^{T}_{X}{\bf q}_{X} = 1 \; \; \text{and} \;
\; {\bf q}^{T}_{X}{\bf q}^{\prime}_{X} = 0.
\end{equation}
Similar to Section \textcolor{blue}{\ref{sec:quats}?}, ${\bf q}_{X}$ and ${\bf q}^{\prime}_{X}$ are the vector representations of $q_{X}$ and $q^{\prime}_{X}$.
Then equation $A_{i}X = XB_{i}$ can be converted into the form below:

\begin{equation}
S_{i}
\underbrace{
\bigg(
\begin{array}{c}
{\bf q}_{X}\\
{\bf q}^{\prime}_{X}
\end{array}
\bigg)}_{\xx} = \bf 0
\label{dqua}
\end{equation} 
where
\begin{equation}
S_{i} = 
\bigg(
\begin{array}{cccc}

{\aaa} - {\bbb} & \; ({\aaa} + {\bbb})^{\wedge} & \; \bf 0_{3\times 1} & \bf 0_{3\times 3}\\

{\aaa}^{\prime} - {\bbb}^{\prime} & ({{\aaa}^{\prime} + {\bbb}^{\prime}})^{\wedge} & {\aaa} - {\bbb} & ({\aaa} + {\bbb})^{\wedge}

\end{array}
\bigg) \in \mathbb{R}^{6 \times 8}.
\end{equation}
The notation for $\bf x$ here will be referred to as in Section \textcolor{blue}{\ref{sec:optimization}.? You should not be referring to a future section, but introduce it here an reference later}%3.6. 
To maintain the consistency of notation throughout the chapter as well as preserve the original notation in \cite{daniilidis1996dual}, for a vector ${\bf v} \in \mathbb{R}^{3 \times 1}$, ${\bf v}^{\wedge}$ is the same as $\tilde{\bf v}$ which maps a vector into the corresponding skew-symmetric matrix. ${\aaa}^{\prime} = \dfrac{1}{2}{\ttt}_{X} \times {\aaa}$ and $\aaa$ is the vector part of $q_{X}$. Similarly,  $\bbb$ is the vector part of $q^{\prime}$.
After concatenating $S_{i}$, the following matrix $T$ can be obtained and used to solve for $X$:
\begin{equation}
T = \big( \; \; S_{1}^{T} \; S_{2}^{T} \; \; ... \; \; S_{n}^{T} \; \; \big)^{T}.
\end{equation}
By calculating the SVD of $T = U\Sigma V^{T}$, the dual quaternion for matrix X can be expressed as a linear combination of the last two right-singular vectors (${\bf v_{7}}$, ${\bf v_{8}}$) of matrix $T$, which are the last two columns of matrix $V$, as shown below: 
\begin{equation}
\bigg(
\begin{array}{c}
{\bf q}_{X}\\
{\bf q}^{\prime}_{X}
\end{array}
\bigg) = 
\lambda_{1}{\bf v_{7}} + \lambda_{2}{\bf v_{8}} \in \mathbb{R}^{8} \; \;
\text{where} \; \; \lambda_{1}, \lambda_{2} \in \mathbb{R}.
\label{dq_closed}
\end{equation}

Different from the quaternion method Section~\textcolor{blue}{\ref{sec:quat_method}?}, the dual quaternion method solves the rotational part and translational part in a united way, and it contains all the information to reconstruct matrix $X$. However, it does not use all of the available information, only the imaginary parts of $\check{a}$ and $\check{b}$. Despite the advantages of the dual quaternion method, its major drawback is the need to filter the data pairs to ensure appropriate solutions when there is noise on $A_{i}$ and $B_{i}$.

\subsection{Kronecker Product Method }
\label{sec:Kronecker}
Inspired by the well known Sylvester equation ( $AX + XB = C$ ) in linear systems, Andreff {\it et al}. \cite{andreff1999line} proposed the Kronecker method which converts  Eq.~(\ref{mainaxxb}) into the form of Kronecker products \cite{andreff1999line}: % as in Eq.~(\ref{KroneckerMethod}):
\begin{equation}
\begin{split}
AX &= XB  \Leftrightarrow\\
\underbrace{\Bigg(
\begin{array}{cc}
\mathbb{I}_{9} - R_{B} \otimes R_{A} \; & \; 0_{9 \times 3}\\
\ttt_{B}^{T} \otimes \mathbb{I}_{3} & \mathbb{I}_{3} - R_{A}
\end{array}
\Bigg)}_{C}
&\underbrace{\Bigg(
\begin{array}{c}
vec(R_{X})\\
\ttt_{X}
\end{array}
\Bigg)}_{\bf x} =
\underbrace{
\Bigg(
\begin{array}{c}
0_{9}\\
\ttt_{A}
\end{array}
\Bigg)}_{d}.
\end{split}
\label{KroneckerMethod}
\end{equation}
where $C, d, \bf x$ will be referred to in Section~\ref{sec:optimization} \textcolor{blue}{Again I would not refer to a future section. Check with Dr. C}. 
%where the symbol $\otimes$ denotes the Kronecker product. The $vec$ operator was introduced in \cite{neudecker1969note} and it's used to reorder the $m \times n$ components of a matrix $M_{m \times n}$ into a $mn$ vector $vec(M_{m \times n})$.\\
Given multiple pairs of $A$s and $B$s with noise, the Kronecker product is reformulated as:% Eq.(\ref{KroneckerRotation}) and Eq.(\ref{KroneckerTrans}):
\begin{equation}
\left(
\begin{array}{c}
\mathbb{I}_{9} - R_{B_{1}} \otimes R_{A_{1}}\\
\mathbb{I}_{9} - R_{B_{2}} \otimes R_{A_{2}}\\
\vdots\\
I_{9} - R_{B_{n}} \otimes R_{A_{n}}
\end{array}
\right) 
vec(R_{X})
 = {\bf{0}}_{9 n \times 1},
\label{KroneckerRotation}
\end{equation}
\textcolor{blue}{and}
\begin{equation}
\left(
\begin{array}{c}
\mathbb{I}_{3} - R_{A_{1}} \\
\mathbb{I}_{3} - R_{A_{2}} \\
\vdots\\
\mathbb{I}_{3} - R_{A_{n}}
\end{array}
\right) 
{\ttt_{X}}
 = 
\left( 
\begin{array}{c}
{\bf{t}}_{A_{1}} - R_{X}{\bf{t}}_{B_{1}}\\
{\bf{t}}_{A_{2}} - R_{X}{\bf{t}}_{B_{2}}\\
\vdots\\
{\bf{t}}_{A_{n}} - R_{X}{\bf{t}}_{B_{n}}\\
\end{array}
\right).
\label{KroneckerTrans}
\end{equation}
The vectorized version of $R_X$ obtained from Eq.~(\ref{KroneckerRotation}) is not an element of $SO(3)$ and
orthogonalization on $R_{X}$ is required to obtain a rotation matrix:% as in Eq.~(\ref{Orthogonolization}):
\begin{equation}
R_{X_{e}} = R_{X}(R_{X}^{T}R_{X})^{-1/2}
\label{Orthogonolization}
\end{equation}
\cite{horn1986robot}
where $R_{X_{e}}$ denotes the orthogonalized $R_{X}$.

The orthogonalized matrix $R_{X_{e}}$ is further normalized as: % in Eq.(\ref{kron_normal}): 
\begin{equation}
R_{X_{n}} = \dfrac{sign(\textrm{det}(R_{X_{e}}))}{{|\textrm{det}(R_{X_{e}})|}^{\tfrac{1}{3}}}R_{X_{e}}
\label{kron_normal}
\end{equation}
where $R_{X_{n}}$ is the normalized matrix of $R_{X_{e}}$.
After getting the estimation of $R_{X}$, a least squares method is implemented on Eq.~(\ref{KroneckerTrans}) to recover $\ttt_{X}$. One advantage of the Kronecker product method is its capability of dealing with small motions, because the associated orthogonal matrix $R_{X_{n}}$ is always defined, while the rotation can be ill-defined when using the axis-angle representation. Moreover, the linear system can also be used to analyze %This is the American version of analyse
 the  recoverable information in $X$ based on the available type and number of motions. Details are included in Section \textcolor{blue}{\ref{sec:data_selection}}. In addition, an on-line hand-eye calibration method is developed for an unknown scene based on the above algorithm, where the camera translations are estimated up to a scaling factor.

\subsection{Optimization Methods}
\label{sec:optimization}
Different optimization methods have been proposed in the literature and most of them are built upon the various parametrizations of the $AX=XB$ equations mentioned previously. 
\subsubsection{Quaternion Based Simultaneous Approach}
When trying to solve for $R_{X}$ and $\ttt_{X}$ simultaneously, it is impossible to find a closed-form solution. Horaud and Dornaika \cite{horaud1995hand} presented an objective function for minimization, which is a sum of squares of nonlinear functions as:
\begin{equation}
\begin{split}
f(q_X,\ttt_{X}) = \lambda_{1} \sum_{i = 1}^{n}||vec(q_{X} \odot t_{B_{i}} \odot \bar{q}_{X}) -(R_{A_i} - \mathbb{I})\ttt_{X} - \ttt_{A_i}||^{2}\\
\lambda_{2} \sum_{i = 1}^{n}||{n_{A_{i}} - q_{X} \odot n_{B_{i}} \odot \bar{q}_{X}}||^{2} + \lambda_{3}(1 - \qq_{X}^{T}\qq_{X})^2\\
\textcolor{blue}{I believe you are missing an operator between the two lines} 
\end{split}
\label{simlqua}
\end{equation}
where $\lambda_1, \lambda_2, \lambda_3 \in \mathbb{R}$. Note that $vec()$ here represents the vector part of a quaternion such that $vec(q) \in \mathbb{R}^{3}$. The third term is a penalty function where the \textcolor{blue}{modulus,modulo?} %module 
of $q$ will approach 1 when $\lambda_{3}$ becomes large. This is a non-convex optimization problem which requires a good initial guess due to the existence of multiple local minima. However, the result can be more accurate than the rest of the solvers for certain motion pairs when the initial guess is ``good".

\subsubsection{Polynomial Global Optimization}
Heller {\it et al.} \cite{heller2014hand} developed a polynomial global optimization method which does not require an initial estimate and is also globally optimal in the $L_2$-norm sense. Defining a certain parametrization of $X \in SE(3)$ as $P(X)$, the previous minimization problem Eq.~(\ref{mainaxxb2}) is formulated as:
\begin{equation}
\begin{split}
&\underset{X \in SE(3)}{\text{min}}\sum_{i=1}^n ||A_{i}X - XB_{i}||^2 \Leftrightarrow \\
&\text{minimize} \; \; \; \; f(P(X)) \\
\; \; &\text{subject to} \; \; {\bf c}(P(X)) \geq {\bf 0} 
\end{split}
\label{LMI}
\end{equation}
where $f(X)$ is the converted multivariate polynomial function using the convex linear matrix inequality (LMI) relaxations technique \cite{lepetit2009epnp}.

When $R_X$ is parametrized using the orthonormal basis as $R_{X}(\uu, \vv) = ( \uu, \vv, \uu \times \vv)$ where $\vv, \uu \in \mathbb{R}^{3}$, then Eq.~(\ref{LMI}) becomes:
\begin{equation}
\begin{split}
\text{minimize} \; \; \; \;&f_{1}(\uu, \vv, \ttt_{X}) = \\
&\sum_{i=1}^n ||A_i X(\uu,\vv,\ttt_{X}) - X(\uu,\vv,\ttt_{X})B_i ||^2\\
\text{subject to} \; \; \; \; &\uu^{T}\uu = 1, \vv^{T}\vv = 1, \uu^{T}\vv = 0.
\end{split}
\label{orLMI}
\end{equation}
Similarly, using the quaternion representation of $R_{X}$, Eq.~(\ref{LMI}) becomes:
\begin{equation}
\begin{split}
\text{minimize} \; \; \; \; &f_{2}(\qq_{X}, \ttt_{X}) = \\
& \sum_{i=1}^{n}||A_iX(\qq_{X}, \ttt_{X}) - X(\qq_{X}, \ttt_{X})B_i||^{2}\\
\text{subject to} \; \; \; \; &\qq_{X}^{T}\qq_{X} = 1, \; \; q_{X1} \geq 0.
\end{split}
\label{qLMI}
\end{equation}
If $A$, $B$ and $X$ are parametrized using dual the quaternion representation, then
\begin{equation}
\begin{split}
\text{minimize} \; \; \; \; &f_{3}(\check{q}_{X}) = \\
 & \sum_{i=1}^{n}||\check{q}_{A} \hat{\odot} \check{q}_{X}- \check{q}_{X} \hat{\odot} \check{q}_{B}||^{2}\\
\text{subject to} \; \; \; \; &\qq_{X}^{T}\qq_{X} = 1, \; \; q_{X1} \geq 0 \\
&q_{X1}q_{X5} + q_{X2}q_{X6} + q_{X3}q_{X7} + q_{X4}q_{X8} = 0.
\end{split}
\label{dqLMI}
\end{equation} 
As pointed out in \cite{heller2014hand}, the polynomial global optimization method as described in Eq.~(\ref{dqLMI}) can give better solutions than Park \cite{park1994robot}, Eq.~(\ref{simlqua}), Eq.~(\ref{orLMI}) and Eq.~(\ref{qLMI}). Several solvers for \textcolor{blue}{$AX=XB$? Introducing AX=YB seems arbitrary} %$AX=YB$ 
using the LMI technique are also given; however, they fail to give better results than the traditional methods.
\subsubsection{Convex Optimization}
Based on different ways of formulating the rotation part of the rigid body transformation, Zhao \cite{zhao2011hand} gives two formulations that use a $L_\infty$ optimization technique. $L_\infty$ optimization is the minimax problem:
\begin{equation}
\underset{\bf x}{\text{min}} \; \; \underset{i}{\text{max}} f_{i}(\bf x) \; \; i = 1,2,... ,n
\label{convex}
\end{equation} 
where $\bf x$ represents all the unknown transformation parameters and $f_{i}(\xx)$ is the error function corresponding to $(A_i, B_i)$. Eq.~(\ref{convex}) can be converted into a convex optimization problem if $f_i(\bf x)$ is a quasi-convex function on a convex domain on which it is to be minimized.

Using the Kronecker formulation as in Eq.~(\ref{KroneckerMethod}) and introducing an additional variable $\delta$, the equivalent form of the $L_\infty$ optimization problem is:
\begin{equation}
\begin{split}
&\underset{\delta, \xx}{\text{min}} \; \; \delta \\
&\text{subject to} \; \; ||C_i\xx - {\bf d}_i||_2 \leq \delta \\
&\text{where} \; \; i = 1,2,...,n.
\end{split}
\end{equation}
The matrix ${\bf C}_i$, vector $\bf x$, and ${\bf d}_i$ correspond to those in Eq.~(\ref{KroneckerMethod}).
Above is a convex optimization problem that can be solved using a \textit{second-order cone program}, which can be solved using toolboxes available online.

When the $AX=XB$ problem is formulated as a dual quaternion representation as in Eq.~(\ref{dqua}), the equivalent $L_\infty$ optimization problem can be written as:
\begin{equation}
\begin{split}
&\underset{\delta, \xx}{\text{min}} \; \; \delta \\
&\text{subject to} \; \; ||S_i\xx||_2 \leq \delta \\
&\text{where} \; \; i = 1,2,...,n \; \; \text{with} \; \; \bf{Dx \geq f}.
\end{split}
\end{equation}
The matrix $S_i$ and vector $\bf x$ correspond to those in Eq.~(\ref{dqua}). 
The inequality constraint $\bf{Dx \geq f}$ is added manually in order to prevent $\xx$ from reaching zero, which is a meaningless solution for the program. \textcolor{blue}{$\bf x$ must also satisfy two additional constraints: $\|\qq_X\|=1$ and $\|\qq_{X}^{\prime}\|=1$.}%Another constraint $\bf x$ has to satisfy is that $||\qq_X||=1$ and $||\qq_{X}^{\prime}||=1$.

The proposed methods need no initial guess and are less time consuming compared to the simultaneous optimization method given in Eq.~($\ref{simlqua}$). However, the errors for both of the convex optimization methods are larger than the latter. 
\subsection{Gradient Descent Method}
Except for the Kronecker product method, all the methods mentioned above are only able to solve for matrix $X$ offline, which means $\{A_{i}, B_{i}\}$ data pairs should be fully collected before being put into the algorithm. The gradient descent method \cite{ackerman2014online} by Ackerman {\it et al.} is an online sensor calibration method which uses a gradient descent optimization on the Euclidean group (SE(3)) given an appropriate cost function.

To begin, define $\mathcal{X} \in se(3)$ as the Lie algebra corresponding to $G = SE(3)$, and let $f:G \rightarrow \mathbb{R}$ be an analytic function and $g \in G$. As defined in \cite{myoldbook}, the concept of directional derivatives in $\mathbb{R}^{n}$ is extended to functions on a Lie group as:
\begin{equation}
\left.(\hat{\mathcal{X}}^{r}f)(g)\doteq \dfrac{d}{dt}f(g\circ \text{exp}(t\mathcal{X}))\right\vert_{t=0}.
\label{r_lie_d}
\end{equation}
Note that $t$ is just a scalar denoting the time, while $\ttt$ represents the translation part of a homogeneous transformation.
Eq.~(\ref{r_lie_d}) is the ``right'' Lie derivative and the ``left'' Lie derivative can be defined in a similar form. A gradient on $SE(3)$ is then defined using the right Lie derivative with the ``natural'' basis of Lie algebra $\{E_{i}\}$ where $i = 1,2,...,6$. Therefore, the gradient of the function on Lie group $f(g)$ is as follows:
\begin{equation}
\nabla f(g)= \left( 
\begin{matrix}
\frac{d}{dt}\left.f(g\circ \text{exp}(tE_{1}))\right\vert _{t=0} \\
\frac{d}{dt}\left.f(g\circ \text{exp}(tE_{2}))\right\vert _{t=0} \\
\vdots \\
\frac{d}{dt}\left.f(g\circ \text{exp}(tE_{6}))\right\vert _{t=0}
\end{matrix}
\right).
\end{equation}

In order to update $g$, the rigid body velocity is introduced where $V^{r}_{g} = g^{-1}\dot{g}$, and the update law is written as below:
\begin{equation}
g_{s+1} = g_{s}\text{exp}(\Delta t V^{r}_{g})
\end{equation}
where $t_{s+1} = t_{s} + \Delta t$ \textcolor{blue}{$t_{s+1}$ is not used in the equation} is the discrete time step. To \textcolor{blue}{prevent steps from becoming too small, the update law of $g_s$ is modified as:}%complete the update law of $g_s$, the rigid body velocity is defined as: 
\begin{equation}
V^{r}_{g} = g^{-1}\dot{g} = -\alpha \widehat{\nabla f(g)}.
\label{gs}
\end{equation} 
\textcolor{blue}{where $\alpha..$}
After choosing the cost function as:
\begin{equation}
C(X) = \sum_{i=1}^{n}||A_{i}X - XB_{i}||
\end{equation}
$X$ can be optimized using Eq.~(\ref{gs}).
The gradient descent method updates the calibrations parameters online based on new incoming data. The initial guess of $X$ will converge to the true $X$; however, the rate of convergence depends on how ``good'' the initial guesses are.

\subsection{Batch Method}
\label{batchnoisefree}
This section presents a probabilistic method \cite{ackermanGSI} by Ackerman and Chirikjian to solve for $X$ \textcolor{blue}{in the absence of} %when there does not need to be any 
a priori knowledge of the correspondence between the exact sets of measurements
$A = \{A_i\}$ and $B = \{B_j\}$. In other words, the sets $A$ and $B$ each can be given as unordered ``batches'' without knowing how each $A_i$ matches to a specific $B_j$.

A commonality of all the methods in the previous sections is that exact knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$ is assumed; however, this is not always the case. There are many instances in the literature when the sensor data used in calibration becomes ``unsynchronized''. Different attempts have been implemented to solve this problem, such as time stamping the data, developing dedicated software modules for syncing the data, and analyzing components of the sensor data stream to determine a correlation \cite{darius1}, to varying effects. The Batch method bypasses these issues altogether without tracking, or recomputing, correspondence. By modelling the set of $A$s and $B$s as probability distributions on $SE(3)$, the data can be taken as an unordered, uncorrelated ``batch" and a solution for $X$ can be generated.

\subsubsection{The Batch Method Formulation}
Given a large set of pairs $(A_i,B_i) \in SE(3) \times SE(3)$ for $i =1,...,n$ that exactly satisfy the equation:
\begin{equation} A_i X = X B_i , \label{main} \end{equation}
a new algorithm is developed to find $X \in SE(3)$. The Batch method addresses a generalization of the standard problem in which
the sets $A=\{A_i\}$ and $B =\{B_j\}$ are provided with elements written in any order and it is known that a correspondence exists between the elements of these sets such that Eq.~(\ref{main}) holds, but no a priori knowledge of this correspondence is known between each $A_i$ and $B_j$.

Define a Gaussian probability distribution on $SE(3)$ (assuming the norm $\|\Sigma\|$ is small) as:
$$ \rho(H; M, \Sigma) = \frac{1}{(2\pi)^3 |\Sigma|^{\half}} e^{-\half F(M^{-1} H)} $$
where $|\Sigma|$ denotes the determinant of $\Sigma$ and
$$ F(H) = [\log^{\vee}(H)]^T \Sigma^{-1} [\log^{\vee}(H)]. $$
When $H$ is parameterized with exponential coordinates, $H = \exp Z$, this means that
$F(\exp Z) = {\bf z}^T \Sigma^{-1}  {\bf z}$ where ${\bf z} = Z^{\vee}$ and
$\rho(\exp Z; \mathbb{I}_4, \Sigma)$ becomes exactly a zero-mean Gaussian distribution on the Lie algebra $se(3)$, with covariance $\Sigma$, that is `lifted up' to the Lie group $SE(3)$. This definition is valid when $\|\Sigma\|$ is small enough that the tails of the distribution decay rapidly enough such that the value of $\rho$
becomes negligible before they ``wrap around'' due to the topology of $SE(3)$.

Using formulations of probability theory on SE(3), Eq.~(\ref{main}) can be thought as:
\begin{equation} (\delta_{A_i} * \delta_X)(H) = (\delta_X * \delta_{B_i})(H) \label{mainconv} \end{equation}
where $*$ denotes the convolution of functions on $SE(3)$, as defined in the Appendix.
\textcolor{blue}{Maybe include the definition of $ \delta_{A_i}$}
\begin{comment}
Whereas the addition (as opposed to multiplication) of homogeneous transformation matrices is nonsensical, the addition of real-valued functions $f_1(H) + f_2(H)$ is a perfectly reasonable operation and
\end{comment}

Because convolution is a linear operation on functions, the following equation can be obtained by adding all $n$ instances of Eq.~(\ref{mainconv}):
\begin{equation} (f_A * \delta_X)(H) = (\delta_X * f_B)(H) \label{mainconvall} \end{equation}
where $$ f_A(H) = \frac{1}{n} \sum_{i=1}^{n} \delta(A_i^{-1} H) \,\,\, {\rm and} \,\,\, f_B(H) = \frac{1}{n} \sum_{i=1}^{n} \delta(B_i^{-1} H). $$
The above functions can be normalized
to be probability densities:
$$ \int_{SE(3)} f_A(H) dH = \int_{SE(3)} f_B(H) dH = 1. $$
See the Appendix for a review of the properties of integration on $SE(3)$.

Let the mean and covariance of a probability density \textcolor{blue}{function} $f(H)$ be defined by the following conditions:
\begin{equation} \begin{split} &\int_{SE(3)} \log(M^{-1} H) f(H) dH = \mathbb{O} \,\,\, {\rm and} \,\,\,\\ &\Sigma = \int_{SE(3)} \log^{\vee}(M^{-1} H) [\log^{\vee}(M^{-1} H)]^T  f(H) dH . \end{split}\label{meancovdef} \end{equation}
If $f(H)$ is of the form of $f_A(H)$ given above, then
\begin{equation} \
\begin{split} &\sum_{i=1}^{n} \log(M_A^{-1} A_i) = \mathbb{O} {\rm \,\,\,\,\, and} \\
&\Sigma_A = \frac{1}{n} \sum_{i=1}^{n} \log^{\vee}(M_A^{-1} A_i) [\log^{\vee}(M_A^{-1} A_i)]^T.  \label{datameancovconvdef} \end{split}
\end{equation}

It can be shown that if these quantities are computed for two highly-focused functions, $f_1$ and $f_2$, that the same quantities for
the convolution of these functions can be closely approximated as \cite{Wang08}:
\begin{equation}
M_{1*2} = M_1 \, M_2 \,\,\, {\rm and} \,\,\, \Sigma_{1*2} = Ad(M_2^{-1}) \,\Sigma_{1}\, Ad^T(M_2^{-1}) + \Sigma_{2}
\label{meancovconvdef} \end{equation}
where \textcolor{blue}{Why not use a \~x to be consistent with your other notation?}
\begin{equation} 
Ad(H) = \left(\begin{array}{ccc}
R && \mathbb{O} \\
\widehat{{\bf x}} R && R \end{array}\right) 
\label{adjdef} \end{equation}
and $\widehat{{\bf a}}$ is the skew-symmetric matrix such that $\widehat{{\bf a}} {\bf b} = {\bf a} \times {\bf b}$.

The mean of $\delta_X(H)$ is $M_X = X$, and its covariance is the zero matrix.
Therefore, Eq.~(\ref{mainconvall}) together with Eq.~(\ref{meancovconvdef}) yields two ``Batch Method" equations:
\begin{equation}
\boxed{\,
M_A \, X = X \, M_B
\,}
\label{mainmain11} \end{equation}
and
\begin{equation}
\boxed{\,
Ad(X^{-1}) \, \Sigma_{A} \, Ad^T(X^{-1}) = \Sigma_{B}
\,}
\label{mainmain12} \end{equation}
In Section~\ref{sec:batch_meth_sol}, it will be shown how $X$ can be recovered using Eq.~(\ref{mainmain11}) and Eq.~(\ref{mainmain12}).

\subsubsection{A Batch Method Solution}
\label{sec:batch_meth_sol}
Starting with Eq.~(\ref{mainmain11}), the solution space of $X$ can be defined as a cylinder. Specifically Eq.~(\ref{mainmain11}) can be rewritten as:

\begin{equation}
\log^{\vee}(M_A)  = Ad(X) \,\log^{\vee}(M_B).
\label{mainmain1rewrite} \end{equation}

In the case of general $M_A$ and $M_B$ (i.e. not degenerate cases in which the rotation angle\footnote{This angle is computed from the Frobenius norm $\theta_A =\|\half \log R_A\| = \|\half \log R_B\|= \theta_B$.} is outside of the range
$(0,\pi)$), the solution space of all possible $X$s that satisfy this equation is known to be two-dimensional.
This can be seen by defining
$$ \log^{\vee}(M) = \left(\begin{array}{c}
\omega \\
{\bf v} \end{array} \right)
=\left(\begin{array}{c}
\theta \, {\bf n} \\
{\bf v} \end{array} \right), $$
where ${\bf \omega} \in \mathbb{R}^3$ and ${\bf v} \in \mathbb{R}^3$ are the elements of the Lie algebra, and writing the rotation and translation parts of Eq.~(\ref{mainmain1rewrite}) separately,
\textcolor{blue}{Again, throughout this section I would think about using consistent notation. Don't use hat some places and tilde in other places.}
\begin{equation}
{\bf n}_A = R_X {\bf n}_B \hspace{5mm}\mbox{and}
\label{nanb} \end{equation}
\begin{equation}
{\bf v}_A = \theta_B \widehat{\,{\bf t}_X} R_X {\bf n}_B + R_X {\bf v}_B.
\label{vavb} \end{equation}
The first of these equations has a one-dimensional solution space of the form
$R_X = R({\bf n}_A, {\bf n}_B) R({\bf n}_B, \phi)$ where $\phi \in [0,2\pi)$ is free and
$R({\bf n}_A, {\bf n}_B)$ is any rotation matrix that rotates the vector ${\bf n}_B$ into ${\bf n}_A$.
In particular, choose
\begin{equation}
R({\bf n}_A, {\bf n}_B)  \,=\,
\II \,+\, \widehat{{\bf n}_B \times {\bf n}_A}
\,+\, \frac{(1- {\bf n}_B \cdot {\bf n}_A)}{\|{\bf n}_B \times {\bf n}_A\|^2} \, \left(\widehat{{\bf n}_B \times {\bf n}_A}\right)^2.
\label{transab}
\end{equation}
The rotation $R({\bf n}_B, \phi)$ is given by \textcolor{blue}{Rodrigues' Formula?} Euler's formula:
$$ R({\bf n}_B, \phi) = \II \,+\, \sin \phi \, \widehat{\,{\bf n}_B} \,+\, (1-\cos \phi)\, \left(\widehat{\,{\bf n}_B}\right)^2. $$

Substituting $R_X = R({\bf n}_A, {\bf n}_B) R({\bf n}_B, \phi)$ into Eq.~(\ref{vavb}) and rearranging terms, we obtain:
\begin{equation}
\frac{R({\bf n}_A, {\bf n}_B) R({\bf n}_B, \phi) {\bf v}_B - {\bf v}_A}{\theta_B} = \widehat{\, {\bf n}_A} {\bf t}_X.
\label{transcon} \end{equation}
The skew-symmetric matrix $\widehat{\, {\bf n}_A}$ has a rank of 2, so a free translational degree of freedom exists in ${\bf t}_X$ along the ${\bf n}_A$ direction. ${\bf t}_X$ can thus be described as:
\begin{equation}
{\bf t}_X =  {\bf t}(s) = s \, {\bf n}_A + a \, {\bf m}_A + b \, {\bf m}_A \times {\bf n}_A
\label{transparam} \end{equation}
where $s \in \mathbb{R}$ is a second free parameter, ${\bf m}_A$ and ${\bf m}_A \times {\bf n}_A$ are
defined to be orthogonal to ${\bf n}_A$ by construction. If
${\bf n}_A  = [n_1, n_2, n_3]^T$ and $n_1, n_2$ are not simultaneously zero, then one can define\footnote{The special case when they are simultaneously zero
is a set of measure zero, and hence is a rare event. Nevertheless, it is easy to handle, since in this case $R_A$ is necessarily a rotation around ${\bf e}_3$.}
$$ {\bf m}_A \doteq \frac{1}{\sqrt{n_1^2 + n_2^2}} \left(\begin{array}{c}
-n_2 \\
n_1 \\
0 \end{array}\right).
$$
The coefficients $a$ and $b$ are then computed by substituting Eq.~(\ref{transparam}) into Eq.~(\ref{transcon}) and using the fact that
$\{{\bf n}_A, {\bf m}_A, {\bf n}_A \times {\bf m}_A\}$ is an orthonormal basis for $\mathbb{R}^3$. Explicitly,
$$ a = - \left(\frac{R({\bf n}_A, {\bf n}_B) R({\bf n}_B, \phi) {\bf v}_B - {\bf v}_A}{\theta_B}\right) \cdot \left({\bf m}_A \times {\bf n}_A\right) \hspace{5mm}\mbox{and}$$
$$ b =\left(\frac{R({\bf n}_A, {\bf n}_B) R({\bf n}_B, \phi) {\bf v}_B - {\bf v}_A}{\theta_B}\right)\cdot {\bf m}_A . $$
This means that the feasible solutions can be completely parameterized as:
\begin{equation}
X(\phi,s) = H(R({\bf n}_A, {\bf n}_B) R({\bf n}_B, \phi), {\bf t}(s))
\label{cylinder} \end{equation}
where $(\phi, s) \in [0,2\pi) \times \IR$.

To provide the additional constraints needed to solve for $X$, decompose $\Sigma_{A}$ and $\Sigma_{B}$ into blocks as:
$$ \Sigma_{i}= \left(\begin{array}{ccc}
\Sigma_{i}^1 && \Sigma_{i}^2 \\
\Sigma_{i}^3 && \Sigma_{i}^4  \end{array}\right)
$$
where $\Sigma_{i}^3 = (\Sigma_{i}^2)^T$, then take the first two blocks of Eq.~(\ref{mainmain12}) and write:
\begin{equation}
\begin{split}
&\Sigma_{M_B}^1 =  R^T_X \Sigma_{M_A}^1 R_X {\rm \,\,\, and \,\,\,} \\
&\Sigma_{M_B}^2 =  R^T_X \Sigma_{M_A}^1 R_X(\widehat{R^T_X t_x}) + R^T_X \Sigma_{M_A}^2 R_X \label{set1}.
\end{split}
\end{equation}

Calculate the eigendecomposition as $ \Sigma_{i}=Q_i \Lambda Q_i^T$, where $Q_i$ is the square matrix whose $i$th column is the eigenvector of $\Sigma_i$ and $\Lambda$ is the diagonal matrix with corresponding eigenvalues as diagonal entries \textcolor{blue}{Note: For this specific decomposition, you have to require that $\Sigma$ is real symmetric, you may have qualified this earlier, but double check}. Write the first block of Eq.~(\ref{set1}) as \cite{ackermanGSI, ackermanIROS2013}:
\begin{align}
\Lambda &= Q_{M_B}^T R_X^T Q_{M_A} \Lambda Q_{M_A}^T R_X Q_{M_B} = {\cal Q} \Lambda {\cal Q}^T.
\label{QAQ}
\end{align}

\begin{comment}
{\color{red} {\color{blue}This is something new that can be served as a complement in the review of batch method.}
When $Q$ is constrained to be a rotation matrix. Eq.(\ref{QAQ}) can be further be written as:
\begin{equation}
\Lambda Q = Q \Lambda.
\end{equation}
This is the same to say that $Q$ commutes with a diagonal matrix $\Lambda$, which forces $Q$ to be block conformal to $\Lambda$. If we further assume that $\Lambda$ does not have repeated diagonal entries, then $Q$ will be constrained to be a diagonal matrix in order to be block conformal to $\Lambda$.} 
\end{comment}

The set of ${\cal Q}$s that satisfy this equation are given as:
\begin{equation}
\begin{split}
{\cal Q} = \left\{ \left(\begin{array}{ccc}
1\,\, & 0 \,\, & 0 \,\, \\
0 & 1 & 0\\
0 & 0 & 1 \end{array}\right) , \left(\begin{array}{ccc}
-1 & 0 & 0 \\
0 & -1 & 0\\
0 & 0 & 1 \end{array}\right), \right.\\
\left. \left(\begin{array}{ccc}
-1 & 0 & 0 \\
0 & 1 & 0\\
0 & 0 & -1 \end{array}\right), \left(\begin{array}{ccc}
1 & 0 & 0 \\
0 & -1 & 0\\
0 & 0 & -1 \end{array}\right)\right\}
\end{split} 
\label{qset}
\end{equation}
This means that the rotation component of $X$ is given by:
\begin{equation}
R_x=Q_{M_A}\,{\cal Q}\,Q_{M_B}^T.
\label{RQ}\end{equation}
When $\Lambda$ has repeated entries, a continuum of symmetries result. For example, in the extreme case when $\Lambda = \lambda \mathbb{I}_3$, the
finite set ${\cal Q}$ would be replaced by $SO(3)$, which is the same as saying that the first equation in Eq.~(\ref{set1}) imposes no constraint. In general, it is possible to construct trajectories that define the sets $\{A_i\}$ and $\{B_j\}$ such that this does not happen, and so the Batch method limits the discussion to the case where Eq.~(\ref{qset}) holds.

Once the four possibilities of $R_X$ are found in this manner, the corresponding possible ${\bf t}_X$ can be found easily from blocks 2 and 4 of in Eq.~(\ref{set1})(b). \textcolor{blue}{Fix Eq. 63 to actually have (a) and (b) labels}

The correct solution, from the set of 4 possibilities (given Eq.~(\ref{RQ})), can be found by applying the cylindrical constraints as in Eq.~(\ref{nanb}) and Eq.~(\ref{vavb}). This is achieved by choosing the \textcolor{blue}{Q?} %possibility 
that minimizes a cost function, such as $\| {\bf n}_{M_A}-R_X {\bf n}_{M_B} \|+w \| {\bf v}_{M_A} - \theta_{M_B} \widehat{\,{\bf t}_X} R_X {\bf n}_{M_B} + R_X {\bf v}_{M_B} \|$
where $w$ is an appropriately chosen weighting factor, and in this case, it is chosen to be unity.

\section{DATA SELECTION AND ERROR METRICS}
\label{sec:data_selection}
When performing hand-eye calibration in experiments, the accuracy of the calibrated $X$ is highly dependent on the data that is obtained in the process. Tsai and Lenz \cite{tsai1989new} proposed several principles on designing the movement of the robot. This is useful when the motion planning under these constraints is practical.  However, data selection has to be considered when such movement is not applicable, such as when there is a lack of free space or a hand-held sensor is used. In this section, several principles and methods for data selection are reviewed. In addition, different error metrics are also discussed to give a more complete picture of the $AX=XB$ problem.

\label{qianli-numerical}
\subsection{Data Selection}
Selection of well defined $(A_i,B_i)$ is very important for the $AX=XB$ solvers. Data selection methods for off-line application have been proposed in \cite{vogt2004vector,schmidt2008data,ackermanIROS2013}, and corresponding selection techniques for on-line solvers are introduced in \cite{shi2005approach,zhang2005adaptive}. For probabilistic methods, data sets $\{A_i\}$ and $\{B_i\}$ must be highly concentrated, which means small and relative motions are preferable \cite{ackermanGSI}. This is opposite to the data selection criterion of other non-probabilistic approaches.

To determine the hand-eye transformation, at least 2 non-parallel rotation axes from the data pairs are needed (which is also referred at the non-parallelism criterion), and further data selection algorithms are all built on top of this.

In the error analysis of \cite{tsai1989new}, four observations are given to show the relationships between the errors in rotation and translation and the features of the robot motions. In addition, seven steps are suggested to improve the calibration accuracy. Shi {\it{et al.}} \cite{shi2005approach} developed a motion selection algorithm based on three out of the four observations in \cite{tsai1989new}. However, the thresholds in \cite{shi2005approach} are chosen in a heuristic manner. To fix this problem,  Zhang {\it{et al.}} \cite{zhang2005adaptive} proposed an adaptive selection method which can update the thresholds online. All of the above approaches share some common standards such that small relative rotations between $(A_i, B_i)$ and $(A_{i+1}, B_{i+1})$ should be avoided, and the rotation angles for both $\{A_i\}$ and $\{B_i\}$ should be large enough to avoid the singularity of the representation. The Kronecker product method, however, has a tolerance on small robot motions as pointed out in Section~\ref{sec:Kronecker}. It also offers an algebraic analysis to show what information of $X$ can be obtained using certain types and numbers of motions. Interesting results are: (1) three independent pure translations can fully define $R_X$ but not $\ttt_{X}$; (2) with two or more independent pure rotations, both $R_{X}$ and $\ttt_{X}$ can be recovered. A more detailed summary can be seen in Table 1 of \cite{andreff1999line}. Schmidt {\it{et al.}} \cite{schmidt2003robust} discussed data selection for the dual quaternion hand-eye calibration algorithm based on a RANSAC approach, which shows that the dual quaternion method can give a better $X$ after data selection, while the algorithm can even fail otherwise. \textcolor{blue}{Note: Explanation the previous sentence better} However, the computation of all possible relative movements from the data set results in a long computational time.

\textcolor{blue}{I added a paragraph separation , seemed like a long wall of text}

For a set of continuous robot motions, a sequence of images or sensor recorded information will be obtained. But due to the small differences between consecutive images or sensor recordings, it is often undesirable to process the data in the temporal order because this can yield high errors. Schmidt {\it{et al.}} \cite{vogt2004vector} then proposed a vector quantization based data selection technique which selects a globally consistent set of motions that optimizes the non-parallelism criterion. The main idea is to select a subset of the given rotation axes of $(A_i, B_i)$ using clustering algorithms. It is shown that compared to the above two approaches, the algorithm presented is both fast and accurate. Ackerman {\it{et al.}} \cite{ackermanIROS2013} also proposed a method which uses the Euclidean group invariants in the structure of $\{A_i\}$ and $\{B_i\}$ to realign asynchronous data streams.

\subsection{Error Metrics}
There are multiple ways to define the errors of rigid body transformations, and some methods rely heavily on the metric that is chosen in \cite{strobl2006optimal}. One approach is to measure the errors of $R_{x}$ and ${\bf t}_{X}$ simultaneously which is rarely seen in more recent literature. The other approach is to measure the rotation error and translation error separately. 
\subsubsection{ Metrics for Rotation and Translation Errors}
Various metrics for rotation error have been used in the literature. In \cite{tsai1989new} and \cite{horaud1995hand}, the matrix error metric is defined as: 
\begin{equation}
E_{rot} \doteq \| R_{X_{true}} - R_{X_{calc}} \|.
\end{equation}
However, this is less preferable because rotation matrices lie in $SO(3)  $ and the deduction operation is not defined for $SO(3)$.
In \cite{daniilidis1999hand} and \cite{andreff1999line}, the quaternion error metric is used as:
\begin{equation}
E_{rot} \doteq \|{\bf q}_{X_{true}} - {\bf q}_{X_{calc}}\|.
\end{equation}
As noted in \cite{daniilidis1996dual}, $\| R_{X_{true}} - R_{X_{calc}}\|_F$ is $2\sqrt{2}$ times larger than $\|{\bf q}_{X_{true}} - {\bf q}_{X_{calc}} \|$ so it is important to maintain a consistent error metric especially for result comparisons. 
Another \textcolor{blue}{rotational error metric} %way
 is to calculate the norm of the relative rotation between $X_{true}$ and $X_{calc}$ as:
\begin{equation}
E_{rot} \doteq \|R^{T}_{X_{true}}R_{X_{calc}}\|.
\end{equation} 
In \cite{ackermanGSI}, the Lie algebra error metric is defined for the relative rotation $R^{T}_{X_{true}}R_{X_{calc}}$ as:
\begin{equation} 
E_{rot} \doteq \|\log^{\vee}(R_{X_{true}}^TR_{X_{calc}})\|.
\label{RotError}
\end{equation}

Metrics for the translation error are relatively simple because translation lies in Euclidean space. A common method is to use the relative translation error to eliminate the influence of the translation unit:
\begin{equation}
E_{tran} \doteq \dfrac{\|\ttt_{X_{true}}-\ttt_{X_{calc}}\|_{2}}{\|\ttt_{X_{true}}\|_{2}}.
\label{TranError}
\end{equation}
Conventionally, multiple trials are performed at each fixed noise level in numerical simulation, and the ``averaged'' errors in rotation and translation are defined in \cite{horaud1995hand} as:
\begin{equation}
e_{rot} \doteq \sqrt{\dfrac{1}{N}\sum_{i=1}^{N} E_{rot}^2},
\end{equation}
\begin{equation}
e_{tran} \doteq \sqrt{\dfrac{1}{N}\sum_{i=1}^{N} E_{tran}^2}.
\end{equation}

It should be noted due to the diversity of rotation error metrics, it is yet to be seen which metric is better or whether different metrics make a difference at all.

\begin{comment}
Furthermore, we compared the accuracy of the 4 methods by calculating their error covariance matrices $^e\Sigma$, which is defined as:
\begin{equation}
^e\Sigma \doteq \sum_{i = 1}^{n}K_{i}K_{i}^{T} \in \mathbb{R}^{6 \times 6}.
\end{equation}
where $K_{i} = \log^{\vee}(A_{i}) - Ad(X_{calc})\log^{\vee}(B_{i})$.
%\begin{figure}[h]
%\includegraphics[scale=0.5]{figure/traceCov}
%\centering
%\label{fig:Trace}
%\caption{Trace of the Error Covariance Matrix}
%\end{figure}
The error covariance matrix $^e\Sigma$ can provide information about the variances of the independent and correlated error on each basis of Lie algebra. 
\end{comment}

\begin{comment}
\subsection{$\{A_{i}, B_{i}\}$ Pairs Generation}
There are various ways of generating noisy $\{A_{i},B_{i}\}$ pairs and different data sets can cause certain methods to perform badly or even to crash. To simulate different $AX=XB$ solvers with synchronous noisy $\{A_{i},B_{i}\}$ pairs, we first generate $B_{i}$ by randomly sampling the Lie algebra of matrix $B_{i}$, and then recover $B_{i}$ using the matrix exponential as shown below:
\begin{equation}
B_{i} = \exp \left(
\begin{array}{ccc}
\Omega_{i}  & & {\bf v_{i}}  \\ \\
{\bf 0}^T & & 0 \end{array}
\right).
\end{equation} 
Next, the noisy $A_{i}$ is obtained by $A_{i}= ^1\hspace{-0.05in}X_{i}\,\,B_i\,\,^2X_{i}^{-1}$ where $^1X_{i}$ and $^2X_{i}$ are calculated by applying small disturbances on the ground truth $X_{true}$: 
\begin{equation}
^mX_{i} = X_{true}\exp \left(
\begin{array}{ccc}
^m\Omega_{X_{i}}  & & ^m{\bf v}_{X_{i}}  \\ \\
{\bf 0}^T & & 0 \end{array}
\right)
\; \;
\text{where} \; \; m = 1,2
\label{X_disturb}
\end{equation}
where $\omega_{X_{i}}$ and ${\bf v}_{X_{i}}$ are drawn from independent Gaussian distributions. In order to test the sensitivity to different noise levels for each $AX=XB$ solver, we choose the mean of $\left(\omega_{X_{i}}^{T}, {\bf v}_{X_{i}}^{T}\right)^{T}$ to be ${\bf 0}_{6 \times 1}$ and its covariance matrix to be $\Sigma_{X_{i}} = \sigma^{2} \mathbb{I}_{6}$ with $\sigma$ ranging from 0 to 0.1.
\end{comment}

\begin{comment}
%-------------------------------------------------
\section{NUMERICAL SIMULATION}
In this section, we numerically simulated the Lie group method, the Kronecker product method, the quaternion method, and the dual quaternion method in Matlab  to compare the errors in both $R_{X}$ and $t_{x}$ with respect to different noise levels on $\{A_{i}, B_{i}\}$.

The numerical simulation results are presented in Fig.\ref{roterror}, Fig.\ref{transerror}, and Fig.\ref{traceerror}. Figure \ref{roterror} shows that as the noise level $\sigma$ increases, Lie group method shows the least increase in rotation error, while the dual quaternion method's increase in the rotation error is the largest. The rotation errors of the Kronecker method (light blue line) and the quaternion method (dark blue line) are pretty close and they are even closer in terms of translational error (figure \ref{transerror}).
\end{comment}

\begin{comment}
\begin{figure}[h]
\includegraphics[width=3.3in]{figure/rotErrorRand}
\centering
\caption{Rotation Error v.s. Noise Level using Lie algebra Error Metric }
\label{roterror}
\end{figure}

{\color{blue} Lie$^{\star}$ is an improved version of the original Lie group method where ill-conditioned $\{A_{i},B_{i}\}$ pairs are eliminated to solve for the estimated $X$. This is due to the limitation of algorithm that $A_{i}$ or $B_{i}$ whose trace is equal or very close to -1 will cause the singularity of numerical computation. Different ways of generating $\{A_{i},B_{i}\}$ can affect the number of filtered pairs and certain ways can render the Lie group method giving $R_{X}$ with $\det(R_{X}) = -1$.\\

Dual Quat$^{\star}$ is an improved version of the original dual quaternion method which also eliminates certain $\{A_{i},B_{i}\}$ pairs by putting a boundary on the scalar parts of the dual quaternions of $A_{i}$ and $B_{i}$. Similar to the Lie group method, the way of generating $\{A_{i},B_{i}\}$ pairs can affect the number of filtered data, and this will affect the accuracy of the estimated $X$. In addition, certain ways of generating the data pairs can cause the dual quaternion method to give an invalid result from the filtered data. This problem can be solved by extracting a smaller portion of the given $\{A_{i},B_{i}\}$ pairs, but this also can degrade the accuracy of the result.  
\begin{figure}[h]
\includegraphics[width=3.3in]{figure/tranErrorRand}
\centering
\caption{Translation Error with Randomly Generated AB Pairs (with the improved Lie and Dual Quaternion methods)}
\label{transerror}
\end{figure}

\begin{figure}[h]
\includegraphics[width=3.3in]{figure/traceCovRand}
\centering
\caption{Trace of the Error Covariance Matrix}
\label{traceerror}
\end{figure}

In general, all of the traditional methods work well with near random Gaussian distributed noisy $\{A_{i},B_{i}\}$ pairs. However, it should be noted that in many applications, the information of $\{A_{i},B_{i}\}$ is obtained by moving the calibration sensor along a trajectory. Depending on the specifics of the trajectory as well as on the sample rate along the trajectory, the data may become ill conditioned for these methods.}
\end{comment}

%\begin{equation}
%\Sigma_{M_B}^3 =  (\widehat{-R^T_X t_x}) R^T_X \Sigma_{M_A}^1 R_X  +  R^T_X \Sigma_{M_A}^3 R_X
%\end{equation}
%\begin{align}
%\Sigma_{M_B}^4 &= -(\widehat{R^T_X t_x}) R^T_X \Sigma_{M_A}^1 R_X -(\widehat{R^T_X t_x})^T +  R^T_X \Sigma_{M_A}^3 R_X \nonumber \\
%&-(\widehat{R^T_X t_x})^T +  (\widehat{-R^T_X t_x}) R^T_X \Sigma_{M_A}^2 R_X + R^T_X \Sigma_{M_A}^4 R_X
%\end{align}

\begin{comment}
\subsection{Identities of Means and Covariances of Pdfs on SE(3)}
In this section we will prove two identities related to the mean and covariance of probability distributions on $SE(3)$ that will become useful to expand elements of the previously presented batch method.

\begin{theorem} \label{thm1}
If $M$ and $\Sigma$ are respectively the mean and covariance of $f(H)$, then
$M^{-1}$ and $Ad(M) \Sigma Ad^T(M)$ are respectively the mean and covariance of $f(H^{-1})$.
\end{theorem}

\begin{proof}
Let $f'(H) = f(H^{-1})$, and then $M'$ and $\Sigma'$ are the mean and covariance of $f'(H)$ satisfying the defining equations:
\begin{equation}
\begin{split}
&\int_{SE(3)} \log({M'}^{-1} H) f'(H) dH = \mathbb{O} \\
&\Sigma' = \int_{SE(3)} \log^{\vee}({M'}^{-1} H) [\log^{\vee}({M'}^{-1} H)]^{T}  f'(H) dH. 
\end{split}
\label{fprime}
\end{equation}
The first of Eq.(\ref{fprime})  can be rewritten as:
\begin{equation}
\int_{SE(3)} \log({M'}^{-1} H) f(H^{-1}) dH = \mathbb{O}
\label{f_prime_mean}
\end{equation}
By changing the variable $K = H^{-1}$ and using the invariance of integration under inversion (as described in the Appendix), Eq.(\ref{f_prime_mean}) can be written as:
$$ \int_{SE(3)} \log({M'}^{-1} K^{-1}) f(K) dK = \mathbb{O}. $$
Multiplying this equation on the left by $M'$ and on the right by ${M'}^{-1}$, and using the general property that
$$ H_1 (\log H_2) H_1^{-1} = \log (H_1 H_2 H_1^{-1}), $$
we get 
$$ \int_{SE(3)} \log(K^{-1} {M'}^{-1}) f(K) dK = \mathbb{O} $$
which is equivalent to 
$$ \int_{SE(3)} \log(({M'} K)^{-1} ) f(K) dK = \mathbb{O}. $$
But since
$$ \log (H^{-1}) = -\log H, $$
this means that
$$ \int_{SE(3)} \log( {M'} K) f(K) dK = \mathbb{O}, $$
and from the definition of mean, it must be that $M' = M^{-1}$.\\
Similarly, 
$$ \Sigma' = \int_{SE(3)} \log^{\vee}({M'}^{-1} H) [\log^{\vee}({M'}^{-1} H)]^{T}  f(H^{-1}) dH $$
which, under change of variables and substitution of $M' = M^{-1}$, becomes
$$ \Sigma' = \int_{SE(3)} \log^{\vee}(M K^{-1}) [\log^{\vee}(M K^{-1})]^{T}  f(K) dK. $$
But since by definition 
$$ Ad(H_1) \log^{\vee}(H_2) = \log^{\vee} (H_1 H_2 H_1^{-1}), $$
$$ Ad(M^{-1}) \Sigma' Ad^T(M^{-1}) = $$
$$ \int_{SE(3)} \log^{\vee}(K^{-1} M) [\log^{\vee}(K^{-1} M)]^{T}  f(K) dK .$$
Using $\log^{\vee}(K^{-1} M) = - \log^{\vee}(M^{-1} K)$ then gives
$$ Ad(M^{-1}) \Sigma' Ad^T(M^{-1}) = \Sigma $$
which, after inversion of the Ad matrices, completes the proof.
\end{proof}

It is also interesting to note that if $A_i X = X B_i$, then $(A_i X)^{-1} = (X B_i)^{-1}$ and rearranging gives 
$A_{i}^{-1} X = X B_{i}^{-1}$. This means that if we wish to, we can double the size of
the sets $A = \{A_i\}$ and $B=\{B_j\}$ by including the inverses of each entry in these sets. The consequence of this along with the fact that 
$$ f_{A^{-1}}(H) = f_A(H^{-1}) $$ 
provides a pdf describing incoming data of the form:
$$ \tilde{f}_A(H) \doteq \half (f_A(H) + f_A(H^{-1})) $$
and similar pdf can be obtained for $B$. These pdfs are ``symmetric functions'' in the sense that
$$ \tilde{f}_A(H) = \tilde{f}_A(H^{-1}) $$
and this has consequences that can be useful, as described in the following theorem.

\begin{theorem}
\label{thm2}
If $f_B(H) \in (L^1 \cap L^2)(SE(3))$ is a symmetric function and $K \in SE(3)$ and $f_X \in (L^1 \cap L^2)(SE(3))$ are arbitrary, then: \\
(a) $f_B(H)$ has its mean at the identity \\
(b)  $(f_X * f_B* f_{X^{-1}})(H)$ has its mean at the identity \\
(c) $f_B(K^{-1} H K)$ has its mean at the identity.
\end{theorem}

\begin{proof}
(a) By definition of mean on $SE(3)$,
$$ \int_{SE(3)} \log (M_B^{-1} H) f_B(H) dH = \mathbb{O} $$
and so
$$ \int_{SE(3)} \log (M_B^{-1} H) f_B(H^{-1}) dH = \mathbb{O}.$$
Let $K = H^{-1}$, and use the same operations as in Theorem \ref{thm1}, we arrive at
$$ \int_{SE(3)} \log (M_B K) f_B(K) dK = \mathbb{O}, $$
indicating that if $M_B$ is unique, then $M_B = M_B^{-1}$ and so $M_B = \mathbb{I}$.
Uniqueness can be guaranteed if $\Sigma$ is sufficiently small, which in turn can be guaranteed in our application if all samples $\{A_i\}$ and $\{B_j\}$ are replaced
by fractional powers $\{A_i^{1/n}\}$ and $\{B_j^{1/n}\}$.

(b) By definition, $M$, the mean of $(f_X * f_B* f_{X^{-1}})(H)$ must satisfy
$$ \int_{SE(3)} \log (M^{-1} H) (f_X * f_B* f_{X^{-1}})(H) dH = \mathbb{O}. $$
By showing that $(f_X * f_B* f_{X^{-1}})(H)$ is symmetric, the fact that $M = \mathbb{I}$ will follow from (a).
Using the definition of the convolution integral given in the Appendix, and expanding out both convolutions, we have:
\begin{equation}
\begin{split}
& (f_X * f_B* f_{X^{-1}})(H)\\
= &\int_{SE(3)} \int_{SE(3)}
f_X(J) f_B(J^{-1} K) f_{X^{-1}}(K^{-1} H) dJ dK
\\
= &\int_{SE(3)} \int_{SE(3)} f_{X^{-1}}(J^{-1}) f_B(K^{-1} J) f_{X}(H^{-1} K) dJ dK
\end{split}
\end{equation}
Here we have used the fact that $f_B$ is symmetric. By the same logic,
\begin{eqnarray*}
&& (f_X * f_B* f_{X^{-1}})(H^{-1}) = \\
&& \int_{SE(3)} \int_{SE(3)}
f_X(J') f_B(J'^{-1} K') f_{X^{-1}}(K'^{-1} H^{-1}) dJ' dK'
\end{eqnarray*}
We have the freedom to define $J'=H^{-1} K$ and $J^{-1} = K'^{-1} H^{-1}$.
The proposition will then be true if the remaining term,
$K^{-1} J = J'^{-1} K'$, holds. Indeed,
$$ J'^{-1} K' = (H^{-1} K)^{-1} H^{-1} J = K^{-1} J, $$
completes the proof of (b). Finally, (c) follows from (b) by letting $f_X(H) = \delta_K(H)$.
\end{proof}

\subsection{Batch Method Results}
To verify that this solution method produces a useful $X$, we used a numerical approach to simulate the $AX=XB$ problem by generating simulated $A$ and $B$ data streams. As is commonly done in the literature, and previously discussed in section \ref{qianli-numerical}, we generate the $\{B_{i}\}$ by randomly sampling each of the elements of the Lie algebra from a gaussian distribution of set mean and variance, and then matrix $B_{i}$ is recovered using matrix exponential. We then generate the noisy $A_{i}$ by $A_{i}= ^1\hspace{-0.05in}X_{i}\,\,B_i\,\,^2X_{i}^{-1}$ where $^1X_{i}$ and $^2X_{i}$ are given by exerting small disturbances on the same known $X_{true}$.

In Fig.\ref{normerror} and Fig.\ref{normerrorsym}, we show the performance of the Batch Method on simulated data. It should be noted that for case with the symmetrized data, the correct batch method solution, from the set of 4 possibilities (given (\ref{RQ})) can no longer be found by applying the cylinder constraints (as previously discussed). This is due to the fact that $M_A=M_B=\mathbb{I}$ for symmetrized data. However, we can still choose the correct $X$ by selecting one among the four candidates which minimizes the previously described objective function, $\| {\bf n}_{M_A}-R_X {\bf n}_{M_B} \|+w \| {\bf v}_{M_A} - \theta_{M_B} \widehat{\,{\bf t}_X} R_X {\bf n}_{M_B} + R_X {\bf v}_{M_B} \|$, by using the non-symmetrized data. The metric used for both cases is the relative normed error between the calculated solution $X_{calc}$ and the true solution $X_{true}$:

$$
E_{X} = \frac{\|X_{calc}-X_{true}\|}{\|X_{true}\|}.
$$

\begin{figure}[h]
\includegraphics[width=3.3in]{figure/normerror}
\centering
\caption{Performance of the Batch Method at Various Noise Levels}
\label{normerror}
\end{figure}

\begin{figure}[h]
\includegraphics[width=3.3in]{figure/normerrorsym}
\centering
\caption{Performance of the Batch Method at Various Noise Levels for Symmeterized Data}
\label{normerrorsym}
\end{figure}

It is observed that symmetrized data provides, to a degree, a better solution of $X$. Additionally, symmetrizing the data provides more $\{A, B\}$ pairs, which will become important for methods described in the following sections.

\section{THE EXPANDED BATCH METHOD (THE CASE OF NOISY A's)} \label{batchnoise}

When the sensor that generates $B=\{B_j\}$ is accurate and there is significant
measurement noise in the set $A = \{A_i\}$, a single $X$ will not solve every instance of Eq.(\ref{main}) and hence the delta function in Eq.(\ref{mainconvall}) 
will not solve the problem. Instead, we seek a distribution $f_X(H)$ with (a priori unknown) mean $M_X$ and covariance $\Sigma_X$.

We can re-write Eq.(\ref{main}) as
\begin{equation} A_i = X B_i X^{-1} \label{main2} \end{equation}
and in a similar fashion as in Eq.(\ref{mainconvall}),we can write the probabilistic form of Eq.(\ref{mainconvall}) as
\begin{equation} f_A(H) = (f_X * f_B* f_{X^{-1}})(H). \label{mainconvallwnoise2} \end{equation}

In the subsections that follow, we derive the conditions on the mean and covariance of $f_X$ and
develop numerical methods for solving for these quantities.

\subsection{Conditions on $M_X$ and $\Sigma_X$}
Using the associativity of convolution, $f_X * f_B* f_{X^{-1}} = f_X * (f_B* f_{X^{-1}})$, 
and applying Eq.(\ref{meancovconvdef}) to Eq.(\ref{mainconvallwnoise2}) twice, we get
\begin{equation}
\boxed{\,
M_A = M_X \, M_B \, M_{X^{-1}}
\,}
\label{covprop2} \end{equation}
and
\begin{equation}
\begin{split}
\Sigma_{A} = Ad(M_{X})[Ad(M_{B^{-1}}) \Sigma_{X} Ad^T(M_{B^{-1}}) + \Sigma_{B}]Ad^T(M_{X})\\
+ \Sigma_{X^{-1}}.
\end{split}
\label{covprop22}
\end{equation}
Note that Eq.(\ref{covprop2}) and Eq.(\ref{covprop22}) are built on the use of (\ref{meancovconvdef}) twice so that they are approximations, unlike
Eq.(\ref{mainmain11}) and Eq.(\ref{mainmain12}) which are exact (by Theorem \ref{exactthm}). 
We can simplify this relationship in Eq.(\ref{covprop22}) by proving two identities related to the mean and 
covariance of probability distributions on $SE(3)$ given below.

As in the noise-free case, $(M_A,\Sigma_A)$ and $(M_B,\Sigma_B)$ are known from the data and are computed from
Eq.(\ref{datameancovconvdef}). The only difference is that now we seek $(M_X, \Sigma_X)$ instead of just $X$.

With these two properties, as well as the fact that $[Ad(H)]^{-1}=Ad(H^{-1})$, we can write Eq.(\ref{covprop22}) as:
\begin{flalign*}
\Sigma_A = &Ad(M_X) \, Ad(M_B^{-1}) \, \Sigma_{X} \, Ad^T(M_B^{-1}) \, Ad^T(M_X)\\
&+ Ad(M_X) \, \Sigma_{B} \, Ad^T(M_X) + Ad(M_X) \, \Sigma_{X}\, Ad^T(M_X), 
\end{flalign*}
or equivalently 
\begin{flalign*}
&Ad(M_X^{-1}) \, \Sigma_A \, Ad^T(M_X^{-1}) =\\
&Ad(M_B^{-1}) \, \Sigma_{X} \, Ad^T(M_B^{-1}) + \Sigma_{B} + \Sigma_{X}, 
\end{flalign*}
which leads to our final result 
\begin{equation}
\boxed{\,
\begin{split}
&\Sigma_{X} + Ad(M_B^{-1}) \, \Sigma_{X} \, Ad^T(M_B^{-1}) =\\
&Ad(M_X^{-1}) \, \Sigma_A \, Ad^T(M_X^{-1}) - \Sigma_{B}.
\end{split}
\,}
\label{covprop1112} \end{equation}
As in the noise-free case, $(A,\Sigma_A)$ and $(B,\Sigma_B)$ are known from the data and are computed from
Eq.(\ref{datameancovconvdef}). The only difference is that now we seek $(M_X, \Sigma_X)$ instead of just $X$.

\subsection{Computing $M_X$ and $\Sigma_X$}
From Eq.(\ref{covprop1112}), we can solve for $\Sigma_X$, given an $M_X$. This is done by taking the Kronecker product of both sides and writing
\begin{equation}
\begin{split}
[&Ad(M_B^{-1}) \otimes Ad(M_B^{-1}) + \mathbb{I}_{36}] {\rm vec}(\Sigma_X)\\
&= {\rm vec}(Ad(M_X^{-1}) \Sigma_{A} Ad^T(M_X^{-1}) - \Sigma_{B}),
\end{split}
\label{kroncovprop1112} \end{equation}
from which we obtain ${\rm vec}(\Sigma_X)$, and hence $\Sigma_X$.
Since $[Ad(M_B^{-1}) \otimes Ad(M_B^{-1}) + \mathbb{I}_6 \otimes  \mathbb{I}_6]$ in general will be non-singular, there is an exact solution of $\Sigma_X$ for every given $M_X$. This unique value of $\Sigma_X$ indicates the variation of $X$s, about the mean ($M_X$), needed to relate the sets of noisy data ($A$'s and $B$'s) in the $A_i=X_iB_iX_i^{-1}$ relationship. $\Sigma_X$ then becomes very useful for quantifying the``correctness" of a $M_X$. $\Sigma_{X_{calc}}$ is composed of the following variances on the values from the 6-dimensional Lie algebra,
\begin{equation}
\Sigma_{X_{calc}}=\left(
\begin{array}{cccccc}
\sigma_{\omega_1}^2 & \sigma_{\omega_1\omega_2} & \sigma_{\omega_1\omega_3} & \sigma_{\omega_1v_1} & \sigma_{\omega_1v_2} & \sigma_{\omega_1v_3}\\
\sigma_{\omega_2\omega_1} & \sigma_{\omega_2}^2 &\sigma_{\omega_2\omega_3} & \sigma_{\omega_2v_1} & \sigma_{\omega_2v_3} & \sigma_{\omega_2v_3}\\
\sigma_{\omega_3\omega_1} & \sigma_{\omega_3\omega_2} & \sigma_{\omega_3}^2 & \sigma_{\omega_3v_1} & \sigma_{\omega_3v_2} & \sigma_{\omega_3v_3}\\
\sigma_{v_1\omega_1} & \sigma_{v_1\omega_2} & \sigma_{v_1\omega_3} & \sigma_{v_1}^2 & \sigma_{v_1v_2} & \sigma_{v_1v_3}\\
\sigma_{v_2 \omega_1} & \sigma_{v_2 \omega_2} & \sigma_{v_2 \omega_3} & \sigma_{v_2 v_1} & \sigma_{v_2}^2 & \sigma_{v_2 v_3}\\
\sigma_{v_3 \omega_1} & \sigma_{v_3\omega_2} & \sigma_{v_3\omega_3} & \sigma_{v_3 v_1} & \sigma_{v_3 v_2} & \sigma_{v_3}^2\\
\end{array}\right).
\end{equation}
The information contained in $\Sigma_{X_{calc}}$ could be used to find the most favorable (least uncertainty in $X_{calc}$) directions for planning trajectories, sensor placement or other pose dependent tasks.

\subsection{Numerical Validation of $\Sigma_X$}
To verify that this formulation produced a meaningful $\Sigma_X$, we used a numerical approach that would allow us to, a prioir, know the true distribution of $X$. We simulate an $AX=XB$ calibration by generating simulated $A$ and $B$ data streams. The $B$s are chosen as poses along a trajectory in $SE(3)$. Since we must use relative motions, we generate $B^{ij}=B_i^{-1}B_{i+1}$ where $B_i$s are drawn from the two sample``s-shaped" trajectories on a sphere. After forming relative motions, $B_{ij}$'s, we calculate $A^{ij}= ^1\hspace{-0.05in}X_{ij}\,\,B_i\,\,^2X_{ij}^{-1}$, where $^1X_{ij}$ and $^2X_{ij}$ are drawn from a distribution with known mean ($X$) and covariance. Each calculation of $^kX_{ij}$ is tweaked as such:
\begin{equation} ^kX_{ij} \,\doteq\, X \,\, ^k\Delta_{ij} \label{noisybdef} \end{equation}
where $^k\Delta_{ij}$ is a matrix of small noises of the the form
$$ ^k\Delta_i \doteq
\exp \left(
\begin{array}{ccc}
\Omega (\delta t) & & {\bf v} (\delta t) \\ \\
{\bf 0}^T & & 0 \end{array}
\right) \,
\approx \, \mathbb{I}_4 + (\delta t) \left(
\begin{array}{ccc}
\Omega & & {\bf v} \\ \\
{\bf 0}^T & & 0 \end{array}
\right). $$
where $\Omega = - \Omega^T$ and ${\bf v}$ are random angular and translational velocities with components drawn independently from
a Gaussian distribution with variance $\sigma^2$, and $\delta t$ is a small finite time.

After calculating $\Sigma_X$ from Eq.($\ref{covprop1112}$), we can compare the calculated sample mean and covariance of $\{X_{ij}\}=\{^1X_{ij}\} \cup \{^2X_{ij}\}$ with the solved for values.

\begin{figure}[h]
\begin{center}
\setlength{\unitlength}{0.012500in}%
 \includegraphics[width=3.3in]{figure/sigerror}
\end{center}
\caption{The Above Plot Shows that the $\Sigma_X$ is Calculated from ($\ref{covprop1112}$) and Becomes More Accurate as the Number of Data Samples Increases}
\label{figure_ASME} 
\end{figure}

\section{Relating the Covariances of a PDF and Its Symmetrized Version}

Recall that given an arbitrary pdf $f(H)$ with mean $M$ and covariance $\Sigma$, a symmetrized version is defined as:
$$ \tilde{f}(H) = \half ({f}(H) + {f}(H^{-1}) ). $$
Let $\tilde{M}$ and $\tilde{\Sigma}$ denote the mean and covariance of $\tilde{f}(H)$. 
Given that symmetrization of a pdf puts the mean of the result at the identity, we already know that $\tilde{M} = \mathbb{I}$.
The remaining question to ask is what the relationship is between the covariances of the original and symmetrized versions of a pdf.
This is answered here.

From the definition of covariance and the invariance of the integral over $SE(3)$ under inversions, and the fact that $\tilde{M} = \mathbb{I}$, the following equation
$$ \tilde{\Sigma} = \int_{SE(3)} \log^{\vee}(H)  [\log^{\vee}(H)]^T \tilde{f}(H) dH $$
can be simplified as:
$$ \tilde{\Sigma} = \int_{SE(3)} \log^{\vee}(H)  [\log^{\vee}(H)]^T {f}(H) dH. $$
This is not to be confused with
$$ {\Sigma} = \int_{SE(3)} \log^{\vee}(M^{-1} H)  [\log^{\vee}(M^{-1} H)]^T {f}(H) dH. $$
where
$$ \int_{SE(3)} \log^{\vee}(M^{-1} H)  {f}(H) dH = \mathbb{O}. $$

Though there appears to be no simple exact relationship between $\tilde{\Sigma}$ and ${\Sigma}$, in the case when $\|\Sigma\|$ and $\|M\|$ are both reasonably
small, an approximate relationship can be constructed by using the Baker-Campbell-Hausdorf formula to expand out $\log^{\vee}(M^{-1} H)$. 
This was done in \cite{wang06}, and the result (modulo different notation) is:
\begin{equation}
\tilde{\Sigma} = \Sigma + (\log^{\vee} M)(\log^{\vee} M)^T + \half \left(\Sigma \, ad^T(\log M) + ad(\log M) \, \Sigma\right)
\label{sigtildesig}
\end{equation}
If $(M,{\Sigma})$ is known a priori, then $\tilde{\Sigma}$ can be computed from them. Due to the simple computation of $\tilde{\Sigma}$, Eq.(\ref{sigtildesig}) can be used as a consistency
check on the accuracy of $M$ and $\Sigma$ by computing the norm of the difference of both sides.
\end{comment}

\section{CONCLUSION AND FUTURE DIRECTIONS}
\label{sec:conclusion}
In this paper, the ``AX=XB'' formulation of the sensor calibration problem is examined, which is widely used in camera calibration, humanoid head-eye calibration, robot eye-to-hand calibration, aerial vehicle sensor calibration, and IGT sensor calibration. A review of some of the most influential and effective methods was presented and their positive and negative traits were discussed. For the various $AX=XB$ solvers, the focus is put on the case where there is noise on the incoming sensor data, and therefore multiple sensor readings are needed. It was clear that each algorithm has strengths and weaknesses in different contexts, and it is important to use the appropriate method for \textcolor{blue}{different circumstances.} %the circumstance.

In addition to measurement error contributing to noise, it was emphasized that the sensor data streams containing the $A$s and $B$s may be present at different sampling rates, may be asynchronous, and/or each stream may contain gaps in information. Therefore, a probabilistic method is reviewed in detail which is used for calculating the calibration transformation that works for data without any a priori knowledge of the correspondence between the $A$s and $B$s. Data selection is of critical importance to $AX=XB$ solvers. Depending on the quality of the data pairs, the usage of data selection techniques can either greatly improve the final result or prevent the solver from failing.

Though many algorithms are available for hand-eye calibration, which algorithm is preferable for the given type and number of motions is still unclear. It will be helpful to categorize the type of motions and their corresponding preferable solvers.

\textcolor{blue}{Re add the acknowledgment section}

\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgment}
The authors would like to recognize NSF Grant RI-Medium: IIS-1162095, which served to support this work. The authors would also like to acknowledge the support of M. Kendal Ackerman, Alexis Cheng and Emad M. Boctor, colleagues in this endeavor at Johns Hopkins University.

Chirikjian’s contribution to this material is based upon work supported by (while serving at) the National Science Foundation.
Any opinion, findings, and conclusions or recommendations expressed in this material are those of the author(s)
and do not necessarily reflect the views of the National Science Foundation.
\end{acknowledgment}
\end{comment}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix       %%% starting appendix
\section*{Appendix A: Integration and Convolution on SE(3)}

This appendix reviews the features of integration and convolution on the group $SE(3)$ that are
relevant to the formulation in this paper. For more detailed treatments see \cite{myoldbook, vol2}.

\subsection*{Integration}

$SE(3)$ is a six-dimensional matrix Lie group. If $H = H({\bf q})$ where ${\bf q} = [q_1,....,q_6]^T$ is a global set of coordinates, then
functions $f:SE(3) \rightarrow \mathbb{R}$ can be integrated as
$$ \int_{SE(3)} f(H) dH \doteq \int_{{\bf q} \in D} f(H({\bf q})) |J({\bf q})| d{\bf q} $$
where $D$ is the domain of integration in the parameter space and $d{\bf q} = dq_1 dq_2 \cdots dq_6$. 
The Jacobian determinant $|J({\bf q})|$ is computed from the Jacobian matrix \textcolor{blue}{Note: You should probably add a quick discussion of right and left Jacobians and clarify that they are different?}
$$ J({\bf q}) = \left[\left(H^{-1} \frac{\partial H}{\partial q_1}\right)^{\vee}; \left(H^{-1} \frac{\partial H}{\partial q_2}\right)^{\vee};\,\cdots\,
\left(H^{-1} \frac{\partial H}{\partial q_6}\right)^{\vee}\right]. $$
For example, if Cartesian coordinates are used for the translation vector and $ZXZ$ Euler angles are used
for rotations, then ${\bf q} = [x,y,z,\alpha,\beta,\gamma]^T$, $D=\mathbb{R}\times\mathbb{R}\times\mathbb{R}\times[0,2\pi]\times[0,\pi]\times[0,2\pi]$ and $|J({\bf q})| = \sin \beta$. And while $D$ and $J({\bf q})$ will change depending on which parametrization is used, the value of the integral itself does not as it is a property of the Lie group and the function themselves and not a matter of how the function is expressed or the coordinates of the integral.
\textcolor{blue}{I fixed the last sentence slightly; it still needs some work}

$SE(3)$ is unimodular, which means that the integation measure, $dH = |J({\bf q})| d{\bf q}$, has the property that for any
fixed $H_0 \in SE(3)$ and ``well-behaved fuction\footnote{Here a well-behaved function means a function for which the integral exists, and hence
$f \in L^1(SE(3))$, and later that the convolution integral exists, which is guaranteed by further requiring that
$f \in L^2(SE(3))$. And so, with the notable exception of the Dirac delta function, the discussion is restricted to
$f \in (L^1 \cap L^2)(SE(3))$.}'' $f:SE(3) \rightarrow \mathbb{R}$, \cite{myoldbook}
\begin{equation}
\int_{SE(3)} f(H_0 \circ H) dH = \int_{SE(3)} f(H \circ H_0) dH = \int_{SE(3)} f(H) dH.
\label{defuni}
\end{equation}
In addition, it can be shown that when these conditions hold, so too does
\begin{equation}
\int_{SE(3)} f(H^{-1}) dH = \int_{SE(3)} f(H) dH.
\label{invdsdcf}
\end{equation}
A common source of confusion is that many books on Lie groups are concerned with compact Lie groups, which possess both bi-invariant metrics
and bi-invariant integration measures. When discussing the noncompact case, bi-invariant metrics generally do not exist (except for special cases
such as products of tori and Euclidean spaces), and they do not exist for $SE(3)$. Though bi-invariant integration measures also do not exist in general,
they do exist for a broader class of special noncompact Lie groups%than those that have bi-invariant metrics
, and this includes $SE(3)$.

\subsection*{Convolution} \label{convsec}

Given two functions, $f_1, f_2 \in (L^1 \cap L^2)(SE(3))$, the convolution is defined as
\begin{equation}
(f_1 * f_2)(H) \doteq \int_{SE(3)} f_1(K) f_2(K^{-1} H) dK. 
\label{convdef}
\end{equation}
This integral can be rewitten in a number of equivalent forms using Eq.~(\ref{defuni}) and Eq.~(\ref{invdsdcf}).
Convolution inherits the associative property from the underlying group, which is written as 
$$ (f_1 * f_2) * f_3 = f_1 * (f_2 * f_3) $$
(where the dependence of these functions on $H$ has been temporarily suppressed). Analogous with the way convolution inherits associativity, it 
also inherits noncommutativity for general functions, with the exception of special functions called ``class functions''.

If the class of functions is expanded to consider beyond $(L^1 \cap L^2)(SE(3))$
to include Dirac delta functions\footnote{As in $\mathbb{R}^n$, these can be thought of as spikes
of infinite height and infinitesimal width centered on the identity}, which are the unique functions such that for every $f \in (L^1 \cap L^2)(SE(3))$
$$ (f * \delta)(H) = (\delta * f)(H) = f(H), $$
then the result is the ``group algebra'' consisting of functions as elements, and the two operations of convolution and addition of
functions: $f_1*f_2$ and $f_1 + f_2$. \textcolor{blue}{Note: The previous sentence does not make sense} A slightly further expansion of allowable functions to include shifted delta functions of the form:
$$ \delta_X(H) \doteq \delta(X^{-1} H) = \delta( H X^{-1}). $$
\textcolor{blue}{The previous sentence is not complete}
The unshifted delta function is an example of a symmetric function, in that $\delta(H) = \delta(H^{-1})$.

Using the properties of the invariant integral on $SE(3)$, convolving a shifted delta function with an arbitrary
function transfers the shift:
\begin{equation}
\begin{split}
(\delta_X * f)(H) =& \int_{SE(3)} \delta(X^{-1} K) f(K^{-1} H) dK \\
=& \int_{SE(3)} \delta(J) f((XJ)^{-1} H) dK = f(X^{-1} H) \\
\end{split}
\end{equation}
where the change of variables $J = X^{-1} K$ and the invariance of integration have been used.

\begin{comment}
Similarly,
$$ (\delta_X * f * \delta_{X^{-1}})(H) = f(X^{-1} H X). $$
Using the associative property,
\begin{equation}
\begin{split}
&(\delta_X * f_1 * \delta_{X^{-1}}) * (\delta_X * f_2 * \delta_{X^{-1}}) \\
&= \delta_X * f_1 * (\delta_{X^{-1}} * \delta_X) * f_2 * \delta_{X^{-1}} \\ 
&= \delta_X * (f_1 * f_2)* \delta_{X^{-1}}. 
\end{split}
\end{equation}
\end{comment}

\begin{comment}
\subsection*{Symmetric Functions and Class Functions}

A symmetric function is one with the property that
$$ s(H) = s(H^{-1}). $$
There are several ways to construct symmetric pdfs from nonsymmetric ones. For example, if $f$ is a pdf, 
$\tilde{f}(H) = \half(f(H) + f(H^{-1})$ is symmetric (with the factor of $1/2$ necessary to make the result a pdf).
$f(H)\cdot f(H^{-1})/((f*f)(\mathbb{I}))$ is also symmetric and normalized to be a pdf (where $\cdot$ is just scalar
multiplication of functions). Also, if $f(H)$ is an arbitrary pdf and $f'(H) = f(H^{-1})$, then $(f*f')(H)$ will be symmetric.

Using the invariance properties of the integral over $SE(3)$, it is not difficult to see that 
\begin{eqnarray*}
(s_1 * s_2)(H) &=& \int_{SE(3)} s_1(K) s_2(K^{-1} H) dK \\
&=& \int_{SE(3)} s_1(K^{-1}) s_2(H^{-1} K) dK. \end{eqnarray*}
Then changing variables as $J = H^{-1} K$, $HJ =K$, and $K^{-1} = J^{-1} H^{-1}$ so
$$ (s_1 * s_2)(H) = \int_{SE(3)} s_2(J) s_1(J^{-1} H^{-1}) dJ = (s_2 * s_1)(H^{-1}). $$
This is not the same as saying that the convolution of two symmetric functions is symmetric. Nor does it say that
the convolution of symmetric functions is commutative. But, it does say that
the convolution of a symmetric function with itself is symmetric.

In general, the only functions on a group that commute under convolution with every function are the class functions.
A class function has the property that
$$ \chi(K H K^{-1}) = \chi(H) $$
for every $H,K$ in the group. For example, $\delta$ is a class function for $SE(3)$, and the fact that it commutes under
convolution was already explained in (\ref{convsec}).
\end{comment}

% Here we show that in general class function commute under convolution.
%
%*** will fill if needed. may not be very relevant ***
%
%Unfortunately, no class functions on $SE(3)$ are in $(L^1 \cap L^2)(SE(3))$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{Appendix B: Head of Second Appendix}
%\subsection*{Subsection head in appendix}
%The equation counter is not reset in an appendix and the numbers will
%follow one continual sequence from the beginning of the article to the very end as shown in the following example.
%\begin{equation}
%a = b + c.
%\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The bibliography is stored in an external database file
% in the BibTeX format (file_name.bib).  The bibliography is
% created by the following command and it will appear in this
% position in the document. You may, of course, create your
% own bibliography by using thebibliography environment as in
%
% \begin{thebibliography}{12}
% ...
% \bibitem{itemreference} D. E. Knudsen.
% {\em 1966 World Bnus Almanac.}
% {Permafrost Press, Novosibirsk.}
% ...
% \end{thebibliography}

% Here's where you specify the bibliography style file.
% The full file name for the bibliography style file 
% used for an ASME paper is asmems4.bst.
\bibliographystyle{asmems4}

% Here's where you specify the bibliography database file.
% The full file name of the bibliography database for this
% article is asme2e.bib. The name for your database is up
% to you.
\bibliography{asme2e}
\end{document}

%%-------------------------------------------------------------------------------------
%\subsection{Solving for $X$ and $\Sigma_X$}
%
%
%
%
%\subsubsection{Gradient descent using the $L^2$ Norm}
%
%One possible method to search for an appropriate $X$ and $\Sigma_X$ could be by minimizing the cost function
%\begin{equation}
%C_2(X) = \left(\int_{SE(3)} \|f_1(H) - f_2(H)\|^2 \, dH \right)^{\half}.
%\label{cost2} \end{equation}
%where
%$$ f_1(H) = \rho(H; A, \Sigma_A) $$
%and
%\begin{equation}
%f_2(H) = \rho(H; X B X^{-1}, \,\, \Sigma_2).
%\end{equation}
%where
%$$ \Sigma_2 = Ad(X) [Ad(B^{-1})\Sigma_X Ad^T(B^{-1}) + \Sigma_{B} + \Sigma_X]Ad^T(X)$$
%In general, the integral in this cost function cannot be solved in closed form because the $\log$ function is nonlinear, and in terms of exponential coordinates
%$dH = |J({\bf z})| d{\bf z}$ where $|J({\bf 0})| =1$, but this Jacobian is a nonlinear function of ${\bf z}$.
%
%However, if we a priori limit the search for $X$ to the cylinder
%defined in (\ref{cylinder}), automatically, $X B X^{-1} = A$.
%Then, we can define a new variable $K = M_A^{-1} H$ and using the property of
%invariance of integration under shifts, can write
%$$ C_2(X(\phi,s), \Sigma_X) = \left(\int_{SE(3)} \left| f'_A(K) - f'_B(K) \right|^2 \, dK \right)^{\half} $$
%where
%$$ f'_1(K) = \rho(K; \mathbb{I}_4, \Sigma_A) $$
%and
%$$  f'_2(K) = \rho(K;\mathbb{I}_4 \,,\, \Sigma_2).$$
%where
%\begin{equation}
%\begin{split}
%\Sigma_2= &Ad(X(\phi,s)) [Ad(B^{-1})\Sigma_{X(\phi,s)} Ad^T(B^{-1})\\
%&+ \Sigma_{B} + \Sigma_X(\phi,s)]Ad^T(X(\phi,s))
%\end{split}
%\end{equation}
%And if covariances are scaled to be small, the benefit of this is that it reduces to the integral of the norm of the difference of two Gaussians.
%This has a closed-form solution
%\begin{equation}
%\begin{split}
%C_2(X(\phi,s), \Sigma_X) = (2\pi)^{-3}&\left[ -2 \frac{\sqrt{\| \Sigma_2^{-1} + \Sigma_A^{-1} \|^{-1}}}{\sqrt{\| \Sigma_A \|}\sqrt{\| \Sigma_2 \|}}\right.\\
%&\left. + \frac{\sqrt{\| \Sigma_2 \|}}{\sqrt{2}\| \Sigma_2 \|} + \frac{\sqrt{\| \Sigma_A \|}}{\sqrt{2}\| \Sigma_A\|} \right]
%\end{split}
%\end{equation}
%which can be minimized by a search over the 2 remaining DOF of $X$ and the 21 unique entries of $\Sigma_X$.
%
%In a similar manner, we can write another cost function, derived from the Kullback–Leibler divergence, and find the global minimum of the cost function
%\begin{equation}
%C_2(X) = D_{KL}(f_A \,\|\, \delta_X * f_B  * \delta_{X^{-1}})
%\label{cost3} \end{equation}
%where $f_A(H) = \rho(H; M_A, \Sigma_A)$ and
%$$ (\delta_X * f_B  * \delta_{X^{-1}})(H) = \rho(H;\, X M_B X^{-1} \,,\, Ad(X) \,\Sigma_{B}\, Ad^T(X)). $$
%
%As before, if we limit the search for $X$ to the cylinder, the KL divergence of
%two distributions on $\mathbb{R}^n$ with means ${\bf m}_i$ and covariances $\Sigma_i$ is
%$$ D_{KL}(f_1 \,\|\, f_2) = $$
%$$ \half\left[{\rm tr}(\Sigma_2^{-1} \Sigma_1) + ({\bf m}_2 - {\bf m}_1)^T \Sigma_2^{-1} ({\bf m}_2 - {\bf m}_1)
%-n - {\rm ln}\left(\frac{|\Sigma_1|}{|\Sigma_2|}\right)\right]. $$
%%% The above is from Wikipedia http://en.wikipedia.org/wiki/Kullback%E2%80%93Leibler_divergence
%In our problem, ${\bf m}_2 - {\bf m}_1 = {\bf 0}$, and since $SE(3)$ is
%unimodular, $|Ad(X)| = 1$. 
%Our cost function then becomes
%$$ C_2(X(\phi,s), \Sigma_X) = D_{KL}(f'_A \,\|\, f'_B) $$
%where
%$$ C'_2(X(\phi,s), \Sigma_X) = {\rm tr}(\Sigma_A^{-1} \Sigma_2) - {\rm ln} \left( \frac{| \Sigma_A |}{|\Sigma_2|} \right), $$
%and we minimize over the 23 parameters.
%
%
%
%
%\subsubsection{Block decomposition}
%
%As in the no noise case, we can obtain the rotational component, $R_X$, of $X$. From (\ref{covprop2}) we have that,
%\begin{equation}
%{\bf n}_{A}=R_X{\bf n}_{B}
%\label{ns}\end{equation}.\\
%
%If we decompose $\Sigma_{A}$ and $\Sigma_{B}$ into blocks as
%$ \Sigma_{i}= \left(\begin{array}{cc}
%\Sigma_{i}^1 & \Sigma_{i}^2 \\
%\Sigma_{i}^3 & \Sigma_{i}^4  \end{array}\right) $\\
%\\
%where $\Sigma_{i}^3 = (\Sigma_{i}^2)^T$, then we can take (\ref{covprop1112})
%$$\Sigma_{X} + Ad(B^{-1}) \Sigma_{X} Ad^T(B^{-1}) = Ad(X^{-1}) \Sigma_A Ad^T(X^{-1}) - \Sigma_{B}$$
%and write
%\begin{equation}
%\begin{split}
%&\left[\begin{array}{cc}
%\Sigma_{X}^1 &\Sigma_{X}^2 \\
%\Sigma_{X}^3 & \Sigma_{X}^4  \end{array}\right]+
%\left[\begin{array}{cc}
%R_{B}^T &  0 \\
%(\widehat{-R_{B}^Tt_B})R_{B}^T &R_{B}^T \end{array}\right]
%\left[\begin{array}{cc}
%\Sigma_{X}^1 &\Sigma_{X}^2 \\
%\Sigma_{X}^3 & \Sigma_{X}^4  \end{array}\right]
%\left[\begin{array}{cc}
%R_{B} &  R_{B}(\widehat{R_{B}^Tt_B}) \\
%0 &R_{B} \end{array}\right]=\\
%&\left[\begin{array}{cc}
%R_{X}^T &  0 \\
%(\widehat{-R_{X}^Tt_X})R_{X}^T &R_{X}^T \end{array}\right]
%\left[\begin{array}{cc}
%\Sigma_{A}^1 &\Sigma_{A}^2 \\
%\Sigma_{A}^3 & \Sigma_{A}^4  \end{array}\right]
%\left[\begin{array}{cc}
%R_{X} &  R_{X}(\widehat{R_{X}^Tt_X}) \\
%0 &R_{X} \end{array}\right]-
%\left[\begin{array}{cc}
%\Sigma_{B}^1 &\Sigma_{B}^2 \\
%\Sigma_{B}^3 & \Sigma_{B}^4  \end{array}\right].
%\end{split}
%\end{equation}
%Given that
%\begin{equation}
%\begin{split}
%&\left[\begin{array}{cc}
%R^T &  0 \\
%(\widehat{-R^Tt})R^T & R^T \end{array}\right]
%\left[\begin{array}{cc}
%\Sigma^1 &\Sigma^2 \\
%\Sigma^3 & \Sigma^4  \end{array}\right]
%\left[\begin{array}{cc}
%R &  R(\widehat{R^Tt}) \\
%0 &R \end{array}\right]=\\
%&\left[\begin{array}{cc}
%R^T \Sigma^1 R &  R^T \Sigma^1 R (\widehat{R^Tt}) +R^T \Sigma^2 R \vspace{0.1in}\\
%\multirow{2}{*}{$(\widehat{-R^Tt})R^T \Sigma^1 R + R^T \Sigma^3 R$} & (\widehat{-R^Tt})R^T \Sigma^1 R (\widehat{R^Tt})+ R^T \Sigma^3 R (\widehat{R^Tt}) \\
% &+ (\widehat{-R^Tt}) R^T \Sigma^2 R + R^T \Sigma^4 R \end{array}\right]
%\end{split}
%\end{equation}
%we can write the block equations as:
%\begin{align} 
%&\Sigma_X^1 + R_B^T \Sigma_X^1 R_B =  R^T_X \Sigma_A^1 R_X - \Sigma_B^1\\
%\nonumber&\Sigma_X^2 + R_B^T \Sigma_X^1 R_B (\widehat{R_B^Tt_B}) + R_B^T \Sigma_X^2 R_B\\ 
%&=  R^T_X \Sigma_A^1 R_X (\widehat{R_X^Tt_X}) +R_X^T \Sigma_A^2 R_X - \Sigma_B^2 \\
%\nonumber &\Sigma_X^3 + (\widehat{-R_B^Tt_B}) R_B^T \Sigma_X^1 R_B + R_B^T \Sigma_X^3 R_B\\
%&=  (\widehat{-R_X^Tt_X}) R^T_X \Sigma_A^1 R_X + R_X^T \Sigma_A^3 R_X - \Sigma_B^3 \\
%\begin{split}& \Sigma_X^4 + (\widehat{-R_B^Tt_B}) R_B^T \Sigma_X^1 R_B (\widehat{R_B^Tt_B})  + R_B^T \Sigma_X^3 R_B (\widehat{R_B^Tt_B})\\ 
%&+ (\widehat{-R_B^Tt_B}) R_B^T \Sigma_X^2 R_B + R_B^T \Sigma_X^4 R_B = \\
%&(\widehat{-R_X^Tt_X}) R_X^T \Sigma_A^1 R_X (\widehat{R_X^Tt_X}) \\
%&+ R_X^T \Sigma_A^3 R_X (\widehat{R_X^Tt_X}) + (\widehat{-R_X^Tt_X}) R_X^T \Sigma_A^2 R_X + R_X^T \Sigma_A^4 R_X - \Sigma_B^4 \end{split}
%\end{align}
%%--------------------------

### 2015-08-26 AXXB_Review/AXXB Review.tex
To be continued

@@
  $\det(R) = 1$\textbf{\textcolor{blue}{,}} where $R \in \mathbb{R}^{3 \times 3}\}$}
-\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \time 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
+\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \times 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
 \entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
@@
 (3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
-\entry{$exp()$}{The matrix exponential of a square matrix. }
-\entry{$log()$}{The matrix logarithm of a square matrix}
+\entry{$\exp()$}{The matrix exponential of a square matrix. }
+\entry{$\log()$}{The matrix logarithm of a square matrix}
 \entry{$H$}{A general rigid body transformation ($H \in SE(3)$) }
@@
 \entry{$^\vee$}{For Lie algebra, the ``vee" operator is defined such that $\left(\displaystyle\sum\limits_{i=1}^n x_iE_i\right)^{\vee}\doteq(x_1,x_2,...,x_n)^T$ where $n = 3$ for $so(3)$ and $n = 6$ for $se(3)$}
-\entry{$\hat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator. $\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$}
+\entry{$\widehat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator.
+$\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$; For a vector ${\bf n} \in \mathbb{R}^{3 \times 1}$.
+$\widehat{\bf n}$ represents the corresponding skew symmetric matrix }
 \entry{$\circ$}{The operator defined for the group product}
@@
 \entry{$vec$}{The ``vec'' operator is defined such that $vec(A) = [a_{11},...,a_{1m},a_{21},...,a_{2m},...,a_{n1},...,a_{nm}]^{T}$ for $A = [a_{ij}] \in \mathbb{R}^{m \times n}$}
-\entry{\textcolor{blue}{Remark:}}{\textcolor{blue}{I would remove the next entry, it will lead to confusion and generally isn't necessary.}}
-\entry{${\bf p}$}{For $P\in G$ (where $G$ is a Lie group, e.g. $SE(3)$ or $SO(3)$), ${\bf p}=(p_1,p_2,...,p_n)^T=\log^{\vee}(P)$}
 \entry{$A_i$}{A rigid body transformation ($A_i \in SE(3)$), associated with one sensor measurement source}
 \entry{$B_i$}{A rigid body transformation ($B_i \in SE(3)$), usually associated with a different sensor measurement source}
-\entry{$X$}{The rigid body transformation ($\textcolor{blue}{X} %X_i 
+\entry{$X$}{The rigid body transformation ($X %X_i 
 \in SE(3)$) that relates $A_i$ to $B_i$}
@@
 \entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
-\entry{$\tilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
+\entry{$\widetilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
 \entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
-\entry{$\rho$}{A probability distribution of $H\in G$ on SE(3)\textcolor{blue}{G not well-defined here}}
+\entry{$\rho$}{A probability distribution of $H\in G$, where G $\subset$ SE(3)}
 \entry{$M$}{For $\rho$, $M$ is the mean of the distribution}
@@
 
-In the fields of robotics and computer vision, sensor calibration problems are often codified using the ``AX=XB'' formulation, (\textcolor{blue}{Figs.~\ref{AXXBfig1}--\ref{AXXBfig3}}%Fig.\ref{AXXBfig1}, Fig.\ref{AXXBfig2}, Fig.\ref{AXXBfig3}
+In the fields of robotics and computer vision, sensor calibration problems are often codified using the ``AX=XB'' formulation, (Figs.~\ref{AXXBfig1}--\ref{AXXBfig3}%Fig.\ref{AXXBfig1}, Fig.\ref{AXXBfig2}, Fig.\ref{AXXBfig3}
 ).
@@
 An alternative name that describes this system is ``hand-eye'' calibration.
-Several methods \textcolor{blue}{exist} %have existed
+Several methods exist %have existed
 in the literature that can perform hand-eye calibration without directly dealing with the $AX=XB$ formulation such as \cite{malm2000new,heller2012branch,ruland2012globally,wu2014hand,kim,liu2015calibration}.
 %Camera calibration is also integrated into hand-eye calibration  in some works \cite{,,,}.
-Another problem, called the robot-world and hand-eye calibration, deals with the case where an additional calibration of the robot pose with respect to the world \textcolor{blue}{frame} is needed.
-This calibration technique is formulated as the ``AX=YB'' problem and multiple methods have been \textcolor{blue}{developed} %brought up
+Another problem, called the robot-world and hand-eye calibration, deals with the case where an additional calibration of the robot pose with respect to the world frame is needed.
+This calibration technique is formulated as the ``AX=YB'' problem and multiple methods have been developed %brought up
 such as \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative,li2010simultaneous,ernst2012non,heller2014hand}.
@@
 In the ``AX=XB'' formulation $A$, $X$, and $B$ are each homogeneous transformations (i.e., elements of the special Euclidean group, $SE(3)$) with each pair of measurements $(A,B)$ coming from sensors such as cameras, ultrasound probes, optical, or electromagnetic pose tracking systems, among others.
-$X$ is the unknown rigid-body \textcolor{blue}{transformation} %motion
+$X$ is the unknown rigid-body transformation %motion
 that is found as a result of solving $AX=XB$. It is well known that it is not possible to solve for
 a unique $X$ from a single pair of exact $(A,B)$, but if there are two instances of independent exact measurements, $(A_1,B_1)$ and $(A_2,B_2)$ satisfying certain constraints,
-then the problem can be solved \textcolor{blue}{for a unique, fixed $X$}.
-However, in practice, sensor noise is always present, and an exact solution is not possible.
-The goal, therefore, becomes one of finding
-an $X$ with the least error given corresponding noisy pairs \textcolor{blue}{of data} $(A_i, B_i)$ for i = 1,2, \ldots,n.
+then the problem can be solved for a unique, fixed $X$. However, in practice, sensor noise is always present, and an exact solution is not possible. The goal, therefore, becomes one of finding
+an $X$ with the least error given corresponding noisy pairs of data $(A_i, B_i)$ for i = 1,2, \ldots,n.
 
@@
 This situation is rectified by considering two pairs of exact measurements of the form in Eq.~(\ref{mainaxxb}), i.e., $ {A_1}X=X{B_1} {\rm \,\, and \,\,} {A_2}X = X{B_2} $, provided that some mild conditions are observed for the selection of the pairs $(A_1,B_1)$ and $(A_2,B_2)$ \cite{chen91,park1994robot,shiu1989calibration}.
-Note that $(A_i, B_i)$ here are relative transformation data pairs, so in real experiments at least 3 absolute transformation data pairs \textcolor{blue}{have to} %should
+Note that $(A_i, B_i)$ here are relative transformation data pairs, so in real experiments at least 3 absolute transformation data pairs have to
 be measured.
@@
 \includegraphics[width=3.3in]{Photos/UR5_Frame_Final.jpg}
-\caption{\textcolor{blue}{Capitalization style changed midway through, I would use all lower case besides beginning of sentences} Application of AX=XB in Ultrasound Sensor Calibration: An Ultrasound Probe Is Attached to the End-effector and the Calibration Phantom Is Used for Ultrasound Probe Calibration.
+\caption{Application of AX=XB in ultrasound sensor calibration: an ultrasound probe is attached to the end-effector and the calibration phantom is used for ultrasound probe calibration.
 (The UR5 robot pictured above is owned by Professor Emad Boctor of Johns Hopkins University)}
@@
 Also, you change the capitalization style midway through} Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
- \textit{Boston Dynamics} Requires Head-Body Calibration before Turning the Knob.
+ \textit{Boston Dynamics} Requires head-body calibration before turning the knob.
 Different pairs of $(A_i, B_i)$ are measured by changing the head pose of the humanoid robot.
@@
 In Section~\ref{sec:sol_methods}, a detailed review is given for the existing methods that solve the $AX=XB$ problem using pairs of $\{A_{i}, B_{i}\}$ with correspondence.
-The notation used throughout the literature is not consistent and the authors \textcolor{blue}{strove} %tried their best
+The notation used throughout the literature is not consistent and the authors strove %tried their best
 to standardize the notation used across the reviewed methods
@@
 \begin{equation}
-R_{X} = e^{\tilde{\nn}_{A}\beta}R_{X_{P}}
+R_{X} = \exp{(\widetilde{\nn}_{A}\beta)}R_{X_{P}}
 \label{RotationCheng}
@@
 \begin{center}
-$R_{X_{p}} =  e^{\tilde{\nn}_{X}\theta_{X}}$\\
+$R_{X_{p}} =  \exp{(\widetilde{\nn}_{X}\theta_{X})}$\\
 $\nn_{X} = \nn_{B} \times \nn_{A}$\\
@@
 \end{center}
-and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\tilde{\nn}$ is a skew-symmetric matrix defined as below:\\
+and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\widetilde{\nn}$ is a skew-symmetric matrix defined as below:\\
 \begin{equation}
@@
 The dual quaternion method proposed by Daniilidis and Bayro-Corrochano \cite{daniilidis1996dual} (Daniilidis \cite{daniilidis1999hand}) treats the rotation and translation parts of the matrix X in a unified way and facilitates a new simultaneous solution of X using SVD.
-To begin, Eq.~(\ref{mainaxxb}) is transformed into an equation \textcolor{blue}{of dual quaternions:} %in dual quaternion form as follows:
+To begin, Eq.~(\ref{mainaxxb}) is transformed into an equation of dual quaternions: %in dual quaternion form as follows:
 \begin{equation}
@@
 
-The dual quaternion that corresponds to a \textcolor{blue}{Be consistent throughout the paper: 4x4} %4 by 4 
+The dual quaternion that corresponds to a 4x4 %4 by 4 
 rigid transformation matrix is defined as follows:
@@
 {\bf q}^{T}_{X}{\bf q}_{X} = 1 \; \; \text{and} \;
-\; {\bf q}^{T}_{X}{\bf q}^{\prime}_{X} = 0.
-\end{equation}
-Similar to Section \textcolor{blue}{\ref{sec:quats}?}, ${\bf q}_{X}$ and ${\bf q}^{\prime}_{X}$ are the vector representations of $q_{X}$ and $q^{\prime}_{X}$.
+\; {\bf q}^{T}_{X}{\bf q}^{\prime}_{X} = 0
+\end{equation}
+where ${\bf q}_{X}$ and ${\bf q}^{\prime}_{X}$ are the vector representations of $q_{X}$ and $q^{\prime}_{X}$.
 Then equation $A_{i}X = XB_{i}$ can be converted into the form below:
@@
 f(q_X,\ttt_{X}) = \lambda_{1} \sum_{i = 1}^{n}||vec(q_{X} \odot t_{B_{i}} \odot \bar{q}_{X}) -(R_{A_i} - \mathbb{I})\ttt_{X} - \ttt_{A_i}||^{2}\\
-\lambda_{2} \sum_{i = 1}^{n}||{n_{A_{i}} - q_{X} \odot n_{B_{i}} \odot \bar{q}_{X}}||^{2} + \lambda_{3}(1 - \qq_{X}^{T}\qq_{X})^2\\
-\textcolor{blue}{I believe you are missing an operator between the two lines} 
++ \lambda_{2} \sum_{i = 1}^{n}||{n_{A_{i}} - q_{X} \odot n_{B_{i}} \odot \bar{q}_{X}}||^{2} + \lambda_{3}(1 - \qq_{X}^{T}\qq_{X})^2
 \end{split}
@@
 Note that $vec()$ here represents the vector part of a quaternion such that $vec(q) \in \mathbb{R}^{3}$.
-The third term is a penalty function where the \textcolor{blue}{modulus,modulo?} %module
+The third term is a penalty function where the modulus %module
 of $q$ will approach 1 when $\lambda_{3}$ becomes large.
@@
 As pointed out in \cite{heller2014hand}, the polynomial global optimization method as described in Eq.~(\ref{dqLMI}) can give better solutions than Park \cite{park1994robot}, Eq.~(\ref{simlqua}), Eq.~(\ref{orLMI}) and Eq.~(\ref{qLMI}).
-Several solvers for \textcolor{blue}{$AX=XB$?
-Introducing AX=YB seems arbitrary} %$AX=YB$
+For those who are also interested in robot-world and hand-eye calibration, several solvers for $AX=YB$
 using the LMI technique are also given; however, they fail to give better results than the traditional methods.
@@
 The inequality constraint $\bf{Dx \geq f}$ is added manually in order to prevent $\xx$ from reaching zero, which is a meaningless solution for the program.
-\textcolor{blue}{$\bf x$ must also satisfy two additional constraints: $\|\qq_X\|=1$ and $\|\qq_{X}^{\prime}\|=1$.}%Another constraint $\bf x$ has to satisfy is that $||\qq_X||=1$ and $||\qq_{X}^{\prime}||=1$.
+$\bf x$ must also satisfy two additional constraints: $\|\qq_X\|=1$ and $\|\qq_{X}^{\prime}\|=1$.
+%Another constraint $\bf x$ has to satisfy is that $||\qq_X||=1$ and $||\qq_{X}^{\prime}||=1$.
 
@@
 \end{equation}
-The rotation $R({\bf n}_B, \phi)$ is given by \textcolor{blue}{Rodrigues' Formula?} Euler's formula:
+The rotation $R({\bf n}_B, \phi)$ is given by Rodrigues' rotation formula:
 $$ R({\bf n}_B, \phi) = \II \,+\, \sin \phi \, \widehat{\,{\bf n}_B} \,+\, (1-\cos \phi)\, \left(\widehat{\,{\bf n}_B}\right)^2. $$
@@
 where $\Sigma_{i}^3 = (\Sigma_{i}^2)^T$, then take the first two blocks of Eq.~(\ref{mainmain12}) and write:
-\begin{equation}
-\begin{split}
-&\Sigma_{M_B}^1 =  R^T_X \Sigma_{M_A}^1 R_X {\rm \,\,\, and \,\,\,} \\
-&\Sigma_{M_B}^2 =  R^T_X \Sigma_{M_A}^1 R_X(\widehat{R^T_X t_x}) + R^T_X \Sigma_{M_A}^2 R_X \label{set1}.
-\end{split}
-\end{equation}
-
-Calculate the eigendecomposition as $ \Sigma_{i}=Q_i \Lambda Q_i^T$, where $Q_i$ is the square matrix whose $i$th column is the eigenvector of $\Sigma_i$ and $\Lambda$ is the diagonal matrix with corresponding eigenvalues as diagonal entries \textcolor{blue}{Note: For this specific decomposition, you have to require that $\Sigma$ is real symmetric, you may have qualified this earlier, but double check}.
+
+\begin{subequations} 
+\begin{align}
+\Sigma_{M_B}^1 &=  R^T_X \Sigma_{M_A}^1 R_X \label{set11} \\
+\Sigma_{M_B}^2 &=  R^T_X \Sigma_{M_A}^1 R_X(\widehat{R^T_X t_x}) + R^T_X \Sigma_{M_A}^2 R_X  \label{set12}
+\end{align}
+\end{subequations}
+
+Calculate the eigendecomposition as $ \Sigma_{i}=Q_i \Lambda Q_i^T$, where $Q_i$ is the square matrix whose $i$th column is the eigenvector of $\Sigma_i$ and $\Lambda$ is the diagonal matrix with corresponding eigenvalues as diagonal entries.
 Write the first block of Eq.~(\ref{set1}) as \cite{ackermanGSI, ackermanIROS2013}:
@@
 
-Once the four possibilities of $R_X$ are found in this manner, the corresponding possible ${\bf t}_X$ can be found easily from blocks 2 and 4 of in Eq.~(\ref{set1})(b).
-\textcolor{blue}{Fix Eq.
-63 to actually have (a) and (b) labels}
+Once the four possibilities of $R_X$ are found in this manner, the corresponding possible ${\bf t}_X$ can be found easily from blocks 2 and 4 of in Eq.~(\ref{set12}).
 
 The correct solution, from the set of 4 possibilities (given Eq.~(\ref{RQ})), can be found by applying the cylindrical constraints as in Eq.~(\ref{nanb}) and Eq.~(\ref{vavb}).
-This is achieved by choosing the \textcolor{blue}{Q?} %possibility
+This is achieved by choosing the Q %possibility
 that minimizes a cost function, such as $\| {\bf n}_{M_A}-R_X {\bf n}_{M_B} \|+w \| {\bf v}_{M_A} - \theta_{M_B} \widehat{\,{\bf t}_X} R_X {\bf n}_{M_B} + R_X {\bf v}_{M_B} \|$
@@
 A more detailed summary can be seen in Table 1 of \cite{andreff1999line}.
-Schmidt {\it{et al.}} \cite{schmidt2003robust} discussed data selection for the dual quaternion hand-eye calibration algorithm based on a RANSAC approach, which shows that the dual quaternion method can give a better $X$ after data selection, while the algorithm can even fail otherwise.
-\textcolor{blue}{Note: Explanation the previous sentence better} However, the computation of all possible relative movements from the data set results in a long computational time.
-
-\textcolor{blue}{I added a paragraph separation , seemed like a long wall of text}
+\textcolor{red}{Schmidt {\it{et al.}} \cite{schmidt2003robust} discussed data selection for the dual quaternion hand-eye calibration algorithm based on a RANSAC approach, which shows that the dual quaternion method can give a better $X$ after data selection, while the dual quaternion method can even fail without data filtering.} \textcolor{blue}{Note: Explanation the previous sentence better} However, the computation of all possible relative movements from the data set results in a long computational time.
 
@@
 As noted in \cite{daniilidis1996dual}, $\| R_{X_{true}} - R_{X_{calc}}\|_F$ is $2\sqrt{2}$ times larger than $\|{\bf q}_{X_{true}} - {\bf q}_{X_{calc}} \|$ so it is important to maintain a consistent error metric especially for result comparisons.
-Another \textcolor{blue}{rotational error metric} %way
+Another rotational error metric %way
  is to calculate the norm of the relative rotation between $X_{true}$ and $X_{calc}$ as:
@@
 For the various $AX=XB$ solvers, the focus is put on the case where there is noise on the incoming sensor data, and therefore multiple sensor readings are needed.
-It was clear that each algorithm has strengths and weaknesses in different contexts, and it is important to use the appropriate method for \textcolor{blue}{different circumstances.} %the circumstance.
+It was clear that each algorithm has strengths and weaknesses in different contexts, and it is important to use the appropriate method for different circumstances.
+%the circumstance.
 
@@
 It will be helpful to categorize the type of motions and their corresponding preferable solvers.
-
-\textcolor{blue}{Re add the acknowledgment section}
 

### 2015-09-02 AXXB_Review/AXXB Review.tex
Adjusted Manuscript for the Review Chapter of Humanoid Robotics : A Reference

@@
 
-\author{Qianli Ma\thanks{Address all correspondence to this author.}\\ 
+\author{Qianli Ma\\ 
 		\textbf{Gregory S. Chirikjian}
@@
 
-\keywords{Sensor Calibration, Hand-Eye Calibration, Humanoid Robot, Review}
+\keywords{ {\color{green}Sensor Calibration, Hand-Eye Calibration, Humanoid Robot, Review}}
 
@@
 \begin{nomenclature}
-\entry{\textcolor{blue}{Note}}{\textcolor{blue}{For SE(3) and se(3) maybe make the inline matrices into actual matrices, it looks a little strange to me the way they are currently.
-Also, possibly consider changing $\Xi$ to $\mathfrak{h}$.
-Also, can you align the beginning of all of the second entries?}}
-\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$\textbf{\textcolor{blue}{,}} %and
- $\det(R) = 1$\textbf{\textcolor{blue}{,}} where $R \in \mathbb{R}^{3 \times 3}\}$}
+\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$ %and
+ $\det(R) = 1$ where $R \in \mathbb{R}^{3 \times 3}\}$}
 \entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \times 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
 \entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
-\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in \textcolor{blue}{so}%SO
+\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in so
 (3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
@@
 \entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
-\entry{$\widetilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
 \entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
@@
 \label{Intro}
-\textcolor{blue}{General Note: Shouldn't alway equations be numbered in an ASME document? It may be IEEE, but I'm just checking}\\
 
@@
 
-\textcolor{blue}{This seems like an awkward transition. Can you add a sentence connecting the two paragraphs?}
-
 Given:
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \includegraphics[width=3.3in]{figure/AX=XB(ASME)_v1.png}
 \centering
-\caption{\textcolor{blue}{Increase the size of text in the image} The AX=XB Sensor Calibration Formulation}
+\caption{The $AX=XB$  Sensor Calibration Formulation}
 \label{AXXBfig1}
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \centering
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \centering
-\includegraphics[width=3.3in]{Photos/Robot_Patern.jpg}
-\caption{\textcolor{blue}{Labels are hard to see in the picture.
-Also, you change the capitalization style midway through} Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
+\includegraphics[width=3.3in]{Photos/Robot_Patern_2.jpg}
+\caption{Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
  \textit{Boston Dynamics} Requires head-body calibration before turning the knob.
@@
 \end{subequations}
-\textcolor{blue}{One strategy for solving Eq.~(\ref{mainaxxb}) reduces to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A$.}
+One strategy for solving Eq.~(\ref{mainaxxb}) reduces to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A$.
 %One strategy to solve Eq.~(\ref{mainaxxb}) \textcolor{blue}{of data}would appear to reduce to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) so as to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A.
 $
-The other strategy is to solve for $R_{X}$ and $\ttt_{X}$ simultaneously based on some cost function $f(R_{X}, \ttt_{X})$ or reformulating the matrix equation into \textcolor{blue}{a dual quaternion representation}.
+The other strategy is to solve for $R_{X}$ and $\ttt_{X}$ simultaneously based on some cost function $f(R_{X}, \ttt_{X})$ or reformulating the matrix equation into a dual quaternion representation.
 %dual quaternion.
 However, when there are only two exact sensor measurements, there are some problems with the first  approach.
-As pointed out in \cite{park1994robot,shiu1989calibration}, in nondegenerate cases, there is a one-parameter set of solutions to \textcolor{blue}{Eq.~\ref{subequ1}}%the first part in Eq.(\ref{subequ1})
+As pointed out in \cite{park1994robot,shiu1989calibration}, in nondegenerate cases, there is a one-parameter set of solutions to Eq.~\ref{subequ1}%the first part in Eq.(\ref{subequ1})
 , and the matrix $R_A - \mathbb{I}_{3}$ in general has a rank of $2$. Hence, there are two unspecified degrees of freedom to the
@@
 to standardize the notation used across the reviewed methods
-\textcolor{blue}{to provide the readers with a straightforward and consistent representation of the methods and their relationships.} %so that readers can have a straightforward and consistent understanding of the methods and their relationships.
+to provide the readers with a straightforward and consistent representation of the methods and their relationships.
+%so that readers can have a straightforward and consistent understanding of the methods and their relationships.
 Some approaches are preferable under certain circumstances and their advantages and disadvantages are also highlighted. 
@@
 \cite{chou1991finding, park1994robot,shiu1989calibration}, with the earliest proposed method introduced by Shiu \cite{shiu1987finding, shiu1989calibration} and Tsai \cite{tsai1989new}.
-\textcolor{blue}{Surprisingly,} applications involving this problem still remain active today \cite{kim,dai}.
+Applications involving this problem still remain active today \cite{kim,dai}.
 Shah \cite{shah2012overview} overviewed several different AX = XB methods qualitatively.
 Fassi and Legnani \cite{fassi2005hand} gave a geometric view of $AX=XB$ and discussed the over-constrained and singular conditions.
-A more complete list of the traditional $AX=XB$ solvers includes: the Shiu method \cite{shiu1989calibration}, the screw motion method \cite{chen91,zhao2006hand}, the Euclidean \textcolor{blue}{g}%G
-roup method \cite{park1994robot,gwak2003numerical}, the quaternion method\cite{chou1988quaternions, chou1991finding, horaud1995hand}, the dual quaternion method \cite{daniilidis1996dual, daniilidis1999hand}, and the Kronecker method \cite{andreff1999line,andreff2001robot}.
+A more complete list of the traditional $AX=XB$ solvers includes: the Shiu method \cite{shiu1989calibration}, the screw motion method \cite{chen91,zhao2006hand}, the Euclidean group method \cite{park1994robot,gwak2003numerical}, the quaternion method\cite{chou1988quaternions, chou1991finding, horaud1995hand}, the dual quaternion method \cite{daniilidis1996dual, daniilidis1999hand}, and the Kronecker method \cite{andreff1999line,andreff2001robot}.
 Several new optimization methods emerged recently such as the convex optimization method \cite{zhao2011hand}, some global optimization methods  \cite{seo2009branch,andreff2001robot,heller2014hand} and a structure from motion (SfM) approach \cite{schmidt2005calibration}.
@@
 The methods mentioned previously are all off-line methods where $X$ can be calculated given a complete list of data pairs.
-However, several online methods \textcolor{blue}{have been} %are
+However, several online methods have been
 proposed that are more preferable to real-time applications \cite{andreff1999line,angeles2000online,ackerman2014online}.
@@
 The closed form expression for $R_{X}$ is:
-\textcolor{blue}{Note: It is hard to \~n in the below equation and also the 2nd subscript on R$_X$}
-\begin{equation}
-R_{X} = \exp{(\widetilde{\nn}_{A}\beta)}R_{X_{P}}
+\begin{equation}
+R_{X} = \exp{(\hat{\nn}_{A}\beta)}R_{X_{P}}
 \label{RotationCheng}
@@
 \begin{center}
-$R_{X_{p}} =  \exp{(\widetilde{\nn}_{X}\theta_{X})}$\\
+$R_{X_{p}} =  \exp{(\widehat{\nn}_{X}\theta_{X})}$\\
 $\nn_{X} = \nn_{B} \times \nn_{A}$\\
@@
 \end{center}
-and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\widetilde{\nn}$ is a skew-symmetric matrix defined as below:\\
-\begin{equation}
-\tilde{\nn}
+and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\widehat{\nn}$ is a skew-symmetric matrix defined as below:\\
+\begin{equation}
+\widehat{\nn}
 =
@@
 \end{subequations}
-Instead of giving a closed-form solution, $R_{X}$ is calculated by solving for $\beta$ in Eq.~(\ref{CYD}), which is formulated \textcolor{blue}{as a system of linear equations obtained} by equating two \textcolor{blue}{instances of} Eq.~(\ref{RotationCheng}) that are obtained from data pairs $(A_{1}, B_{1})$ and $(A_{2}, B_{2})$:
+Instead of giving a closed-form solution, $R_{X}$ is calculated by solving for $\beta$ in Eq.~(\ref{CYD}), which is formulated as a system of linear equations obtained by equating two instances of Eq.~(\ref{RotationCheng}) that are obtained from data pairs $(A_{1}, B_{1})$ and $(A_{2}, B_{2})$:
 \begin{equation}
@@
  $\mathcal{B} = (\nn_{B_{1}}, \nn_{B_{2}}, \nn_{B_{1}} \times \nn_{B_{2}}) \in \mathbb{R}^{3 \times 3} $\\
-\textcolor{blue}{I corrected the format of the two below equations, please make sure they are still correct\\}
 $\tilde{\nn}_{A_{1}} = \log(R_{A_{i}})/\|\log^\vee(R_{A_i})\|$\\
 %(\log R_{A_{i}})^{\vee}||$\\
-$\tilde{\nn}_{B_{1}} = \log(R_{B_{i}})/\|\log^\vee(R_{B_i})\|$
+$\tilde{\nn}_{B_{1}} = \log(R_{B_{i}})/\|\log^\vee(R_{B_i})\|$.
 %(\log R_{B_{i}})^{\vee}||$.
@@
 Note that $i \geq 3$ is a necessary condition for $M$ to be a non-singular matrix, but it does not guarantee $M$ to be nonsingular.
-Theoretically, the Lie group method is more likely to fail when the number of data pairs is small \textcolor{blue}{give an approximation here i.e.
-(<10 pairs)} while in real application, \textcolor{blue}{failure is rarely} %this is barely
-seen as long as the data pairs are not specially chosen \textcolor{blue}{maybe add: specially chosen as ...}.
-Given known $R_{X}$, $\ttt_{X}$ can be calculated using the least squares method shown in Eq.~(\ref{t_least}):
+Theoretically, the Lie group method is more likely to fail when the number of data pairs is small, i.e., close to 3 pairs,  while in real application, failure is rarely %this is barely
+seen as long as the data pairs are not specially chosen such that $M$ is degenerate. Given known $R_{X}$, $\ttt_{X}$ can be calculated using the least squares method shown in Eq.~(\ref{t_least}):
 
@@
 \label{sec:quats}
-The Quaternion method proposed by Chou and Kamel \cite{chou1988quaternions,chou1991finding} uses \textcolor{blue}{unit quaternions?} normalized quaternions to transform the rotation parts of $A_{i}X = XB_{i}$ (i = 1,2) into two linear systems.
+The Quaternion method proposed by Chou and Kamel \cite{chou1988quaternions,chou1991finding} uses unit quaternions normalized quaternions to transform the rotation parts of $A_{i}X = XB_{i}$ (i = 1,2) into two linear systems.
 Then a singular value decomposition (SVD) is performed to obtain a closed-form solution for $R_{X}$.
@@
 Two different approaches are discussed: (1) estimate the rotation matrix $R_{X}$ by minimizing an objective function, and solve for the translation $\ttt_{X}$ using a least squares method separately and (2) estimate $R_{X}$ and $\ttt_{X}$ simultaneously by minimizing an objective function that incorporates both the rotational and translational information.
-Method (1) turns out to have a closed-form solution for \textcolor{blue}{the unit quaternion $q_{X}$ representing the rotation $R_{X}$}%$q_{X}$
+Method (1) turns out to have a closed-form solution for the unit quaternion $q_{X}$ representing the rotation $R_{X}$%$q_{X}$
 , while method (2) is a nonlinear optimization problem which requires an initial guess and will be discussed in Section~\ref{sec:optimization}. 
@@
 \begin{equation}
-\left(\cot(\dfrac{\theta_{A}}{2})\hat{\nn}_{A}(R_{A}-\mathbb{I}_{3})+ R_{A} + \mathbb{I}_{3}\right)\ttt_{x} = \nn_{A}z
+\left(\cot(\dfrac{\theta_{A}}{2})\widehat{\nn}_{A}(R_{A}-\mathbb{I}_{3})+ R_{A} + \mathbb{I}_{3}\right)\ttt_{x} = \nn_{A}z
 \label{QuaternionTranslation} 
@@
 \end{equation}
-The notation for $\bf x$ here will be referred to as in Section \textcolor{blue}{\ref{sec:optimization}.?
-You should not be referring to a future section, but introduce it here an reference later}%3.6.
+The notation for $\bf x$ here will be also used in Section %3.6. 
 To maintain the consistency of notation throughout the chapter as well as preserve the original notation in \cite{daniilidis1996dual}, for a vector ${\bf v} \in \mathbb{R}^{3 \times 1}$, ${\bf v}^{\wedge}$ is the same as $\tilde{\bf v}$ which maps a vector into the corresponding skew-symmetric matrix.
@@
 
-Different from the quaternion method Section~\textcolor{blue}{\ref{sec:quat_method}?}, the dual quaternion method solves the rotational part and translational part in a united way, and it contains all the information to reconstruct matrix $X$.
+Different from the quaternion method Section~\ref{sec:quat_method}, the dual quaternion method solves the rotational part and translational part in a united way, and it contains all the information to reconstruct matrix $X$.
 However, it does not use all of the available information, only the imaginary parts of $\check{a}$ and $\check{b}$.
@@
 \end{equation}
-where $C, d, \bf x$ will be referred to in Section~\ref{sec:optimization} \textcolor{blue}{Again I would not refer to a future section. Check with Dr. C}. 
+where $C, d, \bf x$ will be referred to in Section~\ref{sec:optimization}
 %where the symbol $\otimes$ denotes the Kronecker product.
 The $vec$ operator was introduced in \cite{neudecker1969note} and it's used to reorder the $m \times n$ components of a matrix $M_{m \times n}$ into a $mn$ vector $vec(M_{m \times n})$.\\
-Given multiple pairs of $A$s and $B$s with noise, the Kronecker product is reformulated as:% Eq.(\ref{KroneckerRotation}) and Eq.(\ref{KroneckerTrans}):
+Given multiple pairs of $A$s and $B$s with noise, the Kronecker product is reformulated as:% Eq.~(\ref{KroneckerRotation}) and Eq.~(\ref{KroneckerTrans}):
 \begin{equation}
@@
 \end{equation}
-\textcolor{blue}{and}
+and
 \begin{equation}
@@
 
-The orthogonalized matrix $R_{X_{e}}$ is further normalized as: % in Eq.(\ref{kron_normal}): 
+The orthogonalized matrix $R_{X_{e}}$ is further normalized as: % in Eq.~(\ref{kron_normal}): 
 \begin{equation}
@@
  the  recoverable information in $X$ based on the available type and number of motions.
-Details are included in Section \textcolor{blue}{\ref{sec:data_selection}}.
+Details are included in Section \ref{sec:data_selection}.
 In addition, an on-line hand-eye calibration method is developed for an unknown scene based on the above algorithm, where the camera translations are estimated up to a scaling factor.
@@
 \end{equation}
-where $t_{s+1} = t_{s} + \Delta t$ \textcolor{blue}{$t_{s+1}$ is not used in the equation} is the discrete time step.
-To \textcolor{blue}{prevent steps from becoming too small, the update law of $g_s$ is modified as:}%complete the update law of $g_s$, the rigid body velocity is defined as:
+where $t_{s+1} = t_{s} + \Delta t$ is the discrete time step corresponding to $g_{s+1}$.
+To prevent steps from becoming too small, the update law of $g_s$ is modified as:%complete the update law of $g_s$, the rigid body velocity is defined as:
 \begin{equation}
@@
 \end{equation} 
-\textcolor{blue}{where $\alpha..$}
+where $\alpha..$
 After choosing the cost function as:
 \begin{equation}
-C(X) = \sum_{i=1}^{n}||A_{i}X - XB_{i}||
+C(X) = \sum_{i=1}^{n}||A_{i}X - XB_{i}||.
 \end{equation}
@@
 \label{batchnoisefree}
-This section presents a probabilistic method \cite{ackermanGSI} by Ackerman and Chirikjian to solve for $X$ \textcolor{blue}{in the absence of} %when there does not need to be any 
+This section presents a probabilistic method \cite{ackermanGSI} by Ackerman and Chirikjian to solve for $X$ in the absence of %when there does not need to be any 
 a priori knowledge of the correspondence between the exact sets of measurements
@@
 where $*$ denotes the convolution of functions on $SE(3)$, as defined in the Appendix.
-\textcolor{blue}{Maybe include the definition of $ \delta_{A_i}$}
 \begin{comment}
@@
 
-Let the mean and covariance of a probability density \textcolor{blue}{function} $f(H)$ be defined by the following conditions:
+Let the mean and covariance of a probability density function $f(H)$ be defined by the following conditions:
 \begin{equation} \begin{split} &\int_{SE(3)} \log(M^{-1} H) f(H) dH = \mathbb{O} \,\,\, {\rm and} \,\,\,\\ &\Sigma = \int_{SE(3)} \log^{\vee}(M^{-1} H) [\log^{\vee}(M^{-1} H)]^T  f(H) dH .
@@
 \label{meancovconvdef} \end{equation}
-where \textcolor{blue}{Why not use a \~x to be consistent with your other notation?}
+where
 \begin{equation} 
@@
 where ${\bf \omega} \in \mathbb{R}^3$ and ${\bf v} \in \mathbb{R}^3$ are the elements of the Lie algebra, and writing the rotation and translation parts of Eq.~(\ref{mainmain1rewrite}) separately,
-\textcolor{blue}{Again, throughout this section I would think about using consistent notation. Don't use hat some places and tilde in other places.}
 \begin{equation}
@@
 Calculate the eigendecomposition as $ \Sigma_{i}=Q_i \Lambda Q_i^T$, where $Q_i$ is the square matrix whose $i$th column is the eigenvector of $\Sigma_i$ and $\Lambda$ is the diagonal matrix with corresponding eigenvalues as diagonal entries.
-Write the first block of Eq.~(\ref{set1}) as \cite{ackermanGSI, ackermanIROS2013}:
+Write the first block of Eq.~(\ref{set12}) as \cite{ackermanGSI, ackermanIROS2013}:
 \begin{align}
@@
 {\color{red} {\color{blue}This is something new that can be served as a complement in the review of batch method.}
-When $Q$ is constrained to be a rotation matrix. Eq.(\ref{QAQ}) can be further be written as:
+When $Q$ is constrained to be a rotation matrix. Eq.~(\ref{QAQ}) can be further be written as:
 \begin{equation}
@@
 When $\Lambda$ has repeated entries, a continuum of symmetries result. For example, in the extreme case when $\Lambda = \lambda \mathbb{I}_3$, the
-finite set ${\cal Q}$ would be replaced by $SO(3)$, which is the same as saying that the first equation in Eq.~(\ref{set1}) imposes no constraint.
+finite set ${\cal Q}$ would be replaced by $SO(3)$, which is the same as saying that Eq.~(\ref{set11}) imposes no constraint.
 In general, it is possible to construct trajectories that define the sets $\{A_i\}$ and $\{B_j\}$ such that this does not happen, and so the Batch method limits the discussion to the case where Eq.~(\ref{qset}) holds.
@@
 A more detailed summary can be seen in Table 1 of \cite{andreff1999line}.
-\textcolor{red}{Schmidt {\it{et al.}} \cite{schmidt2003robust} discussed data selection for the dual quaternion hand-eye calibration algorithm based on a RANSAC approach, which shows that the dual quaternion method can give a better $X$ after data selection, while the dual quaternion method can even fail without data filtering.} \textcolor{blue}{Note: Explanation the previous sentence better} However, the computation of all possible relative movements from the data set results in a long computational time.
+Schmidt {\it{et al.}} \cite{schmidt2003robust} discussed data selection for the dual quaternion hand-eye calibration algorithm based on a RANSAC approach for filtering, which shows that the dual quaternion method can yield a better $X$ after data selection; without filtering the method can either fail or perform worse.
+However, the computation of all possible relative movements from the data set results in a long computational time.
 
@@
 \end{equation}
-The first of Eq.(\ref{fprime})  can be rewritten as:
+The first of Eq.~(\ref{fprime})  can be rewritten as:
 \begin{equation}
@@
 \end{equation}
-By changing the variable $K = H^{-1}$ and using the invariance of integration under inversion (as described in the Appendix), Eq.(\ref{f_prime_mean}) can be written as:
+By changing the variable $K = H^{-1}$ and using the invariance of integration under inversion (as described in the Appendix), Eq.~(\ref{f_prime_mean}) can be written as:
 $$ \int_{SE(3)} \log({M'}^{-1} K^{-1}) f(K) dK = \mathbb{O}. $$
@@
 When the sensor that generates $B=\{B_j\}$ is accurate and there is significant
-measurement noise in the set $A = \{A_i\}$, a single $X$ will not solve every instance of Eq.(\ref{main}) and hence the delta function in Eq.(\ref{mainconvall}) 
+measurement noise in the set $A = \{A_i\}$, a single $X$ will not solve every instance of Eq.~(\ref{main}) and hence the delta function in Eq.~(\ref{mainconvall}) 
 will not solve the problem. Instead, we seek a distribution $f_X(H)$ with (a priori unknown) mean $M_X$ and covariance $\Sigma_X$.
 
-We can re-write Eq.(\ref{main}) as
+We can re-write Eq.~(\ref{main}) as
 \begin{equation} A_i = X B_i X^{-1} \label{main2} \end{equation}
-and in a similar fashion as in Eq.(\ref{mainconvall}),we can write the probabilistic form of Eq.(\ref{mainconvall}) as
+and in a similar fashion as in Eq.~(\ref{mainconvall}),we can write the probabilistic form of Eq.~(\ref{mainconvall}) as
 \begin{equation} f_A(H) = (f_X * f_B* f_{X^{-1}})(H). \label{mainconvallwnoise2} \end{equation}
@@
 Using the associativity of convolution, $f_X * f_B* f_{X^{-1}} = f_X * (f_B* f_{X^{-1}})$, 
-and applying Eq.(\ref{meancovconvdef}) to Eq.(\ref{mainconvallwnoise2}) twice, we get
+and applying Eq.~(\ref{meancovconvdef}) to Eq.~(\ref{mainconvallwnoise2}) twice, we get
 \begin{equation}
@@
 \end{equation}
-Note that Eq.(\ref{covprop2}) and Eq.(\ref{covprop22}) are built on the use of (\ref{meancovconvdef}) twice so that they are approximations, unlike
-Eq.(\ref{mainmain11}) and Eq.(\ref{mainmain12}) which are exact (by Theorem \ref{exactthm}). 
-We can simplify this relationship in Eq.(\ref{covprop22}) by proving two identities related to the mean and 
+Note that Eq.~(\ref{covprop2}) and Eq.~(\ref{covprop22}) are built on the use of (\ref{meancovconvdef}) twice so that they are approximations, unlike
+Eq.~(\ref{mainmain11}) and Eq.~(\ref{mainmain12}) which are exact (by Theorem \ref{exactthm}). 
+We can simplify this relationship in Eq.~(\ref{covprop22}) by proving two identities related to the mean and 
 covariance of probability distributions on $SE(3)$ given below.
@@
 As in the noise-free case, $(M_A,\Sigma_A)$ and $(M_B,\Sigma_B)$ are known from the data and are computed from
-Eq.(\ref{datameancovconvdef}). The only difference is that now we seek $(M_X, \Sigma_X)$ instead of just $X$.
-
-With these two properties, as well as the fact that $[Ad(H)]^{-1}=Ad(H^{-1})$, we can write Eq.(\ref{covprop22}) as:
+Eq.~(\ref{datameancovconvdef}). The only difference is that now we seek $(M_X, \Sigma_X)$ instead of just $X$.
+
+With these two properties, as well as the fact that $[Ad(H)]^{-1}=Ad(H^{-1})$, we can write Eq.~(\ref{covprop22}) as:
 \begin{flalign*}
@@
 As in the noise-free case, $(A,\Sigma_A)$ and $(B,\Sigma_B)$ are known from the data and are computed from
-Eq.(\ref{datameancovconvdef}). The only difference is that now we seek $(M_X, \Sigma_X)$ instead of just $X$.
+Eq.~(\ref{datameancovconvdef}). The only difference is that now we seek $(M_X, \Sigma_X)$ instead of just $X$.
 
 \subsection{Computing $M_X$ and $\Sigma_X$}
-From Eq.(\ref{covprop1112}), we can solve for $\Sigma_X$, given an $M_X$. This is done by taking the Kronecker product of both sides and writing
+From Eq.~(\ref{covprop1112}), we can solve for $\Sigma_X$, given an $M_X$. This is done by taking the Kronecker product of both sides and writing
 \begin{equation}
@@
 
-After calculating $\Sigma_X$ from Eq.($\ref{covprop1112}$), we can compare the calculated sample mean and covariance of $\{X_{ij}\}=\{^1X_{ij}\} \cup \{^2X_{ij}\}$ with the solved for values.
+After calculating $\Sigma_X$ from Eq.~($\ref{covprop1112}$), we can compare the calculated sample mean and covariance of $\{X_{ij}\}=\{^1X_{ij}\} \cup \{^2X_{ij}\}$ with the solved for values.
 
@@
 \end{equation}
-If $(M,{\Sigma})$ is known a priori, then $\tilde{\Sigma}$ can be computed from them. Due to the simple computation of $\tilde{\Sigma}$, Eq.(\ref{sigtildesig}) can be used as a consistency
+If $(M,{\Sigma})$ is known a priori, then $\tilde{\Sigma}$ can be computed from them. Due to the simple computation of $\tilde{\Sigma}$, Eq.~(\ref{sigtildesig}) can be used as a consistency
 check on the accuracy of $M$ and $\Sigma$ by computing the norm of the difference of both sides.
@@
 where $D$ is the domain of integration in the parameter space and $d{\bf q} = dq_1 dq_2 \cdots dq_6$. 
-The Jacobian determinant $|J({\bf q})|$ is computed from the Jacobian matrix \textcolor{blue}{Note: You should probably add a quick discussion of right and left Jacobians and clarify that they are different?}
+The Jacobian determinant $|J({\bf q})|$ is computed from the Jacobian matrix:
 $$ J({\bf q}) = \left[\left(H^{-1} \frac{\partial H}{\partial q_1}\right)^{\vee}; \left(H^{-1} \frac{\partial H}{\partial q_2}\right)^{\vee};\,\cdots\,
@@
 for rotations, then ${\bf q} = [x,y,z,\alpha,\beta,\gamma]^T$, $D=\mathbb{R}\times\mathbb{R}\times\mathbb{R}\times[0,2\pi]\times[0,\pi]\times[0,2\pi]$ and $|J({\bf q})| = \sin \beta$.
-And while $D$ and $J({\bf q})$ will change depending on which parametrization is used, the value of the integral itself does not as it is a property of the Lie group and the function themselves and not a matter of how the function is expressed or the coordinates of the integral.
-\textcolor{blue}{I fixed the last sentence slightly; it still needs some work}
+While $D$ and $J({\bf q})$ will change depending on which parametrization is used, the value of the integral itself does not as it is a property of the Lie group.
+The integral depends on the function themselves but not a matter of how the function is expressed or the coordinates of the integral.
 
@@
 This integral can be rewitten in a number of equivalent forms using Eq.~(\ref{defuni}) and Eq.~(\ref{invdsdcf}).
-Convolution inherits the associative property from the underlying group, which is written as 
-$$ (f_1 * f_2) * f_3 = f_1 * (f_2 * f_3) $$
-(where the dependence of these functions on $H$ has been temporarily suppressed). Analogous with the way convolution inherits associativity, it 
+Convolution inherits the associative property from the underlying group, which is written as:
+\begin{equation}
+(f_1 * f_2) * f_3 = f_1 * (f_2 * f_3)
+\end{equation} 
+where the dependence of these functions on $H$ has been temporarily suppressed. Analogous with the way convolution inherits associativity, it 
 also inherits noncommutativity for general functions, with the exception of special functions called ``class functions''.
 
+The Dirac delta function on $SE(3)$ is defined as follows:
+\begin{equation}\label{equ2}
+\delta{(H)}=
+\left\{
+\begin{array}{ll}
++\infty, & H=I \\
+0, & H \neq I
+\end{array}
+\right.
+\end{equation}
+which satisfies the constraint that: 
+\begin{equation}\label{equ3}
+\int_{SE(3)}\delta{(H)}dH=1.
+\end{equation}
+A slightly further expansion of allowable functions to include shifted delta functions of the form:
+\begin{equation}
+\delta_X(H) \doteq \delta(X^{-1} H) = \delta( H X^{-1}).
+\end{equation}
+The unshifted delta function is an example of a symmetric function, in that $\delta(H) = \delta(H^{-1})$.
+
 If the class of functions is expanded to consider beyond $(L^1 \cap L^2)(SE(3))$
-to include Dirac delta functions\footnote{As in $\mathbb{R}^n$, these can be thought of as spikes
-of infinite height and infinitesimal width centered on the identity}, which are the unique functions such that for every $f \in (L^1 \cap L^2)(SE(3))$
-$$ (f * \delta)(H) = (\delta * f)(H) = f(H), $$
-then the result is the ``group algebra'' consisting of functions as elements, and the two operations of convolution and addition of
-functions: $f_1*f_2$ and $f_1 + f_2$.
-\textcolor{blue}{Note: The previous sentence does not make sense} A slightly further expansion of allowable functions to include shifted delta functions of the form:
-$$ \delta_X(H) \doteq \delta(X^{-1} H) = \delta( H X^{-1}). $$
-\textcolor{blue}{The previous sentence is not complete}
-The unshifted delta function is an example of a symmetric function, in that $\delta(H) = \delta(H^{-1})$.
-
+to include Dirac delta functions, then the following is true for every $f \in (L^1 \cap L^2)(SE(3))$:
+\begin{equation}
+(f * \delta)(H) = (\delta * f)(H) = f(H).
+\end{equation}
 Using the properties of the invariant integral on $SE(3)$, convolving a shifted delta function with an arbitrary
@@
 \end{document}
-
-%%-------------------------------------------------------------------------------------
-%\subsection{Solving for $X$ and $\Sigma_X$}
-%
-%
-%
-%
-%\subsubsection{Gradient descent using the $L^2$ Norm}
-%
-%One possible method to search for an appropriate $X$ and $\Sigma_X$ could be by minimizing the cost function
-%\begin{equation}
-%C_2(X) = \left(\int_{SE(3)} \|f_1(H) - f_2(H)\|^2 \, dH \right)^{\half}.
-%\label{cost2} \end{equation}
-%where
-%$$ f_1(H) = \rho(H; A, \Sigma_A) $$
-%and
-%\begin{equation}
-%f_2(H) = \rho(H; X B X^{-1}, \,\, \Sigma_2).
-%\end{equation}
-%where
-%$$ \Sigma_2 = Ad(X) [Ad(B^{-1})\Sigma_X Ad^T(B^{-1}) + \Sigma_{B} + \Sigma_X]Ad^T(X)$$
-%In general, the integral in this cost function cannot be solved in closed form because the $\log$ function is nonlinear, and in terms of exponential coordinates
-%$dH = |J({\bf z})| d{\bf z}$ where $|J({\bf 0})| =1$, but this Jacobian is a nonlinear function of ${\bf z}$.
-%
-%However, if we a priori limit the search for $X$ to the cylinder
-%defined in (\ref{cylinder}), automatically, $X B X^{-1} = A$.
-%Then, we can define a new variable $K = M_A^{-1} H$ and using the property of
-%invariance of integration under shifts, can write
-%$$ C_2(X(\phi,s), \Sigma_X) = \left(\int_{SE(3)} \left| f'_A(K) - f'_B(K) \right|^2 \, dK \right)^{\half} $$
-%where
-%$$ f'_1(K) = \rho(K; \mathbb{I}_4, \Sigma_A) $$
-%and
-%$$  f'_2(K) = \rho(K;\mathbb{I}_4 \,,\, \Sigma_2).$$
-%where
-%\begin{equation}
-%\begin{split}
-%\Sigma_2= &Ad(X(\phi,s)) [Ad(B^{-1})\Sigma_{X(\phi,s)} Ad^T(B^{-1})\\
-%&+ \Sigma_{B} + \Sigma_X(\phi,s)]Ad^T(X(\phi,s))
-%\end{split}
-%\end{equation}
-%And if covariances are scaled to be small, the benefit of this is that it reduces to the integral of the norm of the difference of two Gaussians.
-%This has a closed-form solution
-%\begin{equation}
-%\begin{split}
-%C_2(X(\phi,s), \Sigma_X) = (2\pi)^{-3}&\left[ -2 \frac{\sqrt{\| \Sigma_2^{-1} + \Sigma_A^{-1} \|^{-1}}}{\sqrt{\| \Sigma_A \|}\sqrt{\| \Sigma_2 \|}}\right.\\
-%&\left. + \frac{\sqrt{\| \Sigma_2 \|}}{\sqrt{2}\| \Sigma_2 \|} + \frac{\sqrt{\| \Sigma_A \|}}{\sqrt{2}\| \Sigma_A\|} \right]
-%\end{split}
-%\end{equation}
-%which can be minimized by a search over the 2 remaining DOF of $X$ and the 21 unique entries of $\Sigma_X$.
-%
-%In a similar manner, we can write another cost function, derived from the Kullback–Leibler divergence, and find the global minimum of the cost function
-%\begin{equation}
-%C_2(X) = D_{KL}(f_A \,\|\, \delta_X * f_B  * \delta_{X^{-1}})
-%\label{cost3} \end{equation}
-%where $f_A(H) = \rho(H; M_A, \Sigma_A)$ and
-%$$ (\delta_X * f_B  * \delta_{X^{-1}})(H) = \rho(H;\, X M_B X^{-1} \,,\, Ad(X) \,\Sigma_{B}\, Ad^T(X)). $$
-%
-%As before, if we limit the search for $X$ to the cylinder, the KL divergence of
-%two distributions on $\mathbb{R}^n$ with means ${\bf m}_i$ and covariances $\Sigma_i$ is
-%$$ D_{KL}(f_1 \,\|\, f_2) = $$
-%$$ \half\left[{\rm tr}(\Sigma_2^{-1} \Sigma_1) + ({\bf m}_2 - {\bf m}_1)^T \Sigma_2^{-1} ({\bf m}_2 - {\bf m}_1)
-%-n - {\rm ln}\left(\frac{|\Sigma_1|}{|\Sigma_2|}\right)\right]. $$
-%%% The above is from Wikipedia http://en.wikipedia.org/wiki/Kullback%E2%80%93Leibler_divergence
-%In our problem, ${\bf m}_2 - {\bf m}_1 = {\bf 0}$, and since $SE(3)$ is
-%unimodular, $|Ad(X)| = 1$. 
-%Our cost function then becomes
-%$$ C_2(X(\phi,s), \Sigma_X) = D_{KL}(f'_A \,\|\, f'_B) $$
-%where
-%$$ C'_2(X(\phi,s), \Sigma_X) = {\rm tr}(\Sigma_A^{-1} \Sigma_2) - {\rm ln} \left( \frac{| \Sigma_A |}{|\Sigma_2|} \right), $$
-%and we minimize over the 23 parameters.
-%
-%
-%
-%
-%\subsubsection{Block decomposition}
-%
-%As in the no noise case, we can obtain the rotational component, $R_X$, of $X$. From (\ref{covprop2}) we have that,
-%\begin{equation}
-%{\bf n}_{A}=R_X{\bf n}_{B}
-%\label{ns}\end{equation}.\\
-%
-%If we decompose $\Sigma_{A}$ and $\Sigma_{B}$ into blocks as
-%$ \Sigma_{i}= \left(\begin{array}{cc}
-%\Sigma_{i}^1 & \Sigma_{i}^2 \\
-%\Sigma_{i}^3 & \Sigma_{i}^4  \end{array}\right) $\\
-%\\
-%where $\Sigma_{i}^3 = (\Sigma_{i}^2)^T$, then we can take (\ref{covprop1112})
-%$$\Sigma_{X} + Ad(B^{-1}) \Sigma_{X} Ad^T(B^{-1}) = Ad(X^{-1}) \Sigma_A Ad^T(X^{-1}) - \Sigma_{B}$$
-%and write
-%\begin{equation}
-%\begin{split}
-%&\left[\begin{array}{cc}
-%\Sigma_{X}^1 &\Sigma_{X}^2 \\
-%\Sigma_{X}^3 & \Sigma_{X}^4  \end{array}\right]+
-%\left[\begin{array}{cc}
-%R_{B}^T &  0 \\
-%(\widehat{-R_{B}^Tt_B})R_{B}^T &R_{B}^T \end{array}\right]
-%\left[\begin{array}{cc}
-%\Sigma_{X}^1 &\Sigma_{X}^2 \\
-%\Sigma_{X}^3 & \Sigma_{X}^4  \end{array}\right]
-%\left[\begin{array}{cc}
-%R_{B} &  R_{B}(\widehat{R_{B}^Tt_B}) \\
-%0 &R_{B} \end{array}\right]=\\
-%&\left[\begin{array}{cc}
-%R_{X}^T &  0 \\
-%(\widehat{-R_{X}^Tt_X})R_{X}^T &R_{X}^T \end{array}\right]
-%\left[\begin{array}{cc}
-%\Sigma_{A}^1 &\Sigma_{A}^2 \\
-%\Sigma_{A}^3 & \Sigma_{A}^4  \end{array}\right]
-%\left[\begin{array}{cc}
-%R_{X} &  R_{X}(\widehat{R_{X}^Tt_X}) \\
-%0 &R_{X} \end{array}\right]-
-%\left[\begin{array}{cc}
-%\Sigma_{B}^1 &\Sigma_{B}^2 \\
-%\Sigma_{B}^3 & \Sigma_{B}^4  \end{array}\right].
-%\end{split}
-%\end{equation}
-%Given that
-%\begin{equation}
-%\begin{split}
-%&\left[\begin{array}{cc}
-%R^T &  0 \\
-%(\widehat{-R^Tt})R^T & R^T \end{array}\right]
-%\left[\begin{array}{cc}
-%\Sigma^1 &\Sigma^2 \\
-%\Sigma^3 & \Sigma^4  \end{array}\right]
-%\left[\begin{array}{cc}
-%R &  R(\widehat{R^Tt}) \\
-%0 &R \end{array}\right]=\\
-%&\left[\begin{array}{cc}
-%R^T \Sigma^1 R &  R^T \Sigma^1 R (\widehat{R^Tt}) +R^T \Sigma^2 R \vspace{0.1in}\\
-%\multirow{2}{*}{$(\widehat{-R^Tt})R^T \Sigma^1 R + R^T \Sigma^3 R$} & (\widehat{-R^Tt})R^T \Sigma^1 R (\widehat{R^Tt})+ R^T \Sigma^3 R (\widehat{R^Tt}) \\
-% &+ (\widehat{-R^Tt}) R^T \Sigma^2 R + R^T \Sigma^4 R \end{array}\right]
-%\end{split}
-%\end{equation}
-%we can write the block equations as:
-%\begin{align} 
-%&\Sigma_X^1 + R_B^T \Sigma_X^1 R_B =  R^T_X \Sigma_A^1 R_X - \Sigma_B^1\\
-%\nonumber&\Sigma_X^2 + R_B^T \Sigma_X^1 R_B (\widehat{R_B^Tt_B}) + R_B^T \Sigma_X^2 R_B\\ 
-%&=  R^T_X \Sigma_A^1 R_X (\widehat{R_X^Tt_X}) +R_X^T \Sigma_A^2 R_X - \Sigma_B^2 \\
-%\nonumber &\Sigma_X^3 + (\widehat{-R_B^Tt_B}) R_B^T \Sigma_X^1 R_B + R_B^T \Sigma_X^3 R_B\\
-%&=  (\widehat{-R_X^Tt_X}) R^T_X \Sigma_A^1 R_X + R_X^T \Sigma_A^3 R_X - \Sigma_B^3 \\
-%\begin{split}& \Sigma_X^4 + (\widehat{-R_B^Tt_B}) R_B^T \Sigma_X^1 R_B (\widehat{R_B^Tt_B})  + R_B^T \Sigma_X^3 R_B (\widehat{R_B^Tt_B})\\ 
-%&+ (\widehat{-R_B^Tt_B}) R_B^T \Sigma_X^2 R_B + R_B^T \Sigma_X^4 R_B = \\
-%&(\widehat{-R_X^Tt_X}) R_X^T \Sigma_A^1 R_X (\widehat{R_X^Tt_X}) \\
-%&+ R_X^T \Sigma_A^3 R_X (\widehat{R_X^Tt_X}) + (\widehat{-R_X^Tt_X}) R_X^T \Sigma_A^2 R_X + R_X^T \Sigma_A^4 R_X - \Sigma_B^4 \end{split}
-%\end{align}
-%%--------------------------

### 2015-11-12 submission/root.tex

--- 2015-08-20 Tex_AXYB/paper.tex
@@
 %\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}
-\usepackage{mathtools}   % loads »amsmath«
+\usepackage{mathtools}   % loads Â»amsmathÂ«
 \usepackage{amssymb,amsmath}
@@
 \author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory S. Chirikjian$^{2}$% <-this % stops a space
-\thanks{*This work \textcolor{blue}{was} %is 
-partially
-supported by NSF Grant RI-Medium: \textcolor{blue}{1162095}}%\#IIS-1162095}% <-this % stops a space
+\thanks{*This work was partially supported by NSF Grant RI-Medium: 1162095. Mr. Haiyuan Li's partial work is supported by ¡°863¡± Program
+of China: 2012AA041402.}%% <-this % stops a space
 \thanks{$^{1}$Haiyuan Li and Tianmiao Wang are with the School of Mechanical Engineering and Automation, Beihang University, Beijing 100191, China
         {\tt\small haiyuanli@hotmail.com}, {\tt\small itm@buaa.edu.cn}}%
-\thanks{$^{2}$Qianli Ma and Gregory S. Chirikjian \textcolor{red}{are} with the Department of Mechanical Engineering, Johns Hopkins University,
+\thanks{$^{2}$Qianli Ma and Gregory S. Chirikjian are with the Department of Mechanical Engineering, Johns Hopkins University,
         Baltimore, MD 21218, USA
@@
 For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
-\textcolor{blue}{Calibration is often an important and necessary step in the use of image-guided systems.
+Calibration is often an important and necessary step in the use of image-guided systems.
 In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control.
-As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony is sampling rates and processing time.
+As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony in sampling rates and processing time.
 One common scenario is a constant shift between the two data streams.
@@
 Finally, we numerically simulated the proposed method with shifted, asynchronous data and noise added to the stream of $B$s to verify its efficiency and robustness.
-}
 
@@
 
-Image-guided systems have been widely %used
-\textcolor{blue}{employed in applications throughout} %in 
-robotics such as robot\textbf{\textcolor{blue}{-}}assisted surgery, %automatic
-\textcolor{blue}{autonomously} guided vehicle\textcolor{blue}{s}, etc.
-Sensors such as a camera, a laser scanner\textbf{\textcolor{blue}{,}} or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
-For a typical ``hand-eye'' system as described above, the relative transformation %of
-\textcolor{blue}{between} the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well\textbf{\textcolor{blue}{-}}known $\textbf{AX=XB}$ problem.
+Image-guided systems have been widely employed in applications throughout robotics such as robot-assisted surgery, autonomously guided vehicles, etc.
+Sensors such as a camera, a laser scanner, or an ultrasound probe are usually mounted on the distal end of a robotic manipulator.
+For a typical ``hand-eye'' system as described above, the relative transformation
+between the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well-known $\textbf{AX=XB}$ problem.
 A variation of this problem is the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated.
-In a typical environment, % setup,
-the relationships %among
-\textcolor{blue}{between} the sensor frame, robot frame\textcolor{blue}{,} and world frame are variant and %the
- uncertainties exist. Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robot%s
-  to respond to dynamic environments.
+In a typical environment, the relationships between the sensor frame, robot frame, and world frame are variant and uncertainties exist.
+Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robot to respond to dynamic environments.
 
-In the $\textbf{AX=YB}$ problem, data streams \textcolor{blue}{of} $A$s and $B$s can be respectively obtained via different sensors. The data streams %can be in
-\textcolor{blue}{may arrive in} an asynchronous fashion due to the different working frequencies of the sensors. \textcolor{blue}{This} %The 
-asynchrony causes a shift between the two \textcolor{blue}{data} streams %of data
-which \textcolor{blue}{removes} %damages 
-the correspondence between \textcolor{blue}{the} $A$s and $B$s. In this paper, a novel method is presented to solve for $X$ and $Y$ without %the need to know 
-a priori knowledge of the correspondence between \textcolor{blue}{the} $A$s and $B$s.
+In the $\textbf{AX=YB}$ problem, data streams of $A$s and $B$s can be respectively obtained via different sensors.
+The data streams may arrive in an asynchronous fashion due to the different working frequencies of the sensors.
+This asynchrony causes a shift between the two data streams which removes the correspondence between the $A$s and $B$s.
+In this paper, a novel method is presented to solve for $X$ and $Y$ without a priori knowledge of the correspondence between the $A$s and $B$s.
 
@@
 \caption{
-(1) The hand-eye and robot-world calibration problem %which is 
-formulated as AX=YB. (2) The hand-eye calibration problem %which is 
-formulated as AX=XB. (The Universal Robot \textcolor{blue}{pictured above} %as Shown in the Picture 
-is owned by Prof. Emad Boctor \textcolor{blue}{of} %in the 
-Johns Hopkins University). 
+(1) The hand-eye and robot-world calibration problem formulated as AX=YB.
+(2) The hand-eye calibration problem formulated as AX=XB.
+Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems.
+(The Universal Robot pictured above is owned by Prof.
+Emad Boctor of Johns Hopkins University).
 }
@@
 The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively.
-As shown in Fig.~\ref{fig1} part (2), {\color{red}$A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$}.
-Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ %is
-\textcolor{blue}{are} the relative transformations obtained from the raw data), many \textcolor{blue}{deterministic} methods have been proposed to solve for $X$.
+As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$.
+Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$.
 To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem.
 The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
-All of the methods above assume a prior\textcolor{blue}{i} knowledge of \textcolor{blue}{the} exact correspondence between $A_i$ and $B_i$.
-For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without \textcolor{blue}{a priori knowledge of the} correspondence.
-These %s
-  methods assume that there \textcolor{blue}{are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown}% is exact knowledge of the correspondence between $\{A_i\}$ and $\{B_i\}$
-   \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
+All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$.
+For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence.
+These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
 
@@
 Simulatneous calibration %s
-of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why \textcolor{blue}{a} simultaneous solution for $X$ and $Y$ in \textcolor{blue}{the} $\textbf{AX=YB}$ problem can be a challenging issue.
-Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot \textcolor{blue}{transformations}, %system,
- and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here.
-In the above methods, the correspondence between $A$ and $B$ is known a prior\textcolor{blue}{i}.
-In this paper, we focus on one case of \textcolor{blue}{the} $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.
+of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here.
+In the above methods, the correspondence between $A$ and $B$ is known a priori.
+In this paper, we focus on one case of the $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.
 
-The rest of the paper is organized as follows. {\color{red}In Section
-\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$.} In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, {\color{red} which is used to select the optimal solution among the candidates}.
+The rest of the paper is organized as follows. In Section
+\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$.
+In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates.
 The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}.
-Finally, conclusions are drawn based on the numerical results and possible future work \textcolor{blue}{is} %s are
-pointed out.
+Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.
 
@@
 In this section, a brief introduction to the concept %s
- of probability density function\textcolor{blue}{s (PDFs)} on the special Euclidean group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ \textcolor{blue}{is} %are
-  derived.
+ of probability density functions (PDFs) on the special Euclidean group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ is derived.
 
-Any rigid \textcolor{blue}{body} transformation matrix can be viewed as a group element of $SE(3)$ :
+Any rigid body transformation matrix can be viewed as a group element of $SE(3)$ :
 \begin{equation}\label{equ0}
@@
 \end{equation}
-where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for \textcolor{blue}{the} group element.
+where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for the group element.
 
@@
 \end{equation}
-where $\circ$ denotes the group product, and in this case it is simply matrix multiplication.
-Employing the properties of \textcolor{blue}{the} $\delta$ function, it is straightforward to see that:
+where $\circ$ denotes the group product, and in this case it is simply matrix multiplication. Employing the properties of the $\delta$ function, it is straightforward to see that:
 
@@
 \end{equation}
-
-Defin\textcolor{blue}{ing} %e 
-the \textcolor{blue}{PDF} %probability density function 
+Defing the PDF %probability density function
 of $\{A_i\}$ and $\{B_i\}$ as:
@@
 \end{IEEEeqnarray}
-\textcolor{blue}{then by using the distributivity of convolution, adding $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ8}), and substituting Eq.\textcolor{blue}{~}(\ref{equ7}) in, we have:}
-%Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in, and we will have:
+then by using the distributivity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
 \begin{equation}\label{equ9}
-(f_{A_{i}}\ast \delta_{X})(\textcolor{blue}{H})=(\delta_{Y}\ast f_{B_{i}})(\textcolor{blue}{H})
+(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H)
 %(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
@@
 
-If each of the data stream\textcolor{blue}{s} $\{A_i\}$ and $\{B_i\}$ \textcolor{blue}{are} %is 
-generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly\textbf{\textcolor{blue}{-}}focused''.
-The convolution of two highly\textbf{\textcolor{blue}{-}}focused \textcolor{blue}{PDFs} %probability density functions (PDF)
-have some interesting properties that can be used to solve for $X$. 
-For simplicity, we will drop the integral interval ``$SE(3)$'' for the \textcolor{blue}{remainder of the paper}, 
-%rest of equations, 
-\textcolor{blue}{as} %and 
-it should be self-\textcolor{blue}{evident} %clear 
-given the integration \textcolor{blue}{measure} %variable 
-that is used. %In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ $f(H)$ as:
-\textcolor{blue}{In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:}
+If each of the data streams $\{A_i\}$ and $\{B_i\}$ are generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly-focused''.
+The convolution of two highly-focused PDFs have some interesting properties that can be used to solve for $X$.
+For simplicity, we will drop the integral interval ``$SE(3)$'' for the remainder of the paper, as it should be self-evident given the integration measure that is used.
+In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:
 
@@
 where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
-If $f_A(H)$ is given as in Eq.\textcolor{blue}{~}(\ref{equ8}), then \textcolor{blue}{the} %its
- corresponding discrete version of \textcolor{blue}{the} mean $M_A$ and covariance $\Sigma_A$ will be:
+If $f_A(H)$ is given as in Eq.~\ref{equ8}, then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:
 
@@
 
-The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly\textbf{\textcolor{blue}{-}}focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:
+The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:
 
@@
 Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively.
-Therefore, the following equations can be obtained using Eq.\textcolor{blue}{~}(\ref{equ14}):
+Therefore, the following equations can be obtained using Eq.~\ref{equ14}:
 
@@
 
-To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as \textcolor{blue}{follows:}%below:
+To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as follows:
 
@@
 \end{equation}
-where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$.
-If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.\textcolor{blue}{~}(\ref{equ18}) can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
+where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, the rotation matrix $P$ satisfies Eq.\textcolor{blue}{~}(\ref{equ_P}).
+
+\begin{equation}\label{equ_P}
+\left\{
+\begin{array}{l}
+P^{T} = P^{-1} \\
+det(P) = \pm 1.
+\end{array}
+\right.
+\end{equation}
+Combing Eq.~(\ref{equ18}) and Eq.~(\ref{equ_P}), then a rotation matrix $P$ can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
 
@@
 
-Therefore, there are eight candidates \textcolor{blue}{for} %of 
-$R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained from Eq.\textcolor{blue}{~}(\ref{equ17b}).
-Given known $X$, $Y$  can be solved \textcolor{blue}{from} %for by
-\textcolor{blue}{$Y = M_AXM_B^{-1}$.} %$Y = M_A^{-1}XM_B^{-1}$.
+Therefore, there are eight candidates for $R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained from Eq.\textcolor{blue}{~}(\ref{equ17b}).
+Given known $X$, $Y$  can be solved from $Y = M_AXM_B^{-1}$.
 At last, eight candidate pairs of  $\{X_{k},Y_{k}\}$ can be obtained as:
@@
 The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
-Based on %the
- screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
+Based on screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
 
@@
 
-Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$. Defin\textcolor{blue}{ing} %e
- $B^k = X_k^{-1}Y_kB$, %and 
- we %will
-  have $AX_k=X_kB^k$. There exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
+Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$.
+Defining $B^k = X_k^{-1}Y_kB$, we have $AX_k=X_kB^k$.
+There exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
 
@@
 \end{equation}
-Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$ \textcolor{blue}{to be known}. However,
-the correspondences need %s
- to be recovered to pick the optimal $(X_k, Y_k)$.
+Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$ to be known.
+However, the correspondences need to be recovered to pick the optimal $(X_k, Y_k)$.
 \section{Solution with unknown correspondence between $A_{i}$ and $B_{j}^{k}$}
@@
 Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$ is usually unknown.
-This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-%G
-\textcolor{blue}{g}roup invariants are used to recover the correspondence between the data streams.
-The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is no %t
-a priori knowledge of the correspondence. However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-%G
-\textcolor{blue}{g}roup invariants, it is straightforward to determine which \textcolor{blue}{is the optimal pair} %pair is the optimal one 
-if the correspondence between $A_{i}$ and $B_{j}^{k}$ can be known.
+This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-group invariants are used to recover the correspondence between the data streams.
+The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is no a priori knowledge of the correspondence.
+However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-group invariants, it is straightforward to determine which is the optimal pair if the correspondence between $A_{i}$ and $B_{j}^{k}$ can be known.
 
@@
 
-The discrete convolution of two sequences $f_{n}$ and $g_{n}$ \textcolor{blue}{is} %are 
-defined \textcolor{blue}{as:}
+The discrete convolution of two sequences $f_{n}$ and $g_{n}$ is defined as:
 
 \begin{equation}\label{equ26}
-	\textcolor{blue}{(f \ast g)(\tau)=\sum_{j=0}^{N}f(t_{j})g(t_{j}-\tau).}
+	(f \ast g)(\tau)=\sum_{j=0}^{N}f(t_{j})g(t_{j}-\tau).
 	% Since you are using i for imaginary numbers use j here instead
@@
 \begin{equation}\label{equ28}
-    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot \textcolor{blue}{\mathcal{F^{*}}(g)].}%(\mathcal{F}(g))^{*}].
+    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot \mathcal{F}^{*}(g)].
 \end{equation}
 
-Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the %f
-\textcolor{blue}{F}ast Fourier %t
-\textcolor{blue}{T}ransform (FFT).
+Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the Fast Fourier Transform (FFT).
 
-Given two sequences $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$ corresponding to  $\{A_{i}\}$ and $\{B_{i}^{k}\}$, the shift that is needed to recover the data correspondence is obtained as below.
-Firstly, $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ are normalized as:
-{\color{red}
+Given two sequences $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{j}^{k}}\}$ corresponding to  $\{A_{i}\}$ and $\{B_{j}^{k}\}$, the shift that is needed to recover the data correspondence is obtained as below.
+Firstly, $\theta_{Ai}$ and $\theta_{B_{j}^{k}}$ are normalized as:
+
 \begin{equation}\label{equ29}
-    \theta_{1i}=\frac{(\theta_{A_{i}}-\mu_{A})}{\sigma_{A}}, \theta_{2i}=\frac{(\theta_{B_{i}^{k}}-\mu_{B^{k}})}{\sigma_{B^{k}}}
+    \theta_{1,k}=\frac{(\theta_{A_{i}}-\mu_{A})}{\sigma_{A}}, \theta_{2,k}=\frac{(\theta_{B_{j}^{k}}-\mu_{B^{k}})}{\sigma_{B^{k}}}
 \end{equation}
 where $\mu_{A}(\mu_{B^{k}})$ is the mean of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A}(\sigma_{B^{k}})$ is the standard deviation.
-}
-Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $n$ which describes the probability of these two sequences being separated by this particular index.
-The index corresponding to the maximum of $Corr(\theta_{1},\theta_{2})$  indicates the amount of shift $\tau_{shift}$ between $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$.
+
+Here, the correlation function $Corr(\theta_{1,k},\theta_{2,k})$  is the function of the time sequence index $n$ which describes the probability of these two sequences being separated by this particular index.
+The index corresponding to the maximum of $Corr(\theta_{1,k},\theta_{2,k})$  indicates the amount of shift $\tau_{shift}$ between $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{j}^{k}}\}$.
 
 \begin{equation}\label{equ30}
-    \tau_{shift} = \mathop{\mathbf{arg}max}_{index}(Corr(\theta_{1},\theta_{2}))
+    \tau_{shift} = \mathop{\mathbf{arg}max}_{index}(Corr(\theta_{1,k},\theta_{2,k}))
 \end{equation}
@@
 The data of ${\theta_{A_{i}}}$ or ${d_{A_{i}}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $({\theta_{A_{i}}(i+\tau_{shift})},{\theta_{B_{i}^{k}}})$ and $({d_{A_{i}}(i+\tau_{shift})},{d_{B_{i}^{k}}})$, where $max(0,\tau_{shift})\leq i \leq min(n,n+\tau_{shift})$.
-The data stream can be shifted back to regain correspondence to synchronize the data streams once the shift is computed, and the \textcolor{blue}{optimal} %correct
-solution of $X$ and $Y$ can also be recovered by minimizing the cost function \textcolor{blue}{in} Eq.\textcolor{blue}{~}(\ref{equ23}) using the Euclidean-%G
-\textcolor{blue}{g}roup invariants as shown in Section \ref{sect2}.
+The data stream can be shifted back to regain correspondence to synchronize the data streams once the shift is computed, and the optimal solution of $X$ and $Y$ can also be recovered by minimizing the cost function in Eq.\textcolor{blue}{~}(\ref{equ23}) using the Euclidean-group invariants as shown in Section \ref{sect2}.
 
@@
 \centering
-\includegraphics[width=3in]{fig2.eps}
+\includegraphics[width=3.2in]{fig2.eps}
 \caption{
-%The Errors of Translation and Rotation Versus the Shift between Data Streams $\{A_i\}$ and $\{B_i\}$.
-\textcolor{blue}{The translational and rotational errors versus the shift between data streams $\{A_i\}$ and $\{B_i\}$.} 
+The translational and rotational errors versus the shift between data streams $\{A_i\}$ and $\{B_i\}$.
 }
@@
 \caption{
-Box-and-%W
-\textcolor{blue}{w}hisker %P
-\textcolor{blue}{p}lots of %T
-\textcolor{blue}{t}ranslational and %R
-\textcolor{blue}{r}otational %E
-\textcolor{blue}{e}rrors %V
-\textcolor{blue}{v}ersus the %C
-\textcolor{blue}{c}ovariance %of %N
-\textcolor{blue}{n}oise on %D
-\textcolor{blue}{d}ata %S
-\textcolor{blue}{s}tream $\{B_i\}$.\vspace{6pt}
+Box-and-whisker plots of translational and rotational errors versus the covariance noise on data stream $\{B_i\}$.\vspace{6pt}
 }
@@
 \centering
-\includegraphics[width=3in]{fig4.eps}
+\includegraphics[width=3.2in]{fig4.eps}
 \caption{
-%(a) The Solved $X$ (in Red) and the Actual $X$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.(b) The Solved $Y$ (in Blue) and the Actual $Y$ (in Black) for 10 Trials of Simulation with the Covariance of Noise of 0.05 and the Shift of 2.
-\textcolor{blue}{(a) The solved $X$ (in red) and the actual $X$ (in black) for 10 simulation trials with covariance noise of 0.05 and shift of 2.(b) The solved $Y$ (in blue) and the actual $Y$ (in black) for 10 simulation trials with covariance noise of 0.05 and shift of 2.}
+(a) The solved $X$ (in red) and the actual $X$ (in black) for 10 simulation trials with covariance noise of 0.05 and shift of 2.
+(b) The solved $Y$ (in blue) and the actual $Y$ (in black) for 10 simulation trials with covariance noise of 0.05 and shift of 2.
 }
@@
 \end{IEEEeqnarray}
-where the mean $\mu = {\bf 0} \in se(3)$ and the covariance matrix $\Sigma \in \mathbb{R}^{6 \times 6}$ {\color{red} is a diagonal matrix with same diagonal elements $\sigma$}.
+where the mean $\mu = {\bf 0} \in se(3)$ and the covariance matrix $\Sigma \in \mathbb{R}^{6 \times 6}$  is a diagonal matrix with same diagonal elements $\sigma$.
 The hat operator $\hat{\delta}$ converts a 6 by 1 vector into its corresponding Lie algebra.
@@
 group invariants as defined in Eq.\textcolor{blue}{~}(\ref{equ22}).
-Therefore, a unique pair of $(X_k, Y_k)$ can be selected to minimize the cost function.
-In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ is calculated accurately, the \textcolor{blue}{translational and rotational errors} %errors of translations and rotations
-fluctuate by only a small amount compared to the errors of \textcolor{blue}{the} no-shift data streams.
+Therefore, a unique pair of $(X_k, Y_k)$ ($k=1,\cdots, 8$) can be selected to minimize the cost function.
+In Fig.~\ref{fig2}, because the shift between $\{A_i\}$ and $\{B_i\}$ is calculated accurately, the translational and rotational errors fluctuate by only a small amount compared to the errors of the no-shift data streams.
 
@@
 There are several outliers outside the whiskers, while the median is calculated as the final solved $X$ and $Y$.
-Fig.~\ref{fig4} shows the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black %when the noise covariance
-\textcolor{blue}{with covariance noise of}  $\sigma = 0.05$ and %the
+Fig.~\ref{fig4} shows the solved ($X$,$Y$)s in red and blue with the actual ($X$,$Y$) in black with covariance noise of  $\sigma = 0.05$ and %the
  shift $n = 2$.
+
+ \addtolength{\textheight}{-1.3cm}
 
@@
 \centering
-\includegraphics[width=3in]{fig5.eps}
+\includegraphics[width=3.2in]{fig5.eps}
 \caption{
-%ErrorS of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method without Correspondence.
-\textcolor{blue}{Orientation and translation errors of $X$ and $Y$ versus shift using Li's and Shah's methods without correspondence.}
+Orientation and translation errors of $X$ and $Y$ versus shift using Li's and Shah's methods without correspondence.
 }
@@
 \centering
-\includegraphics[width=3in]{fig6.eps}
+\includegraphics[width=3.2in]{fig6.eps}
 \caption{
-%Errors of Orientation and Translation of $X$ and $Y$ Versus Shift Using Li and Shah Method with Correspondence.
-\textcolor{blue}{Orientation and translation errors of $X$ and $Y$ versus shift using Li's and Shah's methods with correspondence.}
+Orientation and translation errors of $X$ and $Y$ versus shift using Li's and Shah's methods with correspondence.
 }
@@
 The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods.
-In \textcolor{blue}{the} $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence.
+In the $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence.
 However, few of them considered the cases without correspondence.
@@
 
-In this paper, we developed a probabilistic approach to simultaneously obtain $X$ and $Y$ in \textcolor{blue}{the} $AX=YB$ sensor calibration problem.
-Without a prior\textcolor{blue}{i} knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie group\textcolor{blue}{s} is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates.
-Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean\textbf{\textcolor{blue}{-}}group invariants, the correspondence is recovered to determine the correct solution among the eight candidates.
+In this paper, we developed a probabilistic approach to simultaneously obtain $X$ and $Y$ in the $AX=YB$ sensor calibration problem.
+Without a priori knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie groups is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates.
+Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean\textbf{-}group invariants, the correspondence is recovered to determine the correct solution among the eight candidates.
 In the numerical simulation, the method performs well with different sets of data samples.
@@
 
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
+\addtolength{\textheight}{0cm}   % This command serves to balance the column lengths
                                   % on the last page of the document manually. It shortens
@@
 Any opinion, findings, and conclusions or recommendations expressed in this material are those of the author(s)
-and do not necessarily reflect the views of the National Science Foundation.}
+and do not necessarily reflect the views of the National Science Foundation. We thank Mr. Joshua Davis for proofreading of this paper.
+}
 

### 2015-11-16 Matlab_AXYB_Revision/batchAXXB.m
Revision for RA-letter

@@ -1,0 +1,117 @@
+function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B)
+
+X_candidate = zeros(4,4,8);
+Y_candidate = zeros(4,4,8);
+thetaA = zeros(size(A,3),1);
+thetaB = zeros(size(A,3),8);
+dA = zeros(size(A,3),1);
+dB = zeros(size(A,3),8);
+deltaTheta = zeros(size(A,3),8);
+deltaD = zeros(size(A,3),8);
+normMin = zeros(8,1);
+
+[ MeanA, SigA ] = distibutionProps(A);
+[ MeanB, SigB ] = distibutionProps(B);
+
+[ VA, ~ ] = eig( SigA(1:3,1:3) );
+[ VB, ~ ] = eig( SigB(1:3,1:3) );
+
+Q1 = eye(3);
+Q2 = [-1 0 0; 0 -1 0; 0 0 1];
+Q3 = [-1 0 0; 0 1 0; 0 0 -1];
+Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+
+% There are 8 possiblities of Rx
+
+Rx_solved(:,:,1) = VA*Q1*VB';
+Rx_solved(:,:,2) = VA*Q2*VB';
+Rx_solved(:,:,3) = VA*Q3*VB';
+Rx_solved(:,:,4) = VA*Q4*VB';
+Rx_solved(:,:,5) = VA*-Q1*VB';
+Rx_solved(:,:,6) = VA*-Q2*VB';
+Rx_solved(:,:,7) = VA*-Q3*VB';
+Rx_solved(:,:,8) = VA*-Q4*VB';
+
+% Bnew = zeros(4,4,8);
+for i = 1:1:8
+    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
+    tx = -Rx_solved(:,:,i)*tx_temp;
+    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
+    Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
+end
+
+X = X_candidate;
+Y = Y_candidate;
[…]

### 2015-11-16 Matlab_AXYB_Revision/main.m

@@ -1,0 +1,131 @@
+clear all
+close all
+clc
+% [A,B] =  AABB(100);
+% load invariantrandom.mat
+% global xxx yyy bbb
+counter = 0;
+
+Mean=[0;0;0;0;0;0];
+
+Cov = 0.3*eye(6,6); 
+
+point = 10:10:100;
+for k = point
+%     waitbar((k-point(1))/(point(3)-point(1)));
+    
+%  if k==92
+%      continue;
+%  end
+%% --Trajectory Generation-------------------------
+ [A, B, XActual, YActual] =  ABGenerate(k, 0, Mean, Cov);
+% [A,B,XActual,YActual] =  ABGen(k,0);
+
+%% add noise
+gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+nstd = 0.05;  %Gaussian Noise standard deviation Range
+
+% B = sensorNoise(B, gmean, nstd, 1);
+%% Generate A^-1 and B^-1
+A_inv = zeros(4,4,k);
+B_inv = zeros(4,4,k);
+for i = 1:k
+    A_inv(:,:,i) = inv(A(:,:,i));
+    B_inv(:,:,i) = inv(B(:,:,i));
+end
+
+%% --using probility methods------------------------
+% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+[ X1, Y1, MeanA, MeanB, SigA, SigB ] = batchAXXB(A, B);
+[ Y2_inv, X2_inv, ~, ~, ~, ~] = batchAXXB(B_inv, A_inv);
+[ X3, Y3, ~, ~, ~, ~ ] = batchAXYB(A, B);
+
+% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+% Y(4,1:3) = [0 0 0];
+
+m = size(X1,3);
+X2 = zeros(4,4,m);
+Y2 = zeros(4,4,m);
+for i = 1:m
+    X2(:,:,i) = inv(X2_inv(:,:,i));
+    Y2(:,:,i) = inv(Y2_inv(:,:,i));
+end
+
+cost = zeros(8,8);
+for i = 1:size(X1,3)
+    for j = 1:size(Y2,3)
+        cost(i,j) = norm( MeanA*X1(:,:,i) - Y2(:,:,j)*MeanB); 
+    end
+end
+
+[M,I] = min(cost(:));
[…]

### 2015-11-16 Matlab_AXYB_Revision/batchAXXB.m
Added functionality of sovling for X and Y using AX=YB and inv(AX)=inv(YB) & deleted folder Early Versino before 150619

@@ -1,28 +1,27 @@
-function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B)
+function [ X, Y, MeanA, MeanB, SigA, SigB ] = batchAXXB(A, B)
 
 X_candidate = zeros(4,4,8);
 Y_candidate = zeros(4,4,8);
-thetaA = zeros(size(A,3),1);
-thetaB = zeros(size(A,3),8);
-dA = zeros(size(A,3),1);
-dB = zeros(size(A,3),8);
-deltaTheta = zeros(size(A,3),8);
-deltaD = zeros(size(A,3),8);
-normMin = zeros(8,1);
 
-[ MeanA, SigA ] = distibutionProps(A);
-[ MeanB, SigB ] = distibutionProps(B);
+% Reshape A and B for matching the input sies of mex functions
+[a1, a2, a3] = size(A);
+A_mex = reshape(A, a1, a2*a3);
+B_mex = reshape(B, a1, a2*a3);
+
+[ MeanA, SigA ] = distibutionPropsMex_mex(A_mex);
+[ MeanB, SigB ] = distibutionPropsMex_mex(B_mex);
 
 [ VA, ~ ] = eig( SigA(1:3,1:3) );
 [ VB, ~ ] = eig( SigB(1:3,1:3) );
 
 Q1 = eye(3);
-Q2 = [-1 0 0; 0 -1 0; 0 0 1];
-Q3 = [-1 0 0; 0 1 0; 0 0 -1];
-Q4 = [1 0 0; 0 -1 0; 0 0 -1];
+Q2 = [-1 0 0; 0 -1 0; 0 0  1];
+Q3 = [-1 0 0; 0  1 0; 0 0 -1];
+Q4 = [ 1 0 0; 0 -1 0; 0 0 -1];
+
+Rx_solved = zeros(3,3,8);
 
 % There are 8 possiblities of Rx
-
 Rx_solved(:,:,1) = VA*Q1*VB';
 Rx_solved(:,:,2) = VA*Q2*VB';
 Rx_solved(:,:,3) = VA*Q3*VB';
@@ -32,7 +31,6 @@ Rx_solved(:,:,6) = VA*-Q2*VB';
 Rx_solved(:,:,7) = VA*-Q3*VB';
 Rx_solved(:,:,8) = VA*-Q4*VB';
 
-% Bnew = zeros(4,4,8);
 for i = 1:1:8
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/ABGen.m

@@ -1,53 +1,0 @@
-function [A,B,X,Y] = ABGen(len,shift)
-
-numPair = len;
-shift = 0;
-
-A = zeros(4,4,numPair);
-B = zeros(4,4,numPair);
-
-num = numPair + 2;
-t2 = (0:(2*pi)/((num + shift)):2*pi);
-twist = 0.0*sin(16*t2);
-
-ElipseParam = [10, 10, 10];
-
-%% data
-Y1 = [-0.99908 -0.03266 0.02786 164.226/1000;
-      0.02737  0.01553 0.99950 301.638/1000;
-     -0.03308  0.99935 -0.01462 -962.841/1000;
-     0.00000   0.00000 0.00000  1.00000;];
- X1 = [-0.97651 -0.09468 -0.19356 9.190/1000;
-     0.06362 -0.98493 0.16082 5.397/1000;
-     -0.20587 0.14473 0.96782 62.628/1000;
-     0.00000 0.00000 0.00000 1.00000;];
-
-% x = randn(6,1); X = expm(se3_vec(x));
-X=inv(X1);
-Y = Y1;
-trajParam = [.5, .5, .5, 0, 0];
-B1 = createTraj(ElipseParam(1), ElipseParam(2), ElipseParam(3), trajParam(1), trajParam(2), trajParam(3), trajParam(4), trajParam(5), num, twist);
-% [A1, B1] = AB_genTraj(X, ElipseParam, trajParam, num, twist);
-
-trajParam = [.5, .5, .5, 0, 0.5*pi];
-% [A2, B2] = AB_genTraj(X, ElipseParam, trajParam, num, twist);
-B2 = createTraj(ElipseParam(1), ElipseParam(2), ElipseParam(3), trajParam(1), trajParam(2), trajParam(3), trajParam(4), trajParam(5), num/2, twist);
-
-% A = cat(3, A1, A2);
-B = cat(3, B1, B2);
-
-for m = 1:1:size(B,3)
-    A(:,:,m) = Y * B(:,:,m) / X;
-%     figure(1);
-%     trplot(A(:,:,m),'color','r');
-%     axis auto
-%     hold on
-%     figure(2);
-%     trplot(B(:,:,m),'color','b');
-%     axis auto
-%     hold on
-%     pause();
-% end
-% X = inv(X);
-end
-end

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/ABGenerate.m

@@ -1,53 +1,0 @@
-function [A,B,X,Y] =  ABGenerate(length,opt,M,Sig)
-%% 
-% load Asup2;
-% A = Asup2;
-% B = Bsup2;
-% clear;
-% close
-% clc
-%% Times of simulation steps
-len = length;
-% e = precision;
-% digits(64);
-%% generate fixed data X Y
-if opt == 0
-Y = [-0.99908 -0.03266 0.02786 164.226/1000;
-      0.02737  0.01553 0.99950 301.638/1000;
-     -0.03308  0.99935 -0.01462 -962.841/1000;
-     0.00000   0.00000 0.00000  1.00000;];
- X = inv([-0.97651 -0.09468 -0.19356 9.190/1000;
-     0.06362 -0.98493 0.16082 5.397/1000;
-     -0.20587 0.14473 0.96782 62.628/1000;
-     0.00000 0.00000 0.00000 1.00000;]);
-else 
-%% generate random X and Y
-x=randn(6,1); x=x./norm(x); X=expm(se3_vec(x));    %Generate a Random X
-
-y=randn(6,1); y=y./norm(y); Y=expm(se3_vec(y));    %Generate a Random Y
-end
-% using puma560 to generate tranformation B
- qz = [pi/6,pi/3,pi/4,pi/4,-pi/4,0];
- mdl_puma560;
- Binitial = p560.fkine(qz);
-%  Ainitial = Y * Binitial / X;
-%  trplot(Ainitial,'color','b');
-%  trplot(Y,'color','b');
-%  hold on
-% load invariantrandom.mat 
- for m = 1:1:len
-%      r1 = rand(6,1) - 0.5;
-%      B(:,:,m) = Binitial * expm(sig * (twist(r1)));
-%      A(:,:,m) = Y * B(:,:,m) / X;
-%     B(:,:,m) = expm(se3_vec([0;0;0;mvg(M, SigT, 1)]))*(expm(se3_vec([mvg(M, SigR, 1);0;0;0;]))*Binitial);     
-B(:,:,m) = expm(se3_vec(mvg(M, Sig, 1)))*Binitial;      
-A(:,:,m) = Y * B(:,:,m) / X;
-     
-%      A = AA(1:3,4*i-3:4*i-1);
-%      B = BB(1:3,4*i-3:4*i-1);
-%      [OmegaA(:,:,m) thetaA(m)] = rotparam(A(1:3,1:3,m));
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/ABGenerate_rand.m

@@ -1,53 +1,0 @@
-function [A,B,X,Y] =  ABGenerate_rand(length,sig,opt)
-%% 
-% load Asup2;
-% A = Asup2;
-% B = Bsup2;
-% clear;
-% close
-% clc
-%% Times of simulation steps
-len = length;
-% e = precision;
-% digits(64);
-%% generate fixed data X Y
-if opt == 0
-Y = [-0.99908 -0.03266 0.02786 164.226/1000;
-      0.02737  0.01553 0.99950 301.638/1000;
-     -0.03308  0.99935 -0.01462 -962.841/1000;
-     0.00000   0.00000 0.00000  1.00000;];
- X = inv([-0.97651 -0.09468 -0.19356 9.190/1000;
-     0.06362 -0.98493 0.16082 5.397/1000;
-     -0.20587 0.14473 0.96782 62.628/1000;
-     0.00000 0.00000 0.00000 1.00000;]);
-else 
-%% generate random X and Y
-x=randn(6,1); x=x./norm(x); X=expm(se3_vec(x));    %Generate a Random X
-
-y=randn(6,1); y=y./norm(y); Y=expm(se3_vec(y));    %Generate a Random Y
-end
-% using puma560 to generate tranformation B
- qz = [pi/6,pi/3,pi/4,pi/4,-pi/4,0];
- mdl_puma560;
- Binitial = p560.fkine(qz);
-%  Ainitial = Y * Binitial / X;
-%  trplot(Ainitial,'color','b');
-%  trplot(Y,'color','b');
-%  hold on
-% load invariantrandom.mat 
- for m = 1:1:len
-     r1 = rand(6,1) - 0.5;
-     B(:,:,m) = Binitial * expm(sig * (twist(r1)));
-%      A(:,:,m) = Y * B(:,:,m) / X;
-%     B(:,:,m) = expm(se3_vec([0;0;0;mvg(M, SigT, 1)]))*(expm(se3_vec([mvg(M, SigR, 1);0;0;0;]))*Binitial);     
-% B(:,:,m) = expm(se3_vec(mvg(M, Sig, 1)))*Binitial;      
-A(:,:,m) = Y * B(:,:,m) / X;
-     
-%      A = AA(1:3,4*i-3:4*i-1);
-%      B = BB(1:3,4*i-3:4*i-1);
-%      [OmegaA(:,:,m) thetaA(m)] = rotparam(A(1:3,1:3,m));
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/batchAXYB.m

@@ -1,114 +1,0 @@
-function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B)
-
-X_candidate = zeros(4,4,8);
-Y_candidate = zeros(4,4,8);
-thetaA = zeros(size(A,3),1);
-thetaB = zeros(size(A,3),8);
-dA = zeros(size(A,3),1);
-dB = zeros(size(A,3),8);
-deltaTheta = zeros(size(A,3),8);
-deltaD = zeros(size(A,3),8);
-normMin = zeros(8,1);
-
-[ MeanA, SigA ] = distibutionProps(A);
-[ MeanB, SigB ] = distibutionProps(B);
-
-[ VA, ~ ] = eig( SigA(1:3,1:3) );
-[ VB, ~ ] = eig( SigB(1:3,1:3) );
-
-Q1 = eye(3);
-Q2 = [-1 0 0; 0 -1 0; 0 0 1];
-Q3 = [-1 0 0; 0 1 0; 0 0 -1];
-Q4 = [1 0 0; 0 -1 0; 0 0 -1];
-
-% There are 8 possiblities of Rx
-
-Rx_solved(:,:,1) = VA*Q1*VB';
-Rx_solved(:,:,2) = VA*Q2*VB';
-Rx_solved(:,:,3) = VA*Q3*VB';
-Rx_solved(:,:,4) = VA*Q4*VB';
-Rx_solved(:,:,5) = VA*-Q1*VB';
-Rx_solved(:,:,6) = VA*-Q2*VB';
-Rx_solved(:,:,7) = VA*-Q3*VB';
-Rx_solved(:,:,8) = VA*-Q4*VB';
-
-Bnew = zeros(4,4,8);
-for i = 1:1:8
-    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
-    tx = -Rx_solved(:,:,i)*tx_temp;
-    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
-    Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
-end
-% use Fouier transformation to find the correspondence between A and X-1YB
-
-for i = 1:1:size(A,3)
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/batchAXYBshift.m

@@ -1,175 +1,0 @@
-function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(A, B)
-
-X_candidate = zeros(4,4,8);
-Y_candidate = zeros(4,4,8);
-thetaA = zeros(size(A,3),1);
-thetaB = zeros(size(A,3),8);
-dA = zeros(size(A,3),1);
-dB = zeros(size(A,3),8);
-deltaTheta = zeros(size(A,3),8);
-deltaD = zeros(size(A,3),8);
-normMin = zeros(8,1);
-
-[ MeanA, SigA ] = distibutionProps(A);
-[ MeanB, SigB ] = distibutionProps(B);
-
-[ VA, ~ ] = eig( SigA(1:3,1:3) );
-[ VB, ~ ] = eig( SigB(1:3,1:3) );
-
-Q1 = eye(3);
-Q2 = [-1 0 0; 0 -1 0; 0 0 1];
-Q3 = [-1 0 0; 0 1 0; 0 0 -1];
-Q4 = [1 0 0; 0 -1 0; 0 0 -1];
-
-% There are 8 possiblities of Rx
-
-Rx_solved(:,:,1) = VA*Q1*VB';
-Rx_solved(:,:,2) = VA*Q2*VB';
-Rx_solved(:,:,3) = VA*Q3*VB';
-Rx_solved(:,:,4) = VA*Q4*VB';
-Rx_solved(:,:,5) = VA*-Q1*VB';
-Rx_solved(:,:,6) = VA*-Q2*VB';
-Rx_solved(:,:,7) = VA*-Q3*VB';
-Rx_solved(:,:,8) = VA*-Q4*VB';
-
-Bnew = zeros(4,4,8);
-for i = 1:1:8
-    tx_temp = so3_vec(((Rx_solved(:,:,i)'*SigA(1:3,1:3)*Rx_solved(:,:,i))^-1*(SigB(1:3,4:6)-Rx_solved(:,:,i)'*SigA(1:3,4:6)*Rx_solved(:,:,i)))');
-    tx = -Rx_solved(:,:,i)*tx_temp;
-    X_candidate(:,:,i) = [Rx_solved(:,:,i) tx; [0 0 0] 1];
-    Y_candidate(:,:,i) = MeanA * X_candidate(:,:,i) /(MeanB);
-end
-% use Fouier transformation to find the correspondence between A and X-1YB
-
-for i = 1:1:size(A,3)
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/display1.m

@@ -1,16 +1,0 @@
-for i = 1:1:size(sigArray,2)
-figure
-h1 = subplot(4,1,1)
-plot(median(rotErrX(:,1:6,i)));
-axis auto;
-h2 = subplot(4,1,2)
-plot(median(rotErrY(:,1:6,i)));
-axis auto;
-h3 = subplot(4,1,3)
-plot(median(tranErrX(:,1:6,i)));
-
-axis auto;
-h4 = subplot(4,1,4)
-plot(median(tranErrY(:,1:6,i)));
-axis auto;
-end

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/distibutionProps.m

@@ -1,81 +1,0 @@
-function [ M, Sig ] = distibutionProps( X )
-
-
-Xsum = zeros(4);
-
-% 1. Use X to calculate the mean of se(3) Lie algebra
-% 2. Exponentiate the mean of se(3) into Lie group SE(3) 
-for j = 1:size(X,3)
-    Xsum = Xsum + logm(X(:,:,j));
-end
-
-M = expm( (1/size(X,3))*Xsum );
-
-C_old = inf; C = 0;
-
-diff = 0.05; eps = 0.001;
-
-% The six Lie algebra elements for SE(3)
-E(:,:,1) = [0 0 0 0; 0 0 -1 0; 0 1 0 0; 0 0 0 0]; 
-E(:,:,2) = [0 0 1 0; 0 0 0 0; -1 0 0 0; 0 0 0 0]; 
-E(:,:,3) = [0 -1 0 0; 1 0 0 0; 0 0 0 0; 0 0 0 0];
-E(:,:,4) = [0 0 0 1; 0 0 0 0; 0 0 0 0; 0 0 0 0]; 
-E(:,:,5) = [0 0 0 0; 0 0 0 1; 0 0 0 0; 0 0 0 0]; 
-E(:,:,6) = [0 0 0 0; 0 0 0 0; 0 0 0 1; 0 0 0 0];
-
-count = 0;
-while( abs(C-C_old) > diff && count < 10 )
-    
-    C_old = C;
-    
-    for j = 1:6
-        
-        if C_old > 20
-            M1 = M*expm(eps*20*E(:,:,j));
-            M2 = M*expm(-eps*20*E(:,:,j));
-        elseif C_old > 1
-            M1 = M*expm(eps*C_old*E(:,:,j));
-            M2 = M*expm(-eps*C_old*E(:,:,j));
-            
-        else
-            M1 = M*expm(eps*E(:,:,j));
-            M2 = M*expm(-eps*E(:,:,j));
-            
-        end
-        
-        
-        M1sum = zeros(4);
-        M2sum = zeros(4);
-        for k = 1:size(X,3)
-            M1sum = M1sum + logm( M1^-1*X(:,:,k) );
-            M2sum = M2sum + logm( M2^-1*X(:,:,k) );
-            
-        end
-        
-        
-        C1 = norm(M1sum)^2;
-        C2 = norm(M2sum)^2;
-        
-        if (C1 <= C2)
-            C = C1;
-            M = M1;
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main.m

@@ -1,97 +1,0 @@
-clear all
-close all
-clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-counter = 0;
-
-Mean=[0;0;0;0;0;0];
-
-Cov=0.3*eye(6,6); 
-
-point = [100 10 100];
-for k = point(1):point(2):point(3)
-    waitbar((k-point(1))/(point(3)-point(1)));
-    
-%  if k==92
-%      continue;
-%  end
-%% --Trajectory Generation-------------------------
- [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
-% [A,B,XActual,YActual] =  ABGen(k,0);
-
-%% add noise
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-nstd = 0.05;  %Gaussian Noise standard deviation Range
-
-B = sensorNoise(B, gmean, nstd, 1);
-
-%% --using probility methods------------------------
-% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-Y(4,1:3) = [0 0 0];
-%% err analysis
-counter = counter + 1;
-num(counter) = k;
-Err(counter,1) = roterror(X,XActual);
-Err(counter,2) = roterror(Y,YActual);
-Err(counter,3) = tranerror(X,XActual);
-Err(counter,4) = tranerror(Y,YActual);
-%% plot 
-% for j = 1:1:k
-%     figure(3);
-%     trplot(A(:,:,j),'color','r');
-%     axis auto
-%     hold on
-%     figure(4);
-%     trplot(B(:,:,j),'color','b');
-%     axis auto
-%     hold on
-% end
-% figure(3);
-% legend('Generated A');
-% figure(4);
-% legend('Generated B');
-
-%% --plot X and Y-------------------------------------------
-figure(5);
-trplot(X(:,:),'color','b');
-axis auto
-hold on
-figure(6);
-trplot(Y(:,:),'color','b');
-axis auto
-hold on
-% for n = 1:1:k
-% 	figure(3);
-%     trplot(A(:,:,n),'color','b');
-%     axis auto
-%     hold on
-% end
-% for n = 1:1:k
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCov.m

@@ -1,86 +1,0 @@
-clear all
-close all
-clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-counter = 0;
-trials = 20;
-sigArray = [0.1 0.2 0.4 0.6 0.8 1 2];
-
-h = waitbar(0);
-for n = 1:1:size(sigArray,2)
-for m = 1:1:trials
-
-point = [50 10 50];
-for k = point(1):point(2):point(3)
-
-waitbar((m + (n-1)*trials)/(trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(m + (n-1)*trials),trials*size(sigArray,2)))
-% waitbar((k-point(1))/(point(3)-point(1)));
-
-%% --Trajectory Generation-------------------------
- [A,B,XActual,YActual] =  ABGenerate(k,sigArray(n),0);
-% [A,B,XActual,YActual] =  ABGen(k,0);
-
-%% add noise
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-nstd = 0.01;  %Gaussian Noise standard deviation Range
-
-B = sensorNoise(B, gmean, nstd, 1);
-
-%% --using probility methods------------------------
-% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-Y(4,1:3) = [0 0 0];
-%% err analysis
-counter = counter + 1;
-num(counter) = k;
-Err(counter,1) = roterror(X,XActual);
-Err(counter,2) = roterror(Y,YActual);
-Err(counter,3) = tranerror(X,XActual);
-Err(counter,4) = tranerror(Y,YActual);
-
-figure(1)
-trplot(X,'color','r');
-hold on
-axis auto
-% legend('solved and actual X');
-figure(2)
-trplot(Y,'color','r');
-hold on
-axis auto
-
-end
-
-rotErrX(m,n) = Err(counter,1);
-rotErrY(m,n) = Err(counter,2);
-tranErrX(m,n) = Err(counter,3);
-tranErrY(m,n) = Err(counter,4);
-end
-end
-
-figure(1)
-trplot(XActual(:,:),'color','k');
-% legend('solved and actual X');
-figure(2)
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCovNoise.m

@@ -1,102 +1,0 @@
-clear all
-close all
-clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-
-nstd = 0.02;%[0.01 0.02 0.04 0.06 0.08];%[0.01 0.02 0.04 0.06 0.08 0.1];  %Gaussian Noise standard deviation Range
-
-counter = 0;
-trials = 5;
-% sigArrayR =  0.3;
-% sigArrayT =  0.3;%[0.1 0.2 0.3];
-sigArray = 0.3;
-Mean=[0;0;0;0;0;0;];
-
-h = waitbar(0);
-
-for n = 1:1:size(sigArray,2)
-    
-    for n_noise = 1:1:size(nstd,2)
-    
-    for m = 1:1:trials
-
-        point = [50 10 50];
-        for k = point(1):point(2):point(3)
-
-            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
-            % waitbar((k-point(1))/(point(3)-point(1)));
-            Cov=sigArray(n)*eye(6,6); 
-%             CovR=sigArrayR(n)*eye(3,3); 
-%             CovT=sigArrayT(1)*eye(3,3);
-           %% --Trajectory Generation-------------------------
-            [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
-            % [A,B,XActual,YActual] =  ABGen(k,0);
-
-           %% add noise
-%             B = sensorNoise(B, gmean, nstd(n_noise), 1);
-
-           %% --using probility methods------------------------
-            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-            % [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-            Y(4,1:3) = [0 0 0];
-            %% err analysis
-%             counter = counter + 1;
-%             num(counter) = k;
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCovNoiseComparison.m

@@ -1,116 +1,0 @@
-clear all
-close all
-clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-
-nstd = [0.01 0.02 0.04 0.06 0.08 0.1 0.2 0.4 0.6 0.8 1];  %Gaussian Noise standard deviation Range
-
-counter = 0;
-trials = 5;
-sigArray = 2;%[0.1 0.2 0.6 0.8 2];
-
-h = waitbar(0);
-
-for n = 1:1:size(sigArray,2)
-    
-    for n_noise = 1:1:size(nstd,2)
-    
-    for m = 1:1:trials
-
-        point = [100 10 100];
-        for k = point(1):point(2):point(3)
-
-            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
-            % waitbar((k-point(1))/(point(3)-point(1)));
-
-           %% --Trajectory Generation-------------------------
-            [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray(n),0);
-            % [A,B,XActual,YActual] =  ABGen(k,0);
-
-           %% add noise
-            B = sensorNoise(B, gmean, nstd(n_noise), 1);
-
-           %% --using probility methods------------------------
-            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-%             [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-%             [AA,BB] = dataTransAB(A,B);
-%             [X,Y]=zhuang(AA,BB);
-            
-            Y(4,1:3) = [0 0 0];
-            %% err analysis
-            counter = counter + 1;
-            num(counter) = k;
-            Err(counter,1) = roterror(X,XActual);
-            Err(counter,2) = roterror(Y,YActual);
-            Err(counter,3) = tranerror(X,XActual);
-            Err(counter,4) = tranerror(Y,YActual);
-%             figure(n)
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_ABCovNoise_rand.m

@@ -1,102 +1,0 @@
-clear all
-close all
-clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-nstd = [0.01 0.02 0.04 0.06 0.08];
-% nstd = [0.01 0.04 0.06 0.08];%[0.01 0.02 0.04 0.06 0.08 0.1];  %Gaussian Noise standard deviation Range
-
-counter = 0;
-trials = 5;
-% sigArrayR =  0.3;
-% sigArrayT =  0.3;%[0.1 0.2 0.3];
-sigArray = [0.1 0.2 0.4 0.6 0.8 1 2];
-Mean=[0;0;0;0;0;0;];
-
-h = waitbar(0);
-
-for n = 1:1:size(sigArray,2)
-    
-    for n_noise = 1:1:size(nstd,2)
-    
-    for m = 1:1:trials
-
-        point = [100 10 100];
-        for k = point(1):point(2):point(3)
-
-            waitbar((trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2))/(size(nstd,2) * trials * size(sigArray,2)),h,sprintf('Now step %d in total %d ',(trials * (n_noise - 1) + m + (n-1)*trials*size(nstd,2)),size(nstd,2) * trials*size(sigArray,2)))
-            % waitbar((k-point(1))/(point(3)-point(1)));
-%             Cov=sigArray(n)*eye(6,6); 
-%             CovR=sigArrayR(n)*eye(3,3); 
-%             CovT=sigArrayT(1)*eye(3,3);
-           %% --Trajectory Generation-------------------------
-            [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray(n),0);
-            % [A,B,XActual,YActual] =  ABGen(k,0);
-
-           %% add noise
-            B = sensorNoise(B, gmean, nstd(n_noise), 1);
-
-           %% --using probility methods------------------------
-            % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-            [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-            % [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-            Y(4,1:3) = [0 0 0];
-            %% err analysis
-%             counter = counter + 1;
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_shift.m

@@ -1,109 +1,0 @@
-
-clear all
-close all
-clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-counter = 1;
-trials = 5;
-Mean=[0;0;0;0;0;0;];
-% point = [50 1 50];
-% sum = zeros(1,4);
-point = [210 5 210];
-sum = zeros(1,4);
-sigArray = 0.3;
-shift = 2;
-for k = point(1):point(2):point(3)
-for i = 1:1:trials
-%     waitbar((k-point(1))/(point(3)-point(1)));
-    
-%  if k==92
-%      continue;
-%  end
-%% --Trajectory Generation-------------------------
-%  [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray,0);
-% [A,B,X,Y] =  ABGen(k,0);
-Cov=sigArray*eye(6,6);
-[A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
- length = size(A,3);
-i
-As = A(:,:,1:(length - shift));
-Bs = B(:,:,(shift + 1):length);
-
-%% add noise
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-nstd = 0.01;  %Gaussian Noise standard deviation Range
-
-B = sensorNoise(B, gmean, nstd, 1);
-
-%% --using probility methods------------------------
-% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(As, Bs);
-% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-Y(4,1:3) = [0 0 0];
-%% err analysis
-
-% sum(counter,1) = sum(counter,1) + roterror(X,XActual);
-% sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
-% sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
-% sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
-% 
-% 
-% num(counter) = k;
-% counter = counter + 1;
-
-%% plot 
-
-    figure(11);
-    trplot(X,'color','b');
-    axis auto
-    hold on
-    figure(12);
-    trplot(Y,'color','b');
-    axis auto
-    hold on
-end
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/main_shiftVary.m

@@ -1,9 +1,0 @@
-clear all
-close all
-clc
-errXY=zeros(4,11);
-for shift = 0:1:5
-    errXY(:,shift+1) = shift_main(shift);
-    
-end
-plot(errXY')

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/shift_main.m

@@ -1,110 +1,0 @@
-function errXY = shift_main(shift) 
-% clear all
-% close all
-% clc
-% [A,B] =  AABB(100);
-% load invariantrandom.mat
-% global xxx yyy bbb
-counter = 1;
-trials = 5;
-Mean=[0;0;0;0;0;0;];
-% point = [50 1 50];
-% sum = zeros(1,4);
-point = [210 5 210];
-sum = zeros(1,4);
-sigArray = 2;
-% shift = 2;
-for k = point(1):point(2):point(3)
-for i = 1:1:trials
-%     waitbar((k-point(1))/(point(3)-point(1)));
-    
-%  if k==92
-%      continue;
-%  end
-%% --Trajectory Generation-------------------------
- [A,B,XActual,YActual] =  ABGenerate_rand(k,sigArray,0);
-% [A,B,X,Y] =  ABGen(k,0);
-% Cov=sigArray*eye(6,6);
-% [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
- length = size(A,3);
-
-As = A(:,:,1:(length - shift));
-Bs = B(:,:,(shift + 1):length);
-
-%% add noise
-gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
-nstd = 0.01;  %Gaussian Noise standard deviation Range
-
-% B = sensorNoise(B, gmean, nstd, 1);
-
-%% --using probility methods------------------------
-% [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
-% [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
-[ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYBshift(As, Bs);
-% [XX(:,:,k)] = AXYB_LieGroup2( A, B );
-Y(4,1:3) = [0 0 0];
-%% err analysis
-
-sum(counter,1) = sum(counter,1) + roterror(X,XActual);
-sum(counter,2) = sum(counter,2) + roterror(Y,YActual);
-sum(counter,3) = sum(counter,3) + tranerror(X,XActual);
-sum(counter,4) = sum(counter,4) + tranerror(Y,YActual);
-end
-
-num(counter) = k;
-counter = counter + 1;
-
-%% plot 
-% for j = 1:1:k
-%     figure(11);
-%     trplot(A(:,:,j),'color','r');
-%     axis auto
-%     hold on
-%     figure(12);
[…]

### 2015-11-16 Matlab_AXYB_Ver2/Version 2 -Gaussian/test_ABdistribution.m

@@ -1,27 +1,0 @@
-clear all
-%close all
-clc
-
-counter = 0;
-
-Mean=[0;0;0;0;0;0];
-
-Cov=1.2*eye(6,6);   
-
-point = [50 10 50];
-k = 50;
-
-[A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
-
-for n = 1:1:k
-	figure(5);
-    trplot(A(:,:,n),'color','b');
-    axis auto
-    hold on
-end
-for n = 1:1:k
-	figure(6);
-    trplot(B(:,:,n),'color','b');
-    axis auto
-    hold on
-end

### 2015-11-17 submission/root.tex
rewrite .bib file & description for figure & minor changes

@@
 Emad Boctor of Johns Hopkins University).
+Note: the $A$ and $B$ in the above two problems have different physical meanings.
+One is the absolute transformation and the other is relative transformation as can be seen in the figures.
 }
@@
 Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$.
-To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem.
-The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}.
+To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem.
+The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory,motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,fassi2005hand,zhao2011hand,ackerman2014online}.
 All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$.
 For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence.
-These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.
+These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.
 
@@
 The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations.
-This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}.
+This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative, ernst2012non,strobl2006optimal,li2010simultaneous,shah2013solving,heller2014hand}.
 Simulatneous calibration %s
 of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue.
-Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{wang2014towards} which will not be discussed in detail here.
 In the above methods, the correspondence between $A$ and $B$ is known a priori.
@@
 where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
-If $f_A(H)$ is given as in Eq.~\ref{equ8}, then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:
+If $f_A(H)$ is given as in Eq.~(\ref{equ8}), then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:
 
@@
 
-Given $\{A_i\}$ with the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:
+Given $\{A_i\}$ with the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{wang2008nonparametric} as:
 
@@
 
-The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:
+The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{wang2008nonparametric}:
 
@@
 We augment other $AX=YB$ solvers with our probabilistic approach.
-In Li's method \cite{Li2010}, $X$ and $Y$ are solved for at the same time while Shah \cite{Shah2013} uses separable solutions to solve for $X$ and $Y$.
+In Li's method \cite{li2010simultaneous}, $X$ and $Y$ are solved for at the same time while Shah \cite{shah2013solving} uses separable solutions to solve for $X$ and $Y$.
 In Fig.~\ref{fig5}, the correspondence between data streams is unknown and the errors on both rotations and translations are significant.
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,bibIEEEfull}
+\bibliography{IEEEabrv,root}
 %\begin{thebibliography}{1}

### 2015-11-17 submission/root.tex
Added description at the end of section II

@@
 To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem.
-The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory,motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,fassi2005hand,zhao2011hand,ackerman2014online}.
+The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,fassi2005hand,zhao2011hand,ackerman2014online}.
 All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$.
-For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence.
+For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the litefit rature to solve for $X$ using data without a priori knowledge of the correspondence.
 These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.
@@
 Defining $B^k = X_k^{-1}Y_kB$, we have $AX_k=X_kB^k$.
-There exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
+As discussed in \cite{ackerman2013sensor}, for $AX=XB$ problem, there exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
 
@@
 However, the correspondences need to be recovered to pick the optimal $(X_k, Y_k)$.
+Note that the Euclidean-group invariant relationships in the context of $AX=YB$ problem are still unknown.
+Therefore, $AX=YB$ is converted into $AX=XB$ problem to recover the correspondence of data using invariants.
+
 \section{Solution with unknown correspondence between $A_{i}$ and $B_{j}^{k}$}
@@
 
+\section{A Brief Case Study With Completely Scrambled Data}
+
 \section{Conclusions}

### 2015-11-17 submission/root.tex
Added another section for solving B^-1 Y^-1=X^-1 A^-1 problem

@@
 To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem.
-The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,fassi2005hand,zhao2011hand,ackerman2014online}.
+The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,rovelo2008geometric, fassi2005hand,zhao2011hand,ackerman2014online}.
 All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$.
@@
 The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}.
+In Section \ref{sect5}, we briefly discuss the case where one can obtain $\left( X, Y \right)$ without recovering the correspondence between the data sets.
 Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.
@@
 \end{equation}
-Defing the PDF %probability density function
+Defining the PDF %probability density function
 of $\{A_i\}$ and $\{B_i\}$ as:
@@
 \begin{IEEEeqnarray}{l}\label{equ11}
-\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
+\int log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
 \\*
@@
 \end{IEEEeqnarray}
-where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
+where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic} as:
+
+\begin{equation}
+log(H) = \widehat{\bf h} 
+=
+\left(
+\begin{array}{cccc}
+   0 & -h_3 &  h_2 & h_4 \\ 
+ h_3 &    0 & -h_1 & h_5 \\
+-h_2 & -h_1 &    0 & h_6 \\
+   0 &    0 &    0 &  0 
+\end{array}
+\right)
+\end{equation}
+where ${\bf h} = log^\vee(H) \in \mathbb{R}^{6 \times 1}$ and $\widehat{\bf h}$ is the corresponding Lie algebra element ($se(3)$) of $H$.
+
 If $f_A(H)$ is given as in Eq.~(\ref{equ8}), then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:
@@
 \begin{IEEEeqnarray}{l}\label{equ12}
-\sum_{i=1}^{n}log(M_A^{-1}A_i)) = \mathbb{O} \IEEEyessubnumber
+\sum_{i=1}^{n}log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
 \\*
@@
 
-The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods.
+The probabilistic method can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods.
 In the $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence.
@@
 When data streams of ${A}$ and ${B}$ are shifted or asynchronous, most of these methods fail to give a valid solution.
-To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$.
-We augment other $AX=YB$ solvers with our probabilistic approach.
-In Li's method \cite{li2010simultaneous}, $X$ and $Y$ are solved for at the same time while Shah \cite{shah2013solving} uses separable solutions to solve for $X$ and $Y$.
-In Fig.~\ref{fig5}, the correspondence between data streams is unknown and the errors on both rotations and translations are significant.
-After synchronizing the data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as in the no-shift situation as shown in Fig.~\ref{fig6}.
+To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$ such that $A_{k+n}$ ``matches'' $B_k$ where $k = 1, 2, \cdots, m-n$ and $i = 1,2, \cdots, m$.
+We augment other $AX=YB$ solvers with our probabilistic approach by recovering the correspondence between shift data sets.
+In Li's method \cite{li2010simultaneous}, $X$ and $Y$ are solved for at the same time, while Shah \cite{shah2013solving} solved for $X$ and $Y$ in a separate way.
+As shown in Fig.~\ref{fig5}, when dealing with the shifted data streams $\{A_{k+n}, B_k\}$, the errors on both rotations and translations are significant.
+After recovering the correspondence between data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as shown in Fig.~\ref{fig6}.
 
 \section{A Brief Case Study With Completely Scrambled Data}
+\label{sect5}
+
+In this section, we will briefly discuss the case where $\{A_i\}$ and $\{B_j\}$ are completely scrambled.
+Unlike the case of shifted data, it is extremely hard to recover the correspondence between two completely scrambled data sets $\{A_i\}$ and $\{B_j\}$.
+The correlation theorem can't be applied because there is no shift in the scrambled data sets.
+Euclidean group invariants are not practical either because given $\{A_i\}$ and $\{B_j\}$ both of which have the size of $m$, there are $m!
+= m \times m-1 \times \cdots 1$ combinations between the data sets, and it is extremely computationally intensive to test all the combinations.
+Without recovering the correspondence between the data sets, it is impossible to choose the optimal solution from the eight candidates of $\{X_k, Y_k\}$.
+
+In the above approach, we used Eq.~(\ref{equ15b}) to calculate $X_k$ and Eq.~(\ref{equ15a}) to obtain the corresponding $Y_k$.
+However, we now show that one can calculate the eight candidates of $Y$ independently and employ Eq.~(\ref{equ15a}) as a constraint to filter out the optimal $\{X, Y\}$ pair.
+
+Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$.
+Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), and we have:
+\begin{IEEEeqnarray}{l}
+M_{B^{-1}} Y^{-1} = X^{-1} M_{A^{-1}} \IEEEyessubnumber\label{equ33a}
+\\*
+Ad(Y)\Sigma_{B^{-1}}Ad^{T}(Y) = \Sigma_{A^{-1}}. \IEEEyessubnumber\label{equ33b}
+\end{IEEEeqnarray}
+Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently $Y$, Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use either Eq.~(\ref{equ15a}) or Eq.~(\ref{equ33a}) to get the optimal $\left( X_{k1}, Y_{k2} \right)$.
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,root}
+\bibliography{root}
+%\bibliography{IEEEabrv,root}
 %\begin{thebibliography}{1}

### 2015-11-17 Matlab_AXYB_Ver2/Early Version before 150619/batchAXYB.m
Minor changes to the inv(AX) = inv(YB).m file

@@ -1,4 +1,4 @@
-function [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B)
+function [ X,Y, X_candidate, Y_candidate, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B)
 
 X_candidate = zeros(4,4,8);
 Y_candidate = zeros(4,4,8);
@@ -10,8 +10,13 @@ deltaTheta = zeros(size(A,3),8);
 deltaD = zeros(size(A,3),8);
 normMin = zeros(8,1);
 
-[ MeanA, SigA ] = distibutionProps(A);
-[ MeanB, SigB ] = distibutionProps(B);
+% Reshape A and B for matching the input sies of mex functions
+[a1, a2, a3] = size(A);
+A_mex = reshape(A, a1, a2*a3);
+B_mex = reshape(B, a1, a2*a3);
+
+[ MeanA, SigA ] = distibutionPropsMex_mex(A_mex);
+[ MeanB, SigB ] = distibutionPropsMex_mex(B_mex);
 
 [ VA, ~ ] = eig( SigA(1:3,1:3) );
 [ VB, ~ ] = eig( SigB(1:3,1:3) );

### 2015-11-17 Matlab_AXYB_Ver2/Inverse/batchAXYBshift_inverse.m

@@ -9,9 +9,13 @@ X_candidate = zeros(4,4,8);
 % deltaTheta = zeros(size(A,3),8);
 % deltaD = zeros(size(A,3),8);
 % normMin = zeros(8,1);
+% Reshape A and B for matching the input sies of mex functions
+[a1, a2, a3] = size(A);
+A_mex = reshape(A, a1, a2*a3);
+B_mex = reshape(B, a1, a2*a3);
 
-[ MeanA, SigA ] = distibutionProps(A);
-[ MeanB, SigB ] = distibutionProps(B);
+[ MeanA, SigA ] = distibutionPropsMex_mex(A_mex);
+[ MeanB, SigB ] = distibutionPropsMex_mex(B_mex);
 
 [ VA, ~ ] = eig( SigA(1:3,1:3) );
 [ VB, ~ ] = eig( SigB(1:3,1:3) );

### 2015-11-17 Matlab_AXYB_Ver2/Inverse/main.m

@@ -5,96 +5,95 @@ clc
 % load invariantrandom.mat
 % global xxx yyy bbb
 counter = 1;
-trials = 1;
+trials = 30;
 
 % point = [50 1 50];
 % sum = zeros(1,4);
-point = [10 10 10];
+point = [10 10 100];
 sum = zeros( (100 - 100)/10 + 1,4);
+
+Mean=[0; 0; 0; 0; 0 ;0];
+
+Cov = 0.3*eye(6,6);
 
 shift = 10;
 for k = point(1):point(2):point(3)
-
-for i = 1:1:trials
-%     waitbar((k-point(1))/(point(3)-point(1)));
     
-%  if k==92
-%      continue;
-%  end
-%% --Trajectory Generation-------------------------
- [A,B,XActual,YActual] =  ABGenerate(k, 0.2,0);
-% [A,B,X,Y] =  ABGen(k,0);
-length = size(A,3);
+    for i = 1:1:trials
+        %     waitbar((k-point(1))/(point(3)-point(1)));
+        
+        %  if k==92
+        %      continue;
+        %  end
+        %% --Trajectory Generation-------------------------
+        [A,B,XActual,YActual] =  ABGenerate(k, 0, Mean, Cov);
+        % [A,B,X,Y] =  ABGen(k,0);
+        length = size(A,3);
+        
+        % As = A(:,:,1:(length - shift));
+        % Bs = B(:,:,(shift + 1):length);
+        
+        %% add noise
+        % gmean = [0;0;0;0;0;0];	%Gaussian Noise Mean
+        % nstd = 0.1;  %Gaussian Noise standard deviation Range
+        %  C=B;
+        %  B = sensorNoise(B, gmean, nstd, 1);
+        
+        %% --using probility methods------------------------
+        % [XX(:,:,k),YY(:,:,k),err(k,:)]= haiyuan(A,B,X,Y,k,0.1);
+        % [ X,Y, MeanA, MeanB, SigA, SigB ] = batchAXYB(A, B);
+        [ Xc, MeanA, MeanB, SigA, SigB ] = batchAXYBshift_inverse(A, B);
+        
+        [Yc] = batchAXYBinverse(MeanA, MeanB, SigA, SigB);
+        
+        % [XX(:,:,k)] = AXYB_LieGroup2( A, B );
+        [X, Y] = defineXY(Xc, Yc, MeanA, MeanB);
+        
[…]

### 2015-11-18 Matlab_AXYB_Revision/main.m
inv(AX) = inv(YB).m file working

@@ -17,9 +17,12 @@ Mean=[0; 0; 0; 0; 0 ;0];
 
 Cov = 0.3*eye(6,6);
 
-point = 10:20:100;
+point = 10:10:100;
 
 num = 30;
+
+boxplot = false;
+lineplot = true;
 
 for k = point
     
@@ -47,7 +50,7 @@ for k = point
         
         %% ------ using probility methods ------
         [ X1, Y1, MeanA, MeanB, SigA, SigB ] = batchAXXB(A, B);
-        [ Y2_inv, X2_inv, ~, ~, ~, ~] = batchAXXB(B_inv, A_inv);
+        [ Y2_inv, X2_inv, MeanA_inv, MeanB_inv, ~, ~] = batchAXXB(B_inv, A_inv);
         [ X3, Y3, X_can, Y_can, ~, ~, ~, ~ ] = batchAXYB(A, B);
         
         for i = 1:size(X1,3)
@@ -68,35 +71,27 @@ for k = point
         %%
         cost1 = zeros(8,8);
         for i = 1:size(X1,3)
-%             I_RX = X1(1:3,1:3)*X1(1:3,1:3)';
-%             if abs(norm(I_RX(:))^2 - 3) > 0.01
-%                 display('Not a rotation matrix')
-%                 I_RX
-%                 continue;
-%             end
             for j = 1:size(Y2,3)
-%                 diff = (MeanA*X1(:,:,i))\Y2(:,:,j)*MeanB;
-                diff = MeanA*X1(:,:,i) - Y2(:,:,j)*MeanB;
-%                 cost1(i,j) = abs( norm(diff(:))^2 - 4);
-                cost1(i,j) = norm(diff(:));
+                diff1 = MeanA*X1(:,:,i) - Y2(:,:,j)*MeanB;
+                diff2 = MeanB_inv/Y2(:,:,j) - X1(:,:,i)\MeanA_inv;
+                cost1(i,j) = norm(diff1(:)) + norm(diff2(:));
             end
         end
         
         [M1, I1] = min(cost1(:));
+
         
         cost2 = zeros(8,8);
         for i = 1:size(X2,3)
             for j = 1:size(Y1,3)
-%                 diff = (MeanA*X2(:,:,i))\Y1(:,:,j)*MeanB;
-                diff = MeanA*X2(:,:,i) - Y1(:,:,j)*MeanB;
-%                 cost2(i,j) = abs( norm(diff(:))^2 - 4);
-                cost2(i,j) = norm(diff(:));
[…]

### 2015-11-18 Matlab_AXYB_Revision/main.m
Minor change of main.m file && Added Figure folder with four figures

@@ -19,7 +19,7 @@ Cov = 0.3*eye(6,6);
 
 point = 10:10:100;
 
-num = 30;
+num = 50;
 
 boxplot = false;
 lineplot = true;
@@ -92,6 +92,8 @@ for k = point
         
         [M2, I2] = min(cost2(:));
         
+        M2 = 100;
+        
         if M1 <  M2
             
             [I_row, I_col] = ind2sub(size(cost1), I1);
@@ -162,6 +164,7 @@ Err_Avg = sum(Err,3)/num;
 
 %%
 if boxplot
+    
     figure
     boxplot(Err(:,:,1)', point)
     figure
@@ -179,13 +182,23 @@ if boxplot
     boxplot(Err(:,:,6)', point)
     figure
     boxplot(Err(:,:,8)', point)
+    
 elseif lineplot
-    figure
-    plot(point, Err_Avg(:,1:4))
-    legend('rot_{Xnew}','rot_{Ynew}','rot_X','rot_Y')
     
     figure
-    plot(point, Err_Avg(:,5:8))
-    legend('tran_{Xnew}','tran_{Ynew}','tran_X','tran_Y')
+    plot(point, Err_Avg(:,[1,3]))
+    legend('rot_{Xnew}','rot_X')
+
+    figure
+    plot(point, Err_Avg(:,[2,4]))
+    legend('rot_{Ynew}','rot_Y')
+    
+    figure
+    plot(point, Err_Avg(:,[5,7]))
+    legend('tran_{Xnew}','tran_X')
+    
+    figure
+    plot(point, Err_Avg(:,[6,8]))
+    legend('tran_{Ynew}','tran_Y')
     
 end

### 2015-11-19 submission/root.tex
Simulated inv axyb problem w.s.t. different scrambling rates

@@
 \section{A Brief Case Study With Completely Scrambled Data}
-\label{sect5}
+\label{sect4}
 
@@
 Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$.
-Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), and we have:
+Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), we have:
 \begin{IEEEeqnarray}{l}
@@
 \end{IEEEeqnarray}
-Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently $Y$, Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use either Eq.~(\ref{equ15a}) or Eq.~(\ref{equ33a}) to get the optimal $\left( X_{k1}, Y_{k2} \right)$.
+Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently, the eight candidates of $Y$.
+Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use Eq.~(\ref{equ15a}) and Eq.~(\ref{equ33a}) to form a minimization problem as:
+\begin{equation}
+\underset{k1, k2}{min} ||M_A X_{k1} - Y_{k2} M_B ||_F + ||M_B^{-1} Y^{-1}_{k2} - X^{-1}_{k1} M_A^{-1} ||_F
+\end{equation}
+which can give the optimal $(X_{k1}, Y_{k2})$ pair.
+We call this approach the \textit{prob} method, and compare it with Li's method for testing its effectiveness of handling scrambled data sets.
+For simplicity, we use Eq.~(\ref{equ33a}) and Eq.~(\ref{equ33b}) to generate $\{B_i\}$, whereas compute $\{A_i\}$ using $A_i = X^{-1} Y B_i$ without exerting noise on $B_i$.
+Then $\{A_i\}$ is scrambled at each percentage from $0\%$ up to $100\%$.
+50 times of simulations are performed for each percentage rate and the same error metrics are used as in Section \label{sect5}.
+As shown in Fig.~(\ref{fig7}) and Fig.~(\ref{fig8}), as the percentage of scrambled data goes up, the errors in rotation and translation for Li's method gradually diverge, while the errors for the $prob$ method are very stable and small.
+This shows the significant advantage of the probabilistic method in handling disordered data sets.
+However, Li's method is still more accurate when the exact correspondence is known between $\{A_i\}$ and $\{B_i\}$.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3.2in]{Figure/fig7.eps}
+\caption{Rotation error in X and Y v.s. scrambling rate for the $prob$ and Li's methods}
+\label{fig7}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3.2in]{Figure/fig8.eps}
+\caption{Translation error in X and Y v.s. scrambling rate for the $prob$ and Li's methods}
+\label{fig8}
+\end{figure}
 
@@
 In the numerical simulation, the method performs well with different sets of data samples.
+Lastly, we brought up a new approach to deal with completely disordered data sets and show its effectiveness in simulation.
 Future work will be to further develop the existing algorithm to solve for more general asynchronous cases, such as flipped data pairs or missing data in the data streams.

### 2015-11-19 Matlab_AXYB/li.m

@@ -10,7 +10,7 @@ function [X,Y]=li(AA,BB)
 % Mili Shah
 % July 2014
 
-[m,n]=size(AA); n = n/4;
+[~,n]=size(AA); n = n/4;
 
 A = zeros(12*n,24);
 b = zeros(12*n,1);
@@ -26,8 +26,10 @@ end
 x = A\b;
 
 X=reshape(x(1:9),3,3)';
-[u,s,v]=svd(X); X = u*v'; if det(X)<0, X = u*diag([1 1 -1])*v'; end
+[u,~,v]=svd(X); X = u*v'; if det(X)<0, X = u*diag([1 1 -1])*v'; end
 X = [X x(19:21);[0 0 0 1]];
 Y=reshape(x(10:18),3,3)';
-[u,s,v]=svd(Y); Y = u*v'; if det(Y)<0, Y = u*diag([1 1 -1])*v'; end
+[u,~,v]=svd(Y); Y = u*v'; if det(Y)<0, Y = u*diag([1 1 -1])*v'; end
 Y = [Y x(22:24);[0 0 0 1]];
+
+end

### 2015-11-19 Matlab_AXYB/shah.m

@@ -1,4 +1,4 @@
-function [X,Y]=shah(AA,BB)
+function [X,Y] = shah(AA,BB)
 % Solves the problem AX=YB
 % using the formulation of
 %
@@ -10,7 +10,7 @@ function [X,Y]=shah(AA,BB)
 % Mili Shah
 % July 2014
 
-[m,n]=size(AA); n = n/4;
+[~,n]=size(AA); n = n/4;
 A = zeros(9*n,18);
 T = zeros(9,9);
 b = zeros(9*n,1);
@@ -20,15 +20,15 @@ for i = 1:n
     A(9*i-8:9*i,:) = [kron(Rb,Ra) -eye(9)];
     T = T + kron(Rb,Ra);
 end
-[u,s,v]=svd(T);
+[u,~,v]=svd(T);
 x = v(:,1);
 y = u(:,1);
 X = reshape(x,3,3);
 X = sign(det(X))/abs(det(X))^(1/3)*X;
-[u,s,v]=svd(X); X = u*v';
+[u,~,v]=svd(X); X = u*v';
 Y = reshape(y,3,3);
 Y = sign(det(Y))/abs(det(Y))^(1/3)*Y;
-[u,s,v]=svd(Y); Y = u*v';
+[u,~,v]=svd(Y); Y = u*v';
 A = zeros(3*n,6);
 b = zeros(3*n,1);
 for i = 1:n
@@ -39,5 +39,7 @@ t = A\b;
 
 X = [X t(1:3);[0 0 0 1]];
 Y = [Y t(4:6);[0 0 0 1]];
+
+end
 
 

### 2015-11-19 Matlab_AXYB_Revision/Main_Number_of_Data.m

@@ -1,0 +1,192 @@
+clear all
+close all
+clc
+
+%% Edited by Qianli
+counter = 0;
+
+% Require rvctool Matlab toolbox but not the "common" folder inside
+addpath('~/Dropbox/2014Summer/Robotics Research/rvctools/robot')
+addpath('~/Dropbox/2014Summer/Robotics Research/rvctools/common')
+addpath('~/Dropbox/2015Spring/AXXB Journal/Batch_AXXB/Matlab_AXXB/codegen')
+addpath('~/Dropbox/2015Spring/AXXB Journal/Batch_AXXB/Matlab_AXXB')
+addpath('~/Dropbox/2014Summer/Robotics Research/kinematics/kinematics/screws')
+addpath('~/Dropbox/2014Summer/Robotics Research/kinematics/kinematics/util')
+
+Mean=[0; 0; 0; 0; 0 ;0];
+
+Cov = 0.3*eye(6,6);
+
+point = 10:10:100;
+
+num = 50;
+
+boxplot = false;
+lineplot = true;
+
+for k = point
+    
+    counter = counter + 1;
+    for s = 1:num
+        %% ------ Trajectory Generation --------
+        [A, B, XActual, YActual] =  ABGenerate(k, 0, Mean, Cov);
+        
+        % Resize A to fit mex functions
+        [a1,a2,a3] = size(A);
+        
+        %% ------- add noise -------
+        gmean = [0; 0; 0; 0; 0; 0];	% Gaussian Noise Mean
+        nstd = 0.05;                % Gaussian Noise standard deviation Range
+        
+        B = sensorNoise(B, gmean, nstd, 1);
+        
+        %% ------ Generate A^-1 and B^-1 -------
+        A_inv = zeros(4,4,k);
+        B_inv = zeros(4,4,k);
+        for i = 1:k
+            A_inv(:,:,i) = inv(A(:,:,i));
+            B_inv(:,:,i) = inv(B(:,:,i));
+        end
+        
+        %% ------ using probility methods ------
+        [ X1, Y1, MeanA, MeanB, SigA, SigB ] = batchAXXB(A, B);
+        [ Y2_inv, X2_inv, MeanA_inv, MeanB_inv, ~, ~] = batchAXXB(B_inv, A_inv);
+        [ X3, Y3, X_can, Y_can, ~, ~, ~, ~ ] = batchAXYB(A, B);
+        
+        for i = 1:size(X1,3)
[…]

### 2015-11-19 Matlab_AXYB_Revision/Main_Scrambled_Data.m

@@ -1,0 +1,196 @@
+clear all
+close all
+clc
+
+%% Edited by Qianli
+counter = 0;
+
+% Require rvctool Matlab toolbox but not the "common" folder inside
+addpath('~/Dropbox/2014Summer/Robotics Research/rvctools/robot')
+addpath('~/Dropbox/2014Summer/Robotics Research/rvctools/common')
+addpath('~/Dropbox/2015Spring/AXXB Journal/Batch_AXXB/Matlab_AXXB/codegen')
+addpath('~/Dropbox/2015Spring/AXXB Journal/Batch_AXXB/Matlab_AXXB')
+addpath('~/Dropbox/2014Summer/Robotics Research/kinematics/kinematics/screws')
+addpath('~/Dropbox/2014Summer/Robotics Research/kinematics/kinematics/util')
+
+Mean=[0; 0; 0; 0; 0 ;0];
+
+Cov = 0.3*eye(6,6);
+
+point = 0:10:100;
+
+num = 100; % number of simulations
+
+Num  = 50; % number of data
+
+boxplot = false;
+lineplot = true;
+
+for k = point
+    
+    counter = counter + 1;
+    
+    for s = 1:num
+        %% ------ Trajectory Generation --------
+        [A, B, XActual, YActual] =  ABGenerate(Num, 0, Mean, Cov);
+        
+        % Scramble data streams up to a certain percentage 
+        PA = (1:size(A,3));
+        PB = (1:size(B,3));
+        
+        for i = 1:length(PA)
+            
+            if rand <= 0.01*k
+                index = randi(Num,1);
+                PA([i index]) = PA([index i]);
+            end
+            
+        end
+        A_perm = A(:,:,PA);
+        B_perm = B(:,:,PB);
+        
+        %% ------- add noise -------
+%         gmean = [0; 0; 0; 0; 0; 0];	% Gaussian Noise Mean
+%         nstd = 0.05;                % Gaussian Noise standard deviation Range
+        
+%         B = sensorNoise(B, gmean, nstd, 1);
+        
+        %% ------ Generate A^-1 and B^-1 -------
+        A_inv = zeros(4, 4, Num);
+        B_inv = zeros(4, 4, Num);
+        for i = 1:Num
+            A_inv(:,:,i) = inv(A_perm(:,:,i));
+            B_inv(:,:,i) = inv(B_perm(:,:,i));
[…]

### 2015-11-19 Matlab_AXYB_Revision/main.m

@@ -1,204 +1,0 @@
-clear all
-close all
-clc
-
-%% Edited by Qianli
-counter = 0;
-
-% Require rvctool Matlab toolbox but not the "common" folder inside
-addpath('~/Dropbox/2014Summer/Robotics Research/rvctools/robot')
-addpath('~/Dropbox/2014Summer/Robotics Research/rvctools/common')
-addpath('~/Dropbox/2015Spring/AXXB Journal/Batch_AXXB/Matlab_AXXB/codegen')
-addpath('~/Dropbox/2015Spring/AXXB Journal/Batch_AXXB/Matlab_AXXB')
-addpath('~/Dropbox/2014Summer/Robotics Research/kinematics/kinematics/screws')
-addpath('~/Dropbox/2014Summer/Robotics Research/kinematics/kinematics/util')
-
-Mean=[0; 0; 0; 0; 0 ;0];
-
-Cov = 0.3*eye(6,6);
-
-point = 10:10:100;
-
-num = 50;
-
-boxplot = false;
-lineplot = true;
-
-for k = point
-    
-    counter = counter + 1;
-    for s = 1:num
-        %% ------ Trajectory Generation --------
-        [A, B, XActual, YActual] =  ABGenerate(k, 0, Mean, Cov);
-        
-        % Resize A to fit mex functions
-        [a1,a2,a3] = size(A);
-        
-        %% ------- add noise -------
-        gmean = [0; 0; 0; 0; 0; 0];	% Gaussian Noise Mean
-        nstd = 0.05;                % Gaussian Noise standard deviation Range
-        
-        % B = sensorNoise(B, gmean, nstd, 1);
-        
-        %% ------ Generate A^-1 and B^-1 -------
-        A_inv = zeros(4,4,k);
-        B_inv = zeros(4,4,k);
-        for i = 1:k
-            A_inv(:,:,i) = inv(A(:,:,i));
-            B_inv(:,:,i) = inv(B(:,:,i));
-        end
-        
-        %% ------ using probility methods ------
-        [ X1, Y1, MeanA, MeanB, SigA, SigB ] = batchAXXB(A, B);
-        [ Y2_inv, X2_inv, MeanA_inv, MeanB_inv, ~, ~] = batchAXXB(B_inv, A_inv);
-        [ X3, Y3, X_can, Y_can, ~, ~, ~, ~ ] = batchAXYB(A, B);
-        
-        for i = 1:size(X1,3)
[…]

### 2015-11-22 DrC Version 1/root1.tex
Revision by Dr.C & Qianli

--- 2015-11-19 submission/root.tex
@@
 \usepackage{color}
+\usepackage[normalem]{ulem}
 
@@
 In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control.
-As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony in sampling rates and processing time.
+As an added difficulty, the exact correspondence between the streams of sensor data ($A$'s and $B$'s) is typically unknown due to asynchrony in sampling rates and processing time.
 One common scenario is a constant shift between the two data streams.
-Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$s and $B$s.
-We begin by discussing probability density functions on $SE(3)$ and then introduce Euclidean-group invariants to obtain an exact solution for $X$ and $Y$.
-Then, we present a method to simultaneously recover $X$ and $Y$ and the correspondence between the shifted data sets.
-Finally, we numerically simulated the proposed method with shifted, asynchronous data and noise added to the stream of $B$s to verify its efficiency and robustness.
+Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$'s and $B$'s.
+We begin by discussing probability density functions on $SE(3)$ and then use Euclidean-group invariants to obtain an exact solution for $X$ and $Y$.
+We then present a method to simultaneously recover $X$ and $Y$ and the correspondence between temporally shifted data sets using a correlation method.
+Following this, we show how
+to solve the problem in the case when the data are completely scrambled, corresponding to a complete loss of
+temporal information.
+Finally, we numerically simulated the proposed method with asynchronous data and noise added to the stream of $B$'s to verify its efficiency and robustness.
 
@@
 
-In the $\textbf{AX=YB}$ problem, data streams of $A$s and $B$s can be respectively obtained via different sensors.
+In the $\textbf{AX=YB}$ problem, data streams of $A$'s and $B$'s can be respectively obtained via different sensors.
 The data streams may arrive in an asynchronous fashion due to the different working frequencies of the sensors.
-This asynchrony causes a shift between the two data streams which removes the correspondence between the $A$s and $B$s.
-In this paper, a novel method is presented to solve for $X$ and $Y$ without a priori knowledge of the correspondence between the $A$s and $B$s.
+This asynchrony causes a shift between the two data streams which can obscure the correspondence between the $A$'s and $B$'s.
+Moreover, data loss can destroy information about
+ correspondence altogether. In this paper, a novel method is presented to solve for $X$ and $Y$ without a priori knowledge of the correspondence between the $A$'s and $B$'s.
 
@@
 Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems.
-(The Universal Robot pictured above is owned by Prof.
+(The Universal Robot pictured above is from the laboratory of Prof.
 Emad Boctor of Johns Hopkins University).
-Note: the $A$ and $B$ in the above two problems have different physical meanings.
-One is the absolute transformation and the other is relative transformation as can be seen in the figures.
 }
@@
 All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$.
-For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the litefit rature to solve for $X$ using data without a priori knowledge of the correspondence.
-These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.
+For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence.
+These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown a priori \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.
 
@@
 of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue.
-Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{wang2014towards} which will not be discussed in detail here.
+Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange, and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{wang2014towards} which will not be discussed in detail here.
 In the above methods, the correspondence between $A$ and $B$ is known a priori.
@@
 \ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$.
-In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates.
+In Section \ref{sect3}, an algorithm involving both a temporal correlation calculation and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates.
 The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}.
@@
 \end{equation}
-where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for the group element.
+where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector,
+ $T$ denotes the transpose of a vector or matrix, and $H$ is the symbol for an element of $SE(3)$
+ (which is a six-dimensional Lie group) represented as a $4\times 4$ homogeneous transformation matrix.
+ The identity element of $SE(3)$ is then the $4\times 4$ identity matrix, $I$.
 
@@
 \end{equation}
-For a group element $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere:
+For a group element $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere,
 
@@
 \left\{
-\begin{array}{ll}
-+\infty, & H=I \\
-0, & H \neq I.
+\begin{array}{lll}
++\infty& {\rm if} & H=I \\
+0& {\rm if} & H \neq I,
 \end{array}
@@
 \end{equation}
-The Dirac delta function also satisfies the identity constraint as:
+and also satisfies the identity constraint
 
@@
 A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$.
-Given $K,H \in SE(3)$ and two well-defined functions $f_{1}, f_{2} \in \left(L^1 \cap L^2 \right)(SE(3))$, their convolution on $SE(3)$ is defined as:
+Given $K,H \in SE(3)$ and two well-behaved functions $f_{1}$ and $f_{2}$, their convolution on $SE(3)$ is defined as \cite{chirikjian2011stochastic,chirikjiandover}
 
 \begin{equation}\label{equ4}
-(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK.
+(f_{1}\ast f_{2})(H) = \int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK
 \end{equation}
-where $\circ$ denotes the group product, and in this case it is simply matrix multiplication. Employing the properties of the $\delta$ function, it is straightforward to see that:
+where $\circ$ denotes the group product for $SE(3)$, which is simply matrix multiplication.
+The integral over $SE(3)$ can be expressed in various coordinates, and both the bounds of the integral and
+the integration measure $dH$ will take on different appearances that depend on these coordinates.
+For example, if $H$ is parameterized in terms of the Cartesian coordinates ${t} = [x,y,z]^T$,
+and $R = R_{ZXZ}(\alpha,\beta,\gamma)$ is an Euler-angle description of rotations, then the
+integral over $SE(3)$ is the six-dimensional integral where
+$x,y,z$ range over $-\infty$ to $+\infty$, $\alpha,\gamma$ range from $0$ to $2\pi$ and $\beta$ ranges
+from $0$ to $\pi$. In these coordinates, the integration measure takes the form
+$$ dH = \sin\beta d\alpha d\beta d\gamma dx dy dz = dR d{t}. $$
+Alternatively, exponential coordinates can be used, in which case the six-dimensional
+integral over $SE(3)$ and the measure take the form described in \cite{wang2008nonparametric}.
+
+When it is clear that the argument of a function is $H \in SE(3)$, sometimes it will be convenient to
+abbreviate $f(H)$ as $f$ and $(f_{1}\ast f_{2})(H)$ as $f_{1}\ast f_{2}$ to avoid a proliferation of
+parentheses.
+
+The convolution operation is bi-linear in the sense that
+$$ (a_1 f_{1} + b_1 {f'}_{1}) \ast f_{2} = a_1(f_{1} \ast f_{2}) + b_1({f'}_{1} \ast f_{2}) $$
+and
+$$ f_{1} \ast (a_1 f_{2} + b_1 {f'}_{2}) = a_1(f_{1} \ast f_{2}) + b_1(f_{1} \ast {f'}_{2}). $$
+Moreover, convolution inherits associativity from the underlying group:
+$$ f_1 \ast (f_2 \ast f_3) = (f_1 \ast f_2) \ast f_3. $$
+But convolution is generally not commutative, $f_1 \ast f_2 \neq f_2 \ast f_1$.
+
+Employing the properties of the $\delta$ function, it is straightforward to see that:
 
@@
 \begin{equation}\label{equ7}
-(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
+(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H).
 \end{equation}
@@
 \\*
-f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
+f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H), \IEEEyessubnumber
 \end{IEEEeqnarray}
-then by using the distributivity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
+then by using the bi-linearity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
 \begin{equation}\label{equ9}
-(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H)
-%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
+(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H).
 \end{equation}
@@
 
-If each of the data streams $\{A_i\}$ and $\{B_i\}$ are generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly-focused''.
+%If each of the data streams $\{A_i\}$ and $\{B_i\}$ are generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly-focused''.
+
 The convolution of two highly-focused PDFs have some interesting properties that can be used to solve for $X$.
-For simplicity, we will drop the integral interval ``$SE(3)$'' for the remainder of the paper, as it should be self-evident given the integration measure that is used.
+%For simplicity, we will drop the integral interval ``$SE(3)$'' for the remainder of the paper, as it should be self-evident given the integration measure that is used.
 In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:
@@
 \begin{IEEEeqnarray}{l}\label{equ11}
-\int log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
+\int_{SE(3)} \log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
 \\*
-\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
+\Sigma = \int_{SE(3)} \log^{\vee}(M^{-1}H)[\log^{\vee}(M^{-1}H)]^{T}f(H)dH \; \; \; \; \;
+\IEEEyessubnumber
 \end{IEEEeqnarray}
-where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic} as:
+where the explicit expression of the matrix logarithm $\log(H)$ along with its vectorized form $\log^{\vee}(H)$ are given in \cite{MLK} as
 
 \begin{equation}
-log(H) = \widehat{\bf h} 
+\log(H) = \widehat{\bf h}
 =
@@
 \end{equation}
-where ${\bf h} = log^\vee(H) \in \mathbb{R}^{6 \times 1}$ and $\widehat{\bf h}$ is the corresponding Lie algebra element ($se(3)$) of $H$.
+where ${\bf h} = \log^\vee(H) \in \mathbb{R}^{6 \times 1}$ and $\widehat{\bf h}$ is the corresponding Lie algebra element, $\widehat{\bf h} \in se(3)$, such that $H= \exp \widehat{\bf h}$.
 
@@
 \begin{IEEEeqnarray}{l}\label{equ12}
-\sum_{i=1}^{n}log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
+\sum_{i=1}^{n}\log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
 \\*
-\Sigma = \sum_{i=1}^{n}log^{\vee}(M_A^{-1}A_i)[log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
+\Sigma = \sum_{i=1}^{n}\log^{\vee}(M_A^{-1}A_i)[\log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 \begin{equation}\label{equ13}
-    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})]
+    ^{k+1}M_{A} = ^{k}M_{A} \circ \exp\left[\frac{1}{n}\sum_{i=1}^{n}\log(^{k}M_{A}^{-1}\circ A_{i})\right].
 \end{equation}
+An initial estimate of the iterative procedure can be chosen as: $$^{0}M_{A}=\exp\left(\frac{1}{n}\sum_{i=1}^{n}\log(A_{i})\right).$$
 
-An initial estimate of the iterative procedure can be chosen as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then a local minimum of $M_A$ is obtained by solving a nonlinear optimization problem with the cost function of $|| \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) ||^{2}$.
-A similar procedure can be used to compute $M_B$.
-$\Sigma_A$ and $\Sigma_B$ are then straight forward to compute given known $M_A$ and $M_B$.
+Alternatively,
+$M_A$ can be obtained by solving a nonlinear optimization problem with the cost function
+ $$ C_1(M_A) = \left\| \sum_{i=1}^{n}\log(M_{A}^{-1}A_{i}) \right\|^{2}. $$
+Note, however, that mathematically this is not the same as minimizing
+ $$ C_2(M_A) =  \sum_{i=1}^{n} \left\|\log(M_{A}^{-1}A_{i}) \right\|^{2}, $$
+though in practice they often are minimized by very close values of $M_A$.
 
-The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{wang2008nonparametric}:
+A similar procedure can be used to compute $M_B$. $\Sigma_A$ and $\Sigma_B$ are then straightforward to compute once $M_A$ and $M_B$ are known.
+
+The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two ``highly-focused'' functions $f_{1}$ and $f_{2}$ (i.e., those for which $\|\Sigma_i\| << 1$)
+are calculated as in \cite{wang2008nonparametric}:
 
@@
 \\*
-\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2}. \IEEEyessubnumber
+\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2}, \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
              \right).$$
+Here the ``hat'' notation when applied to the three-dimensional vector $t$ gives
+\begin{equation}
+\hat{t}
+=
+\left(
+\begin{array}{ccc}
+   0 & -t_3 &  t_2 \\
+ t_3 &    0 & -t_1 \\
+-t_2 & -t_1 &    0
+\end{array}
+\right)
+\end{equation}
 
 Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively.
-Therefore, the following equations can be obtained using Eq.~\ref{equ14}:
+Therefore, the following equations can be obtained using Eq.~(\ref{equ14}):
 
@@
 \end{IEEEeqnarray}
+This is a nonparametric result, meaning that the underlying probability density functions $f_A(H)$
+and $f_B(H)$ need not be Gaussian or belong to any other family of parametric distributions.
+Moreover, the constraint of being highly-focused is not very restrictive because the original
+data sets $\{A_i\}$ and $\{B_i\}$ can always be transformed into $\{(A_i)^p\}$ and $\{(B_i)^p\}$
+for some fractional power $0 < p < 1$ since
+$$ A_i = X B_i X^{-1} \,\, \Longleftrightarrow \,\, (A_i)^p = X (B_i)^p X^{-1}. $$
+{\color{blue} Question: this is for AX=XB, but for AX =YB, $A_i = Y B_i X^{-1}$ and the above equation doesn't apply.}
 
-To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as follows:
+The smaller the value of $p$ is, the more concentrated the transformed data will be.
+
+The problem of solving the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as follows:
 
@@
 \end{equation}
-where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, the rotation matrix $P$ satisfies Eq.\textcolor{blue}{~}(\ref{equ_P}).
+where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. Since $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, the orthogonal matrix $P$ satisfies Eq.\textcolor{blue}{~}(\ref{equ_P}).
 
@@
 P^{T} = P^{-1} \\
-det(P) = \pm 1.
+\det(P) = \pm 1.
 \end{array}
@@
 \end{equation}
-Combing Eq.~(\ref{equ18}) and Eq.~(\ref{equ_P}), then a rotation matrix $P$ can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
+Combing Eq.~(\ref{equ18}) and Eq.~(\ref{equ_P}), then an orthogonal matrix $P$ can be one of $\mathcal{P}$ or $\mathcal{-P}$ :
 
@@
        R_{X_k} & t_{X_k} \\
-       \mathbf{0}^{T} & \mathbf{1}\\
+       {0}^{T} & {1}\\
 \end{array} \right),&
@@
        R_{Y_k} & t_{Y_k} \\
-       \mathbf{0}^{T} & \mathbf{1}\\
+       {0}^{T} & {1}\\
 \end{array} \right)
@@
 The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
-Based on screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
-
+Based on screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ as:
+% that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
 \begin{equation}\label{equ21}
 H = \left( \begin{array}{cc}
-       e^{\theta \hat{\mathbf{n}}} & (\mathbf{I}_{3} - e^{\theta \hat{\mathbf{n}}})\mathbf{p} + d\mathbf{n} \\
-       \mathbf{0}^{T} & \mathbf{1}
+       e^{\theta \hat{n}} & ({I}_{3} - e^{\theta \hat{n}}) {p} + d{n} \\
+       {0}^{T} & {1}
 \end{array} \right)
 \end{equation}
-where $\theta$ is the angle of rotation, $d$ is the translation along the rotation axis, $\mathbf{n}$ is the unit vector representing the axis of rotation and $\mathbf{p}$ is the position of the line to the origin with $\mathbf{p} \cdot \mathbf{n} = 0$.
+where $\theta$ is the angle of rotation, $d$ is the translation along the rotation axis, ${n}$ is the unit vector representing the axis of rotation and ${p}$ is the position of a point on the line relative to the origin of a space-fixed reference frame with ${ p} \cdot { n} = 0$.
 
@@
 Defining $B^k = X_k^{-1}Y_kB$, we have $AX_k=X_kB^k$.
-As discussed in \cite{ackerman2013sensor}, for $AX=XB$ problem, there exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
+As discussed in \cite{chen91, ackerman2013sensor}, for $AX=XB$ problem, there exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
 
 \begin{equation}\label{equ22}
-    \theta_{A_{i}}=\theta_{B_{i}^{k}}, d_{A_{i}}=d_{B_{i}^{k}}
+    \theta_{A_{i}}=\theta_{B_{i}^{k}}, d_{A_{i}}=d_{B_{i}^{k}}.
 \end{equation}
@@
 \begin{equation}\label{equ23}
-    (X,Y) = \mathop{\mathbf{arg}min}_{(X_{k},Y_{k})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel)
+    (X,Y) = \mathop{argmin}_{(X_{k},Y_{k})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel).
 \end{equation}
@@
 \begin{equation}\label{equ30}
-    \tau_{shift} = \mathop{\mathbf{arg}max}_{index}(Corr(\theta_{1,k},\theta_{2,k}))
+    \tau_{shift} = \mathop{argmax}_{index}(Corr(\theta_{1,k},\theta_{2,k}))
 \end{equation}
@@
 \centering
-\includegraphics[width=3.2in]{fig2.eps}
+\includegraphics[width=3.05in]{fig2.eps}
 \caption{
@@
 
-For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as  $Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel$, $Error(t_X) = \parallel t_{X_{Solved}}-t_{X_{true}} \parallel$, $Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel$ and $Error(t_Y) = \parallel t_{Y_{Solved}}-t_{Y_{true}} \parallel$ respectively.
+For the numerical experiments in this section, the rotational and translational errors for $X$ and $Y$ are measured as
+$$Error(R_X) = \parallel log^{\vee} (R_{X_{Solved}}^{T}R_{X_{true}})\parallel,$$
+$$Error(t_X) = \parallel t_{X_{Solved}}-t_{X_{true}} \parallel,$$
+$$Error(R_Y) = \parallel log^{\vee} (R_{Y_{Solved}}^{T}R_{Y_{true}})\parallel,$$
+ and
+ $$Error(t_Y) = \parallel t_{Y_{Solved}}-t_{Y_{true}} \parallel,$$
+respectively.
 
@@
 Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently, the eight candidates of $Y$.
-Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use Eq.~(\ref{equ15a}) and Eq.~(\ref{equ33a}) to form a minimization problem as:
+Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.~(\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use Eq.~(\ref{equ15a}) and Eq.~(\ref{equ33a}) to form a minimization problem as:
 \begin{equation}
@@
 Then $\{A_i\}$ is scrambled at each percentage from $0\%$ up to $100\%$.
-50 times of simulations are performed for each percentage rate and the same error metrics are used as in Section \label{sect5}.
+50 times of simulations are performed for each percentage rate and the same error metrics are used as in Section \ref{sect5}.
 As shown in Fig.~(\ref{fig7}) and Fig.~(\ref{fig8}), as the percentage of scrambled data goes up, the errors in rotation and translation for Li's method gradually diverge, while the errors for the $prob$ method are very stable and small.
@@
 In the numerical simulation, the method performs well with different sets of data samples.
-Lastly, we brought up a new approach to deal with completely disordered data sets and show its effectiveness in simulation.
-Future work will be to further develop the existing algorithm to solve for more general asynchronous cases, such as flipped data pairs or missing data in the data streams.
+Lastly, we brought up a new approach to deal with completely disordered data sets and show its effectiveness in simulation.Future work will be to improve the $prob$ method and investigate on its performance dealing with noisy scrambled data sets.
 
@@
 \section*{ACKNOWLEDGMENT}
-{Chirikjian's contribution to this material is based upon work supported by (while serving at) the National Science Foundation.
+{Chirikjian's contribution to this material is based upon work supported by (while serving at) the National Science Foundation (under the IR/D Program).
 Any opinion, findings, and conclusions or recommendations expressed in this material are those of the author(s)
@@
 \bibliographystyle{IEEEtran}
-\bibliography{root}
+\bibliography{IEEEabrv,root1}
 %\bibliography{IEEEabrv,root}

### 2015-11-22 DrC Version 1/root1.tex
Added new proof

@@
 \begin{equation}\label{equ9}
-(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H).
+(f_{A}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B})(H).
 \end{equation}
@@
 and $f_B(H)$ need not be Gaussian or belong to any other family of parametric distributions.
-Moreover, the constraint of being highly-focused is not very restrictive because the original
-data sets $\{A_i\}$ and $\{B_i\}$ can always be transformed into $\{(A_i)^p\}$ and $\{(B_i)^p\}$
-for some fractional power $0 < p < 1$ since
-$$ A_i = X B_i X^{-1} \,\, \Longleftrightarrow \,\, (A_i)^p = X (B_i)^p X^{-1}. $$
-{\color{blue} Question: this is for AX=XB, but for AX =YB, $A_i = Y B_i X^{-1}$ and the above equation doesn't apply.}
+Moreover, it can be shown as below that in the context of $AX=YB$, Eq.~(\ref{equ15a}) and Eq.~(\ref{equ15b}) don't require $f_A$ and $f_B$ to be highly concentrated.
 
-The smaller the value of $p$ is, the more concentrated the transformed data will be.
+Starting with Eq.(\ref{equ9}), performing a convolution on both of the left sides of the equation with
+$\delta_{Y^{-1}}(H)$, and using the associativity of convolution, we will have:
+\begin{equation} 
+(\delta_{Y^{-1}} * f_A * \delta_X)(H) = f_B(H).
+\label{equ18new}
+\end{equation}
+Use the definition of mean as in Eq.~(\ref{equ11}) along with Eq.~(\ref{equ18new}), we have 
+$$ \int_{SE(3)} \log({M}_{B}^{-1} H) f_B(H) dH = $$
+$$ \int_{SE(3)} \log({M}_{B}^{-1} H) (\delta_{X^{-1}} * f_A * \delta_{X})(H) dH = $$
+\begin{equation}
+\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}.
+\label{equ19new}
+\end{equation}
+Change the variable as $K = {Y} H {X}^{-1}$ and use the invariance of integration \cite{chirikjian2011stochastic}, then Eq.~(\ref{equ19new}) becomes:
+\begin{equation}
+\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}. 
+\label{equ20new}
+\end{equation}
+which falls into the form of the mean definition of $\{A_i\}$.
+If we further multiply $X$ and $X^{-1}$ on the left and right of both sides of Eq.~(\ref{equ20new}), then $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(M_{A}^{-1}K)$.
+Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
+$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}),
 

### 2015-11-22 DrC Version 1/root1.tex
Change of format to fit into the eight pages limit

@@
 Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
-$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}),
+$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}).
+Eq.(\ref{equ15b}) follows from \cite{wang2008nonparametric} because the F(A,B) term has products of covariances of the functions being convolved, and delta functions have zero covariance so the F term is zero.
 
@@
 However, we now show that one can calculate the eight candidates of $Y$ independently and employ Eq.~(\ref{equ15a}) as a constraint to filter out the optimal $\{X, Y\}$ pair.
-
 Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$.

### 2015-11-22 Final Submission/root1.tex
Final Submission

--- 2015-11-22 DrC Version 1/root1.tex
@@
  (which is a six-dimensional Lie group) represented as a $4\times 4$ homogeneous transformation matrix.
- The identity element of $SE(3)$ is then the $4\times 4$ identity matrix, $I$.
+ The identity element of $SE(3)$ is then the $4\times 4$ identity matrix, $I_4$.
 
@@
 \begin{array}{lll}
-+\infty& {\rm if} & H=I \\
-0& {\rm if} & H \neq I,
++\infty& {\rm if} & H=I_4 \\
+0& {\rm if} & H \neq I_4,
 \end{array}
@@
 \begin{IEEEeqnarray}{l}\label{equ11}
-\int_{SE(3)} \log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
+\int_{SE(3)} \log(M^{-1}H)f(H)dH = \mathbb{O}_4  \IEEEyessubnumber
 \\*
@@
 \begin{IEEEeqnarray}{l}\label{equ12}
-\sum_{i=1}^{n}\log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
+\sum_{i=1}^{n}\log(M_A^{-1}A_i) = \mathbb{O}_4 \IEEEyessubnumber
 \\*
@@
                \begin{array}{cc}
-                 R & O \\
+                 R & \mathbb{O}_4 \\
                  \hat{t}R & R \\
@@
 
-Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively.
+Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 }$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6}$, respectively.
 Therefore, the following equations can be obtained using Eq.~(\ref{equ14}):
@@
 \begin{equation}
-\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}.
+\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}_4.
 \label{equ19new}
@@
 \begin{equation}
-\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}. 
+\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}_4. 
 \label{equ20new}
@@
 $X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}).
-Eq.(\ref{equ15b}) follows from \cite{wang2008nonparametric} because the F(A,B) term has products of covariances of the functions being convolved, and delta functions have zero covariance so the F term is zero.
+Eq.(\ref{equ15b}) follows from \cite{wang2008nonparametric} because the $F(A,B)$ term as defined in \cite{wang2008nonparametric} has products of covariances of the functions being convolved, and delta functions have zero covariance so the $F(A,B)$ term is zero, which results in Eq.~(\ref{equ15b}).
 
